### 2023-01-05 revision/response.tex
latex 1-5

\documentclass{article}
\usepackage{a4wide}

\usepackage{amsthm}
\usepackage{url}
\newtheorem{Comments}{\textbf{Comments}}

\title{Summary of Changes: \\Temporal Graph Cube}
\author{Guoren~Wang,
	Yue~Zeng,
	Rong-Hua~Li,
	Hongchao~Qin,
	Xuanhua Shi,\\
	Yubin Xia, 
	Xuequn Shang, 
	Liang Hong
}
\date{}

\begin{document}
%\Large
\maketitle

We appreciate the opportunity to revise our work, and are very grateful to the anonymous reviewers for their insightful and valuable comments. We have revised the manuscript and tried our best to address all the comments.

The main changes are summarized below.
\begin{itemize}
%\item  As suggested by the reviewer, we have added new experiments against alternative solutions in the revised version (see exp-5 of section 4.1).

\item test

\end{itemize}

The point-to-point responses are given below.

\section{Response to Reviewer \#1}
\begin{Comments}
The expression of motivation is not clearly. Does the limitation of static graph cube is it cannot support range queries or it only can support latest data?
\end{Comments}
\noindent \textbf{Response:} test

\begin{Comments}
Authors should improve their writing. Especially the punctuation makes the definitions hard to be understood.
\end{Comments}
\noindent \textbf{Response:} test

\begin{Comments}
Authors provide similarity of snapshots and two ratios in the Sec. 5. All of them are calculated based on the edges’ number. Why do you use similarity but not two ratios to proof the effectiveness?
\end{Comments}
\noindent \textbf{Response:} test

\begin{Comments}
In the experiments, authors should add an experiment of comparison with existing methods to evaluate the efficiency of their model.
\end{Comments}
\noindent \textbf{Response:} test

\begin{Comments}
The study of related works is insufficient, and some of the results and limitations of existing works are not discussed.
\end{Comments}
\noindent \textbf{Response:} test

\begin{Comments}
The second parameter of MergeSnapshotExtre on Line 11, Algorithm 5 should be (u’, v’, t, a)?
\end{Comments}
\noindent \textbf{Response:} The parameter should remain $ (u',v',a,a) $. The reason is that edges stored in snapshots of each tree node are in form of $ () $

\section{Response to Reviewer \#1.2}
\setcounter{Comments}{0}
\begin{Comments}
It would be better to move Definitions 1 and 2 to be after Definition 3, as the latter does not rely on the first two.
\end{Comments}
\noindent \textbf{Response: } Following your suggestion, we have moved Definitions 1, 2 to be after Definition 3.

\begin{Comments}
In the problem formulation, it appears that parameter $\theta$ is not required.
\end{Comments}
\noindent \textbf{Response: } $\theta$ is a parameter which can control the window size for each snapshot. As shown in Fig.12, we evaluate our algorithms for other window sizes on DBLP. Since the results are similar to the case of $\theta=1$, we do the experiments with $\theta$ setting to 1 month/year.

In the revised version, to avoid misunderstanding, we have removed parameter $\theta$ so the window size will be set as 1 month/year.

\begin{Comments}
 Left column, Page 5, "$cd(u) \geq \mu$ and $\overline{cd}(u) < \mu$" $-->$ "$cd(u) < \mu$ and $\overline{cd}(u) \geq \mu$"
\end{Comments}
\noindent \textbf{Response: } Thank you very much for pointing out the negligence. We have corrected this error.

\section{Response to Reviewer \#2.1}
\setcounter{Comments}{0}
\begin{Comments}
As mentioned in related works, some existing works study the dense subgraphs, quasi-cliques in temporal graphs. Can they be used in finding the communities in temporal graphs? Some discussion can be given in the introduction.
\end{Comments}
\noindent \textbf{Response: }
The existing algorithm for mining quasi-cliques can not be applied in temporal graphs. We can design novel algorithms for mining quasi-cliques in temporal networks. However, since the problem of mining quasi-cliques is NP-hard in static networks, the problem of mining quasi-cliques in temporal networks may be NP-hard, too.

In this manuscript, we focus on the density-based clustering algorithm for temporal graphs, so our definition is relative to the algorithm of SCAN. The proposed TSCAN algorithm only needs polynomial-time to get the answer and it runs quickly in practice.

We have added some additional discussion in the introduction to describe them as above.

\begin{Comments}
It should be better to give a comparison between the result of proposed method and the ground truth if there are available datasets.
Some potential competitors can be discussed in the paper.
\end{Comments}
\noindent \textbf{Response: } The available datasets do not have communities of ground truth in the temporal situation, so it is hard to compare  between the result of proposed method and the ground truth. We have tested 4 evaluation metrics in exp-1, exp-2 and exp-3 which can demonstrate the effectiveness of our proposed algorithms (see Fig.8-11). We also update new case studies which are much more interpretable to show the results of TSCAN (see Fig.13 in the revised version).

\begin{Comments}
The formulated model contains many parameters. Several attempts may required to get an optimal setting. 
\end{Comments}
\noindent \textbf{Response: } Thank you for your insightful comments. In exp-3 we have done effectiveness testing with varying the parameters $\mu$, $\tau$ and $\epsilon$. In the revised version, we have added more analyses of seeking better parameters settings (see exp-4 in section 4.1).

\section{Response to Reviewer \#2.2}
\setcounter{Comments}{0}
\begin{Comments}
1)The article is very hard to read. I’m familiar with dynamic networks and community detection, but it took me 3 hours to understand really what the authors propose, not talking about fully understanding all the optimization strategies.

2) I think that some ideas and concepts are not clear for the authors themselves, or that they should better position their work relatively to the state of the art.

\end{Comments}
\noindent \textbf{Response: } Following your suggestion, we have re-positioned some definitions and examples, so it is easier to be understood.

\begin{Comments}
	The authors do not seem to provide any implementation of their method. Reproducibility is now recognized a very important question in science, and, I think that in 2019, it is not possible any more to propose a complex algorithm that cannot be reproduced in a couple of hours without providing a complete code that the reviewers can test.
\end{Comments}
\noindent \textbf{Response: } Thanks to your insightful comments. Following your suggestion, we have uploaded the codes on Github (\url{https://github.com/VeryLargeGraph/TSCAN}).

%\begin{Comments}
%The principle of the method should be the most important thing to consider in the paper.  I do not think it makes sense to 1) propose a new approach and 2) propose a complex method to optimize it, in the same paper. We should first be convinced that the method is interesting before taking care of making it scalable.  To convince the reader that the method is interesting, it should 1)be presented clearly, 2) be tested on tasks, and compared to related algorithms.
%\end{Comments}
%\noindent \textbf{Response: } Thanks to your insightful comments. Let me introduce our work.
%
%Our goal is to identify the communities in a temporal network that are stable over time. 
%Note that, the traditional existing community detection algorithms focus mainly on traditional graphs, thus they also cannot be directly used for detecting stable communities in temporal graphs.
%To efficiently find the stable communities, we develop a new community detection algorithm based on the density-based graph clustering framework. We also propose several carefully-designed pruning techniques to significantly speed up the proposed algorithm.

\begin{Comments}
Many choices seem arbitrary, or not well supported by the practice, which might be due to a lack of knowledge of the literature. For instance:

-the authors describe their method as a method for link streams, but it seems that the first step of their algorithm requires to build snapshots. There their method is a snapshot based method. Starting from a link stream makes no difference, any snapshot algorithm could require to first build snapshot of the desired duration.

-The authors talk about dynamic networks, but in fact it seems that the order of snapshots makes no difference, so they could work with any multislice/multiplex network.

\end{Comments}
\noindent \textbf{Response: } Thank you for your helpful comments. I think that building snapshots make it better to describe the model and the problem definitions. In reality, we do not need to build snapshots in the progress of the algorithms. We only need to fetch the neighbors and the attached temporal information of each node (see Algorithm 1-3). Also, some existing researches [1][2] for community detection or subgraph discovery in temporal networks all build snapshots for considering the common properties of some clusters.

[1] Shuai Ma, Renjun Hu, Luoshu Wang, Xuelian Lin, and Jinpeng Huai. Fast Computation of Dense Temporal Subgraphs. ICDE 2017.

[2] Ashwin Paranjape, Austin R. Benson, Jure Leskovec. Motifs in Temporal Networks. WSDM 2017.

It is right that the order of snapshots makes no difference, so our algorithms can also work with the multislice/multiplex networks. However, the researches about mining stable communities in multislice/multiplex networks are also elusive now. %In practice, temporal networks are special cases of multislice/multiplex networks as shown in ref.[3][4].

%[3]

%[4]

\begin{Comments}
	The authors decide to use the structural similarity (without never explaining why), but the rest of the method and optimization could in fact work with any similarity measure, right ?
\end{Comments}
\noindent \textbf{Response: } Yes, it is. We use Eq.(1) to define the structural similarity because it measures the number of common neighbor of $u$ and $v$ (normalization by the product of number of their neighbors), same as SCAN proposed by Xu in KDD07.

The computation of the structural similarity is expensive in practice, because we need to compute the set-intersection of neighbors of the considering two nodes. Besides, other similar definitions for the structural similarity all need the item of the set-intersection of neighbors of the considering two nodes, too. So, different definitions for the structural similarity make little difference to the acceleration ratio of the proposed optimized algorithms.

\begin{Comments}	
	The authors define 4 metrics to evaluate their results, but they are poorly explained, as I understand them, they are not dynamic, since they are simply defined on the multigraph of the cumulated graph. If that is well the case, why not compare the results with any community detection algorithm run on this network ?
\end{Comments}
\noindent \textbf{Response: } The proposed 4 metrics are motivated by separability, density, cohesiveness and clustering coefficient which are used to evaluate the communities in the static graphs, proposed by Yang in ICDM2012. We modified them a little so the temporal edges can be counted and they can be used to evaluate the communities in temporal graphs. As we all know, the community detection algorithm in static graph can not be used directly in the temporal networks, or the multigraphs either. 
Since our work mainly focus on the density-based graph clustering, we have compared our proposed TSCAN with the modified traditional density-based graph clustering algorithm PSCAN-W (see section 4, Fig.7-10).

Following your suggestions, we have given clear intuitions about the four evaluation metrics of the communities in the temporal graphs (see Table.4).

\begin{Comments}	
	why talk about snapshot and de-temporal graphs? I could not see a difference between the two in the text.
\end{Comments}
\noindent \textbf{Response: } %The $i$-th snapshot of $\mathcal G$ is a temporal subgraph ${\mathcal G}_i=(\mathcal{V}, \mathcal{E}_i)$ in which $\mathcal{E}_i$ be a set of edges that are extracted from $\mathcal E$ in the time interval $(t_i-\theta, t_i]$. 
%For a temporal graph $\mathcal G$, its \emph{de-temporal} graph is referred to as $G=(V, E)$ by ignoring all the timestamps associated with the temporal edges. 
Snapshot ${\mathcal G}_i$ is a temporal graph that contains all the edges in time interval $(t_i-\theta, t_i]$. \emph{De-temporal} graph $G$ of $\mathcal{G}$ is a simple graph that contains all the edges in time interval $(t_0, t_{\mathcal{T}}]$, in which same edge with different time will be existing only once.

Snapshot is a temporal graph and \emph{de-temporal} graph is a static graph.
$G$ is a simple summarization of temporal graph $\mathcal G$. 
Also, $G_i$  is the \emph{de-temporal} graph of snapshot $\mathcal G_i$.
Obviously, $G = \bigcup_{t_0}^{t_{\mathcal{T}} }G_i$.

\begin{Comments}
Another point that the author should keep in mind is to try to keep their work concise when possible. Maybe some parts of it could go into an annex, so that the core of the paper becomes readable
\end{Comments}
\noindent \textbf{Response: }We have combined some parts together and re-positioned some algorithms and examples, so it is easier to be understood.

\begin{Comments}

To finish, I think that the authors have not made great effort to compare their work (qualitatively or quantitatively) with the state of the art. They start from the premises that they" are the first to study the problem of mining stable communities in temporal graphs”. But in this paper, if I understand correctly, stable communities means that nodes cannot change communities which is rather a limit than a strength in general, since networks can change completely in different times, and giving them a unique affiliation is often misleading. But this is a point of view, stable communities can very well be useful in some contexts, however, some methods to study them already exist, such as Matias et al. 2016 (Statistical clustering of temporal networks through a dynamic stochastic block model), Gauvin et al.  2014 (Detecting the Community Structure and Activity Patterns of Temporal Networks: A Non-Negative Tensor Factorization Approach), Aynaud et al. 2011 (Multi-Step Community Detection and Hierarchical Time Segmentation in Evolving Networks), etc.
Even without comparing to those methods, one could at least compare to a simple clustering of the “de-temporal” weighted graph.
\end{Comments}
\noindent \textbf{Response: } In our works, we mainly focus on detecting stable communities by density-based clustering. I have downloaded the mentioned references and they study different models of communities in the temporal graph, so our proposed algorithms are hard to compare with them.

In our experiments, we have treated PSCAN-W as a baseline of a simple clustering of the weighted de-temporal graph (Figs.8-10). We transform the temporal graph into a weighted de-temporal graph (weight of each edge is the number of temporal edges in the temporal graph), and then PSCAN-W invokes the density-based graph clustering algorithm (SCAN) in the weighted de-temporal graph.

\begin{Comments}

some English mistakes.
P1:in the face-to-face contact network
In the collaboration network, each edge represents two authors, u and v, coauthored a paper at time t.
-to identify a densely-connected community structure that are stable over time
-Similarity, most other existing community detection algorithms

some remarks.
P3:
-its de-temporal graph: de-temporal is not a usual name for this classic process, and you do not precise if the network is a multigraph (as it should be according to your description) or not.
-bad reference, [18] is not using sliding windows

\end{Comments}
\noindent \textbf{Response: } Following your suggestion, we fixed those typos and re-check the manuscript again and again to reduce the typos as much as possible.

\begin{Comments}
	the concepts in the density-based graph clustering framework (SCAN): it would have been important to explain what is this algorithm, why is it interesting, what is density exact, etc. beforehand. (Dates from 2007!)
	Is the approach comparable with Falkowski et al: Studying Community Dynamics with an Incremental Graph Mining Algorithm.

\end{Comments}
\noindent \textbf{Response: } Thanks to your careful comments. Our work is not comparable with the work proposed by Falkowski. Most previous community detection studies on dynamic graphs aim to maintain communities that evolve over time. Unlike this goal, our work mainly focuses on detecting stable communities in the temporal network based on density-based clustering methods. There are a huge number of papers on community detection in dynamic (temporal) graphs, due to the space limit, in our initial submission, we have to ignore some of those references, and focus on surveying the references on "stable community detection" and "structural graph clustering" (SCAN).

%Following your suggestion, we have explained more about the structural graph clustering algorithm (SCAN) so it is better to be understood.

\begin{Comments}

	P10: Case-study: not interpretable by reader, could you find a real-life network to illustrate ?
\end{Comments}
\noindent \textbf{Response: } Following your suggestion, we have updated the case studies and introduced more backgrounds, so they are much more interpretable in the revised version.

\section{Response to Reviewer \#3 }
\setcounter{Comments}{0}
\begin{Comments}
Definition 5 for stable communities is problematic. Consider a (3, 3, 0.6)-stable cores $c_1$. Suppose nodes $v_1$, $v_2$ and $v_3$ are simultaneously similar to $c_1$ in snapshots $t_1$, $t_2$, and $t_3$ and nodes $v_4$, $v_5$ and $v_6$ are simultaneously similar to $c_1$ in snapshots $t_4$, $t_5$, and $t_6$. This may be the case that professor $c_1$ moves to another place and has a new group of coauthors. According to Def. 5, all nodes will be assigned to the same stable cluster. However, ($v_1$, $v_2$, $v_3$) and ($v_4$, $v_5$, $v_6$) should not be in the same stable community.

\end{Comments}
\noindent \textbf{Response: } Thanks to your insightful comments. In our manuscript, definition 5 for stable communities is a relaxed version so it might have the problem as you described. However, if we change the definition to distinguish those nodes which are clustered in different time, we will perform several more frequent pattern minings (each one need $O(C_{\mathcal{T}}^\tau)$ time) and get much more overlap clusters. Those will result in much additional computation time and new problem of choosing the overlap clusters. So, we choose this relaxed definition, results of four evaluation metrics and case studies confirm the effectiveness of our model.

\begin{Comments}
The selection of parameters $\mu$, $\tau$, and $\epsilon$ needs a further discussion: how do they influence the results and how to set them in practice.
\end{Comments}
\noindent \textbf{Response: } Thank you for your insightful comments. In exp-3 we have done effectiveness testings with varying the parameters $\mu$, $\tau$ and $\epsilon$. In the revised version, we have added more analyses of seeking better parameters settings (see exp-4 in section 4.1).

\begin{Comments}
	The experiments are weak, especially no formal baselines are included.
\end{Comments}
\noindent \textbf{Response: } Since our work mainly focuses on the density-based graph clustering, we have compared our proposed TSCAN with the modified traditional density-based graph clustering algorithm PSCAN-W (see section 4, Fig.7-10). We treat PSCAN-W as a baseline and it can be found that PSCAN-W performs worse than our proposed algorithm TSCAN in the effectiveness testings. Also, the case studies demonstrate the results of PSCAN-W and TSCAN. It can be seen that our proposed model TSCAN is much better than the baseline PSCAN-W.

\begin{Comments}
 Para 2, Introduction states "Most existing community ... do not consider the temporal information of the links", how about those community detection algorithms on temporal networks, e.g. ref. [35], [36].
\end{Comments}
\noindent \textbf{Response: } Thank you very much for pointing out the negligence. We want to say that most traditional existing community detection do not consider the temporal information of the links. However, the problem of mining community in temporal graphs are studied in recent years.

Following your suggestions, we have changed the expressions in the introduction.

\begin{Comments}
The notations in the preliminaries are heavy, which makes the section a little bit hard to follow. Consider including a table to summarize these notations.
\end{Comments}
\noindent \textbf{Response: } Following your suggestion, we have added Table.1 to summaries the notations.

\begin{Comments}
$\mathcal{T}$ is used as both the number of timestamps (line 6, page 2) and the number of snapshots (line 59, page 2). Indeed, the transformation from timestamps to snapshots is not clear. How to select $t_i$ and can time intervals $(t_i-\theta, t_i]$ overlap?
\end{Comments}
\noindent \textbf{Response: } Thank you very much for pointing out the negligence. In our experiments, we choose $t_i$  to be an arithmetic progression so each $t_i$ could represent different month/year. 
For a given time interval $\theta$, a snapshot is a temporal subgraph generated in a $\theta$-length sliding window. %In the experiments, we set $\theta$ to a default value of 1 month/year which means that every snapshot contains all the temporal edges in a one month/year length sliding window.
If $\theta=1$, $(t_i-\theta, t_i]$ would not overlap. Else if If $\theta>1$, $(t_i-\theta, t_i]$ would overlap.

As shown in Fig.12 of the last version, we evaluate our algorithms for other window sizes on DBLP. Since the results are similar to the case of $\theta=1$, we do the following experiments with $\theta$ setting to 1 month/year.

In the revised version, to avoid misunderstanding, we removed all the parameter $\theta$ so $(t_i-\theta, t_i]$ will be the time interval.

\begin{Comments}
The statement "Since only one edge is different for any two consecutive snapshots" (line 49, page 4) is not straightforward. How about the case in Fig.2 that multiple edges are associated with the same timestamps. As a result, the incremental maintenance in line 19 of Algorithm 1 is also not clear.
\end{Comments}
\noindent \textbf{Response: } Thanks to your careful comments. Due to the limitation of space, we omit some descriptions. Clearly, $|N_i(u)|$ and $|N_i(v)|$ are easy to get and they can be stored as constants in the structure of the temporal network(similar to adjacency list in the static graph). In the revised version, we use $hashset$ to compute the $|N_i(u) \cap N_i(v)|$ so it only needs time of $O(m)$.

\begin{Comments}
 typos

a) line 11 page 1: stable community $-->$ stable communities

b) line 40, page 1: Similarity $-->$ Similarly

c) line 44, page 1: that are stable over $-->$ that is stable over

d) line 18, page 2: get exact stable core $-->$ cores

e) line 25, page 3: $(\mu, \tau, \epsilon)$-stable u $-->$ $(\mu, \tau, \epsilon)$-stable core u

f) equation in line 51, page 8: $(u, v)\in \mathcal{E}$ $-->$ $(u, v, t)\in \mathcal{E}$

g) line 46, page 8: StrongCore $-->$ StableCore

\end{Comments}
\noindent \textbf{Response: } Following your suggestion, we have fixed the typos in this revision.

\section{Response to Reviewer \#4 }
\setcounter{Comments}{0}
\begin{Comments}
The authors frequently misuse the sentence "statistically significant" and "significantly outperforms" while comparing the results of their algorithm with its competitors. No statistical tests were performed (I strongly suggest to apply something like a Bonferroni-Dunn test for statistical significance).

\end{Comments}
\noindent \textbf{Response: } Thanks to your insightful comments. We have added Bonferroni-Dunn test for effectiveness testing of the compared algorithms in the revised version (see Table.5 in exp-2 of section 4.1).

\begin{Comments}
The authors do not provide public links to their method (and competitors) implementation. To enhance reproducibility - and to support open science - all the code must be packaged and released at submission time. Nowadays, I feel this aspect must represent a mandatory step to allow publication of any paper that introduces a new algorithm/analysis.	
\end{Comments}
\noindent \textbf{Response: } Thanks to your insightful comments. Following your suggestion, we have uploaded the codes on Github (\url{https://github.com/VeryLargeGraph/TSCAN}).

\begin{Comments}
Competitor analysis. I understand the controlled testing against variations of the proposed algorithm, however, I think that external evaluation against alternative solutions could represent a plus to support this work. Among your reference - in [33] - is introduced a family of approaches called "Cross-Time Community Discovery" whose aim seems - to some extent - similar to the one of this study (i.e., identify stable communities over time). Is it possible to identify some algorithms having such rationale (even pursuing it in a different manner w.r.t. the proposed algorithm) to propose an actual comparison and discuss the different contexts of applicability?
\end{Comments}
\noindent \textbf{Response: } In our works, we mainly focus on detecting stable communities by density-based clustering. The works in the references mainly study different models of communities in the temporal graph. For example, in "Community Discovery in Dynamic Networks: a Survey", the "Cross-Time Community Discovery" study four situations of fixed/evolving memberships, fixed/evolving properties. As our work is based on none-attributed graph, we may compare with the works of evolving memberships, fixed properties. But the existed works are not focusing on stable communities, and the models are not density-based. So, our proposed algorithms are hard to compare with them.

In our experiments, we propose PSCAN-W as a baseline algorithm. The PSCAN-W algorithm invokes the density-based graph clustering algorithm (SCAN) in the transformed weighted de-temporal graph. Our proposed model TSCAN is tested to have much better effectiveness then PSCAN-W (see Figs.8-10), and a little slower than PSCAN-W (see Figs.14). So, our proposed model can enhance SCAN into the temporal graphs to find stable communities. However, some other graph clustering/communities discovery models can motivated by us to be transformed into a stable one in temporal graph. But they may cause large increase of computing time.

\end{document}

### 2023-01-05 TemporalGraphCube/TemporalGraphCube_revision.tex
latex 1-5

%% bare_jrnl_compsoc.tex

\documentclass[10pt,journal,compsoc]{IEEEtran}
%\usepackage{ntheorem}
%\usepackage{algorithmic}
%\usepackage{cite}
%\usepackage{times}
\usepackage{amsmath,amsfonts,amssymb, amsthm, xspace}
\usepackage[linesnumbered,ruled,vlined]{algorithm2e}
\usepackage{graphicx, subfigure,stfloats}
\usepackage{epstopdf}
\usepackage{textcomp}
\usepackage{ragged2e, xcolor}
\usepackage{balance}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage{makecell}
\usepackage{url}
\usepackage{booktabs}

\long\def\comment#1{}
%\newcommand{\eop}{\hspace*{\fill}\mbox{$\Box$}}

%
% If IEEEtran.cls has not been installed into the LaTeX system files,
% manually specify the path to it like:
% \documentclass[10pt,journal,compsoc]{../sty/IEEEtran}

% Some very useful LaTeX packages include:
% (uncomment the ones you want to load)

% *** MISC UTILITY PACKAGES ***
%
%\usepackage{ifpdf}
% Heiko Oberdiek's ifpdf.sty is very useful if you need conditional
% compilation based on whether the output is pdf or dvi.
% usage:
% \ifpdf
%   % pdf code
% \else
%   % dvi code
% \fi
% The latest version of ifpdf.sty can be obtained from:
% http://www.ctan.org/pkg/ifpdf
% Also, note that IEEEtran.cls V1.7 and later provides a builtin
% \ifCLASSINFOpdf conditional that works the same way.
% When switching from latex to pdflatex and vice-versa, the compiler may
% have to be run twice to clear warning/error messages.

% *** CITATION PACKAGES ***
%
\ifCLASSOPTIONcompsoc
% IEEE Computer Society needs nocompress option
% requires cite.sty v4.0 or later (November 2003)
\usepackage[nocompress]{cite}
\else
% normal IEEE
\usepackage{cite}
\fi
% cite.sty was written by Donald Arseneau
% V1.6 and later of IEEEtran pre-defines the format of the cite.sty package
% \cite{} output to follow that of the IEEE. Loading the cite package will
% result in citation numbers being automatically sorted and properly
% "compressed/ranged". e.g., [1], [9], [2], [7], [5], [6] without using
% cite.sty will become [1], [2], [5]--[7], [9] using cite.sty. cite.sty's
% \cite will automatically add leading space, if needed. Use cite.sty's
% noadjust option (cite.sty V3.8 and later) if you want to turn this off
% such as if a citation ever needs to be enclosed in parenthesis.
% cite.sty is already installed on most LaTeX systems. Be sure and use
% version 5.0 (2009-03-20) and later if using hyperref.sty.
% The latest version can be obtained at:
% http://www.ctan.org/pkg/cite
% The documentation is contained in the cite.sty file itself.
%
% Note that some packages require special options to format as the Computer
% Society requires. In particular, Computer Society  papers do not use
% compressed citation ranges as is done in typical IEEE papers
% (e.g., [1]-[4]). Instead, they list every citation separately in order
% (e.g., [1], [2], [3], [4]). To get the latter we need to load the cite
% package with the nocompress option which is supported by cite.sty v4.0
% and later. Note also the use of a CLASSOPTION conditional provided by
% IEEEtran.cls V1.7 and later.

% *** GRAPHICS RELATED PACKAGES ***
%
\ifCLASSINFOpdf
% \usepackage[pdftex]{graphicx}
% declare the path(s) where your graphic files are
% \graphicspath{{../pdf/}{../jpeg/}}
% and their extensions so you won't have to specify these with
% every instance of \includegraphics
% \DeclareGraphicsExtensions{.pdf,.jpeg,.png}
\else
% or other class option (dvipsone, dvipdf, if not using dvips). graphicx
% will default to the driver specified in the system graphics.cfg if no
% driver is specified.
% \usepackage[dvips]{graphicx}
% declare the path(s) where your graphic files are
% \graphicspath{{../eps/}}
% and their extensions so you won't have to specify these with
% every instance of \includegraphics
% \DeclareGraphicsExtensions{.eps}
\fi
% graphicx was written by David Carlisle and Sebastian Rahtz. It is
% required if you want graphics, photos, etc. graphicx.sty is already
% installed on most LaTeX systems. The latest version and documentation
% can be obtained at:
% http://www.ctan.org/pkg/graphicx
% Another good source of documentation is "Using Imported Graphics in
% LaTeX2e" by Keith Reckdahl which can be found at:
% http://www.ctan.org/pkg/epslatex
%
% latex, and pdflatex in dvi mode, support graphics in encapsulated
% postscript (.eps) format. pdflatex in pdf mode supports graphics
% in .pdf, .jpeg, .png and .mps (metapost) formats. Users should ensure
% that all non-photo figures use a vector format (.eps, .pdf, .mps) and
% not a bitmapped formats (.jpeg, .png). The IEEE frowns on bitmapped formats
% which can result in "jaggedy"/blurry rendering of lines and letters as
% well as large increases in file sizes.
%
% You can find documentation about the pdfTeX application at:
% http://www.tug.org/applications/pdftex

% *** SPECIALIZED LIST PACKAGES ***

% *** ALIGNMENT PACKAGES ***
%
%\usepackage{array}
% Frank Mittelbach's and David Carlisle's array.sty patches and improves
% the standard LaTeX2e array and tabular environments to provide better
% appearance and additional user controls. As the default LaTeX2e table
% generation code is lacking to the point of almost being broken with
% respect to the quality of the end results, all users are strongly
% advised to use an enhanced (at the very least that provided by array.sty)
% set of table tools. array.sty is already installed on most systems. The
% latest version and documentation can be obtained at:
% http://www.ctan.org/pkg/array

% IEEEtran contains the IEEEeqnarray family of commands that can be used to
% generate multiline equations as well as matrices, tables, etc., of high
% quality.

% *** SUBFIGURE PACKAGES ***
%\ifCLASSOPTIONcompsoc
%  \usepackage[caption=false,font=footnotesize,labelfont=sf,textfont=sf]{subfig}
%\else
%  \usepackage[caption=false,font=footnotesize]{subfig}
%\fi
% subfig.sty, written by Steven Douglas Cochran, is the modern replacement
% for subfigure.sty, the latter of which is no longer maintained and is
% incompatible with some LaTeX packages including fixltx2e. However,
% subfig.sty requires and automatically loads Axel Sommerfeldt's caption.sty
% which will override IEEEtran.cls' handling of captions and this will result
% in non-IEEE style figure/table captions. To prevent this problem, be sure
% and invoke subfig.sty's "caption=false" package option (available since
% subfig.sty version 1.3, 2005/06/28) as this is will preserve IEEEtran.cls
% handling of captions.
% Note that the Computer Society format requires a sans serif font rather
% than the serif font used in traditional IEEE formatting and thus the need
% to invoke different subfig.sty package options depending on whether
% compsoc mode has been enabled.
%
% The latest version and documentation of subfig.sty can be obtained at:
% http://www.ctan.org/pkg/subfig

% *** FLOAT PACKAGES ***
%
%\usepackage{fixltx2e}
% fixltx2e, the successor to the earlier fix2col.sty, was written by
% Frank Mittelbach and David Carlisle. This package corrects a few problems
% in the LaTeX2e kernel, the most notable of which is that in current
% LaTeX2e releases, the ordering of single and double column floats is not
% guaranteed to be preserved. Thus, an unpatched LaTeX2e can allow a
% single column figure to be placed prior to an earlier double column
% figure.
% Be aware that LaTeX2e kernels dated 2015 and later have fixltx2e.sty's
% corrections already built into the system in which case a warning will
% be issued if an attempt is made to load fixltx2e.sty as it is no longer
% needed.
% The latest version and documentation can be found at:
% http://www.ctan.org/pkg/fixltx2e

%\usepackage{stfloats}
% stfloats.sty was written by Sigitas Tolusis. This package gives LaTeX2e
% the ability to do double column floats at the bottom of the page as well
% as the top. (e.g., "\begin{figure*}[!b]" is not normally possible in
% LaTeX2e). It also provides a command:
%\fnbelowfloat
% to enable the placement of footnotes below bottom floats (the standard
% LaTeX2e kernel puts them above bottom floats). This is an invasive package
% which rewrites many portions of the LaTeX2e float routines. It may not work
% with other packages that modify the LaTeX2e float routines. The latest
% version and documentation can be obtained at:
% http://www.ctan.org/pkg/stfloats
% Do not use the stfloats baselinefloat ability as the IEEE does not allow
% \baselineskip to stretch. Authors submitting work to the IEEE should note
% that the IEEE rarely uses double column equations and that authors should try
% to avoid such use. Do not be tempted to use the cuted.sty or midfloat.sty
% packages (also by Sigitas Tolusis) as the IEEE does not format its papers in
% such ways.
% Do not attempt to use stfloats with fixltx2e as they are incompatible.
% Instead, use Morten Hogholm'a dblfloatfix which combines the features
% of both fixltx2e and stfloats:
%
% \usepackage{dblfloatfix}
% The latest version can be found at:
% http://www.ctan.org/pkg/dblfloatfix

%\ifCLASSOPTIONcaptionsoff
%  \usepackage[nomarkers]{endfloat}
% \let\MYoriglatexcaption\caption
% \renewcommand{\caption}[2][\relax]{\MYoriglatexcaption[#2]{#2}}
%\fi
% endfloat.sty was written by James Darrell McCauley, Jeff Goldberg and
% Axel Sommerfeldt. This package may be useful when used in conjunction with
% IEEEtran.cls'  captionsoff option. Some IEEE journals/societies require that
% submissions have lists of figures/tables at the end of the paper and that
% figures/tables without any captions are placed on a page by themselves at
% the end of the document. If needed, the draftcls IEEEtran class option or
% \CLASSINPUTbaselinestretch interface can be used to increase the line
% spacing as well. Be sure and use the nomarkers option of endfloat to
% prevent endfloat from "marking" where the figures would have been placed
% in the text. The two hack lines of code above are a slight modification of
% that suggested by in the endfloat docs (section 8.4.1) to ensure that
% the full captions always appear in the list of figures/tables - even if
% the user used the short optional argument of \caption[]{}.
% IEEE papers do not typically make use of \caption[]'s optional argument,
% so this should not be an issue. A similar trick can be used to disable
% captions of packages such as subfig.sty that lack options to turn off
% the subcaptions:
% For subfig.sty:
% \let\MYorigsubfloat\subfloat
% \renewcommand{\subfloat}[2][\relax]{\MYorigsubfloat[]{#2}}
% However, the above trick will not work if both optional arguments of
% the \subfloat command are used. Furthermore, there needs to be a
% description of each subfigure *somewhere* and endfloat does not add
% subfigure captions to its list of figures. Thus, the best approach is to
% avoid the use of subfigure captions (many IEEE journals avoid them anyway)
% and instead reference/explain all the subfigures within the main caption.
% The latest version of endfloat.sty and its documentation can obtained at:
% http://www.ctan.org/pkg/endfloat
%
% The IEEEtran \ifCLASSOPTIONcaptionsoff conditional can also be used
% later in the document, say, to conditionally put the References on a
% page by themselves.

% *** PDF, URL AND HYPERLINK PACKAGES ***
%
%\usepackage{url}
% url.sty was written by Donald Arseneau. It provides better support for
% handling and breaking URLs. url.sty is already installed on most LaTeX
% systems. The latest version and documentation can be obtained at:
% http://www.ctan.org/pkg/url
% Basically, \url{my_url_here}.

% *** Do not adjust lengths that control margins, column widths, etc. ***
% *** Do not use packages that alter fonts (such as pslatex).         ***
% There should be no need to do such things with IEEEtran.cls V1.6 and later.
% (Unless specifically asked to do so by the journal or conference you plan
% to submit to, of course. )

% correct bad hyphenation here
\hyphenation{op-tical net-works semi-conduc-tor}

\renewcommand{\baselinestretch}{0.97}

\input{command}

\begin{document}
	%
	% paper title
	% Titles are generally capitalized except for words such as a, an, and, as,
	% at, but, by, for, in, nor, of, on, or, the, to and up, which are usually
	% not capitalized unless they are the first or last word of the title.
	% Linebreaks \\ can be used within to get better formatting as desired.
	% Do not put math or special symbols in the title.
	\title{Temporal Graph Cube}
	%
	%
	% author names and IEEE memberships
	% note positions of commas and nonbreaking spaces ( ~ ) LaTeX will not break
	% a structure at a ~ so this keeps an author's name from being broken across
	% two lines.
	% use \thanks{} to gain access to the first footnote area
	% a separate \thanks must be used for each paragraph as LaTeX2e's \thanks
	% was not built to handle multiple paragraphs
	%
	%
	%\IEEEcompsocitemizethanks is a special \thanks that produces the bulleted
	% lists the Computer Society journals use for "first footnote" author
	% affiliations. Use \IEEEcompsocthanksitem which works much like \item
	% for each affiliation group. When not in compsoc mode,
	% \IEEEcompsocitemizethanks becomes like \thanks and
	% \IEEEcompsocthanksitem becomes a line break with idention. This
	% facilitates dual compilation, although admittedly the differences in the
	% desired content of \author between the different types of papers makes a
	% one-size-fits-all approach a daunting prospect. For instance, compsoc
	% journal papers have the author affiliations above the "Manuscript
	% received ..."  text while in non-compsoc journals this is reversed. Sigh.

	\author{Guoren~Wang, Yue Zeng, Rong-Hua Li, Hongchao Qin,\\ Xuanhua Shi, Yubin Xia, Xuequn Shang, Liang Hong
		\IEEEcompsocitemizethanks{
			\IEEEcompsocthanksitem G.~Wang, Y.~Zeng, R.-H.~Li, H.~Qin are with the Beijing Institute of Technology, China; Xuanhua Shi is with Huazhong University of Science and Technology, China; Yubin Xia is with Shanghai Jiao Tong University; Xuequn Shang is with Northwestern Polytechnical University; Liang Hong is with Wuhan University.

E-mail: wanggrbit@126.com, bruceez@163.com, lironghuabit@126.com, qhc.neu@gmail.com, xhshi@hust.edu.cn, xiayubin@sjtu.edu.cn,  shang@nwpu.edu.cn, hong@whu.edu.cn.
%			\IEEEcompsocthanksitem R.~Mao is with the Shenzhen University, Shenzhen 518060, China. E-mail: mao@szu.edu.cn.
		}
	}

	%\author{Michael~Shell,~\IEEEmembership{Member,~IEEE,}
		%        John~Doe,~\IEEEmembership{Fellow,~OSA,}
		%        and~Jane~Doe,~\IEEEmembership{Life~Fellow,~IEEE}% <-this % stops a space
		%\IEEEcompsocitemizethanks{\IEEEcompsocthanksitem M. Shell was with the Department
			%of Electrical and Computer Engineering, Georgia Institute of Technology, Atlanta,
			%GA, 30332.\protect\\
			%% note need leading \protect in front of \\ to get a newline within \thanks as
			%% \\ is fragile and will error, could use \hfil\break instead.
			%E-mail: see http://www.michaelshell.org/contact.html
			%\IEEEcompsocthanksitem J. Doe and J. Doe are with Anonymous University.}% <-this % stops an unwanted space
		%%\thanks{Manuscript received April 19, 2005; revised August 26, 2015.}
		%}

	% note the % following the last \IEEEmembership and also \thanks -
	% these prevent an unwanted space from occurring between the last author name
	% and the end of the author line. i.e.., if you had this:
	%
	% \author{....lastname \thanks{...} \thanks{...} }
	%                     ^------------^------------^----Do not want these spaces!
	%
	% a space would be appended to the last name and could cause every name on that
	% line to be shifted left slightly. This is one of those "LaTeX things". For
	% instance, "\textbf{A} \textbf{B}" will typeset as "A B" not "AB". To get
	% "AB" then you have to do: "\textbf{A}\textbf{B}"
	% \thanks is no different in this regard, so shield the last } of each \thanks
% that ends a line with a % and do not let a space in before the next \thanks.
% Spaces after \IEEEmembership other than the last one are OK (and needed) as
% you are supposed to have spaces between the names. For what it is worth,
% this is a minor point as most people would not even notice if the said evil
% space somehow managed to creep in.

% The paper headers IEEE Transactions on Knowledge and Data Eengineering
\markboth{IEEE Transactions on Knowledge and Data Eengineering, ,~Vol.~X, No.~X, XXXX~2021}%
%\markboth{Journal of \LaTeX\ Class Files,~Vol.~14, No.~8, August~2015}%
{Shell \MakeLowercase{\textit{et al.}}: Bare Demo of IEEEtran.cls for Computer Society Journals}
% The only time the second header will appear is for the odd numbered pages
% after the title page when using the twoside option.
%
% *** Note that you probably will NOT want to include the author's ***
% *** name in the headers of peer review papers.                   ***
% You can use \ifCLASSOPTIONpeerreview for conditional compilation here if
% you desire.

% The publisher's ID mark at the bottom of the page is less important with
% Computer Society journal papers as those publications place the marks
% outside of the main text columns and, therefore, unlike regular IEEE
% journals, the available text space is not reduced by their presence.
% If you want to put a publisher's ID mark on the page you can do it like
% this:
%\IEEEpubid{0000--0000/00\$00.00~\copyright~2015 IEEE}
% or like this to get the Computer Society new two part style.
%\IEEEpubid{\makebox[\columnwidth]{\hfill 0000--0000/00/\$00.00~\copyright~2015 IEEE}%
	%\hspace{\columnsep}\makebox[\columnwidth]{Published by the IEEE Computer Society\hfill}}
% Remember, if you use this you must call \IEEEpubidadjcol in the second
% column for its text to clear the IEEEpubid mark (Computer Society jorunal
% papers do not need this extra clearance.)

% use for special paper notices
%\IEEEspecialpapernotice{(Invited Paper)}

% for Computer Society papers, we must declare the abstract and index terms
% PRIOR to the title within the \IEEEtitleabstractindextext IEEEtran
% command as these need to go into the title area created by \maketitle.
% As a general rule, do not put math, special symbols or citations
% in the abstract or keywords.
\IEEEtitleabstractindextext{%
	\begin{abstract}
		\justifying Data warehouse and OLAP (Online Analytical Processing) are effective tools for decision support on traditional relational data and static multidimensional network data. However, many real-world multidimensional networks are often modeled as temporal multidimensional networks, where the edges in the network are associated with temporal information. Such temporal multidimensional networks typically cannot be handled by traditional data warehouse and OLAP techniques. To fill this gap, we propose a novel data warehouse model, named \kw{Temporal\enspace Graph\enspace Cube}, to support OLAP queries on temporal multidimensional networks. Through supporting OLAP queries in any time range, users can obtain summarized information of the network in the time range of interest, which cannot be derived by using traditional static graph OLAP techniques. We propose a segment-tree based indexing technique to speed up the OLAP queries, and also develop an index-updating technique to maintain the index when the temporal multidimensional network evolves over time. In addition, we also propose a novel concept called \kw{similarity\enspace of\enspace snapshots} which shows a strong correlation with the efficiency of indexing technique and can provide a good reference on the necessity of building the index. The results of extensive experiments on two large real-world datasets demonstrate the effectiveness and efficiency of the proposed method. %With the support of \kw{MinLevel} strategy, the indexes are able to achieve good acceleration effect and space efficiency, especially segment tree, which also has the best scalability.
	\end{abstract}

%	\begin{abstract}
%		\justifying We study the problem of enabling data warehouse and OLAP (Online Analytical Processing) technology to analyze large scale temporal multidimensional networks. Data warehouse and OLAP are effective tools for decision support on traditional relational data and static multidimensional networks. However, many real-world multidimensional networks are often modeled as temporal multidimensional networks, where each edge in the network is associated with temporal information. Such temporal multidimensional networks often cannot be handled by traditional data warehouse and OLAP techniques. To fill this gap, we propose a novel data warehouse model, \kw{Temporal\enspace Graph\enspace Cube}. By extending the basic idea of static graph cube, \kw{Temporal\enspace Graph\enspace Cube} supports OLAP queries on temporal multidimensional networks. Specifically, by supporting OLAP queries in any time range, users can obtain summarized information of the networks in the time range of interest, which is impossible with traditional static graph cube. In conducting OLAP queries of \kw{Temporal\enspace Graph\enspace Cube}, we need to merge snapshots in a certain time range. We model this problem as a range query problem on snapshot arrays, and generalize three indexes in traditional range query problem: prefix array, sparse table and segment tree to accelerate the query. We also develop new updating techniques to maintain these generalized indexes when the temporal multidimensional network evolves over time. To further improve the query efficiency, we propose a new concept called \kw{similarity\enspace of\enspace snapshots} which shows a strong correlation with the efficiency of indexing techniques and can provide a good reference on the necessity of building the indexes. The results of extensive experiments on both real-world and synthetic datasets show the efficiency and effectiveness of the proposed solutions. %With the support of \kw{MinLevel} strategy, the indexes are able to achieve good acceleration effect and space efficiency, especially segment tree, which also has the best scalability.
%	\end{abstract}

	% Note that keywords are not normally used for peerreview papers.
%	\begin{IEEEkeywords}
%		Uncertain Graphs, Cohesive Subgraph Mining, Uncertain Core Decomposition.
%\end{IEEEkeywords}
}

% make the title area
\maketitle

% To allow for easy dual compilation without having to reenter the
% abstract/keywords data, the \IEEEtitleabstractindextext text will
% not be used in maketitle, but will appear (i.e.., to be "transported")
% here as \IEEEdisplaynontitleabstractindextext when the compsoc
% or transmag modes are not selected <OR> if conference mode is selected
% - because all conference papers position the abstract like regular
% papers do.
\IEEEdisplaynontitleabstractindextext
% \IEEEdisplaynontitleabstractindextext has no effect when using
% compsoc or transmag under a non-conference mode.

% For peer review papers, you can put extra information on the cover
% page as needed:
% \ifCLASSOPTIONpeerreview
% \begin{center} \bfseries EDICS Category: 3-BBND \end{center}
% \fi
%
% For peerreview papers, this IEEEtran command inserts a page break and
% creates the second title. It will be ignored for other modes.
\IEEEpeerreviewmaketitle

\IEEEraisesectionheading{\section{Introduction}\label{sec:introduction}}

Data warehouses and OLAP (Online Analytical Processing) techniques are helpful tools for knowledge workers (executive, manager, analyst) to analyze and make decisions, because Data warehouses and OLAP together can efficiently provide summarized information in different resolutions by specifying different views (different combinations of data dimensions) of large-scale real-world data through OLAP operations such as roll-up, drill-down and slice-and-dice \cite{chaudhuri1997overview}. Data warehouse built on traditional relational database (RDB) data is called data cube \cite{gray1997data}. In 2011, Zhao et al.\ \cite{zhao2011graph} proposed \kw{Graph} \kw{Cube} which extends data warehouses and OLAP techniques to analyze static multidimensional networks. For each query, static graph cube returns a static network with summarized information in its structure and statistical values on vertices and edges.

However, many real-life networks, such as human proximity networks, scientific collaboration networks, and biological networks, can be modeled as temporal networks \cite{holme2015modern}, where each relationship or interaction has a timestamp. Also, vertices in temporal networks usually contain attributes of multiple dimensions. For example, vertices in human proximity networks have attributes such as name, gender, nationality, hobbies, and so on. Such an attributed network can be modeled as a temporal multidimensional network. There are many studies focusing on the management and analysis of temporal networks \cite{junghanns2017management}, but none of them have tried to extend OLAP techniques to temporal multidimensional networks, i.e., developing approaches to provide users in real time with summarized information on the temporal multidimensional networks in different resolutions and time ranges.
\begin{figure*}[t!]
	\begin{center}
	\begin{tabular}[t]{c}
		\centering
		\subfigure[{\scriptsize Vertex table}]{
			\includegraphics[width=0.27\textwidth]{fig/example/example_tables/tb_example_dataset_adjust.pdf}
		}
		\subfigure[{\scriptsize Network structure}]{
			\includegraphics[width=0.63\textwidth]{fig/example/example_dataset_trade.pdf}
		}
	\end{tabular}
	\end{center}
	\vspace*{-0.4cm}
	\caption{Running example: a temporal multidimensional network with its vertex table and network structure}
	\vspace*{-0.4cm}
	\label{fig:example_dataset}
\end{figure*}

\begin{example} \label{exam:temp_multi_network}
	Fig.~\ref{fig:example_dataset} shows a sample temporal transaction network, presenting the transactions between individuals of different countries of birth and professions in each day. Table in Fig.~\ref{fig:example_dataset} (a) is the vertex table of the temporal network, showing the information of the 8 individuals. Each individual has a primary key ID and 3 dimensions (3 discrete attributes): gender, country (country of birth), profession. Income is a numeric attribute of individuals. Fig.~\ref{fig:example_dataset} (b) shows the network structure of the temporal network. There are 20 temporal edges, illustrating the transactions between individuals in 5 days. Temporal edges in each day can be organized into a snapshot. The numeric attribute on each temporal edge is the amount of each transaction. The static multidimensional information of individuals in Fig.~\ref{fig:example_dataset} (a) and the temporal information of network structure in Fig.~\ref{fig:example_dataset} (b) form a temporal multidimensional network.
\end{example}
In static graph cube \cite{zhao2011graph}, users can specify different views to obtain summarized information of the static multidimensional network and combine the information under these views through OLAP operations such as roll-up, drill-down and slice-and-dice interactively for decision support and business intelligence. For example, a company tries to use static graph cube to analyze the interaction characteristics of people with different attributes (name, gender, profession, income level, etc.) in a large-scale social network in order to support their marketing strategy making. However, edges in real-world networks usually contain timestamps. For example, in social networks, interactions between people occur at specific times, such as a particular day. In this way, static graph cube does not work when users only need information for a specific time range. Considering the previous example, the company only needs data from the last few years, because data that is too old is less informative. Or, they want to study what the characteristics of people's interactions are during particular time ranges, such as holidays or COVID-19 periods. Or, they wish to compare several different time ranges to see how people's interaction patterns change over time. Static graph cube cannot meet the above requirements. As a result, we need to propose novel approaches to make data warehouses and OLAP capable of analyzing temporal multidimensional networks.

\comment{
\begin{figure}[t!]
	\begin{center}
		\begin{tabular}[t]{c}
			\centering
			\hspace*{+0.3cm}
			\subfigure[{\scriptsize Vertex table}]{
				\includegraphics[width=0.36\columnwidth]{fig/example/example_tables/tb_cuboid_gender_adjust.pdf}
			}
			\hspace*{-0.6cm}
			\subfigure[{\scriptsize Network structure}]{
				\includegraphics[width=0.58\columnwidth]{fig/example/exam_cuboid_gender_2_3.pdf}
			}
			\hspace*{-0.6cm}
		\end{tabular}
	\end{center}
	\vspace*{-0.4cm}
	\caption{The answer to ``What is the amount of transactions between individuals of different genders from day 2 to day 3?"}
	\vspace*{-0.4cm}
	\label{fig:exam_cuboid_gender}
\end{figure}
\begin{figure}[t!]
	\begin{center}
		\includegraphics[width=0.45\columnwidth]{fig/example/exam_cuboid_gender_semi_state.pdf}
	\end{center}
	\vspace*{-0.7cm}
	\caption{Intermediate result of generating network structure in Fig.~\ref{fig:exam_cuboid_gender} (b)}
	\vspace*{-0.4cm}
	\label{fig:exam_inter_result_gender}
\end{figure}

}

%\begin{table}[t!]%\vspace*{-0.3cm}
%	%\scriptsize
%	\small
%	\centering
%	\caption{Vertex table of the first question in Example~\ref{exam:cuboid_query}} \vspace*{-0.2cm} \label{tab:cuboid_gender}
%	\begin{tabular}{c c}
%		\toprule
%		Gender & COUNT($\ast$) \cr %\hline %\hline
%		\midrule
%		male&4 \cr %\hline
%		female&4  \cr %\hline
%		\bottomrule
%	\end{tabular}
%	\vspace*{0.4cm}
%\end{table}

%\begin{figure*}[t!]
%	\begin{center}
%		\includegraphics[width=0.95\textwidth]{fig/example/exam_aggregate_gender.pdf}
%	\end{center}
%	\vspace*{-0.4cm}
%	\caption{example aggregate gender}
%	\vspace*{-0.4cm}
%	\label{fig:aggregation_gender}
%\end{figure*}

%\begin{table}[t!]%\vspace*{-0.3cm}
%	%\scriptsize
%	\small
%	\centering
%	\caption{Vertex table of the second and the third question in Example~\ref{exam:cuboid_query}} \vspace*{-0.2cm} \label{tab:cuboid_gender_profession}
%	\begin{tabular}{c c c}
%		\toprule
%		Gender & Profession & AVERAGE($\ast$) \cr %\hline %\hline
%		\midrule
%		male & teacher& 5,000 \cr %\hline
%		male & shopowner & 10,000  \cr %\hline
%		male & student & 1,000  \cr %\hline
%		female & shopowner & 6,000  \cr %\hline
%		female & lawyer & 7,000  \cr %\hline
%		female & doctor & 9,000  \cr %\hline
%		\bottomrule
%	\end{tabular}
%	\vspace*{-0.4cm}
%\end{table}

%\begin{figure*}[t!]
%	\begin{center}
%		\includegraphics[width=0.95\textwidth]{fig/example/exam_aggregate_gender_pro.pdf}
%	\end{center}
%	\vspace*{-0.4cm}
%	\caption{example aggregate gender profession}
%	\vspace*{-0.4cm}
%	\label{fig:aggregation_gender_profession}
%\end{figure*}
%

%\begin{figure}[t!]
%	\begin{center}
%		\begin{tabular}[t]{c}\hspace*{-0.3cm}
%			\subfigure[{\scriptsize Structure of the answer of the first question in Example~\ref{exam:cuboid_query}}]{
%				\includegraphics[width=0.45\columnwidth]{fig/example/exam_cuboid_gender_2_3_adjust.pdf}
%			}
%			\subfigure[{\scriptsize The intermediate result of generating (a)}]{
%				\includegraphics[width=0.45\columnwidth]{fig/example/exam_cuboid_gender_semi_state.pdf}
%			}
%		\end{tabular}
%	\end{center}
%	\vspace*{-0.4cm}
%	\caption{}
%	\vspace*{-0.4cm}
%	\label{fig:exam_cuboid_gender}
%\end{figure}

\comment{
\begin{figure}[t!]
	\begin{center}
		\begin{tabular}[t]{c}\hspace*{-0.2cm}
			\subfigure[{\scriptsize Vertex table}]{
				\includegraphics[width=0.4\columnwidth]{fig/example/example_tables/tb_cuboid_gender_pro_adjust.pdf}
			}
			\subfigure[{\scriptsize Network structure from day 2 to day 3}]{
				\includegraphics[width=0.5\columnwidth]{fig/example/exam_cuboid_gender_pro_2_3.pdf}
			}
			%\vspace*{-0.3cm}\\\hspace*{-0.3cm}
			\\
			\subfigure[{\scriptsize Network structure from day 4 to day 5}]{
				\includegraphics[width=0.5\columnwidth]{fig/example/exam_cuboid_gender_pro_4_5.pdf}
			}
		\end{tabular}
	\end{center}
	\vspace*{-0.4cm}
	\caption{The answers to ``What is the amount of transactions between individuals of different genders and professions from day 2 to day 3 and from day 4 to day 5?"}
	\vspace*{-0.4cm}
	\label{fig:exam_cuboid_gender_profession}
\end{figure}
\begin{example} \label{exam:cuboid_query}
	Fig.~\ref{fig:exam_cuboid_gender} shows a static aggregate network obtained by summarizing the temporal multidimensional network in Fig.~\ref{fig:example_dataset} on dimension ``Gender'' and time range $ [2,3] $. Fig.~\ref{fig:exam_cuboid_gender} can be regarded as the answer of question ``What is the amount of transactions between individuals of different genders from day 2 to day 3?" Note that the vertex table in Fig.~\ref{fig:exam_cuboid_gender} (a) is directly aggregated from the vertex table in Fig.~\ref{fig:example_dataset} (a) on ``Gender" with COUNT($\ast$) as aggregation function on vertices. All vertices in Fig.~\ref{fig:example_dataset} (a) are included in the aggregation process even those vertices which have no adjacent edge in day 2 and day 3, like $ v_5 $. The reason is that vertices are time independent and vertices having no adjacent edge in specified time ranges are still available in those time ranges. Therefore, from day 2 to day 3, the COUNT($\ast$) value of male should be 4. Fig.~\ref{fig:exam_inter_result_gender} shows the intermediate result of the question, which is obtained by merging all snapshots in day 2 and day 3. All edges of snapshots in day 2 and day 3 are collected to the single snapshot in Fig.~\ref{fig:exam_inter_result_gender}, and if there are two edges in snapshots of day 2 and day 3 respectively share the same vertices, then their numeric attributes will be added together since SUM($\ast$) is the aggregation function upon edges here. Fig.~\ref{fig:exam_cuboid_gender} (b) can be directly aggregated from Fig.~\ref{fig:exam_inter_result_gender} on the basis of aggregated vertices in Fig.~\ref{fig:exam_cuboid_gender} (a), i.e., each edge in Fig.~\ref{fig:exam_cuboid_gender} (b) is the aggregated edge of edges in Fig.~\ref{fig:exam_inter_result_gender}, whose two vertices are aggregated to the two vertices of the corresponding aggregated edge. The numeric attributes of the aggregated edges in Fig.~\ref{fig:exam_cuboid_gender} (b) are still the sum of attributes of their corresponding sets of edges in Fig.~\ref{fig:exam_inter_result_gender}.

	Finally, we can reply the question above. For example, from day 2 to day 3, the amount of transactions between males is 6, while the amount of transactions between male and female is 107, etc. Fig.~\ref{fig:exam_cuboid_gender_profession} shows the answers of two similar questions ``What is the amount of transactions between individuals of different genders and professions from day 2 to day 3 and from day 4 to day 5?" The only difference between these two questions is the time range specified. Both static aggregate networks in Fig.~\ref{fig:exam_cuboid_gender_profession} share the same vertex table in Fig.~\ref{fig:exam_cuboid_gender_profession} (a) and in these two questions the aggregation functions upon vertices are AVERAGE($\ast$).
\end{example}

There are three new OLAP queries in Example~\ref{exam:cuboid_query} compared to queries in static graph cube, for example, the first OLAP query in Example~\ref{exam:cuboid_query} is ``What is the amount of transactions between individuals of different genders from day 2 to day 3", which requests a rough summarized result of the temporal multidimensional network in Fig.~\ref{fig:example_dataset} on ``Gender". Unlike the query in static graph cube, this new query includes a specific time range $ [2,3] $. Conducting the new query includes the same aggregation on vertex table as in static graph cube, but when aggregating the network structure, the basic idea is to first merge snapshots in the time range to build an intermediate result, as shown in Fig.~\ref{fig:exam_inter_result_gender}, then perform the same aggregation on Fig.~\ref{fig:exam_inter_result_gender} as in static graph cube. If the new query specifies the whole time range of the temporal multidimensional network, then it is equivalent to a query in static graph cube. Therefore, static graph cube is a special case of the new data warehouse model proposed in this paper. Conducting the second OLAP query ``What is the amount of transactions between individuals of different genders and professions from day 2 to day 3" can be regarded as performing a drill-down operation on the basis of the first query, since the second query requests more fine-grained information in the same time range than the first query. The third query ``What is the amount of transactions between individuals of different genders and professions from day 4 to day 5" specifies the same dimensions as the second query, but specifies a different time range $ [4,5] $. This allows users to analyze the pattern characteristics in different time ranges, for example, there is no transaction between male students from day 2 to day 3, but there are transactions totaling 100 between them from day 4 to day 5. Note that the aggregation functions upon vertices and edges can be combined arbitrarily as needed. For example, we can specify AVERAGE($\ast$) as the aggregation function upon both vertices and edges in Example~\ref{exam:cuboid_query}, so that we can analyze the transaction network from another perspective.

In \cite{zhao2011graph}, Zhao et al.\ proposed a new OLAP query for static multidimensional networks, called \kw{crossboid}, to analyze the crossed interaction pattern of two different views. It is easy to see that \kw{Crossboid} can also be extended to temporal multidimensional networks as illustrated in Example~\ref{exam:crossboid_query}.

\begin{table}[t!]%\vspace*{-0.3cm}
	%\scriptsize
	\small
	\centering
	\caption{Vertex table obtained by group-by on ``Profession" in Fig.~\ref{fig:example_dataset} (a)} \vspace*{-0.2cm} \label{tab:groupby_profession}
	\begin{tabular}{c c}
		\toprule
		Profession & COUNT($\ast$) \cr %\hline %\hline
		\midrule
		teacher& 1 \cr %\hline
		shopowner & 2  \cr %\hline
		student & 2  \cr %\hline
		lawyer & 2  \cr %\hline
		doctor & 1  \cr %\hline
		\bottomrule
	\end{tabular}
	\vspace*{-0.4cm}
\end{table}

\begin{figure}[t!]
	\begin{center}
		\includegraphics[width=0.85\columnwidth]{fig/example/exam_crossboid_gender_pro_2_3.pdf}
	\end{center}
	\vspace*{-0.7cm}
	\caption{Structure of the answer to the question in Example~\ref{exam:crossboid_query}}
	\vspace*{-0.4cm}
	\label{fig:exam_crossboid_gender_profession}
\end{figure}

\begin{example} \label{exam:crossboid_query}
	Fig.~\ref{fig:exam_crossboid_gender_profession} shows the structure of the answer to ``What is the amount of transactions between individuals grouped by gender and individuals grouped by profession from day 2 to day 3?" The answer can also be regarded as a static aggregate network which has two vertex tables from group-by on ``Gender" and ``Profession" shown in Fig.~\ref{fig:exam_cuboid_gender} (a) and Table~\ref{tab:groupby_profession} respectively. Fig.~\ref{fig:exam_crossboid_gender_profession} shows the crossed transactions between two different views ``Gender" and ``Profession" from day 2 to day 3, e.g., for all transactions between males and individuals of different professions, all 4 males have the biggest amount of transactions with the 2 lawyers and the smallest amount of transactions with the 2 students from day 2 to day 3. Other crossed transactions can also be easily found in Fig.~\ref{fig:exam_crossboid_gender_profession}.
\end{example}
}

In this paper, we propose a new data warehouse model, called \kw{Temporal} \kw{Graph} \kw{Cube}; and we extend the definition of OLAP queries by specifying a time range so that they can be applied to \kw{Temporal} \kw{Graph} \kw{Cube}. Users can explore summarized information on different views of temporal multidimensional networks in any time range using \kw{Temporal} \kw{Graph} \kw{Cube}. The challenge of our problem is: how to efficiently merge snapshots in a specific time range for each online OLAP query. A basic approach is to merge snapshots in the time range one by one. Such a basic method, however, is clearly inefficient when the time ranges are very large or a large number of OLAP queries come. The above problem can be seen as range query on snapshot arrays. Unfortunately, among the existing works for summarizing temporal networks \cite{liu2018graph}, there is no work which focuses on summarizing snapshots within a certain time range online. In this paper, we investigate the problem of how to speed up merging snapshots in certain time ranges. Our solution is to build an index on snapshot arrays to reduce the query processing time. Specifically, we propose a segment-tree based index to support the range query on snapshot arrays. Since new edges are constantly inserted into the temporal multidimensional network, we also propose an index updating technique to handle such an edge-insertion case. In addition, similar to the static graph cube, the implementation of the \kw{Temporal} \kw{Graph} \kw{Cube} also requires determining the materialization strategy of views in order to achieve a balance between time and space. To this end, we adopt a strategy called \kw{MinLevel} proposed in \cite{zhao2011graph} to handle the materialization problem in \kw{Temporal} \kw{Graph} \kw{Cube}, as it fits our model best.

To summarize, the main contributions of this work are as follows:
\begin{enumerate}
	\item We propose a new data warehouse model \kw{Temporal} \kw{Graph} \kw{Cube}, which supports decision making on the basis of temporal multidimensional networks. The key difference compared to static graph cube is that \kw{Temporal} \kw{Graph} \kw{Cube} supports querying summarized information for any time range of temporal multidimensional networks so that it supports more diverse analysis.

	\item We extend the classic segment tree that tailored for traditional range query problems to our range query problems on snapshot arrays to reduce the OLAP query processing time. We also develop \revision{an} index maintainable technique to handle the case when new edges are added to the temporal networks. %Similar requirement has not been seen on common range query problems.

	\item  We propose a new metric, called \kw{similarity\enspace of\enspace snapshots}, to measure the overall similarity of snapshots in a snapshot array, or, the degree to which the edges are shared by different snapshots. We show that this metric has a strong correlation with the effectiveness of the indexes and it can guide us to decide whether an index should be built.

%	\item We point out that the existing methods used to implement traditional data cube and static graph cube: greedy algorithm \cite{harinarayan1996implementing} and its variants \cite{morfonios2007rolap}, are no longer applicable in \kw{Temporal \enspace Graph \enspace Cube} scenario. The main reason is that OLAP queries contain arbitrary time ranges. A more reasonable method is \kw{MinLevel}, which is easy to be implemented and does not take into account the time ranges in OLAP queries.

	\item We conduct extensive experiments on two large-scale real-world datasets. The results demonstrate the effectiveness and efficiency of the \kw{Temporal \enspace Graph \enspace Cube}. The results also confirm the correlation between the efficiency (time and space) of the index and \kw{similarity\enspace of\enspace snapshots}. %We also examined the update performance of our index. Among them, we find that the segment tree index is with the best time and space balance and scalability among the three indexes.
\end{enumerate}

\comment{
%\vspace*{-0.2cm}
\stitle{Organizations.} Section~\ref{sec:temp_graph_cube} introduces the details about \kw{Temporal \enspace Graph \enspace Cube}. We extend all three indexes to snapshot array in Section~\ref{sec:indexes}. In Section~\ref{sec:effec_of_indexes} we discuss a metric, \kw{similarity\enspace of\enspace snapshots}, which affects the efficiency of indexes and how it affects. Section~\ref{sec:partial_materialization} introduces the implementation of \kw{Temporal \enspace Graph \enspace Cube}. We conduct experiments in Section~\ref{sec:experiment} and review the related works in Section~\ref{sec:related_work}. We conclude our work in Section~\ref{sec:conclusion}.
}

\section{Temporal Graph Cube} \label{sec:temp_graph_cube}
%\subsection{Notations and Basic Concepts} \label{subsec:notation}
%\vspace*{-0.1cm}
%\subsection{Definitions}\label{subsec:definitions}
\begin{definition}[Temporal Multidimensional Network]
	\label{def:temp_multi_network}
	Let $\Gr=(\Vr, \Er, A, W)$ be an undirected temporal multidimensional network where $\Vr$ and $\Er$ are the set of nodes and edges respectively. Edges in $\Er$ are in the form of $(u, v, t, a)$, where $u$, $v$ are nodes in $\Vr$ and $t, a$ are timestamp and numeric attribute respectively attached to edges. $A=\{A_1, A_2, ... , A_n\}$ represents the dimensions of the network, or $n$ discrete attributes of nodes in $ \Vr $, i.e., $A(u)=\{A_1(u), A_2(u), ... , A_n(u)\}$ where $A_i(u)$ is the actual value of $u$ on the $i$-th attribute. $ W(u) $ is the numeric value of $u$.
\end{definition}

For convenience, we abbreviate temporal multidimensional network and static multidimensional network to temp-multi-network and static-multi-network respectively. Since we only consider undirected edges in this paper, if not specified, we assume without loss of generality $u \leq v$ for $(u, v, t, a)$ in all following definitions. As shown in Fig.~\ref{fig:example_dataset}, $ A=\{Gender,Country,Profession\} $ and $ W=Income $. We do not consider ID to be an attribute of individuals because ID is only the identification of individuals. $ \Vr $ is the set of IDs of individuals in Fig.~\ref{fig:example_dataset} (a) and $ \Er $ is the set of temporal edges in Fig.~\ref{fig:example_dataset} (b). A temp-multi-network can also be represented by a sequence of snapshots.

\begin{definition}[Snapshot]
	\label{def:snapshot}
	Let $\Tr=\{t|(u, v, t, a)\in \Er\}$ be the set of timestamps. For each $t_i\in \Tr$, we can obtain a snapshot $S_i=\{(u,v,a)|(u,v,t_i,a)\in \Er\}$.
\end{definition}

For example, in Fig.~\ref{fig:example_dataset} (b), we can extract 5 snapshots; and the snapshot at timestamp 1 is $ S_1=\{(v_1,v_2,10),(v_2,v_3,20),(v_3,v_4,10),(v_1,v_4,15)\} $. With the definition of snapshot, we can define temp-multi-network in Definition~\ref{def:temp_multi_network} as $\Gr=(\Vr,\Sr,A,W)$ where $\Sr=\{S_1,S_2,...,S_{|\Tr|}\}$ and $ S_i $ is the snapshot at $t_i$.

\stitle{Biased Timestamp.} To store snapshots in a snapshot array and access snapshots directly by corresponding timestamps, we replace the original timestamps of snapshots with \emph{biased timestamps}. For each temp-multi-network, suppose $ t_1 $ is the smallest timestamp, $ t_{|\Tr|} $ is the biggest timestamp and $ t_{base}=t_1-1 $, biased timestamp of snapshot $ S_i $ is computed by $ t_i-t_{base} $. Through biased timestamp we can map timestamps in $ [t_1,t_{|\Tr|}] $ to $ [1,t_{end}] $, where $ t_{end}=t_{|\Tr|}-t_{base} $. The above strategy is useful when timestamps in temp-multi-network are dense. If timestamps are sparse, i.e., $ |\Tr| \ll t_{|\Tr|}-t_1 $, there will be many empty snapshots in snapshot array. We can sacrifice a little in efficiency, hashing all the timestamps into a denser space and relocating time range $ [l,r] $ of each query (we will discuss queries in Section~\ref{sec:queries}) to the actual time range. However, in large scale real-world temp-multi-networks, temporal relations can be built at almost all time, so the timestamps are unlikely to be sparse, which is confirmed in our datasets. All algorithms in this paper are designed based on the definition of temp-multi-network $\Gr=(\Vr,\Sr,A,W)$, where $ \Sr $ is a snapshot array with biased timestamps of snapshots start from 1.

\comment{
Aggregation, or traditional group-by, is a key operation in data warehouses and OLAP for traditional RDB data and static-multi-network. In traditional RDB data, for an aggregation in form of $(A_1',A_2',...,A_n')$ where some (or all) dimension $A_i'$ could be $\ast$ (ALL), the result is another table in which tuples in source table having the same value in all specified dimensions (NOT $\ast$) are grouped in the same tuple. In the above process, numeric attributes of tuples in source table can be summed by aggregation functions, e.g., COUNT($\ast$), AVERAGE($\ast$), MAX($\ast$) and MIN($\ast$). In static-multi-network, aggregations are not only conducting group-by on the vertex table but constructing static aggregate networks and computing the aggregation result of attributes of edges using specified aggregation function. The results of aggregations on static-multi-network, static aggregate networks, are exactly the answers of OLAP queries on static-multi-network \cite{zhao2011graph}. However, situations are different in temp-multi-networks. Below, we first define temporal aggregate network (the results of aggregations on temp-multi-network), and show the difference between static aggregate network and temporal aggregate network. Then, we describe the benefit of temporal aggregate network in conducting OLAP queries on temp-multi-network.
}

\begin{definition}[Temporal Aggregate Network]
	\label{def:temp_aggregate_network}
	Given a temporal multidimensional network $\Gr=(\Vr,\Sr,A,W)$ and an aggregation $A'=(A'_1,A'_2,...,A'_n)$ where $A'_i$ equals $A_i$ or $\ast$, the obtained temporal aggregate network is another temporal multidimensional network $\Gr'=(\Vr',\Sr',B,W_{\Gr'})$ where $B=\{A'_i|A'_i \neq \ast\}$ and
	\begin{enumerate}
		\item $\Vr' \subseteq \Vr$ and $\forall [v]$, an equivalence class in $\Vr$, where $ v \in \Vr $ and $[v]=\{u|B(u)=B(v),u \in \Vr\}$, $\exists v' \in \Vr'$ satisfying $v' \in [v]$ and $\nexists u' \in \Vr', u' \neq v'$ satisfying $u' \in [v]$. The weight of $v'$, $W_{\Gr'}(v')$, is the aggregation result of $W(v)$ for $v \in [v']$ obtained by aggregation function upon vertices specified by user.
%		\item For any $S'_i$ in $\Sr'$ and each $(u',v',a')$ in $S'_i$, there exists a nonempty maximum edge set $E=\{(u,v,a)|(u,v,a) \in S_i, u \in [u'] \wedge v \in [v']\; or\; u \in [v'] \wedge v \in [u']\}$, $a'$ is the aggregation result of numeric attributes ($a$) of edges in $E$ obtained by aggregation function specified by user.
		\item $\forall u',v' \in \Vr'$ where $u' \leq v'$ and any $\Sr[i], i \in [1,t_{end}]$, if there exists a nonempty maximum edge set $E=\{(u,v,a)|(u,v,a) \in \Sr[i],(u \in [u'] \wedge v \in [v']) \vee (u \in [v'] \wedge v \in [u']) \}$, then $ \exists (u',v',a') \in \Sr'[i] $, where $a'$ is the aggregation result of numeric attributes of edges in $E$ obtained by aggregation function upon edges specified by user.
	\end{enumerate}
\end{definition}
In short, conducting aggregations on temp-multi-network contains two stages: aggregating, or group-by on the vertex table as 1) in Definition~\ref{def:temp_aggregate_network} and aggregating each snapshots in the temp-multi-network as 2) in Definition~\ref{def:temp_aggregate_network}.

\begin{figure}[t!]
	\begin{center}
		\includegraphics[width=0.95\columnwidth]{fig/example/exam_aggregate_gender.pdf}
	\end{center}
	\vspace*{-0.9cm}
	\caption{Snapshots of the first temporal aggregate network in Example~\ref{exam:temporal_aggregate_network}}
	\vspace*{-0.4cm}
	\label{fig:aggregation_gender}
\end{figure}

\begin{figure}[t!]
	\begin{center}
		\includegraphics[width=0.95\columnwidth]{fig/example/exam_aggregate_gender_pro.pdf}
	\end{center}
	\vspace*{-0.9cm}
	\caption{Snapshots of the second temporal aggregate network in Example~\ref{exam:temporal_aggregate_network}. $ v_1= $ ``male, teacher", $ v_2= $ ``male, shopowner", $ v_3= $ ``male, student", $ v_4= $ ``female, shopowner", $ v_5= $ ``female, lawyer", $ v_6= $ ``female, doctor"}
	\vspace*{-0.4cm}
	\label{fig:aggregation_gender_profession}
\end{figure}

\begin{example} \label{exam:temporal_aggregate_network}
	Fig.~\ref{fig:aggregation_gender} shows the snapshots of a temporal aggregate network, which is obtained by aggregating temp-multi-network in Fig.~\ref{fig:example_dataset} on dimension ``Gender". The obtained temporal aggregate network is also a temp-multi-network. There are 5 snapshots in Fig.~\ref{fig:aggregation_gender}, each of them is corresponding to the snapshot with the same timestamp in Fig.~\ref{fig:example_dataset} (b). For each snapshot in Fig.~\ref{fig:aggregation_gender}, each edge $ e' $ is the aggregated edge of a set of edges $ E $ in the corresponding snapshot. Each edge in $ E $ have two vertices aggregated to the two vertices of $ e' $, as 2) in Definition~\ref{def:temp_aggregate_network}. In this example, the attribute in $ e' $ is the amount of the attributes of edges in $ E $, i.e., the total transactions between individuals of two genders in each day. We can also choose other aggregation functions for edges like COUNT($\ast$), MAX($\ast$), and so on. Similarly, Fig.~\ref{fig:aggregation_gender_profession} shows another temporal aggregate network by aggregating temp-multi-network in Fig.~\ref{fig:example_dataset} on dimension ``Gender" and ``Profession".
\end{example}

%As in Example~\ref{exam:temporal_aggregate_network}, Fig.~\ref{fig:aggregation_gender} and Fig.~\ref{fig:aggregation_gender_profession} are temporal aggregate networks $ \Gr'_1 $ and $ \Gr'_2 $ aggregated from Fig.~\ref{fig:example_dataset} on $ (Gender,\ast,\ast) $ and $ (Gender,\ast,Profession) $ respectively. For $ \Gr'_1=(\Vr'_1,\Sr'_1,B_1,W'_1) $, $ \Vr'_1 $ is the set of nodes, which are represented by tuples in "Gender" column of Table~\ref{tab:aggregation_gender}. $ \Sr'_1 $ is the snapshot array starting from subscript 1 and storing the 5 snapshots in Fig.~\ref{fig:aggregation_gender}. $ B_1=\{Gender\} $. $ W'_1 $ is the mapping from $ \Vr'_1 $ to COUNT($\ast$) value of nodes in $ \Vr'_1 $ as shown in "COUNT($\ast$)" column in Table~\ref{tab:aggregation_gender}. The aggregation function upon edges is SUM($\ast$). For $ \Gr'_2 $, [mention it in introduction].

\comment{
From Definition~\ref{def:temp_aggregate_network} and Example~\ref{exam:temporal_aggregate_network}, we can find that aggregation on static-multi-network is a special case of aggregation on temp-multi-network, if there is only one snapshot in temp-multi-network. For most cases, compared to aggregation on static-multi-network, aggregation on temp-multi-network contains aggregating each snapshot of the temp-multi-network to condensed snapshot independently.
}

Obviously, the temporal aggregate network is not the direct answer of OLAP query on temp-multi-network, because temporal aggregate network contains aggregated snapshot at each timestamp, but OLAP query on temp-multi-network requires a summarized snapshot of a specified time range. However, temporal aggregate network can provide a cheaper way to conduct queries compared to conducting queries directly on the original temp-multi-network. We will explain in detail in Section~\ref{sec:queries}. %For example, the snapshot in Fig.~\ref{fig:exam_cuboid_gender} (b) can be obtained by merging snapshots in day 2 and day 3 in Fig.~\ref{fig:aggregation_gender}, without generating the intermediate result in Fig.~\ref{fig:exam_inter_result_gender}. We will explain in detail in Section~\ref{subsec:queries}.

\begin{algorithm}[t]
	\scriptsize
	\caption{$\kw{Temporal Aggregate Network Construction}$}
	\label{alg:view_construct_baseline}
	\KwIn{A temp-multi-network $\Gr=(\Vr,\Sr,A,W)$; Aggregation $A'$; Aggregation function $f_v$ and $f_e$ upon vertices and edges respectively}
	\KwOut{Temporal aggregate network $\Gr'=(\Vr',\Sr',B,W_{\Gr'})$, $B=\{A'_i|A'_i \neq \ast\}$}
	$ \Vr' \gets \{\} $, let $ h $ be hash structure: $ \{B(u)|u \in \Vr\} \rightarrow \Vr' $;

	\ForEach{$u \in \Vr$}{
		\If{$h(B(u))=NULL$}{
			$ \Vr' \gets \Vr' \cup \{u\} $;
			$ W_{\Gr'}(u) \gets W(u) $;
			$ h(B(u)) \leftarrow u $;
		}
		\Else{
			$ u' \gets h(B(u)) $;
			$ W_{\Gr'}(u') \gets f_v(W_{\Gr'}(u'),W(u)) $;
		}
	}
	$ \Sr' \gets $ a snapshot array with $ t_{end}+1 $ empty snapshots;

	\ForEach{$ i \in [1,t_{end}] $}{
		$ EP \gets \{\} $;

		\ForEach{$ (u,v,a) \in \Sr[i] $}{
			$u' \gets h(B(u))$;
			$v' \gets h(B(v))$;

			\lIf{$ u'>v' $}{
				$ u',v' \gets v',u' $
			}

			\If{$(u',v') \notin EP$}{
				$ EP \gets EP \cup \{(u',v')\}$;
				$ \Sr'[i] \gets \Sr'[i] \cup \{(u',v',a)\} $;
			}
			\Else{
				Let $ (u',v',a') $ be edge in $\Sr'[i]$ which has $ u',v' $ as vertices\;
				$ \Sr'[i] \gets \Sr'[i]-\{(u',v',a')\} $\;
				$ \Sr'[i] \gets \Sr'[i] \cup \{(u',v',f_e(a',a))\} $;
			}
		}
	}
	\Return $ \Gr'=(\Vr',\Sr',B,W_{\Gr'}) $;
\end{algorithm}

We devise a basic algorithm, as outlined in Algorithm~\ref{alg:view_construct_baseline},  to construct the temporal aggregate network with aggregation $ A' $ from the original network $ \Gr $. Note that there are two things to be concerned about aggregation functions:
\begin{itemize}[leftmargin=*]
	\item We assume $ f_v $ and $ f_e $ are not AVERAGE($\ast$), since the result of AVERAGE($\ast$) can be easily computed by SUM($\ast$)/COUNT($\ast$).

	\item If $ f_v =$ COUNT($\ast$), we assign $1$ to all $ W(u),u \in \Vr $, because $ 1 $ is the correct attribute value of each vertex when counting is needed. The same assignment should be done to numeric attributes of all edges if $ f_e= $ COUNT($\ast$).
\end{itemize}
Algorithm~\ref{alg:view_construct_baseline} first conducts the specified aggregation on all vertices of the original network. In line~1, we first create a hash structure, $h$, to maintain a mapping from all possible $ B(u),u \in \Vr $ to vertices of the temporal aggregate network. In lines~2-6, we group all vertices in $ \Vr $ with the specified aggregation $ A' $ and compute the aggregation result of numeric attributes of vertices with the specified aggregation function $ f_v $. Each snapshot $ \Sr[i] $ of $ \Gr $ is aggregated into a smaller representation, i.e., the corresponding snapshot $ \Sr'[i] $ at the same timestamp in $ \Gr' $ (lines~8-18). For each edge $ (u,v,a) $, we first map the two vertices $ u,v $ to $ u',v' $ using $ h $ (line~11-12). If there exists an aggregated edge $ (u',v',a') $ in $ \Sr'[i] $, we update $ a' $ with $ a $ using $ f_e $ (lines~16-18), otherwise we insert $ (u',v',a) $ into $ \Sr'[i] $ directly (line~14).

It is easy to derive that the time complexity of Algorithm~\ref{alg:view_construct_baseline} is $ O(|\Vr|+\sum_{i=1}^{t_{end}}{|\Sr[i]|}) $. The space used to maintain $ h,W_{\Gr'} $ is $ O(\Vr') $ and we need $ O(|\Vr'|+\sum_{i=1}^{t_{end}}{|\Sr'[i]|}) $ space to maintain $ \Gr' $. Moreover, we can easily derive that $ |\Vr'| \leq |\Vr| $ and $ |\Sr'[i]| \leq |\Sr[i]| $. As a result, the space complexity of Algorithm~\ref{alg:view_construct_baseline} is $ O(|\Vr|+\sum_{i=1}^{t_{end}}{|\Sr[i]|}) $.

%The time complexity of Algorithm~\ref{alg:view_construct_baseline} is $ O(|\Vr|+\sum_{i=1}^{t_{end}}{|\Sr[i]|}) $, which contains time used for traversing $ \Vr $ and $ \Sr $. The space used to maintain $ h,W_{\Gr'} $ is $ O(\Vr') $ and we need $ O(|\Vr'|+\sum_{i=1}^{t_{end}}{|\Sr'[i]|}) $ space to maintain $ \Gr' $. From Algorithm~\ref{alg:view_construct_baseline} we can easily find $ |\Vr'| \leq |\Vr| $ and $ |\Sr'[i]| \leq |\Sr[i]| $, so the space complexity of Algorithm~\ref{alg:view_construct_baseline} is also $ O(|\Vr|+\sum_{i=1}^{t_{end}}{|\Sr[i]|}) $.

\comment{
Similar to the static aggregate network in static graph cube, temporal aggregate networks can also be constructed from other existing temporal aggregate networks. For example, the temporal aggregate network with dimensions $ \{B_1,B_2\} $ can be constructed from the temporal aggregate network with dimensions $ \{B_1,B_2,B_3\} $, $ \{B_1,B_2,B_4\} $. The proof can be easily obtained by extending the proof from \cite{zhao2011graph}.
}

\begin{definition}[Temporal Graph Cube]
	\label{def:temp_graph_cube}
	Given a temporal multidimensional network $\Gr=(\Vr,\Sr,A,W)$, the temporal graph cube is obtained by decomposing $ A $ into all possible aggregations. Each aggregation $ A' $ is a node in the temporal graph cube and it corresponds to a temporal aggregate network $ \Gr' $ as defined in Definition~\ref{def:temp_aggregate_network}.
\end{definition}

In \cite{zhao2011graph}, Zhao et al.\ used equivalently the terms \textit{cuboid}, \textit{view} and \textit{aggregation}. In this paper, however, we only use \textit{view} and \textit{aggregation} equivalently, while \textit{temporal cuboid} is used to refer to temporal cuboid query. In following sections, computing a view $ A' $ means materializing the corresponding temporal aggregate network $ \Gr' $ in memory. If $ A' $ is precomputed, then for simplicity, $ A' $ also refers to the corresponding temporal aggregate network $ \Gr' $.

For a view $ A' $ in the temporal graph cube, $ dim(A') $ denotes the set of non-$\ast$ dimensions of $ A' $, i.e., $ dim(A')=B $ where $ B $ is the discrete attributes of vertices in $ \Gr' $, the corresponding temporal aggregate network of $ A' $. For two views $ A' $ and $ A'' $, $ A' $ is an \textit{ancestor} of $ A'' $ and $ A'' $ is a \textit{descendant} of $ A' $ if $ dim(A') \subset dim(A'') $, denoted as $ A' \preceq A'' $. Especially, the base view $ A_{base} $ is a view where $ dim(A_{base})=A $, $ A $ is the dimensions of the original temp-multi-network. It is easy to see that $ A_{base} $ is a descendant of all other views. Another special view is $ A_{apex}=(\ast,\ast,...,\ast) $; and it is an ancestor of all other views in the temporal graph cube. %It is easy to check that the

%\comment{
\begin{figure}[t]
	\begin{center}
		\includegraphics[width=0.75\columnwidth]{fig/example/cube_lattice.pdf}
	\end{center}
	\vspace*{-1cm}
	\caption{A sample cube lattice}
	\vspace*{-0.6cm}
	\label{fig:cube_lattice}
\end{figure}
\begin{example} \label{exam:cube_lattice}
	Fig.~\ref{fig:cube_lattice} shows the temporal graph cube lattice built on the temp-multi-network in Fig.~\ref{fig:example_dataset}, each node on the lattice represents a view. For each edge in the lattice, the upper view is an ancestor of the lower view.
\end{example}
%}

Temporal graph cube has the same form with static graph cube. The only difference is that each node in temporal graph cube is corresponding to a temporal aggregate network, not a static aggregate network. For each temporal aggregate network corresponding to a view, it contains more coarse-grained information than that of temporal aggregate network corresponding to a descendent view at each timestamp. In temporal graph cube, users can obtain summarized information in different resolution of the original temp-multi-network in a certain period by traversing the temporal graph cube lattice with specified time range. Users can also stay at some nodes in the lattice and query the summarized information in different time ranges. In these ways, summarized information of temp-multi-network in different resolutions and time ranges can be analyzed for decision support and business intelligence purposes.

%\subsection{OLAP Queries}\label{subsec:queries}
\section{Temporal OLAP Queries}  \label{sec:queries}
Cuboid and crossboid are two important OLAP queries on static-multi-networks, or in static graph cubes \cite{zhao2011graph}. In this section, we propose a generalized definition of OLAP queries in temporal graph cube, by extending cuboid and crossboid to temporal cuboid and temporal crossboid respectively. %From the previous sections, we can find that the main difference of queries in static graph cube and temporal graph cube is the designation of time range.

%\stitle{Temporal cuboid.}
\subsection{Temporal Cuboid Query} \label{subsec:cuboid}
The inputs of temporal cuboid query $ Q=(A',[l,r]) $ in temporal graph cube contain a specified view $A'=(A'_1,A'_2,...,A'_n)$ and a time range $[l,r]$. The output is a static aggregate network obtained by the query. %As illustrated in Example~\ref{exam:cuboid_query}, the first question can be represented by $ Q=((Gender),[2,3]) $, and the static aggregate network as the answer is shown in Fig.~\ref{fig:exam_cuboid_gender}.

\begin{algorithm}[t]
	\scriptsize
	\caption{$\kw{Temporal Cuboid Query}$}
	\label{alg:temp_cuboid_baseline}
	\KwIn{A temp-multi-network $\Gr=(\Vr,\Sr,A,W)$; Aggregation $A'$; Time range $[l,r]$; Aggregation function $f_v$ and $f_e$ upon vertices and edges respectively}
	\KwOut{A static aggregate network $G=(V,E,B,W_{G})$, $B=\{A'_i|A'_i \neq \ast\}$}
	$V \leftarrow \{\}$, let $h$ be hash structure: $\{B(u)|u \in \Vr\} \rightarrow V$;

	\ForEach{$u \in \Vr$}{
		\If{$h(B(u))=NULL$}{
			$ V \leftarrow V \cup \{u\} $;
			$ W_{G}(u) \gets W(u) $;
			$ h(B(u)) \leftarrow u $;
		}
		\Else{
			$ u'\gets h(B(u)) $;
			$ W_{G}(u') \gets f_v(W_{G}(u'),W(u)) $;
		}
	}
	$E' \leftarrow \{\}$;
	$EP \leftarrow \{\}$;
	$ l \gets l-t_{base} $;
	$ r \gets r-t_{base} $;

	\ForEach{$i \in [l,r]$}{
		\ForEach{$(u,v,a) \in \Sr[i]$}{
			\If{$(u,v) \notin EP$}{
				$EP \leftarrow EP \cup \{(u,v)\}$;
				$E' \leftarrow E' \cup \{(u,v,a))\}$;
			}
			\Else{
				Let $(u,v,a')$ be edge in $E'$ which has $u,v$ as vertices\;
				$E' \leftarrow E'-\{(u,v,a')\}$\;
				$E' \leftarrow E' \cup \{(u,v,f_e(a',a))\}$;
			}
		}
	}
	$EP \leftarrow \{\}$;
	$ E \gets \{\} $;

	\ForEach{$(u,v,a) \in E'$}{
		$u' \leftarrow h(B(u))$;
		$v' \leftarrow h(B(v))$;

		\lIf{$ u'>v' $}{
			$ u',v' \gets v',u' $
		}

		\If{$(u',v') \notin EP$}{
			$ EP \gets EP \cup \{(u',v')\}$;
			$ E \gets E \cup \{(u',v',a)\} $;
		}
		\Else{
			Let $ (u',v',a') $ be edge in $E$ which has $ u',v' $ as vertices\;
			$ E \gets E-\{(u',v',a')\} $\;
			$ E \gets E \cup \{(u',v',f_e(a',a))\} $;
		}
	}
	\Return $ G=(V,E,B,W_{G}) $;
\end{algorithm}
Algorithm~\ref{alg:temp_cuboid_baseline} is a basic algorithm to conduct temporal cuboid query on the original temp-multi-network (or on $ A_{base} $). Same as Algorithm~\ref{alg:view_construct_baseline}, Algorithm~\ref{alg:temp_cuboid_baseline} first conducts the specified aggregation on the whole vertex table of the original network, even those vertices who do not exist in any edge of snapshots in $[l,r]$ (lines~1-6). In lines~7-15, we merge all snapshots in $[l,r]$ by collecting all edges of those snapshots and summing the numeric attributes of edges sharing the same vertices using $ f_e $. Then, in lines~17-25, we map the two vertices of all edges in $ E' $ using $ h $ and compute the aggregation result of edges sharing the same mapped vertices using $ f_e $, which is similar to what Algorithm~\ref{alg:view_construct_baseline} does in each snapshot $ \Sr[i] $ of $ \Gr $ (lines~8-18 of Algorithm~\ref{alg:view_construct_baseline}).

%As we have mentioned in Example~\ref{exam:cuboid_query}, it is necessary to aggregate all vertices in temporal cuboid query, since vertices are time independent and they are available in all time ranges.

%Lines~1-6 in Algorithm~\ref{alg:temp_cuboid_baseline} is the same as lines~1-6 in Algorithm~\ref{alg:view_construct_baseline}. In lines~7-15, we merge all snapshots in $[l,r]$ by collecting all edges of those snapshots and summing the numeric attributes of edges sharing the same vertices using $ f_e $. Then, in lines~17-25, we map the two vertices of all edges in $ E' $ using $ h $ and compute the aggregation result of edges sharing the same mapped vertices using $ f_e $, which is similar to what Algorithm~\ref{alg:view_construct_baseline} does in each snapshot $ \Sr[i] $ of $ \Gr $ (lines~8-18 of Algorithm~\ref{alg:view_construct_baseline}).

Before analyzing the time and space complexity of Algorithm~\ref{alg:temp_cuboid_baseline}, we first give a brief definition of summarized snapshot.
\begin{definition}[Summarized Snapshot]
	\label{def:sum_snap}
	Given a temporal multidimensional network $\Gr=(\Vr,\Sr,A,W)$, the summarized snapshot $ S $ of $ \Gr $ is a special snapshot of $ \Gr $, which is the network structure in the result of a temporal cuboid query $ Q=(A,[1+t_{base},t_{end}+t_{base}]) $ on $ \Gr $.
\end{definition}
In other words, summarized snapshot $ S $ of $ \Gr $ can be obtained by merging all snapshots in a snapshot array $ \Sr $.

The time complexity of Algorithm~\ref{alg:temp_cuboid_baseline} contains three parts: conducting aggregation on all vertices (lines~1-6), merging all snapshots in specified time range into $ E' $ (lines~7-15) and aggregating on $ E' $ (lines~17-25). Thus, the time complexity of Algorithm~\ref{alg:temp_cuboid_baseline} is $ O(|\Vr|+\sum_{i=l-t_{base}}^{r-t_{base}}|\Sr[i]|+|E'|) $. With the definition of summarized snapshot, we can rewrite the time complexity as $ O(|\Vr|+\sum_{i=l-t_{base}}^{r-t_{base}}|\Sr[i]|+|S|) $, since we can easily find $ |E'| \leq |S|$, where $ S $ is the summarized snapshot of $ \Gr $. The memory consumed by $V$, $h$ and $W_{G}$ is linearly with respect to $ |V| $ and $ |V| \leq |\Vr| $. The size of $ E $, $ E' $ and $ EP $ are all smaller than $ |S| $, so the space complexity of Algorithm~\ref{alg:temp_cuboid_baseline} is $ O(|\Vr|+|S|) $.

Given a temporal cuboid query $ Q=(A',[l,r]) $, if we have precomputed the view $ A' $ with the same aggregation functions, we can derive the result of $ Q $ from $ \Gr' $ by merging snapshots of $ \Gr' $ in $ [l,r] $ instead.  Due to the space limit, all the proofs of this paper are omitted.

\begin{theorem} \label{thm:cuboid_by_temp_aggre_network}
	A temporal cuboid query $ Q=(A',[l,r]) $ can be directly answered from $ A' $ if $ A' $ is precomputed with the same aggregation functions.
\end{theorem}

\comment{
\begin{proof}
	Suppose that the result of $ Q=(A',[l,r]) $ is $ G=(V,E,B,W_{G}) $, and the original temp-multi-network is $ \Gr=(\Vr,\Sr,A,W) $, the temporal aggregate network of $ A' $ is $ \Gr'=(\Vr',\Sr',B,W_{\Gr'}) $. $ G $ is obtained from $ \Gr $ by Algorithm~\ref{alg:temp_cuboid_baseline}. Since aggregating all vertices is the first step of both constructing $ \Gr' $ and obtaining $ G $, we have $ V=\Vr' $ and $ W_{G}=W_{\Gr'} $, i.e., the vertex table of $ G $ can be obtained from vertex table of $ \Gr' $ directly. For the network structure of $ G $, we only need to prove that the merging result of snapshots of $ \Gr' $ in $ [l,r] $, $ E' $, is identical to $ E $.

	Suppose $ l,r $ have been converted to biased timestamps. Recall that we have a hash structure $ h $ used to maintain the mapping from $ \{B(u)|u \in \Vr\} $ to aggregated vertices set $ \Vr' $ and $ V $ in Algorithm~\ref{alg:view_construct_baseline} and Algorithm~\ref{alg:temp_cuboid_baseline} respectively. Since $ \Vr \rightarrow \{B(u)|u \in \Vr\} $ can also be regarded as a mapping, we can regard $ H $ as a mapping from $ \Vr $ to both $ \Vr' $ and $ V $, i.e., $ H(u)=h(B(u)) $. We first ignore the numeric attribute of each edge and prove that $ E'=E $. Since $ H $ can map the two vertices of edges in $ \Sr $ to their aggregated vertices, we let $ H^e $ be a mapping from edges in $ \Sr $ to their aggregated edges in $ \Sr' $ and in $ E $, i.e., $ H^e(e)=e' $ where $ e $ is an arbitrary edge in $ \Sr $ and $ e' $ is the aggregated edge of $ e $ in $ \Sr' $ or in $ E $. For $ E $, by Algorithm~\ref{alg:temp_cuboid_baseline}, we know that all snapshots of $ \Sr $ in $ [l,r] $ are merged into an intermediate result $ X=\bigcup_{i=l}^{r}\Sr[i] $ first. Then, $ E=\{H^e(e)|e \in X\} $. For $ E' $, we know that $ E' $ is obtained by merging all snapshots of $ \Sr' $ in $ [l,r] $ directly, i.e., $ E'=\bigcup_{i=l}^{r}\Sr'[i] $. By Algorithm~\ref{alg:view_construct_baseline}, we have $\forall i, \Sr'[i]=\{H^e(e)|e \in \Sr[i]\} $, so $ E'=\bigcup_{i=l}^{r}\{H^e(e)|e\in\Sr[i]\}=\{H^e(e)|e\in\bigcup_{i=l}^{r}\Sr[i]\} $. As a result, $ E=E' $.

	Then, we take numeric attributes of edges into account and suppose that the aggregation functions upon edges in $ \Gr' $ and in $ Q $ are both $ f_e $. The original form of edges in $ \Sr $ and in $ \Sr' $ is $ (u,v,a) $. We add the timestamp into the form of edges as $ (u,v,a,t) $ to distinguish edges in different snapshots but with the same vertices. Each aggregated edge $ e\in E $ corresponds to a set of edges $TX_{\Sr}(e)=\{(u,v,a,i)|(u,v,a,i)\in \Sr[i],i\in [l,r],H^e((u,v))=(e.u,e.v)\} $, because $ e $ is obtained by merging and aggregating edges in $ TX_{\Sr}(e) $, and $ e.a $ is computed by executing $ f_e $ on multiset $ \{a|(u,v,a,t)\in TX_{\Sr}(e)\} $. According to the previous proof, there must exist $ e' \in E'$ where $(e'.u,e'.v)=(e.u,e.v) $. $ e' $ is obtained by merging edges in $TX_{\Sr'}(e')= \{(u,v,a,i)|(u,v,a,i) \in \Sr'[i],i \in [l,r],(u,v)=(e'.u,e'.v)\} $, and $ e'.a $ is computed by executing $ f_e $ on multiset $ \{a|(u,v,a,t)\in TX_{\Sr'}(e')\} $. Furthermore, each $ e'_t\in TX_{\Sr'}(e') $ where $ e'_t=(u,v,a,t) $ corresponds to a set of edges in $ \Sr[t] $, which is $TX_{\Sr[t]}(e'_t)= \{(u,v,a,t)|(u,v,a,t)\in \Sr[t],H^e((u,v))=(e'_t.u,e'_t.v)\} $. $ e'_t.a $ is computed by executing $ f_e $ on multiset $ \{a|(u,v,a,t)\in TX_{\Sr[t]}(e'_t)\} $. As a result, $ e'.a $ can be computed by executing $ f_e $ on multiset $ \{a|(u,v,a,t)\in \bigcup_{e'_t\in TX_{\Sr'}(e')}TX_{\Sr[t]}(e'_t)\}=\{a|(u,v,a,t)\in TX_{\Sr}(e')\} $. Since $ (e'.u,e'.v)=(e.u,e.v) $, we have $ TX_{\Sr}(e')=TX_{\Sr}(e) $, and thus $ e'.a=e.a $. This completes the proof. %Finally, we prove that $ E' $, obtained by directly merging snapshots of $ \Gr' $, is equal to $ E $, the network structure in the result of $ Q $ by conducting $ Q $ on $ \Gr $.
\end{proof}
}

Theorem~\ref{thm:cuboid_by_temp_aggre_network} gives another way to conduct $ Q $. The static aggregate network as the result of $ Q $ contains two parts: vertex table and a snapshot presenting the network structure. When $ A' $ is precomputed, the vertex table of the resulting static aggregate network is the same with vertex table of $ \Gr' $, the corresponding temporal aggregate network of $ A' $, and the network structure can be obtained by merging all snapshots of $ \Gr' $ in $ [l,r] $.

The algorithm of conducting $ Q $ on $ \Gr' $ is exactly the subprocess in lines~7-15 of Algorithm~\ref{alg:temp_cuboid_baseline} if we replace $ \Gr $ with $ \Gr' $. The time complexity of the simpler algorithm is $ O(\sum_{i=l-t_{base}}^{r-t_{base}}|\Sr'[i]|) $. It is easy to see that $ |\Sr'[i]| \leq |\Sr[i]| $, so this simpler algorithm is better than the baseline algorithm.

If the view $ A' $ is not precomputed while some other view $ A'' $ is precomputed with the same aggregation functions and $ dim(A') \subset dim(A'') $, we can use the corresponding temporal aggregate network $ \Gr'' $ of $ A'' $ to get the result of $ Q $. The algorithm is exactly Algorithm~\ref{alg:temp_cuboid_baseline}, where we only need to replace $ \Gr $ with $ \Gr'' $.

\begin{theorem} \label{thm:cuboid_by_small_temp_aggre_network}
	A temporal cuboid query $ Q=(A',[l,r]) $ can be answered from $ A'' $ where $ dim(A') \subset dim(A'') $ and $ A'' $ is precomputed with the same aggregation functions.
\end{theorem}
\comment{
\begin{proof}
	Suppose $ G=(V,E,B,W_{G}) $ is the result of conducting $ Q $ from the original temp-multi-network $ \Gr=(\Vr,\Sr,A,W) $, $ \Gr''=(\Vr'',\Sr'',B'',W_{\Gr''}) $ is the temporal aggregate network corresponds to $ A'' $, $ G''=(V'',E'',B,W_{G''}) $ is the result of conducting $ Q $ from $ \Gr'' $. Three hash structures will be involved in this proof, $ h_1 $: $ \{B(u)|u \in \Vr\} \rightarrow V $, used in Algorithm~\ref{alg:temp_cuboid_baseline} when answering $ Q $ from $ \Gr $; $ h_2 $: $ \{B''(u)|u\in \Vr\} \rightarrow \Vr'' $, used in Algorithm~\ref{alg:view_construct_baseline} when constructing $ \Gr'' $ from $ \Gr $; $ h_3 $: $ \{B(u)|u\in \Vr''\} \rightarrow V'' $, used in Algorithm~\ref{alg:temp_cuboid_baseline} when answering $ Q $ from $ \Gr'' $. The key is to prove $ G=G'' $.

	We first prove that $ G $ and $ G'' $ share the same vertex table, i.e., $ T=(V,B,W_{G})$ and $T''=(V'',B,W_{G''}) $ are the same vertex table. $T$ is obtained by the traditional group-by operation on $ (\Vr,A,W) $ with aggregation $ A' $. $ T'' $ is obtained by two group-by operations: group-by on $ (\Vr,A,W) $ with $ A'' $, obtaining $ (\Vr'',B'',W_{\Gr''}) $, and group-by on $ (\Vr'',B'',W_{\Gr''}) $ with $ A' $. It is easy to know that the two group-by operations to obtain $ T'' $ is equivalent to the single group-by operation to obtain $ T $, because $ dim(A') \subset dim(A'') $. So $ T $ and $ T'' $ are the same vertex table. However there is no guarantee that $ V=V'' $, i.e., the label sets of vertices in $ T $ and $ T'' $ are not necessarily the same. The reason is that in line~2-6 of Algorithm~\ref{alg:view_construct_baseline} and Algorithm~\ref{alg:temp_cuboid_baseline}, we simply map $ B(u) $ to the first $ u $ that satisfies $ h(B(u))=NULL $ and the order $ u $ is traversed is uncertain. It is not important for group-by operations, but to prove $ E=E'' $, we need to assume that $ u $ is traversed in ascending order first ($ V=V'' $ in this case).

	Suppose the above condition of traversing $ u $ in ascending order holds, and equivalence class $ [u]_{B,\Vr}=\{v|B(u)=B(v),v\in \Vr\} $. Similar to proof of Theorem~\ref{thm:cuboid_by_temp_aggre_network}, we let $ H_1 $ be a mapping where $ H_1(u)=h_1(B(u)),u\in \Vr $ and $ H_2 $, $ H_3 $ are similar. We have $ V=\{H_1(u)|u\in \Vr\} $, $ \Vr''=\{H_2(u)|u\in \Vr\} $ and $ V''=\{H_3(u)|u\in \Vr''\} $. Since $ u $ is traversed in ascending order, we can rewrite $ H_1(u)=MIN([u]_{B,\Vr}),u\in \Vr $, $ H_2(u)=MIN([u]_{B'',\Vr}),u\in \Vr $ and $ H_3(u)=MIN([u]_{B,\Vr''}),u\in \Vr'' $, where $ MIN(\ast) $ returns the smallest label in the equivalence class. We first prove $ \forall u\in \Vr, H_1(u)=H_3(H_2(u)) $. It is clear that $ [u]_{B'',\Vr}\subseteq [u]_{B,\Vr} $ because $ B\subset B'' $ ($ dim(A')\subset dim(A'') $). Since $ H_1(u)=MIN([H_1(u)]_{B,\Vr}) $, $ [H_1(u)]_{B'',\Vr}\subseteq [H_1(u)]_{B,\Vr} $ and $ H_1(u)\in [H_1(u)]_{B'',\Vr}$, we have $ H_1(u)=MIN([H_1(u)]_{B'',\Vr}) $, so $ H_2(H_1(u))=H_1(u) $. Since $ H_2(H_1(u))=H_1(u) $, $ H_1(u) $ is in $ \Vr'' $, the vertex set of $ \Gr'' $. Since $ [u]_{B'',\Vr}\subseteq [u]_{B,\Vr} $, $ H_2(u)\in [u]_{B,\Vr} $. As a result, both $ H_1(u) $ and $ H_2(u) $ are elements in $ [u]_{B,\Vr} $ and in $ \Vr'' $, so $ B(H_1(u))=B(H_2(u)) $ and $ H_1(u)\in [H_2(u)]_{B,\Vr''} $. Since $ H_1(u) $ is the smallest label in $ \Vr $ satisfying $ B(H_1(u))=B(u) $ and $ \Vr''\subseteq \Vr $, $ H_1(u)=MIN([H_2(u)]_{B,\Vr''}) $. So $ H_3(H_2(u))=H_1(u) $.

	As we have mentioned before, $ V=\{H_1(u)|u\in \Vr\} $, $ \Vr''=\{H_2(u)|u\in \Vr\} $ and $ V''=\{H_3(u)|u\in \Vr''\} $, we can further get $ V''=\{H_3(H_2(u))|u\in \Vr\}=\{H_1(u)|u\in \Vr\} $. So $ V=V'' $. Similar to proof of Theorem~\ref{thm:cuboid_by_temp_aggre_network}, we can also define mappings between edges $ H_1^e $, $ H_2^e $ and $ H_3^e $ on the basis of $ H_1 $, $ H_2 $ and $ H_3 $. Since $ \forall u\in \Vr, H_1(u)=H_3(H_2(u)) $, we can also have $ \forall e \in \Er, H_1^e(e)=H_3^e(H_2^e(e)) $, where $ \Er $ is the edge set of $ \Gr $. Using similar process in the proof of Theorem~\ref{thm:cuboid_by_temp_aggre_network}, we can prove that $ E=E'' $. We omit the details here. In fact, the order in which $ u $ is traversed in line~2 of Algorithm~\ref{alg:view_construct_baseline} and Algorithm~\ref{alg:temp_cuboid_baseline} is not important, and $ E $ is always isomorphic to $ E'' $ because the labels of vertices have no actual meaning.
\end{proof}
}

The time complexity of conducting $ Q $ on $ \Gr'' $ is $ O(|\Vr''|+\sum_{i=l-t_{base}}^{r-t_{base}}|\Sr''[i]|+|S''|) $, where $ |\Vr''|,|\Sr''[i]| $ and $ |S''| $ are vertex set, snapshot at $ i $ and summarized snapshot of $ \Gr'' $ respectively. We also have $ |\Vr''| \leq |\Vr|,|\Sr''[i]| \leq |\Sr[i]|$ and $|S''| \leq |S| $; and in practice, $ |\Vr''|,|\Sr''[i]| $ and $ |S''| $ are much smaller than $ |\Vr|,|\Sr[i]| $ and $ |S| $ respectively.

If we have a set of precomputed views $ \{A_1'',A_2'',...\} $ with the same aggregation functions and for each $ A_i'' $, $ dim(A') \subset dim(A_i'') $, which one should we choose in conducting $ Q $ using Algorithm~\ref{alg:temp_cuboid_baseline}? There is a similar problem in static graph cube, in which we only need to choose the view in $ \{A_1'',A_2'',...\} $ with the smallest size, since the time complexity of conducting a query $ Q=(A') $ on the basis of $ A_i'' $ in static graph cube equals the size of $ A_i'' $. It is easy to obtain the size of precomputed views of static graph cube in $ O(1) $ time.

However, in temporal graph cube, extra time range should be specified in each query, so the time complexity of conducting a query $ Q=(A',[l,r]) $ on $ A_i'' $ is not the size of $ A_i'' $. It is hard to compute the accurate time complexity of Algorithm~\ref{alg:temp_cuboid_baseline} in $ O(1) $ time. The reasons are as follows:
\begin{itemize}[leftmargin=*]
	\item If we want to compute the accumulation part ($ \sum_{i=l-t_{base}}^{r-t_{base}}|\Sr[i]| $) in the time complexity of Algorithm~\ref{alg:temp_cuboid_baseline} in $ O(1) $ time, an extra prefix array should be maintained.
	\item The size of summarized snapshot $ |S| $ is just an upper bound of the number of edges visited in $ E' $ of Algorithm~\ref{alg:temp_cuboid_baseline}. To get the accurate value of $ |E'| $ as fast as possible, we may have to build some indexes to get $ E' $ first. However, it is also difficult to get $ |E'| $ in $ O(1) $ time using indexes (we will discuss building indexes in Section~\ref{sec:indexes}).
\end{itemize}

Interestingly, we can avoid the problem of choosing an ideal $ A_i'' $ by adopting the partial materialization strategy \kw{MinLevel} \cite{zhao2011graph}, which we will discuss in Section~\ref{sec:partial_materialization}.
%
%Let's recall the time complexity of Algorithm~\ref{alg:temp_cuboid_baseline}: $ O(|\Vr|+\sum_{i=l-t_{base}}^{r-t_{base}}|\Sr[i]|+|S|) $, where $ \Vr $ and $ \Sr[i] $ are the node set and snapshot of the inputed temp-multi-network, $ S $ is the summarized snapshot of the inputed temp-multi-network. Our goal is to get the value of time complexity of Algorithm~\ref{alg:temp_cuboid_baseline} with corresponding $ \Gr_i'' $ of each $ A_i'' $ as the inputed temp-multi-network in $ O(1) $ time and then choose the lowest time complexity and the corresponding $ \Gr_i'' $. We can not stand a higher time complexity to compute the time complexity of Algorithm~\ref{alg:temp_cuboid_baseline}, which will make the process of choosing an ideal $ \Gr_i'' $ unworthy compared to choosing a arbitrary $ \Gr_i'' $. In time complexity of Algorithm~\ref{alg:temp_cuboid_baseline}, . For our basic Algorithm~\ref{alg:temp_cuboid_baseline}, if we maintain a prefix array $ pArray $ for each precomputed $ \Gr_i'' $ of $ A_i'' $, in which
%\begin{equation}
%	\label{eqt:pre_array_baseline}
% 	pArray[i]=\sum_{j=1}^{i}|\Sr''[j]|, i \leq t_{end},
%\end{equation}
%$ \Sr''[j] $ is the snapshot at timestamp $ j+t_{base} $ as defined in Definition~\ref{def:snapshot}, we can easily compute the value of accumulation part ($ \sum_{i=l-t_{base}}^{r-t_{base}}|\Sr[i]| $) in the time complexity of Algorithm~\ref{alg:temp_cuboid_baseline} by
%\begin{equation}
%	\label{eqt:pre_array_base_use}
%	pArray[r-t_{base}]-pArray[l-t_{base}-1].
%\end{equation}
%It is easy to update $ pArray $ and $ \Sr''[j] $ according to their definitions when adding new edges at the latest timestamp in each $ \Gr_i'' $ (we will talk about adding new edges into temporal graph cube in Section~\ref{subsec:growing}). As a result, we can compute the value of time complexity of Algorithm~\ref{alg:temp_cuboid_baseline} with different $ \Gr_i'' $ as the inputed temp-multi-network by $ |\Vr_i''|+pArray[r-t_{base}]-pArray[l-t_{base}-1]+|S_i''| $ in $ O(1) $ time. .[not accurate because of $ |S_i''| $]

After discussing the temporal cuboid query, we can describe the OLAP operations in temporal graph cube, such as roll-up, drill-down and slice-and-dice. Suppose that we have conducted a temporal cuboid query $ Q_0=(A_0,[l,r]) $. Roll-up means conducting another query $ Q_1=(A_1,[l,r]) $ where $ A_1 $ is an ancestor of $ A_0 $, so that we get a coarser resolution of summarized information of temp-multi-network in the same time range. Drill-down is a contrary operation to obtain a finer summarized information in the same time range by conducting $ Q_2=(A_2,[l,r]) $ where $ A_2 $ is a descendent of $ A_0 $. Slice-and-dice can be performed by selecting a subset of vertices in the vertex table of $ Q_0 $'s result and generating the induced network. For example, $ Q_0=((Profession),[2,5]) $ in temporal graph cube built on temp-multi-network in Fig.~\ref{fig:example_dataset}, we can choose to build an induced network based on the result of $ Q_0 $ with only ``teacher" and ``student" being selected to show the transactions between ``teacher" and ``student" from day 2 to 5.

We can also extend roll-up and drill-down according to the specified time ranges. A time related roll-up means conducting a query $ Q_1=(A_0,[l_1,r_1]) $ where $ l_1 \leq l $ and $ r_1 \geq r $, so that we can get a coarser resolution of summarized information in time axis. On the contrary, time related drill-down means conducting a query $ Q_2=(A_0,[l_2,r_2]) $ where $ l_2 \geq l $ and $ r_2 \leq r $.

%\stitle{Temporal crossboid.}
\subsection{Temporal Crossboid Query} \label{subsec:crossboid}
The inputs of temporal crossboid query $ Q_{cross}=(A'_1,A'_2,[l,r]) $ in temporal graph cube contain two specified views $ A_1'=(A_{11}',A_{12}',...,A_{1n}') $, $ A_2'=(A_{21}',A_{22}',...,A_{2n}') $ and a time interval $ [l,r] $, where $ A_1' \neq A_2' $. The output is a static aggregate bipartite network with two types of aggregated vertices corresponding to aggregations $ A_1' $ and $ A_2' $ respectively. %For example, the question in Example~\ref{exam:crossboid_query} can be represented by $ Q_{cross}=((Gender),(Profession),[2,3]) $.

We can conduct a temporal crossboid query directly on the original temp-multi-network. However, it is inefficient due to the large size of the original temp-multi-network. We omit the algorithm to conduct a temporal crossboid query on the original temp-multi-network, but give a more efficient way to conduct the query.
\begin{definition}[Nearest Common Descendant]
	\label{def:ncd}
	Given two different views $ A_1' $ and $ A_2' $, the common descendant of $ A_1' $ and $ A_2' $, $ cd(A_1',A_2') $ is also a view in temporal graph cube, satisfying $ dim(A_1') \cup dim(A_2') \subseteq dim(cd(A_1',A_2')) $. The nearest common descendant of $ A_1' $ and $ A_2' $, $ ncd(A_1',A_2') $, is one of the common descendants satisfying $ dim(ncd(A_1',A_2'))=dim(A_1') \cup dim(A_2') $.
\end{definition}
\begin{theorem}
	\label{thm:ans_cross_by_ncd}
	Given a temporal crossboid query $ Q_{cross}=(A_1',A_2',[l,r]) $, $ Q_{cross} $ can be answered from the result of the temporal cuboid query $ Q=(ncd(A_1',A_2'),[l,r]) $ where $ Q,Q_{cross} $ share the same aggregation function upon vertices and edges.
\end{theorem}
\comment{
\begin{proof}
	Although the result of $ Q_{cross} $ is a bipartite network, we can treat the edges in it as directed edges and treat each edge in materialized views of the temporal graph cube and in the result of $ Q $ as two directed edges, so that we can use the similar idea from the previous proofs of Theorem~\ref{thm:cuboid_by_temp_aggre_network} and Theorem~\ref{thm:cuboid_by_small_temp_aggre_network} to prove this theorem. We omit the details of this proof due to the space limitation.
\end{proof}
}
%With Theorem~\ref{thm:ans_cross_by_ncd}, a temporal crossboid query can be turned into a temporal cuboid query and we have discussed how to conduct a temporal cuboid query efficiently in \stitle{Temporal cuboid} section.
With Theorem~\ref{thm:ans_cross_by_ncd}, a temporal crossboid query can be turned into a temporal cuboid query, and thus can be solved by our previous techniques.

%\begin{theorem}
%	\label{thm:ans_cross_by_cuboid}
%	Given a temporal crossboid query $ Q_{cross}=(A_1',A_2',[l,r]) $, $ Q_{cross} $ can be directly answered from the result of a temporal cuboid query $ Q=(A_3',[l,r]) $ where $ dim(A_1') \cup dim(A_2') \subseteq dim(A_3') $ and $ Q,Q_{cross} $ share the same aggregation function upon vertices and edges.
%\end{theorem}
%\begin{proof}
%	todo
%\end{proof}
\begin{algorithm}[t]
	\scriptsize
	\caption{$\kw{Temporal Crossboid Query}$}
	\label{alg:temp_crossboid_on_cuboid}
	\KwIn{$ G=(V,E,B,W_{G}) $, result of $ Q=(ncd(A_1',A_2'),[l,r]) $; A temporal crossboid query $ Q_{cross}=(A_1',A_2',[l,r]) $; Aggregation functions $f_v$ and $f_e$}
	\KwOut{A bipartite graph $ G_B=(V_1,V_2,E_B,W_1,W_2,B_1,B_2) $}
	$ B_1 \gets dim(A_1') $, $ B_2 \gets dim(A_2') $\;
	Let $ h_1 $ be hash structure: $ \{B_1(u)|u \in V\} \rightarrow V_1 $, $ h_2 $ be hash structure: $ \{B_2(u)|u \in V\} \rightarrow V_2 $;

	\ForEach{$ u \in V $}{
		\If{$ h_1(B_1(u))=NULL $}{
			$ V_1 \gets V_1 \cup \{u\} $;
			$ W_1(u) \gets W_{G}(u) $;
			$ h_1(B_1(u)) \gets u $;
		}
		\Else{
			$ u' \gets h_1(B_1(u)) $;
			$ W_1(u') \gets f_v(W_1(u'),W(u)) $;
		}
		\If{$ h_2(B_2(u))=NULL $}{
			$ V_2 \gets V_2 \cup \{u\} $;
			$ W_2(u) \gets W_{G}(u) $;
			$ h_2(B_2(u)) \gets u $;
		}
		\Else{
			$ u'' \gets h_2(B_2(u)) $;
			$ W_2(u'') \gets f_v(W_2(u''),W(u)) $;
		}
	}
	$ EP \gets \{\} $;
	$ E_B \gets \{\} $;

	\ForEach{$ (u,v,a) \in E $}{
		$ u' \gets h_1(u) $;
		$ v'' \gets h_2(v) $;

		\If{$ (u',v'') \notin EP $}{
			$ EP \gets EP \cup \{(u',v'')\} $;
			$ E_B \gets E_B \cup \{(u',v'',a)\} $;
		}
		\Else{
			Let $ (u',v'',a') $ be an edge in $ E_B $ which has $ u',v'' $ as vertices\;
			$ E_B \gets E_B-\{(u',v'',a')\} $\;
			$ E_B \gets E_B \cup \{(u',v'',f_e(a',a))\} $;
		}
		$ v' \gets h_1(v) $;
		$ u'' \gets h_2(u) $;

		\If{$ (v',u'') \notin EP $}{
			$ EP \gets EP \cup \{(v',u'')\} $;
			$ E_B \gets E_B \cup \{(v',u'',a)\} $;
		}
		\Else{
			Let $ (v',u'',a'') $ be an edge in $ E_B $ which has $ v',u'' $ as vertices\;
			$ E_B \gets E_B-\{(v',u'',a'')\} $\;
			$ E_B \gets E_B \cup \{(v',u'',f_e(a'',a))\} $;
		}
	}
	\Return $ G_B=(V_1,V_2,E_B,W_1,W_2,B_1,B_2) $;
\end{algorithm}
Algorithm~\ref{alg:temp_crossboid_on_cuboid} is an algorithm to compute the result of $ Q_{cross}=(A_1',A_2',[l,r]) $ from the result of $ Q=(ncd(A_1',A_2'),[l,r]) $. Unlike Algorithm~\ref{alg:temp_cuboid_baseline}, we need aggregate each vertex on two different aggregations $ A_1' $ and $ A_2' $ (lines~3-11). For each edge $ (u,v,a) $ in $ G $, we need to create or update two aggregated edges $ (u',v'',\ast) $ and $ (v',u'',\ast) $ (lines~12-27), because the two directions of $ (u,v,a) $ represent two interactions of aggregated vertices respectively (note that we do not assign $ u' \leq v'' $ or $ v' \leq u'' $ in $ E_B $). The time complexity of Algorithm~\ref{alg:temp_crossboid_on_cuboid} is $ O(|V|+|E|) $. We can easily derive that $ |V_1|+|V_2| \leq 2|V| $ and $ |E_B| \leq 2|E| $ in Algorithm~\ref{alg:temp_crossboid_on_cuboid}, so the space complexity of Algorithm~\ref{alg:temp_crossboid_on_cuboid} is also $ O(|V|+|E|) $.

\comment{
\subsection{Growth of Network}\label{subsec:growing}
Compared to static network, temporal network records ongoing relationships between vertices, which means that we should append new edges into temporal network. For example, the temp-multi-network in Fig.~\ref{fig:example_dataset} should record new transactions between any two individuals in day 5 and in all following days. Specifically, suppose that we need to add a new edge $ (u,v,t,a) $ with discrete and numeric attributes $ (A(u),W(u),A(v),W(v)) $ of two vertices, there are two situations: 1) $ t-t_{base}=t_{end} $ ($ t=t_{|\Tr|} $, i.e., $ t $ equals the latest timestamp in the temporal graph cube). 2) $ t-t_{base}>t_{end} $.

For the original temp-multi-network $ \Gr=(\Vr,\Sr,A,W) $, it is simple to add a new edge in both situations. In situation 1), we only need to add $ u,v $ into $ \Vr $, update $ A,W $ with $ (A(u),W(u),A(v),W(v)) $ if $ u $ and $ v $ are new vertices and then $ (u,v,a) $ will be added into $ \Sr[t_{end}] $. In situation 2), the only difference is that we should extend $ \Sr $ and create an empty snapshot $ \Sr[t-t_{base}] $, then we add $ (u,v,a) $ into $ \Sr[t-t_{base}] $. Finally, we update $ t_{end} $ to $ t-t_{base} $.

For any precomputed view $ A' $ and its corresponding temporal aggregate network $ \Gr'=(\Vr',\Sr',B,W_{\Gr'}) $, if $ u $ is a new vertex in the original temp-multi-network, we need to create or update an aggregated vertex $ u' $ in $ \Vr' $ according to $ h(B(u)) $, where $ h $ is the hash structure used in construction of $ \Gr' $ and update $ h $ if $ h(B(u))=NULL $ (lines~3-6 in Algorithm~\ref{alg:view_construct_baseline}). We do the same process for $ v $. Then, we map $ (u,v,a) $ to $ (u',v',a) $ (lines~11-12 in Algorithm~\ref{alg:view_construct_baseline}), which can be regarded as the new edge for $ \Gr' $. If situation 1) is met, we create or update aggregated edge $ (u',v',\ast) $ in $ \Sr'[t_{end}] $ with $ (u',v',a) $ as lines~13-18 in Algorithm~\ref{alg:view_construct_baseline}. If situation 2) is met, we also extend $ \Sr' $ and create an empty snapshot $ \Sr'[t-t_{base}] $, then add $ (u',v',a) $ directly into $ \Sr'[t-t_{base}] $ and update $ t_{end} $ to $ t-t_{base} $ in $ \Gr' $.

}

\comment{
\begin{figure}[t!]
	\begin{center}
		\begin{tabular}[t]{c}\hspace*{-0.3cm}
			\subfigure[{\scriptsize Original network}]{
				\includegraphics[width=0.33\columnwidth]{fig/example/add_edge_at_5_original.pdf}
			}
			\hspace*{-0.3cm}
			\subfigure[{\scriptsize (Gender)}]{
				\includegraphics[width=0.33\columnwidth]{fig/example/add_edge_at_5_gender_adjust.pdf}
			}
			\hspace*{-0.3cm}
			\subfigure[{\scriptsize (Gender, Profession)}]{
				\includegraphics[width=0.33\columnwidth]{fig/example/add_edge_at_5_gender_pro_adjust.pdf}
			}
		\end{tabular}
	\end{center}
	\vspace*{-0.4cm}
	\caption{Snapshots of temp-multi-network in memory at day 5 after a new edge is added}
	\vspace*{-0.4cm}
	\label{fig:add_edge_at_5}
\end{figure}

\begin{figure}[t!]
	\begin{center}
		\begin{tabular}[t]{c}\hspace*{-0.3cm}
			\subfigure[{\scriptsize Original network}]{
				\includegraphics[width=0.33\columnwidth]{fig/example/add_edge_at_6_original.pdf}
			}
			\hspace*{-0.3cm}
			\subfigure[{\scriptsize (Gender)}]{
				\includegraphics[width=0.31\columnwidth]{fig/example/add_edge_at_6_gender_adjust.pdf}
			}
			\hspace*{-0.3cm}
			\subfigure[{\scriptsize (Gender, Profession)}]{
				\includegraphics[width=0.33\columnwidth]{fig/example/add_edge_at_6_gender_pro_adjust.pdf}
			}
		\end{tabular}
	\end{center}
	\vspace*{-0.4cm}
	\caption{Snapshots of temp-multi-network in memory at day 6 after a new edge is added}
	\vspace*{-0.4cm}
	\label{fig:add_edge_at_6}
\end{figure}
\begin{example} \label{exam:network_growth}
	Suppose that we need to add two new edges $ e_1=(v_2,v_3,5,10) $ and $ e_2=(v_6,v_9,6,5) $ successively where $ A(v_9)=(female,cn,student) $, $ W(v_9)=800 $ into temporal graph cube built on temp-multi-network in Fig.~\ref{fig:example_dataset} and only two views are precomputed: $ (Gender,\ast,\ast) $ and $ (Gender,\ast,Profession) $. Fig.~\ref{fig:add_edge_at_5} shows the snapshots at day 5 of all temp-multi-networks in the temporal graph cube after $ e_1 $ is added. Since $ v_2 $ and $ v_3 $ are both females, the self loop edge on ``female" in the 5-th snapshot in Fig.~\ref{fig:aggregation_gender} should be updated to the corresponding self loop in Fig.~\ref{fig:add_edge_at_5} (b). Similar update should be performed in the 5-th snapshot in Fig.~\ref{fig:aggregation_gender_profession}, and the result is shown in Fig.~\ref{fig:add_edge_at_5} (c).

	When adding $ e_2 $, we need to create new snapshot in each temp-multi-network of the temporal graph cube because $ e_2 $ leads to a new timestamp day 6. For the original network, we create a new snapshot at day 6 as Fig.~\ref{fig:add_edge_at_6} (a) with only $ e_2 $ being stored after all attributes of $ v_9 $ are added into the vertex table of the original temp-multi-network. For other temp-multi-networks of precomputed views, we should also create new snapshots at day 6, holding the aggregated edges of $ e_2 $ as in Fig.~\ref{fig:add_edge_at_6} (b) and (c) after the aggregated vertices of $ v_9 $ are added or updated.
\end{example}
}

%\section{The Proposed Indexes} \label{sec:indexes}
\section{The Index-based Approach}\label{sec:indexes}
In this section, we propose an index-based approach to process the temporal cuboid query (temporal crossboid queries can be transformed to temporal cuboid queries). Recall that for a temporal cuboid query $ Q=(A',[l,r]) $, we need to merge snapshots of a certain temp-multi-network in time range $ [l,r] $ whether $ A' $ is precomputed or not (see lines~8-15 of Algorithm~\ref{alg:temp_cuboid_baseline}). Merging snapshots in time ranges is similar to the classic range query problem: answering online queries $ q=(func,[l,r]) $ on a numeric array $ Arr $, where $ func $ might be SUM($\ast$), AVERAGE($\ast$), MAX($\ast$) or MIN($\ast$), specifying the needed statistical results of values in range $ [l,r] $ of $ Arr $. We can regard merging snapshots in snapshot array as a range query problem on a snapshot array.

\begin{figure}[t!]
	\begin{center}
		\begin{tabular}[t]{c}\hspace*{-0.3cm}
%			\subfigure[{\scriptsize A numeric array}]{
%				\includegraphics[width=0.85\columnwidth]{fig/example/example_numeric_array_adjust.pdf}
%			}
%			\hspace*{-0.3cm}
%			\\
			\subfigure[{\scriptsize A snapshot array extracted from Fig.~\ref{fig:aggregation_gender_profession}}]{
				\includegraphics[width=0.7\columnwidth]{fig/example/example_snapshot_array.pdf}
			}
			\hspace*{-0.3cm}
	%		\\
			\subfigure[{\scriptsize Result of range query $ Q $ in Example~\ref{exam:range_query_num_snap_array}}]{
				\includegraphics[width=0.25\columnwidth]{fig/example/example_range_query_snapshot.pdf}
			}
		\end{tabular}
	\end{center}
	\vspace*{-0.6cm}
	\caption{Range query on a snapshot array}
	\vspace*{-0.4cm}
	\label{fig:range_query_num_snap_array}
\end{figure}
\begin{example} \label{exam:range_query_num_snap_array}
Fig.~\ref{fig:range_query_num_snap_array} (a) is a snapshot array of temporal aggregate network of precomputed view $ (Gender,\ast,Profession) $ in Fig.~\ref{fig:aggregation_gender_profession}. Here we renumber all vertices and omit the isolated vertices in each snapshot for simplicity. Suppose that a range query on the snapshot array in Fig.~\ref{fig:range_query_num_snap_array} (a) is $ Q=((Gender,\ast,Profession),[2,4]) $ with SUM($\ast$) specified upon edges. We can derive that the result of $ Q $ as shown in Fig.~\ref{fig:range_query_num_snap_array} (b).
\end{example}

%%%%%%%%%
\comment{
Note that there are two differences between the range query on the numeric array and the snapshot array:
\begin{itemize}[leftmargin=*]
	\item We need to merge both the structural information of snapshots and the numeric attributes of edges in snapshots in certain ranges. The range query on the snapshot array can be regarded as the range query on a set array, in which we calculate the union of sets in specified range and maintain the statistical results of numeric attributes on all elements (edges).

	\item For the range query on the numeric array, modifying the value at an arbitrary place in the array can be well supported, but updating the size of the array is often hard to support.  However, in temp-multi-network, with the time goes on, the edges will be added into the temp-multi-network. Thus, we need to consider update the size of the array.
\end{itemize}

To address these differences, we propose a segment-tree based index structure to handle the range query in the snapshot array.
}

\comment{
There are many existing methods to build indexes to accelerate range query on the numeric array. In this paper, we implement some representative indexes to accelerate range query on snapshot array and extend them to support self maintenance when new edges are added. Specifically, we divide our problems into two kinds according to aggregation function specified upon edges $ f_e $: 1) $ f_e = $ COUNT($\ast$) or SUM($\ast$). 2) $ f_e= $ MAX($\ast$) or MIN($\ast$). In range query problem on numeric array, if $ func= $ SUM($\ast$) (COUNT($\ast$) is meaningless most of the time) in a query and there is no modification at arbitrary place, we can maintain a simple prefix array $ preArr $, in which
\begin{equation}
	\label{eqt:prearr_range_query}
	preArr[i]=\sum_{j=0}^{j \leq i}Arr[j].
\end{equation}
A query $ q=(func,[l,r]) $ can be easily answered by
\begin{equation}
	\label{eqt:prearr_ans_range_query}
	preArr[r]-preArr[l-1].
\end{equation}
However, if $ func= $ MAX($\ast$) or MIN($\ast$) and we still maintain each $ preArr[i] $ as the maximum (or minimum) of $ Arr $ in $ [0,i] $, we can not tell the maximum (or minimum) in $ [l,r] $ of $ Arr $ if $ preArr[r]=preArr[l-1] $.

It is the same with our problem because range query on numeric array can be regarded as a special case of our problem if each snapshot in snapshot array has only one edge and all edges of those snapshots share the same vertices. As a result, in Section~\ref{subsec:prefix_array}, we briefly discuss how to use prefix array to accelerate temporal cuboid queries when $ f_e $ equals COUNT($\ast$) or SUM($\ast$) and maintain prefix array while new edges are added into the temporal graph cube. In Section~\ref{subsec:sparse_table} and Section~\ref{subsec:segment_tree}, we discuss two different methods to accelerate queries when $ f_e $ equals MAX($\ast$) or MIN($\ast$) and their maintenance while new edges added.

\subsection{Prefix Array} \label{subsec:prefix_array}
Before discussing prefix array, we need to explain that in practical implementation, to support all kinds of aggregation functions we maintain all kinds of statistical results at the same time, i.e., in all snapshots of all temporal aggregate networks of precomputed views, each edge is in form of $ (u,v,c,a,max,min) $ where $ c,a $ are count of edges and amount of attributes respectively.

\stitle{Build.} We can build a prefix array for each precomputed view and $ A_{base} $. The elements in prefix array is still snapshots, but edges in these snapshots are in form of $ (u,v,c,a) $, since we only maintain counts of edges and amounts of numeric attributes of edges using prefix array.
\begin{algorithm}[t]
	\scriptsize
	\caption{$\kw{Build Prefix Array}$}
	\label{alg:build_prefix_array}
	\KwIn{A temp-multi-network $ \Gr=(\Vr,\Sr,A,W) $}
	\KwOut{Prefix Array $ preArray $ for $ \Gr $}
	Let $ preArray $ be an array initialized with $ t_{end}+1 $ empty snapshots;

	\ForEach{$ i \in [1,t_{end}] $}{
		$ preArray[i] \gets \Sr[i] $;
	}

	\ForEach{$ i \in [2,t_{end}] $}{
		$ \kw{MergeSnapshotSum}(preArray[i],preArray[i-1]) $;
	}
	\Return $ preArray $;

	\vspace*{0.2cm}
	{\bf Procedure} {$\kw{MergeSnapshotSum}(S_a,S_b)$}

	\ForEach{$ e_b \in S_b $}{
		\If{$\exists e_a \in S_a, e_a.u=e_b.u \wedge e_a.v=e_b.v $}{
			$ e_a.c \gets e_a.c+e_b.c $\;
			$ e_a.a \gets e_a.a+e_b.a $;
		}
		\Else{
			$ S_a \gets S_a \cup \{(e_b.u,e_b.v,e_b.c,e_b.a)\} $;
		}
	}
\end{algorithm}

We construct prefix array in Algorithm~\ref{alg:build_prefix_array}. Line~2-5 is the basic process of building a prefix array. The key part in Algorithm~\ref{alg:build_prefix_array} is the \kw{MergeSnapshotSum} procedure, which merges a snapshot $ S_b $ into another snapshot $ S_a $. In detail, for each edge $ e_b $ in $ S_b $, we add $ e_b $ into $ S_a $ (line~13) or update $ e_a $ in $ S_a $ which shares the same vertices with $ e_b $ (line~10-11).

Suppose the summarized snapshot of $ \Gr $ is $ S $, the time complexity and space complexity of Algorithm~\ref{alg:build_prefix_array} are both $ O(t_{end}\times |S|) $.

\stitle{Query.} It is easy to use prefix array to answer $ Q=(A',[l,r]) $ when $ f_e $ is COUNT($\ast$) or SUM($\ast$). Suppose conducting $ Q $ we need merge snapshots in $ [l,r] $ of a temp-multi-network $ \Gr $ ($ \Gr $ may not be the corresponding temporal aggregate network of $ A' $, the reason can be found in Section~\ref{subsec:queries}), and prefix array built for $ \Gr $ is $ preArray $, then the result of merging snapshots of $ \Gr $ can be easily obtained by Algorithm~\ref{alg:prefix_array_query}. If $ A' $ is precomputed, then $ \Gr=\Gr' $ and $ S_E $ (the output of Algorithm~\ref{alg:prefix_array_query}) is the network structure of $ Q $'s result, otherwise the same process in line~17-25 of Algorithm~\ref{alg:temp_cuboid_baseline} should be performed.
\begin{algorithm}[t]
	\scriptsize
	\caption{$\kw{Prefix Array Query}$}
	\label{alg:prefix_array_query}
	\KwIn{Prefix array $ preArray $ for $ \Gr $; Biased time range $ [l,r] $}
	\KwOut{A snapshot $ S_E $, the result of merging snapshots of $ \Gr $ in $ [l,r] $ }
	$ S_E \gets \{\} $;
	$ l \gets l-1 $;

	\ForEach{$ e_r \in preArray[r] $}{
		\If{$\exists e_l \in preArray[l], e_r.u=e_l.u \wedge e_r.v=e_l.v $}{
			\lIf{$ e_r.c>e_l.c $}{$ S_E \gets S_E \cup \{(e_r.u,e_r.v,e_r.c-e_l.c,e_r.a-e_l.a)\} $}
		}
		\Else{
			$ S_E \gets S_E \cup \{(e_r.u,e_r.v,e_r.c,e_r.a)\} $;
		}
	}
	\Return $ S_E $;
\end{algorithm}
It is clear that the time complexity of Algorithm~\ref{alg:prefix_array_query} is $ O(|preArray[r]|) $.

\stitle{Update.} We have discussed that there are two situations when adding a new edge $ (u,v,t,a) $: 1) $ t-t_{base}=t_{end} $. 2) $ t-t_{base}>t_{end} $. We directly give the updating algorithm Algorithm~\ref{alg:prefix_array_update}.
\begin{algorithm}[t]
	\scriptsize
	\caption{$\kw{Prefix Array Update}$}
	\label{alg:prefix_array_update}
	\KwIn{Prefix array $ preArray $ for $ \Gr $; Mapped edge $ (u',v',a) $ of new edge $ e=(u,v,t,a) $ used to update $ \Gr $; $ t_{end} $ of $ \Gr $ before $ \Gr $ was updated}
	\KwOut{Updated $ preArray $}
	\If{$ t-t_{base}>t_{end} $}{
		Append $ (t-t_{base}-t_{end}) $ $ preArray[t_{end}] $s to $ preArray $;
	}
	\If{$ \exists e_t \in preArray[t-t_{base}],e_t.u=u' \wedge e_t.v=v' $}{
		$ e_t.c \gets e_t.c+1 $;
		$ e_t.a \gets e_t.a+a $;
	}
	\Else{
		$ preArray[t-t_{base}] \gets preArray[t-t_{base}] \cup \{(u',v',1,a)\} $;
	}
	\Return $ preArray $;
\end{algorithm}

In Algorithm~\ref{alg:prefix_array_update}, the mapped edge $ (u',v',a) $ in the input is used to update $ \Gr $ as we discussed in Section~\ref{subsec:growing}. If $ \Gr $ is the original temp-multi-network, $ (u',v',a)=(u,v,a) $. $ t_{end} $ is the biased timestamp of the latest timestamp in $ \Gr $ before $ \Gr $ was updated. If condition in line~1 is true, then the second situation of adding a new edge is met, and we should extend $ preArray $ to a new length by appending $ (t-t_{base}-t_{end}) $ $ preArray[t_{end}] $s to $ preArray $ (line~2). Whether condition in line~1 is true or false, the last step is updating $ preArray[t-t_{base}] $ with $ (u',v',a) $ (line~3-6).

The time complexity of Algorithm~\ref{alg:prefix_array_update} still depends on situations of adding a new edge. If the first situation is met, the time complexity is $ O(1) $. If the second situation is met, the time complexity is $ O((t-t_{base}-t_{end})\times |preArray[t_{end}]|) $.
}

\comment{
\subsection{Sparse Table} \label{subsec:sparse_table}
Sparse table (STable) is an efficient data structure to accelerate range query on numeric array $ Arr $ with $ O(1) $ time complexity and $ O(nlog(n)) $ space complexity ($ n $ is the length of $ Arr $) only when $ func $ is MAX($\ast$) or MIN($\ast$) in $ q $. If $ func $ is SUM($\ast$), time complexity of conducting $ q $ becomes $ O(log(n)) $. We briefly explain the principle of STable bellow.
\begin{itemize}[leftmargin=*]
	\item For a numeric array $ Arr $ of length $ n $, STable maintains a two-dimensional array $ f $. $ f[i][j] $ represents the maximum (or minimum) in range $ [i-2^j+1,i] $ of $ Arr $.

	\item For each query $ q=(func,[l,r]) $, let $ len=r-l+1 $, if $ log(len) $ is an integer, then the answer of $ q $ is $ f[r][log(len)] $. Otherwise, let $ m=\lfloor log(len) \rfloor $, the answer of $ q $ is $ func(f[l+2^m-1][m],f[r][m]) $.
\end{itemize}
When $ log(len) $ is not an integer, we can not use a single element in $ f[r] $ to answer $ q $, but we can use two elements in $ f[l+2^m-1] $ and $ f[r] $, representing two overlapping ranges to answer $ q $. If $ func $ is SUM($\ast$), we can not use the same method to answer $ q $, because in this case, values in overlapping area will be added twice. It doesn't matter if $ func $ is MAX($\ast$) (or MIN($\ast$)), because MAX($ x,x $) still equals $ x $.

For a snapshot $ S $, we can also get MAX($ S,S $) $ =S $, because numeric value $ x $ on each edge of $ S $ still satisfies MAX($ x,x $) $ =x $. Note that the execution of MAX($\ast$) when the parameters are snapshots is similar to \kw{MergeSnapshotExtre} in Algorithm~\ref{alg:stable_build}. Next, we discuss how to extend STable to solve our problem.

First, we switch all elements in $ f $ to snapshots. We first consider the case where $ f_e= $ MAX($\ast$). For a temp-multi-network $ \Gr $ and its snapshot array $ \Sr $, we have
\begin{equation}
	\label{eqt:stable_elements}
	\begin{split}
		f[i][j]=MAX(\Sr[i-2^j+1],\\\Sr[i-2^j+2],...,\Sr[i]).
	\end{split}
\end{equation}
That is, $ f[i][j] $ is the MAX($\ast$) result of snapshots of $ \Sr $ in time range $ [i-2^j+1,i] $.

\stitle{Build.} Building a STable relies on the following equation:
\begin{equation}
	\label{eqt:build_stable}
	f[i][j]=MAX(f[i][j-1],f[i-2^{j-1}][j-1]).
\end{equation}
To support MIN($\ast$), we use edges in form of $ (u,v,max,min) $ in snapshots of $ f $.
\begin{algorithm}[t]
	\scriptsize
	\caption{$\kw{STable Build}$}
	\label{alg:stable_build}
	\KwIn{A temp-multi-network $ \Gr=(\Vr,\Sr,A,W) $}
	\KwOut{STable $ f $ for $ \Gr $}
	Let $ f $ be an array initialized with $ t_{end}+1 $ empty arrays\;
	\ForEach{$ i \in [1,t_{end}] $}{
		$ \kw{BuildSinglePlace}(i,f,\Sr) $;
	}
	\Return $ f $;

	\vspace*{0.2cm}
	{\bf Procedure} {$\kw{MergeSnapshotExtre}(S_a,S_b)$}

	\ForEach{$ e_b \in S_b $}{
		\If{$\exists e_a \in S_a, e_a.u=e_b.u \wedge e_a.v=e_b.v $}{
			$ e_a.max \gets MAX(e_a.max,e_b.max) $\;
			$ e_a.min \gets MIN(e_a.min,e_b.min) $;
		}
		\Else{
			$ S_a \gets S_a \cup \{(e_b.u,e_b.v,e_b.max,e_b.min)\} $;
		}
	}

	\vspace*{0.2cm}
	{\bf Procedure} {$\kw{BuildSinglePlace}(pos,f,snapArr)$}

	$ f[pos].append(snapArr[pos]) $\;
	$ range \gets 2 $;
	$ i \gets 1 $\;
	\While{$ pos-range+1 \geq 1 $}{
		$ halfRange \gets range>>1 $;
		$ prePos \gets pos-halfRange $\;
		$ f[pos].append(f[pos][i-1]) $\;
		$ \kw{MergeSnapshotExtre}(f[pos][i],f[prePos][i-1]) $\;
		$ range \gets range<<1 $;
		$ i=i+1 $;
	}
\end{algorithm}
Algorithm~\ref{alg:stable_build} is used to build STable for every temp-multi-network.

In line~3 of Algorithm~\ref{alg:stable_build}, \kw{BuildSinglePlace} is executed to build each $ f[i],i\in [1,t_{end}] $. \kw{BuildSinglePlace} procedure is designed based on Equation~\ref{eqt:build_stable} as line~14-19. The key part of Algorithm~\ref{alg:stable_build} is the \kw{MergeSnapshotExtre} procedure, which conducts MAX($\ast$) for snapshots. The time complexity and space complexity of Algorithm~\ref{alg:stable_build} are both $ O(t_{end}\times log(t_{end})|S|) $ where $ S $ is the summarized snapshot of the inputed temp-multi-network.

\stitle{Query.} Algorithm~\ref{alg:stable_query} conducts the range query on snapshot array using STable.
\begin{algorithm}[t]
	\scriptsize
	\caption{$\kw{STable Query}$}
	\label{alg:stable_query}
	\KwIn{STable $ STable $ for $ \Gr $; Biased time range $ [l,r] $}
	\KwOut{A snapshot $ S_E $, the result of merging snapshots of $ \Gr $ in $ [l,r] $}
	$ S_E \gets \{\} $;
	$ range \gets r-l+1 $\;
	$ f \gets STable.f $\;
	\If{$ log(range) $ is an integer}{
		$ S_E \gets f[r][log(range)] $;
	}
	\Else{
		$ logVal \gets \lfloor log(range) \rfloor $\;
		$ S_E \gets f[r][logVal] $\;
		$ powerVal \gets 1<<logVal $\;
		$ \kw{MergeSnapshotExtre}(S_E,f[l+powerVal-1][logVal]) $;
	}

	\Return $ S_E $;
\end{algorithm}
The idea of Algorithm~\ref{alg:stable_query} is similar to algorithms conducting queries on numeric arrays using STable. The only difference is the use of \kw{MergeSnapshotExtre}. The time complexity of Algorithm~\ref{alg:stable_query} is $ O(|S|) $

\stitle{Update.} It is generally considered that STable doesn't support to be updated when modifying at arbitrary places of $ Arr $ in range query problem on numeric array because of the low efficiency. However, in our problem, we only need to modify snapshot array at the last place (i.e., adding a new edge to the last snapshot) or create a new snapshot holding the new edge at the end of the snapshot array. It is possible to update STable in our problem.
\begin{algorithm}[t]
	\scriptsize
	\caption{$\kw{STable Update}$}
	\label{alg:stable_update}
	\KwIn{STable $ STable $ for $ \Gr=(\Vr,\Sr,A,W) $; Mapped edge $ (u',v',a) $ of new edge $ e=(u,v,t,a) $ used to update $ \Gr $; $ t_{end} $ of $ \Gr $ before $ \Gr $ was updated}
	\KwOut{Updated $ STable $}
	$ f \gets STable.f $\;
	\If{$ t-t_{base}>t_{end} $}{
		Append $ (t-t_{base}-t_{end}) $ empty arrays to $ f $;

		\ForEach{$ i \in [t_{end}+1,t-t_{base}] $}{
			$ \kw{BuildSinglePlace}(i,f,\Sr) $;
		}
	}
	\Else{
		\ForEach{$ S \in f[t_{end}] $}{
			$ \kw{MergeSnapshotExtre}(S,\{(u',v',a,a)\}) $;
		}
	}
	\Return $ STable $;
\end{algorithm}

We use Algorithm~\ref{alg:stable_update} to update STable. For the second situation of adding new edges, we only need to append $ (t-t_{base}-t_{end}) $ empty 1-D arrays to $ f $ and execute \kw{BuildSinglePlace} at extra places of $ f $ (line~3-5), because the update of STable is later than the update of $ \Gr $ the STable built on, and the process in line~3-5 of Algorithm~\ref{alg:stable_update} can be regarded as a continuing process of line~2-3 in Algorithm~\ref{alg:stable_build}.

The time complexity of Algorithm~\ref{alg:stable_update} still depends on situations of adding a new edge. If situation 1) is met, we should update each snapshot in $ STable.f[t_{end}] $ with mapped edge $ (u',v',a,a) $ (line~7-8), so the time complexity is $ O(log(t_{end})) $. If situation 2) is met, we should conduct \kw{BuildSinglePlace} for $ STable.f[i],i \in [t_{end}+1,t-t_{base}] $, so the time complexity is $ O((t-t_{base}-t_{end})\times log(t-t_{base})|S|) $, $ S $ is the summarized snapshot of $ \Gr $ which STable is built on.

}

\subsection{The Segment Tree Index} \label{subsec:segment_tree}
\comment{
Segment tree (STree) is an efficient data structure to accelerate range query on numeric array, and it supports all kinds of statistical functions mentioned above.
\begin{figure}[t]
	\begin{center}
		\includegraphics{fig/example/example_segtree.pdf}
	\end{center}
	\vspace*{-0.4cm}
	\caption{An example of STree}
	\vspace*{-0.4cm}
	\label{fig:exam_segtree}
\end{figure}
For example, Fig.~\ref{fig:exam_segtree} shows the structure of STree built for numeric array in Fig.~\ref{fig:range_query_num_snap_array} (a).
}

Here we focus mainly on extending the classic segment tree (STree) structure to support range query on snapshot array when $ f_e $ is MAX($\ast$) or MIN($\ast$) and the maintenance of STree when adding new edges. For the other aggregation functions, including SUM($\ast$) and AVERAGE($\ast$), can be processed in a similar way. Below, we first briefly describe the basic properties of STree.
\begin{enumerate}
	\item STree is a full binary tree, maintaining values for an array. If the length of the array is $ N $, the height of STree is $ \lceil log(N) \rceil+1 $.
	\item Each node in STree maintains statistical result of values in a sub-range of the array. The root of STree maintains the whole range of the array, i.e., $ [1,N] $. The left child and the right child maintain range $ [1,\lfloor(1+N)/2\rfloor] $ and range $ [\lfloor(1+N)/2\rfloor+1,N] $ respectively, which split $ [1,N] $ equally. Both left child and right child can be regarded as roots of sub-STrees and they both have their own childs sharing their ranges equally. The above process for a node ends when its range can not be divided (length equals $ 1 $).
	\item The time complexity of building a STree is $ O(N) $. The space complexity of STree is also $ O(N) $. The time complexity of processing a query $ q=(func,[l,r]) $ is $ O(log(N)) $.
\end{enumerate}

Unlike traditional range query problem, there are two differences in our range query problem: 1) elements in the array and statistical results in nodes of STree are not numeric values but snapshots, with edges in form of $ (u,v,max,min) $; and 2) the range of STree might be expanded because of inserting new edges. Merging statistical information of nodes is a basic and frequent operation in both building and querying of STree, in which two statistical results of two nodes produce a new result. For the first difference, all we need to do is replacing the original operation on numeric values with \kw{MergeSnapshotExtre} procedure (see Algorithm~\ref{alg:stree_query}). We will address the second difference in the \stitle{Update} algorithm (see Algorithm~\ref{alg:update_stree}).  Below, we first briefly describe the index building procedure, followed by the query processing procedure and index updating procedure.

\stitle{STree building.} We omit the detailed algorithm to build the STree for a snapshot array, because we only need to replace the merging operation of two numeric values in the traditional algorithm of building STree for numeric array with the proposed \kw{MergeSnapshotExtre} procedure  (see Algorithm~\ref{alg:stree_query}). For example, Fig.~\ref{fig:exam_segtree} illustrates a STree $ STree $ for the snapshot array in Fig.~\ref{fig:range_query_num_snap_array}. Note that each node of $ STree $ maintains a snapshot. Fig.~\ref{fig:exam_stree_node} shows the snapshot of the node $ [1,3] $ of $ STree $ in Fig.~\ref{fig:exam_segtree}.

\begin{figure}[t]
	\begin{center}
		\begin{tabular}[t]{c}\hspace*{-0.3cm}
\subfigure[{\scriptsize The STree}]{
				\includegraphics[width=0.5\columnwidth, height=3cm]{fig/example/example_segtree.pdf} \label{fig:exam_segtree}
			} %\hspace*{-0.3cm}
\subfigure[{\scriptsize Snapshot in the node $ [1,3] $}]{
				\includegraphics[width=0.4\columnwidth]{fig/example/example_stree_node_1_3.pdf} 	\label{fig:exam_stree_node}
			}
\end{tabular}
	\end{center}
	\vspace*{-0.6cm}
	\caption{A STree built on the snapshot array in Fig.~\ref{fig:range_query_num_snap_array}}
	\vspace*{-0.6cm}
	\label{fig:stree}
\end{figure}

As we have mentioned before, the time complexity for building a traditional STree is $ O(N) $. Since \kw{MergeSnapshotExtre} will be called in building each node, the time complexity of building STree for snapshot array of length $ N $ is $ O(N|S|) $, where $ S $ is the summarized snapshot of the snapshot array. Also, it is easy to derive that the space usage of the STree building procedure is  $ O(N|S|) $.

%The space consumed by STree built for the snapshot array is also $ O(N|S|) $. Note that each node $ node $ in STree is a struct, where $ node.lchild $ and $ node.rchild $ are left child and right child of $ node $ respectively and $ [node.timel,node.timer] $ is the range which $ node $ maintains. For leaves of STree, $ lchild $ and $ rchild $ are $ NULL $. Suppose the snapshot array STree built on is $ \Sr $, $ node.snapshot $ can be regarded as the summarized snapshot of snapshot sub-array $ [\Sr[node.timel-t_{base}],...,\Sr[node.timer-t_{base}]] $. STree $ STree $ is also a struct, where $ STree.root $ is the root of $ STree $.

\stitle{Query processing.} Algorithm~\ref{alg:stree_query} conducts the range query on snapshot array using STree, and it shares the same framework with original query algorithm on STree but uses \kw{MergeSnapshotExtre} to merge snapshots. Merging snapshots only happens when the current split range $ [timel,timer] $ equals the range held by the current node $ treeNode $ (line~2 in Algorithm~\ref{alg:stree_query}). In the worst case, it happens at each depth of STree, so the time complexity of Algorithm~\ref{alg:stree_query} is $ O(log(N)|S|) $. For example, suppose we conduct a query $ Q=(\ast,[2,5]) $ on snapshot array in Fig.~\ref{fig:range_query_num_snap_array} (a) (the view in $ Q $ is omitted), we have to merge snapshots in nodes with range $ [2,2] $, $ [3,3] $ and $ [4,5] $ as in grey nodes in Fig.~\ref{fig:exam_segtree}.
\begin{algorithm}[t]
	\scriptsize
	\caption{$\kw{STreeQuery(treeNode,timel,timer,ans)}$}
	\label{alg:stree_query}
	\KwIn{$ treeNode $, node to be visited; Time range $ [timel,timer] $; $ ans $, a snapshot holding the current result}
	\lIf{$ treeNode=NULL $}{\Return}
	\If{$ timel=treeNode.timel \wedge timer=treeNode.timer $}{
		$\kw{MergeSnapshotExtre}(ans,treeNode.snapshot)$\;
		\Return;
	}
	$ mid \gets (treeNode.timel+treeNode.timer)/2 $\;
	\lIf{$ timel > mid $}{$ STreeQuery(treeNode.rchild,timel,timer,ans) $}
	\lElseIf{$ timer \leq mid $}{$ STreeQuery(treeNode.lchild,timel,timer,ans) $}
	\Else{
		$ STreeQuery(treeNode.lchild,timel,mid,ans) $\;
		$ STreeQuery(treeNode.rchild,mid+1,timer,ans) $;
	}

\vspace*{0.2cm}
	{\bf Procedure} {$\kw{MergeSnapshotExtre}(S_a,S_b)$}

	\ForEach{$ e_b \in S_b $}{
		\If{$\exists e_a \in S_a, e_a.u=e_b.u \wedge e_a.v=e_b.v $}{
			$ e_a.max \gets MAX(e_a.max,e_b.max) $\;
			$ e_a.min \gets MIN(e_a.min,e_b.min) $;
		}
		\Else{
			$ S_a \gets S_a \cup \{(e_b.u,e_b.v,e_b.max,e_b.min)\} $;
		}
	}
	\Return;
\end{algorithm}

\stitle{Index updating.} Let $ STree.root.timer $ be the current largest timestamp in the STree. When a new edge $ (u,v,t,a) $ with $t>STree.root.timer $ comes, we need to expand the range of STree by creating new nodes to maintain larger range and switch the root of STree to one of the new nodes.

%The largest timestamp that STree maintains is $ STree.root.timer $, so the two cases in updating STree when adding a new edge $ (u,v,t,a) $ are: 1) $ t \leq STree.root.timer $. 2) $ t>STree.root.timer $. If case 2) is met, we need to expand the range of STree by creating new nodes to maintain larger range and switch the root of STree to one of the new nodes.

Suppose that $ l=STree.root.timel,r=STree.root.timer $, if $ t>r $, we first create a new node $ newNode $ with range $ [l,2r-l+1] $, which is twice the length of $ [l,r] $, so that $ STree.root $ can be a valid left child of $ newNode $. Then, we let $ STree.root $ be the left child of $ newNode $. Finally, we let $ newNode $ be the new root of $ STree $. If $ [l,2r-l+1] $ still can not cover $ t $, we continue the process above until $ t $ is coverd. The updated $ STree $ is not a fully binary tree, since there is only a left subtree for the new root which violates the basic properties of STree. However, it can be seen as a part of a standard STree, which might be completed by continuously added new edges.

\comment{
\begin{figure}[t]
	\begin{center}
		\begin{tabular}[t]{c}\hspace*{-0.3cm}
			\subfigure[{\scriptsize Expanded STree waiting for the new edge}]{
				\includegraphics[width=0.75\columnwidth, height=3cm]{fig/example/example_segtree_expand.pdf}
			}
			\hspace*{-0.3cm}
			\\
			\subfigure[{\scriptsize Expanded STree being inserted with a new edge}]{
				\includegraphics[width=0.75\columnwidth, height=3cm]{fig/example/example_segtree_expand_inserted.pdf}
			}
		\end{tabular}
	\end{center}
	\vspace*{-0.4cm}
	\caption{Update STree when new edges are added}
	\vspace*{-0.4cm}
	\label{fig:exam_segtree_expand}
\end{figure}
\begin{example} \label{exam:stree_expand}
	Suppose we have built a STree $ STree $ for snapshot array in Fig.~\ref{fig:range_query_num_snap_array} (a) and $ STree.root.timer=5 $. If we want to add the new edge $ e_2 $ with timestamp 6, we should update $ STree $ so that it can cover $ [1,6] $. The updated $ STree $ is shown in Fig.~\ref{fig:exam_segtree_expand} (a), where we create a new node $ newNode $ with range $ [1,10] $ and let $ STree.root $ be the $ lchild $ of $ newNode $. Finally we assign $ newNode $ to be the new root of $ STree $. The updated $ STree $ without the nodes presented by dotted rectangles in Fig.~\ref{fig:exam_segtree_expand} (a) is not a complete STree. As shown in Fig.~\ref{fig:exam_segtree_expand} (b) (we omit the left subtree of the root for simplicity), only nodes on path from the root to leaf with range $ [6,6] $ are needed to maintain the aggregated edge of $ e_2 $, so we only need to create or update nodes on that path.
\end{example}
}

\begin{algorithm}[t]
	\scriptsize
	\caption{$\kw{UpdateSTree}$}
	\label{alg:update_stree}
	\KwIn{STree $ STree $ built for $ \Gr $; Mapped edge $ (u',v',a) $ of new edge $ e=(u,v,t,a) $ used to update $ \Gr $;}
	\KwOut{Updated STree $ STree $}
	\While{$ STree.root.timer<t $}{
		$ newRoot \gets $ a new empty STree node\;
		$ newRoot.timel \gets STree.root.timel $\;
		$ newRoot.timer \gets 2 \times STree.root.timer+1-STree.root.timel $\;
		$ newRoot.lchild \gets STree.root $\;
		$ newRoot.snapshot \gets STree.root.snapshot $\;
		$ STree.root \gets newRoot $;
	}
	$\kw{STreeInsertEdge}(STree.root,(u',v',t,a))$;

	\Return $ STree $;

	\vspace*{0.2cm}
	{\bf Procedure} {$\kw{STreeInsertEdge}(treeNode,e'=(u',v',t,a))$}

	$ \kw{MergeSnapshotExtre}(treeNode.snapshot,\{(u',v',a,a)\}) $;

	\lIf{$ treeNode.timel=treeNode.timer $}{\Return}
	$ mid \gets \lfloor(treeNode.timel+treeNode.timer)/2\rfloor $\;
	\If{$ t \leq mid $}{
		\If{$ treeNode.lchild=NULL $}{
			$ newNode \gets $ a new empty STree node\;
			$ treeNode.lchild \gets newNode $\;
			$ newNode.timel \gets treeNode.timel $\;
			$ newNode.timer \gets mid $;
		}
		$\kw{STreeInsertEdge}(treeNode.lchild,e')$;
	}
	\Else{
		\If{$ treeNode.rchild=NULL $}{
			$ newNode \gets $ a new empty STree node\;
			$ treeNode.rchild \gets newNode $\;
			$ newNode.timel \gets mid+1 $\;
			$ newNode.timer \gets treeNode.timer $;
		}
		$ \kw{STreeInsertEdge}(treeNode.rchild,e') $;
	}
\end{algorithm}

Algorithm~\ref{alg:update_stree} is used to update STree. In line~1, the condition in the while loop is true which means that the current root of $ STree $ can not cover $ t $. So, we need to create a new root, which has a double size of range compared to the current root (line~3-4). In line~6, we directly copy the snapshot of the current root to the new root, since there is no possible right child for the new root before new edge is added. If the range of the candidate new root can not cover $ t $ (it hardly happens because of the density of timestamps in real-word large scale temporal network), then the loop in line~1 continues. When $ STree.root.timer \geq t $ is true, we can use \kw{STreeInsertEdge} procedure to update STree. In line~11, we update the snapshot of $ treeNode $ with the mapped edge, since $ t $ is in $ [treeNode.timel,treeNode.timer] $. In line~15 and line~22, we need to test whether the left child or the right child exists or not and create left child (lines~16-19) or right child (lines~23-26). %We have discussed the reason before, that the STree is not complete after being expanded to maintain a larger range.

The time complexity of Algorithm~\ref{alg:update_stree} contains two parts: creating new root in lines~1-7 and inserting new edge using \kw{STreeInsertEdge} procedure. Suppose the length of range maintained by the root of STree is $ len_1=STree.root.timer-STree.root.timel+1 $ before new edge is added, and the length of new range of timestamps in $ \Gr $ becomes $ len_2=t-STree.root.timel+1 $ after $ \Gr $ is updated. To cover $ len_2 $, we need repeat the loop in line~1 at least $ x $ times, and we have
\begin{equation}
	\label{eqt:new_root_create_times}
%	\begin{split}
		len_1*2^x \geq len_2, \quad
		x \geq log(\frac{len_2}{len_1}).
%	\end{split}
\end{equation}
For each loop, the cost mainly comes from line~6. Suppose that the snapshot maintained in root is $ S_{root} $ before a new edge is added, the time complexity of creating the new root is $ O(log(\frac{len_2}{len_1})\times |S_{root}|) $. In practice, $ len_2>len_1 $ is hardly true because $ len_1 $, the length of range maintained by root, grows exponentially (lines~3-4) but $ len_2 $ grows linearly since timestamps in real-world temporal graph are dense. In \kw{STreeInsertEdge} procedure, let the length of range in the final new root is $ len $, the procedure go through the $ log(len)+1 $ layers of STree, in each layer it updates the snapshot of node covering $ t $ or creates necessary node first. Since updating a snapshot and creating a new empty node both contain a constant number of operations, the time complexity of \kw{STreeInsertEdge} procedure is $ O(log(len)+1) $.

\section{Effectiveness of the Index} \label{sec:effec_of_indexes}
In traditional range query problems, indexes are helpful to accelerate the query processing. However, similar indexes cannot always work in our problem, since the elements in the array are not numeric values but snapshots.

\begin{figure}[t] %\vspace*{-0.5cm}
	\begin{center}
		\begin{tabular}[t]{c}\hspace*{-0.3cm}
			\subfigure[{\scriptsize }]{
				\includegraphics[width=0.95\columnwidth]{fig/example/example_index_fail.pdf}
			}
			\hspace*{-0.3cm}
			\\
			\subfigure[{\scriptsize }]{
				\includegraphics[width=0.95\columnwidth]{fig/example/example_index_success.pdf}
			}
		\end{tabular}
	\vspace*{-0.3cm}
		\caption{Two cases of range query on snapshot array}
		\vspace*{-0.6cm}
		\label{fig:index_fail_success_example}
	\end{center}
\end{figure}
Consider an example in Fig.~\ref{fig:index_fail_success_example} (a), there is no single edge shared by any two snapshots (edge $ e $ is shared by snapshots means that there exists an edge that share the vertices with $ e $ in each of those snapshots). In this case, if we merge snapshots in $ [t_1,t_4] $, the best choice is the baseline method, i.e., traversing all snapshots in the range and computing the result one by one. In baseline method, only $ 4 $ edges will be visited and each of them is visited only once. The edges in the result (snapshot at the right of the arrow in Fig.~\ref{fig:index_fail_success_example} (a)) are exactly those $ 4 $ edges, thus the baseline method achieves the highest efficiency and there is no need to build indexes in this case.

Consider the second example in Fig.~\ref{fig:index_fail_success_example} (b), all snapshots share the same edges. In this case, if we still merge snapshots in $ [t_1,t_4] $, each edge will be visited $ 4 $ times in the baseline method, therefore it is necessary to build index. Next, we describe the measurement of the necessity of index and the key factor we found which affects the necessity of index.
\begin{definition}[Acceleration Ratio of Index]
	\label{def:acceleration_ratio_index}
	For an array $ Arr $ with numeric values or snapshots, we build a segment tree index on it. For a query $ q=(func,[l,r]) $, assume that the basic components are visited $ C_b $ times using the baseline method and $ C_i $ times using the index-based method, the acceleration ratio of the index on $ q $ is $ \frac{C_b}{C_i} $.
\end{definition}
The basic components in snapshot array and index built on snapshot array are edges. We use the number of visited edges as the measure of time consumption when conducting a query using the baseline method and using the index-based method in Definition~\ref{def:acceleration_ratio_index}.
\begin{definition}[Similarity of Snapshots]
	\label{def:similarity_snapshots}
	Given a snapshot array $ snapArr $ starting from $ 1 $ and containing $ n $ snapshots, the summarized snapshot $ S $ of all snapshots in $ snapArr $, $ E=\sum_{i=1}^{n}|snapArr[i]| $, the similarity of snapshots in $ snapArr $ is $ s=\frac{E}{|S|} $.
\end{definition}
In other words, the similarity of snapshots is the ratio of the total number of edges in snapshot array to the size of the summarized snapshot. For simplicity, we assume that each snapshot in $ snapArr $ has at least one edge. Clearly, for a snapshot array of length $ n $, similarity of snapshots $ s $ is in $ [1,n] $.
\begin{example}
	Consider examples in Fig.~\ref{fig:similarity}.
	\begin{figure}[t] %\vspace*{-0.5cm}
		\begin{center}
			\begin{tabular}[t]{c}\hspace*{-0.3cm}
				\subfigure[{\scriptsize $ s=1 $}]{
					\includegraphics[width=0.5\columnwidth]{fig/example/example_similarity_a.pdf}
				}
				\hspace*{-0.5cm}
				\subfigure[{\scriptsize $ s=4 $}]{
					\includegraphics[width=0.5\columnwidth]{fig/example/example_similarity_b.pdf}
				}
				\\
				\subfigure[{\scriptsize $ s=\frac{5}{3} $}]{
					\includegraphics[width=0.5\columnwidth]{fig/example/example_similarity_c.pdf}
				}
				\hspace*{-0.5cm}
				\subfigure[{\scriptsize $ s=4 $}]{
					\includegraphics[width=0.5\columnwidth]{fig/example/example_similarity_d.pdf}
				}
			\end{tabular}
			\vspace*{-0.5cm}
			\caption{Four snapshot arrays with different similarity of snapshots}
			\vspace*{-0.8cm}
			\label{fig:similarity}
		\end{center}
	\end{figure}
	There are 4 snapshot arrays having the same length of 4 but different similarities of snapshots $ s $. In Fig.~\ref{fig:similarity} (a), $ s=1 $, and we can see that there is no edge shared by any two snapshots, or, snapshots in Fig.~\ref{fig:similarity} (a) are not similar to each other. In Fig.~\ref{fig:similarity} (b) and (d), $ s=4 $, all snapshots share the same edges. In Fig.~\ref{fig:similarity} (c), $ s=\frac{5}{3} $, and there are edges shared by some snapshots.
\end{example}
From the above examples, we can see that with the similarity of snapshots grows, there will be more snapshots in snapshot array which are similar to each other, or, more edges are shared by snapshots.

\begin{theorem}
	\label{thm:best_index_efficiency}
	For two arrays of length $ n $ and starting from $ 1 $, snapshot array $ snapArr $ and numeric array $ numArr $, if similarity of snapshots in $ snapArr $ equals $ n $, then for any query $ q=(func,[l,r]) $ on both $ snapArr $ and $ numArr $, the acceleration ratios of the same index built on them are equal.
\end{theorem}
\comment{
\begin{proof}
	In Section~\ref{sec:indexes}, we know that the elements in all indexes built on snapshot array are snapshots, which can be regarded as summarized snapshots of different snapshot sub-arrays of the original snapshot array. If the similarity of snapshots in $ snapArr $ is $ n $, then all snapshots in $ snapArr $, as well as their summarized snapshot, share the same edges. It is clear that all snapshots in indexes also share the same edges with snapshots in $ snapArr $. Suppose the indexes built on $ snapArr $ and $ numArr $ are two STrees $ snapSTree $ and $ numSTree $ (the proofs on prefix array and STable are simple, so we only analyse STree here), and summarized snapshot of snapshots in $ snapArr $ is $ S $. In baseline method, conducting $ q $ requires $ r-l+1 $ visits on numeric values in $ numArr $ and $ (r-l+1)|S| $ visits on edges in $ snapArr $. In STree, the structures of $ snapSTree $ and $ numSTree $ are the same, because the structure of STree is only related to the entire range of the array maintained by STree, and nodes where merging happens in $ snapSTree $ and $ numSTree $ (when condition in line~2 of Algorithm~\ref{alg:stree_query} is true) correspond one by one, because the ways that $ [l,r] $ in $ q $ split are the same in $ snapSTree $ and $ numSTree $. If there are $ C_n $ nodes being merged in $ numSTree $, then there are $ C_n $ nodes being merged in $ snapSTree $ and $ C_n|S| $ edges being visited. Thus, the acceleration ratio of $ snapSTree $ ($ \frac{(r-l+1)|S|}{C_n|S|} $) is equal to that of $ numSTree $ ($ \frac{r-l+1}{C_n} $).
\end{proof}
}
\begin{theorem}
	\label{thm:worst_index_efficiency}
	For a snapshot array $ snapArr $ of length $ n $ and starting from 1. If similarity of snapshots in $ snapArr $ equals 1, then for query $ q=(func,[l,r]) $ on $ snapArr $, the acceleration ratio of STree is less than or equal to 1.
\end{theorem}
\comment{
\begin{proof}
	Suppose $ l,r $ are biased timestamps. Since the similarity of snapshots in $ snapArr $ is 1, there is no edge shared by any snapshots in $ snapArr $, e.g., snapshot array in Fig.~\ref{fig:index_fail_success_example} (a). For any summarized snapshot $ S_{ij} $ of sub-array $ [snapArr[i],snapArr[i+1],...,snapArr[j]] $, we can easily get $ |S_{ij}|=\sum_{k=i}^{j}|snapArr[k]| $. For STree $ snapSTree $ built for $ snapArr $ (time range in $ q $ should be $ [l+t_{base},r+t_{base}] $ when using STree, and the proof on STable is simple so we omit it here), suppose the set of nodes being merged in conducting $ q $ is $ NS $, we can easily get $ \sum_{node \in NS}|node.snapshot|=\sum_{k=l}^{r}|snapArr[k]| $, where $ \forall node \in NS,|node.snapshot|=\sum_{k=node.timel}^{node.timer}|snapArr[k-t_{base}]| $. As a result, in query functions of baseline method and STree, we must visit the same number of edges. Considering the cost of visiting nodes in STree, the acceleration ratio of STree is less than or equal to 1. For prefix array $ preArray $ built for $ snapArr $, as in Algorithm~\ref{alg:prefix_array_query}, the number of edges being visited in conducting $ q $ is $ |preArray[r]|=\sum_{k=1}^{r}|snapArr[k]| $. Thus, the acceleration ratio of prefix array is $ \frac{\sum_{k=l}^{r}|snapArr[k]|}{\sum_{k=1}^{r}|snapArr[k]|} $.
\end{proof}
}

The above two theorems show the necessity of building index in two extreme cases. As in Theorem~\ref{thm:best_index_efficiency}, if similarity of snapshots in snapshot array equals the length of the snapshot array, the index-based solution achieves the designed acceleration ratio as they perform in range query on numeric arrays. As in Theorem~\ref{thm:worst_index_efficiency}, if similarity of snapshots in snapshot array equals 1, STree has no acceleration effect. The baseline method is the best approach to conduct any query in this case, because the number of edges in the result is exactly the number of edges being visited in the baseline method.

It is difficult to model the relationship between similarity of snapshots and acceleration ratio of the index-based solution on all possible queries precisely, because similarity of snapshots describes the overall similarity of snapshots in the snapshot array, but in specific queries, snapshots in sub-arrays specified by ranges of the queries may not show the same similarity as the overall similarity. However, it is possible to model the relationship roughly. If the similarity of snapshots in snapshot array equals 1, there is no edge shared by two snapshots and visited more than once in baseline method. If the similarity of snapshots in snapshot array equals the length of the array, all edges are shared by all snapshots. In this case, each edge will be visited repeatedly in each cycle of baseline method (line~8 in Algorithm~\ref{alg:temp_cuboid_baseline}), while the index stores summarized snapshots of some sub-arrays of the snapshot array in advance to reduce the number of repeated visits on edges. With the similarity of snapshots grows from 1 to the length of snapshot array, more edges will be shared by snapshots, making the efficiency of baseline method lower and efficiency of indexes higher. As a result, the acceleration ratio of the index grows when similarity of snapshots grows, which will be confirmed in our experiments in Section~\ref{subsec:efficiency_eva}.

The similarity of snapshots also affects the space consumption of the index. Since the elements in all snapshot arrays and the STree built on them are snapshots, we use the total number of edges in all snapshots to indicate the space consumption. For example, if we build two STrees $ STree_a $ and $ STree_b $ on both snapshot arrays in Fig.~\ref{fig:similarity} (a) and (b), the snapshot in each node of $ STree_b $ has only one edge, while the snapshot in each node of $ STree_a $ may have to store more than one edge, even if Fig.~\ref{fig:similarity} (a) and (b) have the same number of edges.

\begin{definition}[Space Consumption Ratio]
	\label{def:space_consum_ratio}
	Consider an array $ Arr $ holding numeric values or snapshots. If $ Arr $ is a snapshot array, suppose the total number of edges in $ Arr $ is $ E_a $, and the total number of edges in the index is $ E_i $. If $ Arr $ is a numeric array, $ E_a,E_i $ are the total number of numeric values in $ Arr $ and in the index respectively. The space consumption ratio of the index is $ \frac{E_i}{E_a} $.
\end{definition}
\begin{theorem}\label{thm:best_index_space_ratio}
	For two arrays of length $ n $ and starting from 1, snapshot array $ snapArr $ and numeric array $ numArr $, if similarity of snapshots in $ snapArr $ equals $ n $, then the space consumption ratios of the same index built on the two arrays are equal.
\end{theorem}
\comment{
\begin{proof}
	We mentioned that in proof of Theorem~\ref{thm:best_index_efficiency}, the structures of STree built on $ numArr $ and $ snapArr $ are the same. It is the same with the array structure of prefix array and STable. We can turn indexes into sets holding elements like: $ (SumElement,[l,r]) $, and if an index is built on $ numArr $, $ SumElement $ is the aggregation result of numeric values in $ [l,r] $, otherwise the summarized snapshot of snapshots in $ [l,r] $. For each index, suppose we build the index on $ numArr $ and $ snapArr $, named $ numIndex $ and $ snapIndex $. There must be a bijection between elements in $ numIndex $ and $ snapIndex $ that for each $ i $ in $ numIndex $, there is a corresponding $ j $ in $ snapIndex $ that $ i $ and $ j $ have the same time range $ [l,r] $, since the structures of $ numIndex $ and $ snapIndex $ are the same. It is easy to know that the space consumption ratio of $ numIndex $ is $ \frac{|numIndex|}{n} $. Since the similarity of snapshots in $ snapArr $ is $ n $, all snapshots in $ snapArr $ and $ snapIndex $ share the same edges. Suppose the summarized snapshot of snapshots in $ snapArr $ is $ S $, the space consumption ratio of $ snapIndex $ is $ \frac{|snapIndex||S|}{n|S|} $, since $ |snapIndex|=|numIndex| $, so the space consumption ratio of $ snapIndex $ and $ numIndex $ are equal.
\end{proof}
}

Similar to the acceleration ratio, the space consumption ratio of the index is also negatively affected by the decrease of similarity of snapshots. %Specifically, we discuss the space consumption ratio of STree if similarity of snapshots equals 1.
\begin{theorem}\label{thm:stree_worst_index_space_ratio}
	For a snapshot array $ snapArr $ of length $ n $ and starting from 1. If similarity of snapshots in $ snapArr $ equals 1, the space consumption ratio of STree built on $ snapArr $ is in $ (\lceil log(n) \rceil,\lceil log(n) \rceil+1] $.
\end{theorem}
\comment{
\begin{proof}
	Let $ m=\sum_{i=1}^{n}|snapArr[i]| $. If $ log(n) $ is an integer, the height of STree built on $ snapArr $ is $ log(n)+1 $. Consider the $ (log(n)+1) $-th layer of STree, all nodes on the $ (log(n)+1) $-th layer of STree are leaves. It is clear that the total number of edges in snapshots of the leaves is $ m $. For each node on the $ log(n) $-th layer, the snapshot in the node is the summarized snapshot of snapshots in the two siblings of the node. Since the similarity of snapshots in $ snapArr $ is 1, no edge is shared by snapshots in $ snapArr $, so the size of snapshot of each node on the $ log(n) $-th layer is the sum of the size of snapshots in the two siblings. Thus, the total number of edges in snapshots of nodes on the $ log(n) $-th layer is still $ m $. It is the same for nodes on each layer. Finally, the total number of edges in snapshots of all nodes in STree is $ (log(n)+1)\times m $, so the space consumption ratio of STree is $ log(n)+1 $.

	If $ log(n) $ is not an integer, then the number of leaves on the $(\lceil log(n) \rceil +1)$-th layer is less than $ n $, so there are less than $ m $ edges on the $(\lceil log(n) \rceil +1)$-th layer, but still $ m $ edges on other layers. Thus, the total number of edges in STree is in $ (\lceil log(n) \rceil\times m, (\lceil log(n) \rceil+1)\times m) $. As a result, in this case, the space consumption ratio of STree is in $ (\lceil log(n) \rceil , \lceil log(n) \rceil+1) $.
\end{proof}
}

From Theorem~\ref{thm:stree_worst_index_space_ratio}, if similarity of snapshots equals 1, we need more space to store STree, which may be $ log(n)+1 $ times the space of the original snapshot array, while only 2 times the space is needed to store STree if similarity of snapshots equals the length of the original snapshot array. %For prefix array and STable, it is impossible to derive a clear mathematical expression of the space consumption ratio related to $ n $ only. But similar to STree, with the decrease of similarity of snapshots, each snapshot in indexes has to store more edges even if the number of edges in its corresponding sub-array of the original snapshot array remains the same. We will prove the above findings in experiment of Section~\ref{subsec:efficiency_eva}.

Based on the above analysis, we can conclude that the necessity of building indexes, which can be determined by acceleration ratio and space consumption ratio of indexes, varies with the similarity of snapshots. This is the main difference of range query on a snapshot array compared to range query on a numeric array. Based on this observation, it is better to build index on the snapshot array with high similarity of snapshots. This is compatible with the implementation strategy of \kw{Temporal\enspace Graph\enspace Cube} presented in the next section, which requires precomputing views with high similarity of snapshots in their snapshot arrays.
%In particular, we use, we know that if similarity of snapshots $ s $ equals $ 1 $, baseline method is the best method and there is no need to build indexes. If $ s $ equals the length of the snapshot array, indexes achieve the designed acceleration ratio, so it is necessary to build indexes just like what we usually do in common range query problem. However, in real-world temp-multi-networks and their precomputed temp-aggre-networks, similarities of snapshots in snapshot arrays are hardly to be exactly $ n $ or $ 1 $ ($ n $ is the length of snapshot arrays). For a fixed length $ n $, with $ s $ drops from $ n $ to $ 1 $, it is more likely that the number of reduplicate edges visited in baseline method compared to the size of result snapshot decrease in any query, making baseline method more efficient and indexes more unnecessary.

%It is difficult to model the relationship between similarity of snapshots and acceleration ratio of each index on all possible queries precisely, because similarity of snapshots describes the overall similarity of snapshots in snapshot array, but in specific queries, snapshots in ranges of the queries may not show the same similarity as the overall similarity. So in Section~\ref{sec:experiment}, we mainly discuss the relationship between similarity of snapshots and the overall acceleration ratio of each index on all possible queries.[deffinition of overall?]

%\vspace{-0.2cm}
\section{Partial Materialization} \label{sec:partial_materialization}
To implement a temporal graph cube, we need precompute, or materialize some or all views in the temporal graph cube, since precomputed views can reduce the response time of OLAP queries and operations like roll-up, drill-down and slice-and-dice as we discussed in Section~\ref{sec:queries}.

%Like static graph cube, there are three possible alternatives: 1) Full materialization. 2) No materialization. 3) Partial materialization. Both the first and the second alternatives are intractable, because: 1) Full materialization means that we need to precompute all possible views, but the number of views grows exponentially with $ |dim(A_{base})| $. It is work only if $ |dim(A_{base})| $ is small enough. 2) Not precomputing any view (except $ A_{base} $) leads to long response time in almost all OLAP queries and operations.

In this work, we adopt a partial materialization strategy, i.e., we select a set of views to be precomputed in order to balance the space consumption and average response time according to the probability distribution of all possible queries. \textit{View selection} in traditional data cube scenario is a NP-hard problem \cite{karloff1999complexity}. It is also a NP-hard problem in static graph cube scenario because traditional data cube can be regarded as a special case of static graph cube \cite{zhao2011graph}. Similarly, static graph cube can also be regarded as a special case of temporal graph cube, if only one timestamp exists in the temporal graph cube. Thus, \textit{view selection} problem in temporal graph cube is also a NP-hard problem. In traditional data cube and static graph cube, \textit{view selection} problem is usually solved by heuristic sub-optimal solutions \cite{karloff1999complexity,zhao2011graph}, such as greedy algorithm and its variations \cite{morfonios2007rolap}. Those heuristic solutions always measure the effectiveness of the selected views by benefit those views bring. Here the concept of \textit{Benefit} was first introduced in \cite{harinarayan1996implementing}, we briefly review the definition of \textit{benefit} below.
\begin{definition}[Benefit of Selected Views]
	\label{def:benefit_views}
	For a sequence of selected views $ u_1,u_2,...,u_{k-1} $ in the order of being selected ($ u_1 $ is always $ A_{base} $), the benefit of the candidate view $ u $ to be selected next is $ B(u,S_{k-1}) $, i.e., benefit brought by $ u $ w.r.t. $ S_{k-1}=\{u_i|i \in [1,k-1]\}$. $ B(u,S_{k-1}) $ is defined as follows:
	\begin{enumerate}
		\item For each $ w \preceq u $, define the quantity $ B_w $ by:
		\begin{enumerate}[label={(\alph*)}]
			\item Let $ v $ be the view of least cost in $ S_{k-1} $ and $ w \preceq v $.
			\item If $ C(u)<C(v) $, then $ B_w=C(v)-C(u) $. Otherwise $ B_w=0 $.
		\end{enumerate}
		\item $ B(u,S_{k-1})=\sum_{w \preceq u}B_w $.
	\end{enumerate}
	$ C(\ast) $ returns the cost of views. In traditional data cube and static graph cube scenario, cost of views is the size of their corresponding precomputed tables or networks. The total benefit of selected view sequence is $ \sum_{i=2}^{k}B(u_i,S_{i-1}) $.
\end{definition}

In greedy algorithm, among all candidate views, the view $ u $ with the largest $ B(u,S_{k-1}) $ is selected to be $ u_k $. For the total benefit of view sequence generated by each heuristic solution, the closer to the benefit of the optimal view sequence, the more effective the solution is.

In Definition~\ref{def:benefit_views}, the cost of views is used in representation of the benefit, because the cost of views is also the time complexity or cost of queries in data cube and static graph cube. However, cost of views in temporal graph cube (space consumption of the corresponding temporal aggregate networks of views) cannot be used as the cost of temporal cuboid queries. First, in Definition~\ref{def:benefit_views}, $ C(u) $ cannot be the cost of temporal cuboid query $ Q=(w,[l,r]) $ if we conduct $ Q $ on $ u $. It is similar to $ C(v) $. The reason is that there is a specified time range $ [l,r] $ in $ Q $, which does not exist in any query of traditional data cube or static graph cube. In implementation of temporal graph cube, we know nothing about the specified time ranges in all possible queries. Second, if we use an expected range $ [l_e,r_e] $ as the representative of all ranges in all queries according to the probability distribution of specified ranges in all queries, we may be able to get the time complexity of conducting $ Q=(w,[l_e,r_e]) $ on $ u $ using the baseline method by precomputing the total size of snapshots in $ [l_e,r_e] $ and the size of summarized snapshot of snapshots in $ [l_e,r_e] $. Only in this way can we get a relatively accurate benefit for each $ u $. Third, the above precomputing process is very costly, and it is based on conducting all queries with the baseline method. %In Section~\ref{sec:effec_of_indexes} and \ref{sec:experiment}, we show the effectiveness of indexes in specific cases, so the cost of temporal cuboid queries is determined by the indexes. However, it is more costly to precompute the time complexity of conducting $ Q=(w,[l_e,r_e]) $ on $ u $ using indexes of $ u $, not to mention that timestamps will be added into temporal networks constantly, making that we cannot find a stable $ [l_e,r_e] $.

As a result, the greedy algorithm and its variations are not suitable for view selection problem in temporal graph cube. In this paper, we adopt a much simpler solution to select views to be precomputed, \kw{MinLevel}, which was originally introduced in \cite{zhao2011graph}. The idea of \kw{MinLevel} is simple: users are more willing to query with small number of dimensions, i.e., $ |dim(A)| $ is small in $ Q=(A,[l,r]) $. In \kw{MinLevel}, view $ A $ where $ |dim(A)|=l_0 $ is in the first batch of views to be selected ($ l_0 $ is an empirical value). If all the views with $ l_0 $ dimensions have been selected and the number of selected views or the total size needed for precomputing the selected views has not reach the limit, then we continue to select views with $ l_0+1 $ dimensions until we select enough number or size of views. In this paper, we select $ k $ views to be precomputed and $ l_0=1 $.

Using \kw{MinLevel}, we precompute views with small number of dimensions; and these views also have high similarity of snapshots in their snapshot arrays (as shown in Table~\ref{tab:materialized_view}). In processing temporal cuboid query $ Q=(A',[l,r]) $, if $ A' $ is not precomputed and $ l_0=1 $, only $ A_{base} $ can be used to process the query $ Q $. If $ l_0>1 $ and $ |dim(A')|<l_0 $, then there may be some precomputed views $ \{A_1'',A_2'',...\} $ where $ |dim(A_i'')|=l_0 $ can be used to process $ Q $. In this case, choosing an arbitrary $ A_i'' $ to process $ Q $ is efficient enough because the size of $ A_i'' $ and its index is usually small since $ l_0 $ is a small value.

\section{Experiments} \label{sec:experiment}
%In this section, we conduct extensive experiments to evaluate the effectiveness and efficiency of the temporal graph cube model.

\subsection{Datasets} \label{subsec:datasets}
We conduct experiments on two real-world temp-multi-networks: DBLP (\url{https://dblp.org/xml}) and IMDB (\url{https://www.imdb.com/interfaces}), to evaluate the effectiveness and efficiency of the temporal graph cube respectively. Below we introduce the details of the two datasets.

\begin{table}[t!]%\vspace*{-0.3cm}
	\scriptsize
	%\small
	\centering
	\caption{Basic information of datasets} \vspace*{-0.2cm} \label{tab:datasets}
	\begin{tabular}{c c c c c}
		\toprule
		\bf Dataset & $|\Vr|$ & $|\Er|$ & $ t_{end} $ & Time scale \cr %\hline %\hline
		\midrule
		\kw{DBLP} & 1,242,883 & 9,532,533 & 85 & year \cr %\hline
		\kw{IMDB} & 3,497,300 & 39,682,231 & 151 & year  \cr %\hline
		\bottomrule
	\end{tabular}
	\vspace*{-0.2cm}
\end{table}

\stitle{DBLP.} The DBLP datasets covers $ 9 $ areas in computer science: CA (computer architecture), CN (computer network), NS (network security), SE (software engineering), DB (database), TH (computer science theory), CG (computer graphics), AI (artificial intelligence) and HI (human-computer interaction). Table~\ref{tab:datasets} illustrates the statistic information of this dataset. For each vertex (author), there are three dimensions of information: \kw{Name}, \kw{Area}, \kw{Productivity}. Since we classify all publications into $ 9 $ areas, \kw{Area} of an author is one of the $ 9 $ areas where he or she has the most publications ever, which can be regarded as the representative of the focus of his or her papers. For \kw{Productivity}, we discrete the number of publications per year of an author into four different buckets, which is shown in Table~\ref{tab:productivity}. The number of publications per year of an author equals the total number of publications of the author divided by $ 2022-y $, $ y $ is the first year when the author had his or her first publication. \kw{Productivity} specifies the ability of producing academic papers of an author. Each temporal edge represents that two authors coauthored a paper at a certain time (year).

%This dataset is extracted from DBLP computer science bibliography data which is downloaded in September, 2021. Specifically, we extract publication information of all conferences and journals listed in \textit{Catalogue of international academic conferences and periodicals recommended by China Computer Federation} (\url{https://www.ccf.org.cn/ccf/contentcore/resource/download?ID=99185}) except conferences and journals which focus on cross field since we can not classify them into AI, DB or other specific fields. We gain $ 545 $ conferences and journals in total, covering $ 9 $ fields in computer science: CA(computer architecture), CN(computer network), NS(network security), SE(software engineering), DB(database), TH(computer science theory), CG(computer graphics), AI(artificial intelligence) and HI(human-computer interaction). Table~\ref{tab:datasets} illuminates the basic information of temp-multi-network based on DBLP dataset. For each vertex(author), there are three dimensions of information: \kw{Name}, \kw{Area}, \kw{Productivity}. Since we classify all publications into $ 9 $ areas, \kw{Area} of an author is one of the $ 9 $ areas where he or she has the most publications ever, which can be regarded as the representative of focus of his or her works. For \kw{Productivity}, we discrete the number of publications per year of an author into four different buckets, which is shown in Table~\ref{tab:productivity}. The number of publications per year of an author equals the total number of publications of the author divided by $ 2022-y $, $ y $ is the first year when the author had his or her first publication. \kw{Productivity} specifies the ability of producing academic papers of an author.
\begin{table}[t!]%\vspace*{-0.3cm}
	\scriptsize
	%\small
	\centering
	\caption{Discretization of publication number per year} \vspace*{-0.2cm} \label{tab:productivity}
	\begin{tabular}{c c}
		\toprule
		\bf Productivity & Publication number per year $ x $ \cr %\hline %\hline
		\midrule
		Excellent & $ 8<x $ \cr %\hline
		Good & $ 3 < x \leq 8 $  \cr %\hline
		Fair & $ 1 < x \leq 3 $  \cr %\hline
		Poor & $ x \leq 1 $  \cr %\hline
		\bottomrule
	\end{tabular}
	\vspace*{-0.4cm}
\end{table}

%Note that there is no numeric attribute in dimensions of vertices of temp-multi-network in \kw{DBLP}, so we can only specify $ f_v= $ COUNT($\ast$). It is not important because the processes of aggregating on vertices are the same when $ f_v $ varies. Temporal edges in \kw{DBLP} also have no numeric attribute, so $ f_e $ can only be COUNT($\ast$). Fortunately, there are numeric attributes in temporal edges of the second dataset.

\stitle{IMDB.} The IMDB dataset contains various types of works like movie, short, video, etc. Each work has the following attributes: \kw{tile}, \kw{time}, \kw{titleType}, \kw{genre}, \kw{isAdult}, \kw{rating}, \kw{voteNum}. \kw{rating} is a numeric attribute, representing the average rating for the work from users. \kw{voteNum} is the number of votes the work has received. There are some other files about principals of each work, which will be used as vertices of the temporal network. In summary, we extract several dimensions for each principal: \kw{Name}, \kw{Pro}, \kw{Field}, \kw{Genre}, \kw{isAdult}, \kw{Averating}, \kw{Hotness}. \kw{Pro} is the primary profession of a person, e.g., director, actor, producer, soundtrack, etc., which can be directly extracted from certain files. \kw{Field} specifies the field that a person belongs to, e.g., movie, short, video, etc., which is obtained by counting the types of the works that the person participates in and choosing the type having the biggest count. \kw{Genre} denotes the genre of works that a person usually participates in, which is obtained by the same process in obtaining \kw{Field}. \kw{IsAdult} represents if a person mainly works for adult works or not. \kw{Averating} specifies the average rating of works that a person participates in, and it shows the average quality of works related to the person. \kw{Hotness} denotes the hotness of works a person usually participates in, which is expressed by the average vote number of works related to the person. Both \kw{Averating} and \kw{Hotness} are discretized as shown in Table~\ref{tab:attr}.

\begin{table}[t!]%\vspace*{-0.3cm}
	\scriptsize
	%\small
	\centering
	\caption{Attributed information of IMDB} \vspace*{-0.2cm} \label{tab:attr}
	\begin{tabular}{c c | c c}
		\toprule
		\bf Averating & \kw{Averating} value $ x $ & \bf Hotness & Average votes of works $ w $ \cr %\hline %\hline
		\midrule
		5 & $ 8 \leq x $ & hot & $ 100,000 \leq w $\cr %\hline
		4 & $ 6 \leq x < 8 $  &popular & $ 10,000 \leq w < 100,000 $ \cr %\hline
		3 & $ 4 \leq x < 6 $ & fair & $ 1,000 \leq w < 10,000 $ \cr %\hline
		2 & $ 2 \leq x < 4 $ & cold & $ w < 1,000 $  \cr %\hline
		1 & $ x < 2 $  &\cr %\hline
		\bottomrule
	\end{tabular}
	\vspace*{-0.3cm}
\end{table}

\comment{
\begin{table}[t!]%\vspace*{-0.3cm}
	%\scriptsize
	\small
	\centering
	\caption{Discretization of average rating} \vspace*{-0.2cm} \label{tab:averating}
	\begin{tabular}{c c}
		\toprule
		\bf Averating & \kw{Averating} value $ x $ \cr %\hline %\hline
		\midrule
		5 & $ 8 \leq x $ \cr %\hline
		4 & $ 6 \leq x < 8 $  \cr %\hline
		3 & $ 4 \leq x < 6 $  \cr %\hline
		2 & $ 2 \leq x < 4 $  \cr %\hline
		1 & $ x < 2 $  \cr %\hline
		\bottomrule
	\end{tabular}
	\vspace*{-0.3cm}
\end{table}
\begin{table}[t!]%\vspace*{-0.3cm}
	%\scriptsize
	\small
	\centering
	\caption{Discretization of average vote number} \vspace*{-0.2cm} \label{tab:hotness}
	\begin{tabular}{c c}
		\toprule
		\bf Hotness & Average vote number of works $ x $ \cr %\hline %\hline
		\midrule
		hot & $ 100,000 \leq x $ \cr %\hline
		popular & $ 10,000 \leq x < 100,000 $  \cr %\hline
		fair & $ 1,000 \leq x < 10,000 $  \cr %\hline
		cold & $ x < 1,000 $  \cr %\hline
		\bottomrule
	\end{tabular}
	\vspace*{-0.4cm}
\end{table}
}

We refer to each person (each principal of the work) as a vertex in the temp-multi-network, and two vertices can form a temporal edge if they work together for the same work. The timestamp of the temporal edge is the release time of the work, and the numeric attribute of the temporal edge is the average rating of the work. The statistical information of temp-multi-network in IMDB is shown in Table~\ref{tab:datasets}.

\subsection{Effectiveness Evaluation} \label{subsec:effectiveness_eva}
In this section, we evaluate the effectiveness of temporal graph cube as a decision-support tool on \kw{DBLP}. First, we conduct a series of temporal cuboid queries $ Q_1=((\kw{Area}),[2001,2006]) $, $ Q_2=((\kw{Area}),[2006,2011]) $, $ Q_3=((\kw{Area}),[2011,2016]) $, $ Q_4=((\kw{Area}),[2016,2021]) $ on \kw{DBLP}. Aggregation functions upon vertices and edges are both COUNT($\ast$). The network structures of $ Q_1 $-$ Q_4 $ are shown in Fig.~\ref{fig:dblp_area}, illustrating the co-authorship patterns between authors grouped by different areas in the specified time ranges. For simplicity, in Fig.~\ref{fig:dblp_area} (a) we omit those co-authorships with COUNT($\ast$) values less than 10,000, which are also omitted in Fig.~\ref{fig:dblp_area} (b)-(d), regardless of their COUNT($\ast$) values.

\comment{
\begin{table}[t!]%\vspace*{-0.3cm}
	\scriptsize
%	\small
	\centering
	\caption{Vertex table of $ Q_1-Q_4 $} \vspace*{-0.2cm} \label{tab:vertex_table_dblp_area}
	\begin{tabular}{c c| c c| c c}
		\toprule
		Area & COUNT($\ast$)  & Area & COUNT($\ast$) &Area & COUNT($\ast$)\cr %\hline %\hline
		\midrule
		CA & 228,429 & CN & 156,329&NS & 60,880 \cr %\hline
		 SE & 114,727  & DB & 102,931& TH & 109,293\cr %\hline
		CG & 156,982 & AI & 256,048 &HI & 57,264\cr %\hline
		\bottomrule
	\end{tabular}
	\vspace*{-0.4cm}
\end{table}
}

\comment{
\begin{table}[t!]%\vspace*{-0.3cm}
	%\scriptsize
	\small
	\centering
	\caption{Vertex table of $ Q_1-Q_4 $} \vspace*{-0.2cm} \label{tab:vertex_table_dblp_area}
	\begin{tabular}{c c}
		\toprule
		Area & COUNT($\ast$) \cr %\hline %\hline
		\midrule
		CA & 228,429 \cr %\hline
		CN & 156,329  \cr %\hline
		NS & 60,880  \cr %\hline
		SE & 114,727  \cr %\hline
		DB & 102,931  \cr %\hline
		TH & 109,293  \cr %\hline
		CG & 156,982  \cr %\hline
		AI & 256,048 \cr %\hline
		HI & 57,264  \cr %\hline
		\bottomrule
	\end{tabular}
	\vspace*{-0.4cm}
\end{table}
}

\begin{figure*}[t!]
	\begin{center}
		\begin{tabular}[t]{c}\hspace*{-0.3cm}
			\subfigure[{\scriptsize $ Q_1 $}]{
				\includegraphics[width=0.23\textwidth]{fig/exp/visio_area_2001_2006.pdf}
			}
			\hspace*{-0.3cm}
			\subfigure[{\scriptsize $ Q_2 $}]{
				\includegraphics[width=0.23\textwidth]{fig/exp/visio_area_2006_2011.pdf}
			}
			\hspace*{-0.3cm}
			%\vspace*{-0.3cm}\\\hspace*{-0.3cm}
			\subfigure[{\scriptsize $ Q_3 $}]{
				\includegraphics[width=0.23\textwidth]{fig/exp/visio_area_2011_2016.pdf}
			}
			\hspace*{-0.3cm}
			\subfigure[{\scriptsize $ Q_4 $}]{
				\includegraphics[width=0.23\textwidth]{fig/exp/visio_area_2016_2021.pdf}
			}
		\end{tabular}
	\end{center}
	\vspace*{-0.4cm}
	\caption{Network structures in the results of queries $ Q_1-Q_4 $}
	\vspace*{-0.4cm}
	\label{fig:dblp_area}
\end{figure*}
\comment{
The results are shown in Table~\ref{tab:vertex_table_dblp_area} and Fig.~\ref{fig:dblp_area}. The network structures of $ Q_1 $-$ Q_4 $ are shown in Fig.~\ref{fig:dblp_area}, illustrating the co-authorship patterns between authors grouped by different areas in the specified time ranges. For simplicity, in Fig.~\ref{fig:dblp_area} (a) we omit those co-authorships with COUNT($\ast$) values less than 10,000, which are also omitted in Fig.~\ref{fig:dblp_area} (b)-(d), regardless of their COUNT($\ast$) values.
}

Some interesting observations can be obtained in these results. For example, authors in each area co-author most with authors in the same area even in different time ranges. We can clearly see that in recent 20 years, the number of co-authorship between each pair of areas increases over time. We can also find that in recent 20 years researchers in \kw{AI} co-authored with researchers in \kw{CG} most. This is because there are many problems in computer graphics like automatic modeling, image processing and digital photography which can be solved by AI technologies. More interestingly, in $ [2001,2006] $, researchers in \kw{TH} co-authored most with researchers in \kw{CA}, but with the time evolves, researchers in \kw{TH} are more willing to co-author with researchers in \kw{AI}. The reason may be that theoretical research on AI becomes more and more important with the wide applications of AI in recent years. %The above findings can also be obtained from uncut results.
%[ns and cn,ca and ai;ai and cg;th and ai,ca]

In each period we can zoom into a more fine-grained view by conducting a drill-down operation. For example, for $ Q_4=((\kw{Area}),[2016,2021]) $, drill-down can be a query $ Q_4'=((\kw{Area},\kw{Productivity}),[2016,2021]) $. The network structure of $ Q_4' $ is shown in Fig.~\ref{fig:dblp_area_pro_2016_2021}.
\begin{figure}
	\begin{center}
		\includegraphics[width=0.8\columnwidth]{fig/exp/visio_area_pro_2016_2021.pdf}
	\end{center}

	\vspace*{-0.6cm}
	\caption{Network structure in the result of $ Q_4' $}
	\vspace*{-0.4cm}
	\label{fig:dblp_area_pro_2016_2021}
\end{figure}
For simplicity, we drop edges with weight less than 10,000 and we only keep vertices related to areas in $ \{\kw{AI},\kw{DB}\} $ (it can be regarded as a slice-and-dice operation). In Fig.~\ref{fig:dblp_area} (d), there are 117,338 co-authorships between researchers of \kw{AI} and \kw{DB} in $ [2016,2021] $. In fine-grained view of Fig.~\ref{fig:dblp_area_pro_2016_2021}, we can see that the most co-authorships belong to researchers of poor and fair productivity in \kw{AI} and \kw{DB}.

We then examine the effectiveness of temporal crossboid query.
\begin{figure*}[t!]
	\begin{center}
		\begin{tabular}[t]{c}\hspace*{-0.3cm}
			\subfigure[{\scriptsize $ Q_{cross1} $}]{
				\includegraphics[width=0.25\textwidth]{fig/exp/dblp_cross_name_area_2001_2006.pdf}
			}
			\hspace*{-0.3cm}
			\subfigure[{\scriptsize $ Q_{cross2} $}]{
				\includegraphics[width=0.25\textwidth]{fig/exp/dblp_cross_name_area_2006_2011.pdf}
			}
			\hspace*{-0.3cm}
			%\vspace*{-0.3cm}\\\hspace*{-0.3cm}
			\subfigure[{\scriptsize $ Q_{cross3} $}]{
				\includegraphics[width=0.25\textwidth]{fig/exp/dblp_cross_name_area_2011_2016.pdf}
			}
			\hspace*{-0.3cm}
			\subfigure[{\scriptsize $ Q_{cross4} $}]{
				\includegraphics[width=0.25\textwidth]{fig/exp/dblp_cross_name_area_2016_2021.pdf}
			}
		\end{tabular}
	\end{center}
	\vspace*{-0.4cm}
	\caption{Network structures in the results of $ Q_{cross1}-Q_{cross4} $}
	\vspace*{-0.4cm}
	\label{fig:dblp_cross}
\end{figure*}
Fig.~\ref{fig:dblp_cross} shows the results of a series of temporal crossboid queries:
\begin{center}
	$ Q_{cross1}=((\kw{Name}),(\kw{Area}),[2001,2006]) $,\\$ Q_{cross2}=((\kw{Name}),(\kw{Area}),[2006,2011]) $,\\$ Q_{cross3}=((\kw{Name}),(\kw{Area}),[2011,2016]) $,\\$ Q_{cross4}=((\kw{Name}),(\kw{Area}),[2016,2021]) $.
\end{center}
The above queries focus on the cross interaction between \kw{Name} and \kw{Area}, i.e., the co-authorship with each area for each researcher. We further slice-and-dice the results on \kw{Name} to show the results related to ``Jiawei Han". We can find that in recent 20 years, Jiawei cooperated with researchers in \kw{DB} most. Meanwhile, in recent 10 years he has more and more cooperations with researchers in \kw{AI}, which can be ignored compared to cooperations with researchers in \kw{DB} in early 10 years.

\subsection{Efficiency Evaluation} \label{subsec:efficiency_eva}
%In this section we mainly evaluate the efficiency of temporal graph cube on \kw{IMDB}, especially the efficiency of indexes.

\stitle{Exp-1: Performance of the index-based method.} Here we aim to evaluate how much the index-based solution can accelerate the merging operation of snapshots in time ranges while processing temporal cuboid queries, compared to the baseline algorithm (Algorithm~\ref{alg:temp_cuboid_baseline}). As we analyzed before, the average acceleration ratio of the index-based solution can vary if the similarity of snapshots in temp-multi-networks changes. In this experiment, we mainly use \kw{IMDB} dataset, since vertices in \kw{IMDB} dataset have 7 dimensions and $ 2^7 $ views can be obtained. For convenience, we only materialize views in Table~\ref{tab:materialized_view}, among which we only materialize one view containing dimension \kw{Name}, because \kw{Names} of two persons are hardly the same in \kw{IMDB}, and thus \kw{Name} can be approximately regarded as a primary key and having only one view containing dimension \kw{Name} is enough.
\begin{table}[t!]%\vspace*{-0.3cm}
	\scriptsize
	%\small
	\centering
	\caption{Materialized views} \vspace*{-0.2cm} \label{tab:materialized_view}
	\begin{tabular}{c c c}
		\toprule
		\bf No. & Materialized Views & Similarity of Snapshots \cr %\hline %\hline
		\midrule
		1 & \kw{Pro} & 53.48 \cr %\hline
		\midrule
		2 & \kw{Pro}, \kw{Field} & 18.16 \cr %\hline
		\midrule
		3 & \kw{Pro}, \kw{Field}, \kw{Genre} & 6.15 \cr %\hline
		\midrule
		4 & \makecell[c]{\kw{Pro}, \kw{Field}, \kw{Genre},\\\kw{isAdult}}  & 6.07 \cr %\hline
		\midrule
		5 & \makecell[c]{\kw{Pro}, \kw{Field}, \kw{Genre},\\\kw{isAdult}, \kw{Averating}} & 4.70 \cr %\hline
		\midrule
		6 & \makecell[c]{\kw{Pro}, \kw{Field}, \kw{Genre},\\\kw{isAdult}, \kw{Averating}, \kw{Hotness}} & 3.97 \cr %\hline
		\midrule
		7 & \makecell[c]{\kw{Name}, \kw{Pro}, \kw{Field}, \kw{Genre},\\\kw{isAdult}, \kw{Averating}, \kw{Hotness}} & 1.12 \cr %\hline
		\bottomrule
	\end{tabular}
	\vspace*{-0.4cm}
\end{table}

We conduct a series of temporal cuboid queries on materialized views to examine the efficiency of the index-based method (conducting temporal cuboid queries on materialized views are all about merging snapshots in time ranges as we analyzed in Section~\ref{subsec:cuboid}). We set a series of time ranges to be specified in the queries, which are shown in Table~\ref{tab:time_ranges_set}.
\begin{table}[t!]%\vspace*{-0.3cm}
	\scriptsize
%	\small
	\centering
	\caption{Time ranges of queries} \vspace*{-0.2cm} \label{tab:time_ranges_set}
	\begin{tabular}{c c}
		\toprule
		\bf Length & Time ranges \cr %\hline %\hline
		\midrule
		4 & \makecell[c]{[1878,1880],[1891,1895],[1906,1910],\\{[1921,1925]},[1936,1940],[1951,1955],\\{[1966,1970]},[1981,1985],[1996,2000],[2011,2015]} \cr %\hline
		\midrule
		10 & \makecell[c]{[1878,1883],[1888,1898],[1903,1913],\\{[1918,1928]},[1933,1943],[1948,1958],\\{[1963,1973]},[1978,1988],[1993,2003],[2008,2018]} \cr %\hline
		\midrule
		20 & \makecell[c]{[1878,1888],[1883,1903],[1898,1918],\\{[1913,1933]},[1928,1948],[1943,1963],\\{[1958,1978]},[1973,1993],[1988,2008],[2003,2023]} \cr %\hline
		\midrule
		50 & \makecell[c]{[1878,1903],[1878,1918],[1883,1933],\\{[1898,1948]},[1913,1963],[1928,1978],\\{[1943,1993]},[1958,2008],[1973,2023],[1988,2028]} \cr %\hline
		\midrule
		100 & \makecell[c]{[1878,1928],[1878,1943],[1878,1958],\\{[1878,1973]},[1888,1988],[1903,2003],\\{[1918,2018]},[1933,2028],[1948,2028],[1963,2028]} \cr %\hline
		\bottomrule
	\end{tabular}
	\vspace*{-0.4cm}
\end{table}
The earliest and the latest timestamps in \imdb are 1878 and 2028 respectively. We set 5 groups of time ranges of different length: 4, 10, 20, 50, 100. For each length, we set 10 ranges which are evenly distributed in $ [1878,2028] $ as shown in Table~\ref{tab:time_ranges_set}. Ranges at two ends in each length group may be truncated since we try to keep each time range in $ [1878,2028] $. Specifically, we set a series of queries $ QS_1,QS_2,...,QS_7 $, where $ QS_i $ is a set of queries specifying the No.$ i $ materialized view in Table~\ref{tab:materialized_view} and covering all time ranges of all lengths in Table~\ref{tab:time_ranges_set}, i.e., $ QS_1=\{((Pro),[1878,1880]),...,((Pro),[2011,2015]),\\((Pro),[1878,1883]),...,((Pro),[2008,2018]),...,\\((Pro),[1878,1928]),...,((Pro),[1963,2028])\} $.

\comment{
\begin{table}[t!]%\vspace*{-0.3cm}
	\scriptsize
	%\small
	\centering
	\caption{Performance of the index-based solution} \vspace*{-0.2cm} \label{tab:effi_prearray}
	\begin{tabular}{c c c c c| c c c}
		\toprule
		\makecell[c]{Views\\No.}& $ s $ & \makecell[c]{baseline\\(ms)} &\makecell[c]{STree\\(ms)}&\makecell[c]{acce-ratio\\(ave)} & \makecell[c]{Original\\view size} &  \makecell[c]{STree\\size}&\makecell[c]{STree\\ratio}\cr %\hline %\hline
		\midrule
		1&53.48&16,960 &3,960 &3.45 &41,448 &93,975 &2.27 \cr
		\midrule
		2&18.16&172,614 &57,637 &2.32 &396,755 &1,077,456 &2.72\cr
		\midrule
		3&6.15&279,684 &144,849 &1.59&3,738,125 &13,788,570 &3.69\cr
		\midrule
		4&6.07&285,623 &147,565 &1.59&3,758,885 &13,918,066 &3.70 \cr
		\midrule
		5&4.70&515,607 &293,546 &1.50&5,467,826 &22,063,352 &4.04\cr
		\midrule
		6&3.97&896,386 &550,376 &1.40&8,304,421 &35,837,987 &4.32\cr
		\midrule
		7&1.12&6,719,417 &6,366,660 &1.05&37,096,632 &285,623,583 &7.70\cr
		\bottomrule
	\end{tabular}
	\vspace*{-0.4cm}
\end{table}

\begin{table}[t!]%\vspace*{-0.3cm}
	\scriptsize
	%\small
	\centering
	\caption{Performance of the index-based solution} \vspace*{-0.2cm} \label{tab:effi_prearray}
	\begin{tabular}{c c c c c| c c c}
		\toprule
		\makecell[c]{Views\\No.}& $ s $ & \makecell[c]{baseline\\(ms)} &\makecell[c]{STree\\(ms)}&\makecell[c]{acce-ratio\\(ave)} & \makecell[c]{Original\\view size} &  \makecell[c]{STree\\size}&\makecell[c]{STree\\ratio}\cr %\hline %\hline
		\midrule
		1&53.48&16,960 &3,960 &3.45 &41KB &94KB &2.27 \cr
		\midrule
		2&18.16&172,614 &57,637 &2.32 &397KB &1.1MB &2.72\cr
		\midrule
		3&6.15&279,684 &144,849 &1.59&3.7MB &13.8MB &3.69\cr
		\midrule
		4&6.07&285,623 &147,565 &1.59&3.8MB &13.9MB &3.70 \cr
		\midrule
		5&4.70&515,607 &293,546 &1.50&5.4MB &22.1MB &4.04\cr
		\midrule
		6&3.97&896,386 &550,376 &1.40&8.3MB &35.8MB &4.32\cr
		\midrule
		7&1.12&6,719,417 &6,366,660 &1.05&37.1MB &285.6MB &7.70\cr
		\bottomrule
	\end{tabular}
	\vspace*{-0.4cm}
\end{table}
}

\begin{table}[t!]%\vspace*{-0.3cm}
	\scriptsize
	%\small
	\centering
	\caption{Performance of the index-based solution (K=1,000, M=1,000,000)} \vspace*{-0.2cm} \label{tab:effi_index}
	\begin{tabular}{c c c c c c c c}
		\toprule
		\makecell[c]{View\\No.}& $ s $ & \makecell[c]{Baseline\\(sec.)} &\makecell[c]{STree\\(sec.)}&\makecell[c]{acce-ratio\\(ave)} & \makecell[c]{View\\ size} &  \makecell[c]{STree\\size}&\makecell[c]{Space\\ratio}\cr %\hline %\hline
		\midrule
		1&53.48&17 &4 &4.25 &41K &94K &2.29 \cr
		\midrule
		2&18.16&173 &58 &2.98 &397K &1.1M &2.77\cr
		\midrule
		3&6.15&280 &145 &1.93&3.7M &13.8M &3.72\cr
		\midrule
		4&6.07&286 &148 &1.93&3.7M &13.9M &3.76 \cr
		\midrule
		5&4.70&516 &294 &1.76&5.4M &22.1M &4.09\cr
		\midrule
		6&3.97&896 &550 &1.63&8.3M &35.8M &4.31\cr
		\midrule
		7&1.12&6,719 &6,367 &1.06&37.1M &285.6M &7.70\cr
		\bottomrule
	\end{tabular}
	\vspace*{-0.4cm}
\end{table}

We set $ f_e= $ MAX($\ast$) and use the queries in $ QS_1,\cdots,QS_7 $ to test the efficiency of our index-based algorithm. The results are shown in Table~\ref{tab:effi_index}. Similar results can also be observed for the other aggregation functions ($ f_e= $ COUNT($\ast$), $ f_e= $ SUM($\ast$), and $ f_e= $ MIN($\ast$)). In Table~\ref{tab:effi_index}, \kw{View No.} denotes the No. of materialized views in Table~\ref{tab:materialized_view}, and $ s $ is the similarity of snapshots. The third and the fourth columns are time used to process all the queries on each materialized view using the baseline method and the index-based algorithm respectively. For example, in the first line, processing all queries in $ QS_1 $ takes $ 17s $ using the baseline method, but consumes $ 4s $ using the segment-tree index based algorithm. The \kw{acce-ratio(ave)} is the average acceleration ratio of the index-based algorithm on each query, compared to the baseline algorithm. In most cases, the index-based algorithm can accelerate merging snapshots in time ranges in conducting queries. However, the effect of acceleration varies with $ s $. In the No.1 view, where $s$ is the largest, we can see that the index-based solution achieves the best average acceleration ratio. We can observe that the average acceleration ratio of the index-based solution drops if $ s $ drops in general, which confirms our analysis in Section~\ref{sec:effec_of_indexes}.

Table~\ref{tab:effi_index} also shows the space usage of the index-based solution (6th-8th columns). As can be seen, the size of the segment-tree based index is only several times larger than the original size of the views. For example, in the first line, the original view size is 41K, while our index-based solution takes only 94K space, with 2.27\kw{x} more space usage. Also, we can see that with $s$ increasing, the space usage of the index-based solution decreases. These results demonstrate that our segment-tree based index structure is very space-efficient when $s$ is relatively large. However, when $s$ is small, e.g., near to 1, the space overhead of our index-based solution is high. Moreover, when $s$ is near to 1, the average acceleration ratio is also near to 1 (i.e., the index-based solution is only slightly better than the baseline method). These results indicate that when $s$ is very small, there is no need to build an index.

\stitle{Exp-2: Updating performance of the index-based solution.} Here we evaluate the updating performance of our index-based solution. We divide all temporal edges in a materialized view into 10 batches equally according to the order of timestamps, e.g., the first batch of temporal edges are edges with the smallest timestamps, and they are added into the index one by one following the order of timestamps. When edges in a single batch are added into the index, we record both the time and space consumption of adding edges in the batch. The results are shown in Fig.~\ref{fig:index_update}. From Fig.~\ref{fig:index_update}(a), we can see that with the number of batch increasing, the time consumption of the index-updating algorithm increases. These results are consistent with our analysis in Section~\ref{subsec:segment_tree}. Moreover, we can observe that for a large $s$, the time cost of our index-updating algorithm is low, while for a small $s$, the cost is often high. The reason could be that updating STree involves copying snapshot, i.e., snapshot in root, which maintains all snapshots in snapshot array, and thus gets larger if $ s $ gets smaller. As shown in Fig.~\ref{fig:index_update}(b), the space consumption of the index-updating algorithm is linear with respect to the number of batches, indicating that our algorithm is space-efficient. Likewise, we can observe that the algorithm takes more space for a smaller $s$. These results further confirm our analysis in Section~\ref{subsec:segment_tree}.

\begin{figure}[t!]
	\begin{center}
		\begin{tabular}[t]{c}\hspace*{-0.3cm}
		%	\subfigure[{\scriptsize Prefix Array}]{
%				\includegraphics[width=0.25\textwidth]{fig/exp/index_update/index_update_single_a.pdf}
%			}
%			\hspace*{-0.3cm}
%			\subfigure[{\scriptsize STable}]{
%				\includegraphics[width=0.25\textwidth]{fig/exp/index_update/index_update_single_b.pdf}
%			}
%			\hspace*{-0.3cm}
%			%\vspace*{-0.3cm}\\\hspace*{-0.3cm}
			\subfigure[{\scriptsize Time consumption}]{
				\includegraphics[width=0.23\textwidth]{fig/exp/index_update/index_update_single_c.pdf}
			}
	%		\\
%			\hspace*{-0.3cm}
%			\subfigure[{\scriptsize Prefix Array}]{
%				\includegraphics[width=0.25\textwidth]{fig/exp/index_update/index_update_single_d.pdf}
%			}
%			\hspace*{-0.3cm}
%			\subfigure[{\scriptsize STable}]{
%				\includegraphics[width=0.25\textwidth]{fig/exp/index_update/index_update_single_e.pdf}
%			}
			\hspace*{-0.3cm}
			\subfigure[{\scriptsize Space usage}]{
				\includegraphics[width=0.23\textwidth]{fig/exp/index_update/index_update_single_f.pdf}
			}
		\end{tabular}
	\end{center}
	\vspace*{-0.5cm}
	\caption{The updating performance of the index-based solution}
	\vspace*{-0.4cm}
	\label{fig:index_update}
\end{figure}

\section{Related Work} \label{sec:related_work}
Our work extends data warehouse and OLAP techniques to temporal multidimensional networks. There are many works applying data warehouse and OLAP to other data types, such as stream data \cite{han2005stream}, spatio-temporal data \cite{gomez2009survey}, sequence data \cite{lo2008olap,liu2011cube}, and text data \cite{lin2008text}. Except the traditional relational data, Dehdouh et al. \cite{dehdouh2014columnar} tried to compute data cubes from column-oriented NoSQL data. As for graph data, except \cite{zhao2011graph}, some other works focus on heterogeneous networks \cite{yin2012hmgraph,wang2015tsmh}, but none of them focus on temporal multidimensional networks.

Our work is also related to graph summarization and analysis. For static graphs, there are some representative works, including graph compression with MDL (Minimum Description Length) principle \cite{navlakha2008graph}, attributed graph compression \cite{wu2014graph} and graph clustering based on vertices partitioning \cite{zhou2009graph}. Recently, there exist several studies on static graph summarization, such as summarizing directed acyclic graph (DAG) \cite{zhu2020top}, summarizing multi-relation graph \cite{ke2022multi} where multiple edges of different types may exist between any pair of vertices, and DPGS model \cite{zhou2021dpgs}, which can preserve properties like graph spectrum and the authorities and hubnesses of vertices especially in highly degree-skewed graphs while reconstructing graph. For temporal graph and dynamic graph, TimeCrunch \cite{shah2015timecrunch} summarizes a large dynamic graph with a set of important temporal structures using MDL, such as ranged full clique, periodic bipartite core, oneshot star, etc. \cite{fernandes2018dynamic,tsalouchidou2018scalable} investigate the problem of summarizing dynamic graph in real time, which use a sliding window of fixed length to summarize the latest snapshots. When a new snapshot is generated, the window slides forward, discarding the oldest snapshot in the window and generating a new summary. However, in this paper, we can specify arbitrary time window to query summarized result in real time. In addition, we summarize the graph based on the selected dimensions of vertices, while the previous studies summarize the graph based on the super-node and super-edge. MoSSo \cite{ko2020incremental} incrementally summarizes fully dynamic graph. The difference of \cite{ko2020incremental} with \cite{fernandes2018dynamic,tsalouchidou2018scalable} is that the edges in the graph are dynamically added and removed, and MoSSo incrementally summarizes the whole graph after any modification on the graph.

\section{Conclusion} \label{sec:conclusion}
In this paper, we extend data warehouse and OLAP technology to temporal multidimensional networks by proposing a new data warehouse model \kw{Temporal\enspace Graph\enspace Cube}, which provides knowledge workers with tools to analyze temporal multidimensional networks. We first extend the basic concepts in static graph cube and introduce two new queries, \kw{temporal\enspace cuboid} and \kw{temporal\enspace crossboid}, allowing \kw{Temporal\enspace Graph\enspace Cube} to support OLAP queries on temporal multidimensional networks. Then, we propose a segment-tree based index method to accelerate the OLAP queries. We also present a new metric to measure the efficiency of the index. We conduct extensive experiments on two large real-world datasets, and the results demonstrate the effectiveness and efficiency of the proposed solutions.

%We point out that some classical methods are no longer applicable in the implementation of \kw{Temporal\enspace Graph\enspace Cube}.

%Our experimental results show the effectiveness of \kw{Temporal\enspace Graph\enspace Cube} and corroborate our inferences about the relationship between the efficiency of indexes and the metric. With the support of the implementation strategy for \kw{Temporal\enspace Graph\enspace Cube}, the indexes are able to achieve an acceleration effect. Moreover, the best time and space balance, as well as the best scalability, is achieved by segment tree among the three indexes.

% if have a single appendix:
%\appendix[Proof of the Zonklar Equations]
% or
%\appendix  % for no appendix heading
% do not use \section anymore after \appendix, only \section*
% is possibly needed

% use appendices with more than one appendix
% then use \section to start each appendix
% you must declare a \section before using any
% \subsection or using \label (\appendices by itself
% starts a section numbered zero.)
%

\comment{

% use section* for acknowledgment
\ifCLASSOPTIONcompsoc
% The Computer Society usually uses the plural form
\section*{Acknowledgments}
\else
% regular IEEE prefers the singular form
\section*{Acknowledgment}
\fi
This work was partially supported by (i) National Key Research and Development Program of China 2020AAA0108503, (ii) NSFC Grants 62072034 and 61772346, and (iii) CCF-Baidu Open Fund;
%(ii) NSFC Grants 61772346, 61732003, U1809206, 61772091, 61802035;
%(iii) Beijing Institute of Technology Research Fund Program for Young Scholars;
%(iv) Research Grants Council of the Hong Kong SAR, China No. 14221716 and 14203618;
%(v) ARC Discovery Project Grant DP160101513;
%and (vi) MOE, Singapore under grant MOE2015-T2-2-069 and NUS, Singapore under an SUG.

% Can use something like this to put references on a page
% by themselves when using endfloat and the captionsoff option.
\ifCLASSOPTIONcaptionsoff
\newpage
\fi

}

% trigger a \newpage just before the given reference
% number - used to balance the columns on the last page
% adjust value as needed - may need to be readjusted if
% the document is modified later
%\IEEEtriggeratref{8}
% The "triggered" command can be changed if desired:
%\IEEEtriggercmd{\enlargethispage{-5in}}

% references section

% can use a bibliography generated by BibTeX as a .bbl file
% BibTeX documentation can be easily obtained at:
% http://mirror.ctan.org/biblio/bibtex/contrib/doc/
% The IEEEtran BibTeX style support page is at:
% http://www.michaelshell.org/tex/ieeetran/bibtex/
%\bibliographystyle{IEEEtran}
% argument is your BibTeX string definitions and bibliography database(s)
%\bibliography{IEEEabrv,../bib/paper}
%
% <OR> manually copy in the resultant .bbl file
% set second argument of \begin to the number of references
% (used to reserve space for the reference number labels box)

%\balance
\bibliographystyle{IEEEtran}
\bibliography{IEEEabrv,temporal_graph_cube}

%\begin{thebibliography}{1}
%
%\bibitem{IEEEhowto:kopka}
%H.~Kopka and P.~W. Daly, \emph{A Guide to \LaTeX}, 3rd~ed.\hskip 1em plus
%  0.5em minus 0.4em\relax Harlow, England: Addison-Wesley, 1999.
%
%\end{thebibliography}

% biography section
%
% If you have an EPS/PDF photo (graphicx package needed) extra braces are
% needed around the contents of the optional argument to biography to prevent
% the LaTeX parser from getting confused when it sees the complicated
% \includegraphics command within an optional argument. (You could create
% your own custom macro containing the \includegraphics command to make things
% simpler here.)
%\begin{IEEEbiography}[{\includegraphics[width=1in,height=1.25in,clip,keepaspectratio]{mshell}}]{Michael Shell}
% or if you just want to reserve a space for a photo:
\vspace*{-20mm}

% if you will not have a photo at all:
%\begin{IEEEbiographynophoto}{Rong-Hua Li}
%Biography text here.
%\end{IEEEbiographynophoto}

% insert where needed to balance the two columns on the last page with
% biographies
%\newpage

%\begin{IEEEbiographynophoto}{Jane Doe}
%Biography text here.
%\end{IEEEbiographynophoto}

% You can push biographies down or up by placing
% a \vfill before or after them. The appropriate
% use of \vfill depends on what kind of text is
% on the last page and whether or not the columns
% are being equalized.

%\vfill

% Can be used to pull up biographies so that the bottom of the last one
% is flush with the other column.
%\enlargethispage{-5in}

% that's all folks

\begin{IEEEbiography}[{\includegraphics[width=1in,height=1.25in,clip,keepaspectratio]{biophoto/grwang.jpg}}]{Guoren Wang}
	received the BS, MS, and PhD degrees from the Department of Computer Science, Northeastern University, China, in 1988, 1991, and
1996, respectively. Currently, he is a professor with the Beijing Institute of Technology (BIT), Beijing, China. His research interests include graph data management, graph mining, and graph computational systems.
\end{IEEEbiography}
\vspace{-10ex}
\begin{IEEEbiography}[{\includegraphics[width=1in,height=1.25in,clip,keepaspectratio]{biophoto/yuez.jpg}}]{Yue Zeng}
	is currently a master student at Beijing Institute of Technology (BIT), Beijing, China. His research interests include graph data management and social network analysis.
\end{IEEEbiography}
\vspace{-10ex}
\begin{IEEEbiography}[{\includegraphics[width=1in,height=1.25in,clip,keepaspectratio]{biophoto/RonghuaLi}}]{Rong-Hua Li}
	received the PhD degree from the Chinese University of Hong Kong, in 2013. He is currently a professor with the Beijing Institute of Technology (BIT), Beijing, China. His research interests include graph data management and mining, social network analysis, graph computational systems, and graph-based machine learning.
\end{IEEEbiography}
\vspace{-10ex}
\begin{IEEEbiography}[{\includegraphics[width=1in,height=1.30in,clip,keepaspectratio]{biophoto/hcqin}}]{Hongchao Qin}
is currently a Postdoc at Beijing Institute of Technology, China. He received the B.S. degree in mathematics, M.E. degree and Ph.D. degree in computer science from Northeastern University, China in 2013, 2015 and 2020, respectively. His current research interests include social network analysis and data-driven graph mining.
\end{IEEEbiography}
\vspace{-10ex}
\begin{IEEEbiography}[{\includegraphics[width=1in,height=1.30in,clip,keepaspectratio]{biophoto/xhshi.jpg}}]{Xuanhua Shi}
received his Ph.D. degree in Computer Engineering from HUST (China) in 2005. He is a professor in Service Computing Technology and System Lab and Cluster and Grid
Computing Lab, HUST (China). His current research interests focus on the scalability, resilience and autonomy of large-scale distributed systems, such as peta-scale systems, and data centers.
\end{IEEEbiography}
\vspace{-10ex}
\begin{IEEEbiography}[{\includegraphics[width=1in,height=1.30in,clip,keepaspectratio]{biophoto/ybxia.jpg}}]{Yubin Xia}
received the deploma degree in software school, Fudan University, Shanghai, China, in 2004, and the Ph.D. degree in computer science and technology from Peking University, Beijing, China, in 2010. He is now an associate professor in Shanghai Jiao Tong University since September 2012. His research interests include computer architecture, operating system, and security.
\end{IEEEbiography}
\vspace{-10ex}
\begin{IEEEbiography}[{\includegraphics[width=1in,height=1.30in,clip,keepaspectratio]{biophoto/xqshang.jpg}}]{Xuequn Shang} 
received her Ph.D. in computer science from University of Magdeburg, Germany, in 2005. She is currently a professor in School of Computer Science, Northwestern Polytechnical University, China. Her research interests include data mining, bioinformatics and machine learning.
\end{IEEEbiography}
\vspace{-10ex}
\begin{IEEEbiography}[{\includegraphics[width=1in,height=1.30in,clip,keepaspectratio]{biophoto/lhong}}]{Liang Hong}
received his BS degree and Ph.D. degree in Computer Science at Huazhong University of Science and Technology (HUST) in 2003 and 2009, respectively. Now, he is an associate professor
in School of Information Management of Wuhan University. His research interests include graph database, spatio-temporal data management and social networks.
\end{IEEEbiography}

%\begin{IEEEbiography}[{\includegraphics[width=1in,height=1.25in,clip,keepaspectratio]{biophoto/wanggr}}]{Guoren Wang}
%	received the BS, MS, and PhD degrees from the Department of Computer Science, Northeastern University, China, in 1988, 1991, and
%1996, respectively. Currently, he is a professor with the Beijing Institute of Technology (BIT), Beijing, China. His research interests include graph data management, graph mining, and graph computational systems. 
%\end{IEEEbiography}
%
%\begin{IEEEbiography}[{\includegraphics[width=1in,height=1.25in,clip,keepaspectratio]{biophoto/zengyue}}]{Yue Zeng}
%	is currently a master student at Beijing Institute of Technology (BIT), Beijing, China. His research interests include graph data management and social network analysis.
%\end{IEEEbiography}
%
%\begin{IEEEbiography}[{\includegraphics[width=1in,height=1.25in,clip,keepaspectratio]{biophoto/RonghuaLi}}]{Rong-Hua Li}
%	received the PhD degree from the Chinese University of Hong Kong, in 2013. He is currently a professor with the Beijing Institute of Technology (BIT), Beijing, China. His research interests include graph data management and mining, social network analysis, graph computational systems, and graph-based machine learning.
%\end{IEEEbiography}
%
%
%\begin{IEEEbiography}[{\includegraphics[width=1in,height=1.25in,clip,keepaspectratio]{biophoto/RuiMao}}]{Rui Mao}
%	received the PhD degree in computer science from the University of Texas at Austin, in 2007. He is currently a professor in Shenzhen University. His research interests include big data analysis and management, content-based similarity query of multimedia and biological data, data mining, and machine learning.
%\end{IEEEbiography}
%
%\begin{IEEEbiography}[{\includegraphics[width=1in,height=1.25in,clip,keepaspectratio]{biophoto/ZhiweiZhang}}]{Zhiwei Zhang}
%	received the BS degree from Renmin University of China in 2010, and PhD degree from the Chinese University of Hong Kong in 2014. He is currently a professor with the Beijing Institute of Technology (BIT), Beijing, China. His research interests include federal learning, data pricing and transaction, distributed system, blockchain, and algorithm analysis.
%\end{IEEEbiography}
%
%\begin{IEEEbiography}[{\includegraphics[width=1in,height=1.25in,clip,keepaspectratio]{biophoto/YeYuan}}]{Ye Yuan}
%	received the BS, MS, and PhD degrees in computer science from Northeastern University, in 2004, 2007, and 2011, respectively. He is now a professor with the Beijing Institute of Technology (BIT), Beijing, China. His research interests include graph databases, probabilistic databases, and social network analysis.
%\end{IEEEbiography}
\end{document}

### 2023-01-05 TemporalGraphCube/old-version/TemporalGraphCube_advisor.tex
latex 1-5

--- 2023-01-05 TemporalGraphCube/TemporalGraphCube_revision.tex
@@
 	\item We extend the classic segment tree that tailored for traditional range query problems to our range query problems on snapshot arrays to reduce the OLAP query processing time.
-We also develop \revision{an} index maintainable technique to handle the case when new edges are added to the temporal networks.
+We also develop a index maintainable technique to handle the case when new edges are added to the temporal networks.
 %Similar requirement has not been seen on common range query problems.
@@
 
-\stitle{Index updating.} Let $ STree.root.timer $ be the current largest timestamp in the STree.
+\stitle{Index updating.} Let $ STree.root.timer $ is the current largest timestamp in the STree.
 When a new edge $ (u,v,t,a) $ with $t>STree.root.timer $ comes, we need to expand the range of STree by creating new nodes to maintain larger range and switch the root of STree to one of the new nodes.
@@
 Finally, we let $ newNode $ be the new root of $ STree $.
-If $ [l,2r-l+1] $ still can not cover $ t $, we continue the process above until $ t $ is coverd.
+If $ [l,2r-l+1] $ still cannot cover $ t $, we continue the process above until $ t $ is coverd.
 The updated $ STree $ is not a fully binary tree, since there is only a left subtree for the new root which violates the basic properties of STree.

### 2023-01-05 TemporalGraphCube/old-version/TemporalGraphCube_full.tex
latex 1-5

--- 2023-01-05 TemporalGraphCube/old-version/TemporalGraphCube_advisor.tex
@@
 \usepackage{booktabs}
-
-\long\def\comment#1{}
-%\newcommand{\eop}{\hspace*{\fill}\mbox{$\Box$}}
-
 %
@@
 
-\renewcommand{\baselinestretch}{0.97}
+\renewcommand{\baselinestretch}{0.99}
 
@@
 
-	\author{Guoren~Wang, Yue Zeng, Rong-Hua Li, Hongchao Qin,\\ Xuanhua Shi, Yubin Xia, Xuequn Shang, Liang Hong
+	\author{Qiangqiang~Dai, Rong-Hua~Li, Guoren~Wang, Rui~Mao, Zhiwei~Zhang, Ye~Yuan
 		\IEEEcompsocitemizethanks{
-			\IEEEcompsocthanksitem G.~Wang, Y.~Zeng, R.-H.~Li, H.~Qin are with the Beijing Institute of Technology, China; Xuanhua Shi is with Huazhong University of Science and Technology, China; Yubin Xia is with Shanghai Jiao Tong University; Xuequn Shang is with Northwestern Polytechnical University; Liang Hong is with Wuhan University.
-
-E-mail: wanggrbit@126.com, bruceez@163.com, lironghuabit@126.com, qhc.neu@gmail.com, xhshi@hust.edu.cn, xiayubin@sjtu.edu.cn,  shang@nwpu.edu.cn, hong@whu.edu.cn.
-%			\IEEEcompsocthanksitem R.~Mao is with the Shenzhen University, Shenzhen 518060, China. E-mail: mao@szu.edu.cn.
+			\IEEEcompsocthanksitem Q.~Dai, R.-H.~Li, G.~Wang, Z.~Zhang and Y.~Yuan are with the Beijing Institute of Technology, Beijing 100081, China.
+E-mail: qiangd66@gmail.com, lironghuascut@gmail.com, wanggrbit@126.com, cszwzhang@outlook.com, yuanye@mail.neu.edu.cn.
+			\IEEEcompsocthanksitem R.~Mao is with the Shenzhen University, Shenzhen 518060, China. E-mail: mao@szu.edu.cn.
 		}
@@
 % column for its text to clear the IEEEpubid mark (Computer Society jorunal
-% papers do not need this extra clearance.)
+% papers don't need this extra clearance.)
 
@@
 	\begin{abstract}
-		\justifying Data warehouse and OLAP (Online Analytical Processing) are effective tools for decision support on traditional relational data and static multidimensional network data.
-However, many real-world multidimensional networks are often modeled as temporal multidimensional networks, where the edges in the network are associated with temporal information.
-Such temporal multidimensional networks typically cannot be handled by traditional data warehouse and OLAP techniques.
-To fill this gap, we propose a novel data warehouse model, named \kw{Temporal\enspace Graph\enspace Cube}, to support OLAP queries on temporal multidimensional networks.
-Through supporting OLAP queries in any time range, users can obtain summarized information of the network in the time range of interest, which cannot be derived by using traditional static graph OLAP techniques.
-We propose a segment-tree based indexing technique to speed up the OLAP queries, and also develop an index-updating technique to maintain the index when the temporal multidimensional network evolves over time.
-In addition, we also propose a novel concept called \kw{similarity\enspace of\enspace snapshots} which shows a strong correlation with the efficiency of indexing technique and can provide a good reference on the necessity of building the index.
-The results of extensive experiments on two large real-world datasets demonstrate the effectiveness and efficiency of the proposed method.
-%With the support of \kw{MinLevel} strategy, the indexes are able to achieve good acceleration effect and space efficiency, especially segment tree, which also has the best scalability.
+		\justifying We study the problem of enabling data warehouse and OLAP technology to analyze large scale temporal multidimensional networks.
+Data warehouse and OLAP (Online Analytical Processing) are effective tools for decision support on traditional relational data and static multidimensional network.
+However, real-world networks can usually be modeled as temporal multidimensional networks and they can not be handled by data warehouse and OLAP technology yet.
+In this paper, we propose a new data warehouse model, \kw{Temporal\enspace Graph\enspace Cube}.
+By extending the basic idea of static graph cube, \kw{Temporal\enspace Graph\enspace Cube} supports OLAP queries on temporal multidimensional networks.
+Specifically, by supporting OLAP queries in any time range, users can obtain summative information of the networks in the time range of interest, which is impossible with static graph cube.
+In conducting OLAP queries of \kw{Temporal\enspace Graph\enspace Cube}, we should merge snapshots in a certain time range.
+We abstract this problem as range query problem on snapshot array, and we extend three typical indexes in commong range query problem: prefix array, sparse table and segment tree to accelerate the query.
+We enable these indexes to be updated in real time, because the size of real-world temporal networks grow over time.
+We find that the above indexes are not always work, and sometimes the baseline method is the best method.
+Based on this, we define \kw{similarity\enspace of\enspace snapshots}, which is proved to have a strong correlation with the efficiency of indexes and can provide a reference on the necessity to build indexes.
+In implementing \kw{Temporal\enspace Graph\enspace Cube}, we find that the traditional algorithms used to implement traditional data cube and static graph cube are no longer applicable to \kw{Temporal\enspace Graph\enspace Cube}.
+Instead, we adopt another simple method \kw{MinLevel}, which is introduced in implementation of static graph cube.
+The results of extensive experiments on real-world and man-made datasets show the effectiveness of \kw{Temporal\enspace Graph\enspace Cube} and corroborate the correlation between \kw{similarity\enspace of\enspace snapshots} and the efficiency of indexes.
+With the support of \kw{MinLevel} strategy, the indexes are able to achieve good acceleration effect and space efficiency, especially segment tree, which also has the best scalability.
 	\end{abstract}
 
-%	\begin{abstract}
-%		\justifying We study the problem of enabling data warehouse and OLAP (Online Analytical Processing) technology to analyze large scale temporal multidimensional networks.
-Data warehouse and OLAP are effective tools for decision support on traditional relational data and static multidimensional networks.
-However, many real-world multidimensional networks are often modeled as temporal multidimensional networks, where each edge in the network is associated with temporal information.
-Such temporal multidimensional networks often cannot be handled by traditional data warehouse and OLAP techniques.
-To fill this gap, we propose a novel data warehouse model, \kw{Temporal\enspace Graph\enspace Cube}.
-By extending the basic idea of static graph cube, \kw{Temporal\enspace Graph\enspace Cube} supports OLAP queries on temporal multidimensional networks.
-Specifically, by supporting OLAP queries in any time range, users can obtain summarized information of the networks in the time range of interest, which is impossible with traditional static graph cube.
-In conducting OLAP queries of \kw{Temporal\enspace Graph\enspace Cube}, we need to merge snapshots in a certain time range.
-We model this problem as a range query problem on snapshot arrays, and generalize three indexes in traditional range query problem: prefix array, sparse table and segment tree to accelerate the query.
-We also develop new updating techniques to maintain these generalized indexes when the temporal multidimensional network evolves over time.
-To further improve the query efficiency, we propose a new concept called \kw{similarity\enspace of\enspace snapshots} which shows a strong correlation with the efficiency of indexing techniques and can provide a good reference on the necessity of building the indexes.
-The results of extensive experiments on both real-world and synthetic datasets show the efficiency and effectiveness of the proposed solutions.
-%With the support of \kw{MinLevel} strategy, the indexes are able to achieve good acceleration effect and space efficiency, especially segment tree, which also has the best scalability.
-%	\end{abstract}
-
 	% Note that keywords are not normally used for peerreview papers.
-%	\begin{IEEEkeywords}
-%		Uncertain Graphs, Cohesive Subgraph Mining, Uncertain Core Decomposition.
-%\end{IEEEkeywords}
-}
+	\begin{IEEEkeywords}
+		Uncertain Graphs, Cohesive Subgraph Mining, Uncertain Core Decomposition.
+\end{IEEEkeywords}}
 
@@
 
-Data warehouses and OLAP (Online Analytical Processing) techniques are helpful tools for knowledge workers (executive, manager, analyst) to analyze and make decisions, because Data warehouses and OLAP together can efficiently provide summarized information in different resolutions by specifying different views (different combinations of data dimensions) of large-scale real-world data through OLAP operations such as roll-up, drill-down and slice-and-dice \cite{chaudhuri1997overview}.
-Data warehouse built on traditional relational database (RDB) data is called data cube \cite{gray1997data}.
-In 2011, Zhao et al.\ \cite{zhao2011graph} proposed \kw{Graph} \kw{Cube} which extends data warehouses and OLAP techniques to analyze static multidimensional networks.
-For each query, static graph cube returns a static network with summarized information in its structure and statistical values on vertices and edges.
-
-However, many real-life networks, such as human proximity networks, scientific collaboration networks, and biological networks, can be modeled as temporal networks \cite{holme2015modern}, where each relationship or interaction has a timestamp.
-Also, vertices in temporal networks usually contain attributes of multiple dimensions.
-For example, vertices in human proximity networks have attributes such as name, gender, nationality, hobbies, and so on.
-Such an attributed network can be modeled as a temporal multidimensional network.
-There are many studies focusing on the management and analysis of temporal networks \cite{junghanns2017management}, but none of them have tried to extend OLAP techniques to temporal multidimensional networks, i.e., developing approaches to provide users in real time with summarized information on the temporal multidimensional networks in different resolutions and time ranges.
+Data warehouses and OLAP (Online Analytical Processing) technology have proven to be helpful tools for knowledge workers (executive, manager, analyst) to analyze and make decisions, because Data warehouses and OLAP together can efficiently provide summarized information in different resolutions by specifying different views (different combinations of data dimensions) of large-scale real-world data through OLAP operations such as roll-up, drill-down and slice-and-dice \cite{chaudhuri1997overview}.
+Data warehouse built on traditional RDB data can be called data cube \cite{gray1997data}.
+Zhao et al.
+\cite{zhao2011graph} proposed \kw{Graph} \kw{Cube} in 2011 which extends data warehouses and OLAP techniques so that they can be used to analyze static multidimensional networks.
+For each query, static graph cube returns a static network, and the summative information is in it's structure and statistical values on vertices and edges, unlike traditional data cube which only returns the statistical values obtained by group-by operations.
+However, many real-life networks, such as human proximity networks, scientific collaboration networks, and biological networks can be modeled as temporal networks \cite{holme2015modern}, where each relationship or interaction has a corresponding timestamp.
+Also, vertices in temporal networks usually contain attributes of multiple dimensions, for example, vertices in human proximity networks have attributes such as name, gender, nationality, hobbies, etc.
+Therefore, we can further construct the above networks as temporal multidimensional networks.
+There has been many works focusing on the management and analysis of temporal networks \cite{junghanns2017management}, but none of them have tried to extend OLAP techniques to temporal multidimensional networks, i.e., developing ways to provide users in real time with summative information about temporal multidimensional networks in different resolutions and time ranges.
 \begin{figure*}[t!]
@@
 	\vspace*{-0.4cm}
-	\caption{Running example: a temporal multidimensional network with its vertex table and network structure}
+	\caption{A sample temporal multidimensional network with its vertex table and network structure}
 	\vspace*{-0.4cm}
@@
 \begin{example} \label{exam:temp_multi_network}
-	Fig.~\ref{fig:example_dataset} shows a sample temporal transaction network, presenting the transactions between individuals of different countries of birth and professions in each day.
-Table in Fig.~\ref{fig:example_dataset} (a) is the vertex table of the temporal network, showing the information of the 8 individuals.
+	Figure~\ref{fig:example_dataset} shows a sample temporal transaction network, presenting the transactions between individuals of different countries of birth and professions in each day.
+Table in Figure~\ref{fig:example_dataset} (a) is the vertex table of the temporal network, showing the information of the 8 individuals.
 Each individual has a primary key ID and 3 dimensions (3 discrete attributes): gender, country (country of birth), profession.
 Income is a numeric attribute of individuals.
-Fig.~\ref{fig:example_dataset} (b) shows the network structure of the temporal network.
+Figure~\ref{fig:example_dataset} (b) shows the network structrue of the temporal network.
 There are 20 temporal edges, illustrating the transactions between individuals in 5 days.
@@
 The numeric attribute on each temporal edge is the amount of each transaction.
-The static multidimensional information of individuals in Fig.~\ref{fig:example_dataset} (a) and the temporal information of network structure in Fig.~\ref{fig:example_dataset} (b) form a temporal multidimensional network.
+The static multidimensional information of individuals in Figure~\ref{fig:example_dataset} (a) and the temporal information of network structure in Figure~\ref{fig:example_dataset} (b) form a temporal multidimensional network.
 \end{example}
-In static graph cube \cite{zhao2011graph}, users can specify different views to obtain summarized information of the static multidimensional network and combine the information under these views through OLAP operations such as roll-up, drill-down and slice-and-dice interactively for decision support and business intelligence.
+In static graph cube, users can specify different views to obtain summative information about the static multidimensional network and combine the information under these views through OLAP operations such as roll-up, drill-down and slice-and-dice interactively for decision support and business intelligence.
 For example, a company tries to use static graph cube to analyze the interaction characteristics of people with different attributes (name, gender, profession, income level, etc.) in a large-scale social network in order to support their marketing strategy making.
@@
 In this way, static graph cube does not work when users only need information for a specific time range.
-Considering the previous example, the company only needs data from the last few years, because data that is too old is less informative.
+Taking the previous example, the company only needs data from the last few years, because data that is too old is less informative.
 Or, they want to study what the characteristics of people's interactions are during particular time ranges, such as holidays or COVID-19 periods.
-Or, they wish to compare several different time ranges to see how people's interaction patterns change over time.
-Static graph cube cannot meet the above requirements.
-As a result, we need to propose novel approaches to make data warehouses and OLAP capable of analyzing temporal multidimensional networks.
-
-\comment{
+Or, they want to compare several different time ranges to see how people's interaction patterns change over time.
+Static graph cube can not meet the above needs.
+As a result, we need to extend static graph cube to make data warehouses and OLAP capable of analyzing temporal multidimensional networks.
+
 \begin{figure}[t!]
@@
 	\vspace*{-0.7cm}
-	\caption{Intermediate result of generating network structure in Fig.~\ref{fig:exam_cuboid_gender} (b)}
+	\caption{Intermediate result of generating network structure in Figure~\ref{fig:exam_cuboid_gender} (b)}
 	\vspace*{-0.4cm}
@@
 \end{figure}
-
-}
 
@@
 %		\begin{tabular}[t]{c}\hspace*{-0.3cm}
-%			\subfigure[{\scriptsize Structure of the answer of the first question in Example~\ref{exam:cuboid_query}}]{
+%			\subfigure[{\scriptsize Structrue of the answer of the first question in Example~\ref{exam:cuboid_query}}]{
 %				\includegraphics[width=0.45\columnwidth]{fig/example/exam_cuboid_gender_2_3_adjust.pdf}
@@
 
-\comment{
 \begin{figure}[t!]
@@
 \begin{example} \label{exam:cuboid_query}
-	Fig.~\ref{fig:exam_cuboid_gender} shows a static aggregate network obtained by summarizing the temporal multidimensional network in Fig.~\ref{fig:example_dataset} on dimension ``Gender'' and time range $ [2,3] $.
-Fig.~\ref{fig:exam_cuboid_gender} can be regarded as the answer of question ``What is the amount of transactions between individuals of different genders from day 2 to day 3?" Note that the vertex table in Fig.~\ref{fig:exam_cuboid_gender} (a) is directly aggregated from the vertex table in Fig.~\ref{fig:example_dataset} (a) on ``Gender" with COUNT($\ast$) as aggregation function on vertices.
-All vertices in Fig.~\ref{fig:example_dataset} (a) are included in the aggregation process even those vertices which have no adjacent edge in day 2 and day 3, like $ v_5 $.
+	Figure~\ref{fig:exam_cuboid_gender} shows a static aggregate network obtained by summarizing the temporal multidimensional network in Figure~\ref{fig:example_dataset} on dimension ``Gender'' and time range $ [2,3] $.
+Figure~\ref{fig:exam_cuboid_gender} can be regarded as the answer of question ``What is the amount of transactions between individuals of different genders from day 2 to day 3?" Note that the vertex table in Figure~\ref{fig:exam_cuboid_gender} (a) is directly aggregated from the vertex table in Figure~\ref{fig:example_dataset} (a) on ``Gender" with COUNT($\ast$) as aggregation function on vertices.
+All vertices in Figure~\ref{fig:example_dataset} (a) are included in the aggregation process even those vertices which have no adjacent edge in day 2 and day 3, like $ v_5 $.
 The reason is that vertices are time independent and vertices having no adjacent edge in specified time ranges are still available in those time ranges.
-Therefore, from day 2 to day 3, the COUNT($\ast$) value of male should be 4.
-Fig.~\ref{fig:exam_inter_result_gender} shows the intermediate result of the question, which is obtained by merging all snapshots in day 2 and day 3.
-All edges of snapshots in day 2 and day 3 are collected to the single snapshot in Fig.~\ref{fig:exam_inter_result_gender}, and if there are two edges in snapshots of day 2 and day 3 respectively share the same vertices, then their numeric attributes will be added together since SUM($\ast$) is the aggregation function upon edges here.
-Fig.~\ref{fig:exam_cuboid_gender} (b) can be directly aggregated from Fig.~\ref{fig:exam_inter_result_gender} on the basis of aggregated vertices in Fig.~\ref{fig:exam_cuboid_gender} (a), i.e., each edge in Fig.~\ref{fig:exam_cuboid_gender} (b) is the aggregated edge of edges in Fig.~\ref{fig:exam_inter_result_gender}, whose two vertices are aggregated to the two vertices of the corresponding aggregated edge.
-The numeric attributes of the aggregated edges in Fig.~\ref{fig:exam_cuboid_gender} (b) are still the sum of attributes of their corresponding sets of edges in Fig.~\ref{fig:exam_inter_result_gender}.
-
-	Finally, we can reply the question above.
-For example, from day 2 to day 3, the amount of transactions between males is 6, while the amount of transactions between male and female is 107, etc.
-Fig.~\ref{fig:exam_cuboid_gender_profession} shows the answers of two similar questions ``What is the amount of transactions between individuals of different genders and professions from day 2 to day 3 and from day 4 to day 5?" The only difference between these two questions is the time range specified.
-Both static aggregate networks in Fig.~\ref{fig:exam_cuboid_gender_profession} share the same vertex table in Fig.~\ref{fig:exam_cuboid_gender_profession} (a) and in these two questions the aggregation functions upon vertices are AVERAGE($\ast$).
+So from day 2 to day 3, the COUNT($\ast$) value of male should be 4.
+Figure~\ref{fig:exam_inter_result_gender} shows the intermediate result of the question, which is obtained by merging all snapshots in day 2 and day 3.
+All edges of snapshots in day 2 and day 3 are collected to the single snapshot in Figure~\ref{fig:exam_inter_result_gender}, and if there are two edges in snpshots of day 2 and day 3 respectively share the same vertices, then their numeric attributes will be added together since SUM($\ast$) is the aggregation function upon edges here.
+Figure~\ref{fig:exam_cuboid_gender} (b) can be directly aggregated from Figure~\ref{fig:exam_inter_result_gender} on the basis of aggregated vertices in Figure~\ref{fig:exam_cuboid_gender} (a), i.e., each edge in Figure~\ref{fig:exam_cuboid_gender} (b) is the aggregated edge of edges in Figure~\ref{fig:exam_inter_result_gender}, whose two vertices are aggregated to the two vertices of the corresponding aggregated edge.
+The numeric attributes of the aggregated edges in Figure~\ref{fig:exam_cuboid_gender} (b) are still the sum of attributes of their corresponding sets of edges in Figure~\ref{fig:exam_inter_result_gender}.
+
+	Finally we can reply the question above, for example, from day 2 to day 3, the amount of transactions between males is 6, while the amount of transactions between male and female is 107, etc.
+Figure~\ref{fig:exam_cuboid_gender_profession} are the answers of two similar questions ``What is the amount of transactions between individuals of different genders and professions from day 2 to day 3 and from day 4 to day 5?" The only difference between these two questions is the time range specified.
+Both static aggregate networks in Figure~\ref{fig:exam_cuboid_gender_profession} share the same vertex table in Figure~\ref{fig:exam_cuboid_gender_profession} (a) and in these two questions the aggregation functions upon vertices are AVERAGE($\ast$).
 \end{example}
-
-There are three new OLAP queries in Example~\ref{exam:cuboid_query} compared to queries in static graph cube, for example, the first OLAP query in Example~\ref{exam:cuboid_query} is ``What is the amount of transactions between individuals of different genders from day 2 to day 3", which requests a rough summarized result of the temporal multidimensional network in Fig.~\ref{fig:example_dataset} on ``Gender".
+There are three new OLAP queries in Example~\ref{exam:cuboid_query} compared to queries in static graph cube, for example, the first OLAP query in Eample~\ref{exam:cuboid_query} is ``What is the amount of transactions between individuals of different genders from day 2 to day 3", which requests a rough summative result of the temporal multidimensional network in Figure~\ref{fig:example_dataset} on ``Gender".
 Unlike the query in static graph cube, this new query includes a specific time range $ [2,3] $.
-Conducting the new query includes the same aggregation on vertex table as in static graph cube, but when aggregating the network structure, the basic idea is to first merge snapshots in the time range to build an intermediate result, as shown in Fig.~\ref{fig:exam_inter_result_gender}, then perform the same aggregation on Fig.~\ref{fig:exam_inter_result_gender} as in static graph cube.
-If the new query specifies the whole time range of the temporal multidimensional network, then it is equivalent to a query in static graph cube.
-Therefore, static graph cube is a special case of the new data warehouse model proposed in this paper.
+Conducting the new query includes the same aggregation on vertex table as in static graph cube, but when aggregating the network structure, the basic idea is to first merge snapshots in the time range to build an intermediate result, as in Figure~\ref{fig:exam_inter_result_gender}, then perform the same aggregation on Figure~\ref{fig:exam_inter_result_gender} as in static graph cube.
+If the new query specifies the whole time range of the temporal multidimensional network, then it's equivalent to a query in static graph cube.
+Therefore, static graph cube is a special version of the new data warehouse model to be proposed in this paper.
 Conducting the second OLAP query ``What is the amount of transactions between individuals of different genders and professions from day 2 to day 3" can be regarded as performing a drill-down operation on the basis of the first query, since the second query requests more fine-grained information in the same time range than the first query.
@@
 
-In \cite{zhao2011graph}, Zhao et al.\ proposed a new OLAP query for static multidimensional networks, called \kw{crossboid}, to analyze the crossed interaction pattern of two different views.
-It is easy to see that \kw{Crossboid} can also be extended to temporal multidimensional networks as illustrated in Example~\ref{exam:crossboid_query}.
+In \cite{zhao2011graph}, Zhao et al.
+proposed a new OLAP query especially for static multidimensional networks \kw{crossboid}, to analyze the crossed interaction pattern of two different views.
+\kw{Crossboid} can also be easily extended to the temporal multidimensional network scenario as in Example~\ref{exam:crossboid_query}.
 
@@
 	\centering
-	\caption{Vertex table obtained by group-by on ``Profession" in Fig.~\ref{fig:example_dataset} (a)} \vspace*{-0.2cm} \label{tab:groupby_profession}
+	\caption{Vertex table obtained by group-by on ``Profession" in Figure~\ref{fig:example_dataset} (a)} \vspace*{-0.2cm} \label{tab:groupby_profession}
 	\begin{tabular}{c c}
@@
 \begin{example} \label{exam:crossboid_query}
-	Fig.~\ref{fig:exam_crossboid_gender_profession} shows the structure of the answer to ``What is the amount of transactions between individuals grouped by gender and individuals grouped by profession from day 2 to day 3?" The answer can also be regarded as a static aggregate network which has two vertex tables from group-by on ``Gender" and ``Profession" shown in Fig.~\ref{fig:exam_cuboid_gender} (a) and Table~\ref{tab:groupby_profession} respectively.
-Fig.~\ref{fig:exam_crossboid_gender_profession} shows the crossed transactions between two different views ``Gender" and ``Profession" from day 2 to day 3, e.g., for all transactions between males and individuals of different professions, all 4 males have the biggest amount of transactions with the 2 lawyers and the smallest amount of transactions with the 2 students from day 2 to day 3.
-Other crossed transactions can also be easily found in Fig.~\ref{fig:exam_crossboid_gender_profession}.
+	Figure~\ref{fig:exam_crossboid_gender_profession} shows the structure of the answer to ``What is the amount of transactions between individuals grouped by gender and individuals grouped by profession from day 2 to day 3?" The answer can also be regarded as a static aggregate network which has two vertex tables from group-by on ``Gender" and ``Profession" shown in Figure~\ref{fig:exam_cuboid_gender} (a) and Table~\ref{tab:groupby_profession} respectively.
+Figure~\ref{fig:exam_crossboid_gender_profession} shows the crossed transactions between two different views ``Gender" and ``Profession" from day 2 to day 3, e.g., for all transactions between males and individuals of different professions, all 4 males have the biggest amount of transactions with the 2 laywers and the smallest amount of transactions with the 2 students from day 2 to day 3.
+Other crossed transactions can also be easily found in Figure~\ref{fig:exam_crossboid_gender_profession}.
 \end{example}
-}
-
-In this paper, we propose a new data warehouse model, called \kw{Temporal} \kw{Graph} \kw{Cube}; and we extend the definition of OLAP queries by specifying a time range so that they can be applied to \kw{Temporal} \kw{Graph} \kw{Cube}.
+In this paper, we propose a new data warehouse model, \kw{Temporal} \kw{Graph} \kw{Cube}, and we extend the definition of OLAP queries by specifying a time range so that they can be applied to \kw{Temporal} \kw{Graph} \kw{Cube}.
 Users can explore summarized information on different views of temporal multidimensional networks in any time range using \kw{Temporal} \kw{Graph} \kw{Cube}.
-The challenge of our problem is: how to efficiently merge snapshots in a specific time range for each online OLAP query.
-A basic approach is to merge snapshots in the time range one by one.
-Such a basic method, however, is clearly inefficient when the time ranges are very large or a large number of OLAP queries come.
+Here, we face a new problem: how to efficiently merge snapshots in a specific time range for each online OLAP query.
+In Example~\ref{exam:cuboid_query}, we merge snapshots in time ranges $ [2,3] $ and $ [4,5] $ one by one.
+Such a basic idea is inefficient when the time ranges expand and a large number of queries come.
 The above problem can be seen as range query on snapshot arrays.
 Unfortunately, among the existing works for summarizing temporal networks \cite{liu2018graph}, there is no work which focuses on summarizing snapshots within a certain time range online.
-In this paper, we investigate the problem of how to speed up merging snapshots in certain time ranges.
-Our solution is to build an index on snapshot arrays to reduce the query processing time.
-Specifically, we propose a segment-tree based index to support the range query on snapshot arrays.
-Since new edges are constantly inserted into the temporal multidimensional network, we also propose an index updating technique to handle such an edge-insertion case.
-In addition, similar to the static graph cube, the implementation of the \kw{Temporal} \kw{Graph} \kw{Cube} also requires determining the materialization strategy of views in order to achieve a balance between time and space.
-To this end, we adopt a strategy called \kw{MinLevel} proposed in \cite{zhao2011graph} to handle the materialization problem in \kw{Temporal} \kw{Graph} \kw{Cube}, as it fits our model best.
-
-To summarize, the main contributions of this work are as follows:
+In this paper, we investigate the problem of how to speed up merging snapshots in certain time ranges, i.e., building indexes on snapshot arrays to reduce response time of queries.
+Specifically, we extend typical indexes that are useful in traditional range query problems: prefix array, sparse table, and segment tree to the range query problem on snapshot arrays.
+In addition, since new edges are constantly added to the real-world temporal multidimensional networks, we also need to consider the maintenance of \kw{Temporal} \kw{Graph} \kw{Cube} and the indexes built in it when adding new edges.
+As with static graph cube, the implementation of the \kw{Temporal} \kw{Graph} \kw{Cube} requires determining the materialization strategy of views in order to achieve a balance between time and space.
+We refer to the strategy \kw{MinLevel} proposed in \cite{zhao2011graph}, as it fits our model best.
+
+The main contributions of our work are summarized as follows:
 \begin{enumerate}
 	\item We propose a new data warehouse model \kw{Temporal} \kw{Graph} \kw{Cube}, which supports decision making on the basis of temporal multidimensional networks.
-The key difference compared to static graph cube is that \kw{Temporal} \kw{Graph} \kw{Cube} supports querying summarized information for any time range of temporal multidimensional networks so that it supports more diverse analysis.
-
-	\item We extend the classic segment tree that tailored for traditional range query problems to our range query problems on snapshot arrays to reduce the OLAP query processing time.
-We also develop a index maintainable technique to handle the case when new edges are added to the temporal networks.
-%Similar requirement has not been seen on common range query problems.
-
-	\item  We propose a new metric, called \kw{similarity\enspace of\enspace snapshots}, to measure the overall similarity of snapshots in a snapshot array, or, the degree to which the edges are shared by different snapshots.
-We show that this metric has a strong correlation with the effectiveness of the indexes and it can guide us to decide whether an index should be built.
-
-%	\item We point out that the existing methods used to implement traditional data cube and static graph cube: greedy algorithm \cite{harinarayan1996implementing} and its variants \cite{morfonios2007rolap}, are no longer applicable in \kw{Temporal \enspace Graph \enspace Cube} scenario.
+The biggest difference compared to static graph cube is that \kw{Temporal} \kw{Graph} \kw{Cube} supports querying summative information for any time range of temporal multidimensional networks so that it supports more diverse analysis.
+
+	\item We extend three typical indexes that work on common range query problems to range query problems on snapshot arrays to reduce response time of queries.
+We also make these indexes support self-updating when new edges are added to the temporal networks.
+Similar requirement has not been seen on common range query problems.
+
+	\item We find that these indexes do not always work as in common range query problem, and their effectiveness is related to some nature of the snapshot arrays.
+We propose a metric: \kw{similarity\enspace of\enspace snapshots}, to measure the overall similarity of snapshots in a snapshot array, or, the degree to which the edges are shared by different snapshots.
+We find that this metric has a strong correlation with the effectiveness of the indexes and it indicates which snapshot arrays indexes should be built on.
+
+	\item We point out that the common methods used to implement traditional data cube and static graph cube: greedy algorithm \cite{harinarayan1996implementing} and its variants \cite{morfonios2007rolap}, are no longer applicable in \kw{Temporal \enspace Graph \enspace Cube} scenario.
 The main reason is that OLAP queries contain arbitrary time ranges.
-A more reasonable method is \kw{MinLevel}, which is easy to be implemented and does not take into account the time ranges in OLAP queries.
-
-	\item We conduct extensive experiments on two large-scale real-world datasets.
-The results demonstrate the effectiveness and efficiency of the \kw{Temporal \enspace Graph \enspace Cube}.
-The results also confirm the correlation between the efficiency (time and space) of the index and \kw{similarity\enspace of\enspace snapshots}.
-%We also examined the update performance of our index.
-Among them, we find that the segment tree index is with the best time and space balance and scalability among the three indexes.
+A more reasonable method is \kw{MinLevel}, which is very simple to be implemented and does not take into account the time ranges in OLAP queries.
+
+	\item We conduct extensive experiments on real-world and man-made datasets.
+The results demonstrate the effectiveness of the \kw{Temporal \enspace Graph \enspace Cube}.
+The results also demonstrate the correlation between the efficiency (time and space) of the three indexes and \kw{similarity\enspace of\enspace snapshots}.
+We also examined the update performance of the three indexes.
+Among them, we find that segment tree is with the best time and space balance and scalability among the three indexes.
 \end{enumerate}
 
-\comment{
 %\vspace*{-0.2cm}
@@
 We conclude our work in Section~\ref{sec:conclusion}.
-}
 
@@
 %\vspace*{-0.1cm}
-%\subsection{Definitions}\label{subsec:definitions}
+\subsection{Definitions}\label{subsec:definitions}
 \begin{definition}[Temporal Multidimensional Network]
@@
 , A_n\}$ represents the dimensions of the network, or $n$ discrete attributes of nodes in $ \Vr $, i.e., $A(u)=\{A_1(u), A_2(u), ...
-, A_n(u)\}$ where $A_i(u)$ is the actual value of $u$ on the $i$-th attribute.
+, A_n(u)\}$ where $A_i(u)$ is the actual value of $u$ on the i-th attribute.
 $ W(u) $ is the numeric value of $u$.
 \end{definition}
-
-For convenience, we abbreviate temporal multidimensional network and static multidimensional network to temp-multi-network and static-multi-network respectively.
-Since we only consider undirected edges in this paper, if not specified, we assume without loss of generality $u \leq v$ for $(u, v, t, a)$ in all following definitions.
-As shown in Fig.~\ref{fig:example_dataset}, $ A=\{Gender,Country,Profession\} $ and $ W=Income $.
-We do not consider ID to be an attribute of individuals because ID is only the identification of individuals.
-$ \Vr $ is the set of IDs of individuals in Fig.~\ref{fig:example_dataset} (a) and $ \Er $ is the set of temporal edges in Fig.~\ref{fig:example_dataset} (b).
+In convenience, we abbreviate temporal multidimensional network and static multidimensional network to temp-multi-network and static-multi-network respectively.
+Since we only consider undirected edges in this paper, if not specified, we assign $u \leq v$ in $(u, v, t, a)$ and in all following definitions.
+
+As in Figure~\ref{fig:example_dataset}, $ A=\{Gender,Country,Profession\} $ and $ W=Income $.
+We don't consider ID to be an attribute of individuals because ID is only the identification of individuals.
+$ \Vr $ is the set of IDs of individuals in Figure~\ref{fig:example_dataset} (a) and $ \Er $ is the set of temporal edges in Figure~\ref{fig:example_dataset} (b).
+
 A temp-multi-network can also be represented by a sequence of snapshots. 
-
 \begin{definition}[Snapshot]
@@
 \end{definition}
-
-For example, in Fig.~\ref{fig:example_dataset} (b), we can extract 5 snapshots; and the snapshot at timestamp 1 is $ S_1=\{(v_1,v_2,10),(v_2,v_3,20),(v_3,v_4,10),(v_1,v_4,15)\} $.
+For example, in Figure~\ref{fig:example_dataset} (b), we can extract 5 snapshots and snapshot at timestamp 1 $ S_1=\{(v_1,v_2,10),(v_2,v_3,20),(v_3,v_4,10),(v_1,v_4,15)\} $.
 With the definition of snapshot, we can define temp-multi-network in Definition~\ref{def:temp_multi_network} as $\Gr=(\Vr,\Sr,A,W)$ where $\Sr=\{S_1,S_2,...,S_{|\Tr|}\}$ and $ S_i $ is the snapshot at $t_i$.
 
-\stitle{Biased Timestamp.} To store snapshots in a snapshot array and access snapshots directly by corresponding timestamps, we replace the original timestamps of snapshots with \emph{biased timestamps}.
+\stitle{Biased Timestamp.} To store snapshots in a snapshot array and access snapshots directly by corresponding timestamps, we replace the original timestamps of snapshots with biased timestamps.
 For each temp-multi-network, suppose $ t_1 $ is the smallest timestamp, $ t_{|\Tr|} $ is the biggest timestamp and $ t_{base}=t_1-1 $, biased timestamp of snapshot $ S_i $ is computed by $ t_i-t_{base} $.
@@
 If timestamps are sparse, i.e., $ |\Tr| \ll t_{|\Tr|}-t_1 $, there will be many empty snapshots in snapshot array.
-We can sacrifice a little in efficiency, hashing all the timestamps into a denser space and relocating time range $ [l,r] $ of each query (we will discuss queries in Section~\ref{sec:queries}) to the actual time range.
-However, in large scale real-world temp-multi-networks, temporal relations can be built at almost all time, so the timestamps are unlikely to be sparse, which is confirmed in our datasets.
-All algorithms in this paper are designed based on the definition of temp-multi-network $\Gr=(\Vr,\Sr,A,W)$, where $ \Sr $ is a snapshot array with biased timestamps of snapshots start from 1.
-
-\comment{
+We can sacrifice a little in efficiency, hashing all the timestamps into a denser space and relocating time range $ [l,r] $ of each query (we will discuss queries in Section~\ref{subsec:queries}) to the actual time range.
+However, in large scale real-world temp-multi-networks, temporal relations can be built at almost all time, so the timestamps are unlikely to be sparse, which is proven in our datasets.
+
+All algorithms in this paper are designed based on definition of temp-multi-network where $\Gr=(\Vr,\Sr,A,W)$ and $ \Sr $ is a snapshot array where biased timestamps of valid snapshots start from 1.
+
 Aggregation, or traditional group-by, is a key operation in data warehouses and OLAP for traditional RDB data and static-multi-network.
@@
 The results of aggregations on static-multi-network, static aggregate networks, are exactly the answers of OLAP queries on static-multi-network \cite{zhao2011graph}.
-However, situations are different in temp-multi-networks.
-Below, we first define temporal aggregate network (the results of aggregations on temp-multi-network), and show the difference between static aggregate network and temporal aggregate network.
-Then, we describe the benefit of temporal aggregate network in conducting OLAP queries on temp-multi-network.
-}
-
+However, situations are different in temp-multi-network.
+Next, we first define temporal aggregate network, the results of aggregations on temp-multi-network and show the difference between static aggregate network and temporal aggregate network, then we describe the benefit of temporal aggregate network in conducting OLAP queries on temp-multi-network.
 \begin{definition}[Temporal Aggregate Network]
@@
 	\end{center}
-	\vspace*{-0.9cm}
+	\vspace*{-0.4cm}
 	\caption{Snapshots of the first temporal aggregate network in Example~\ref{exam:temporal_aggregate_network}}
@@
 	\end{center}
-	\vspace*{-0.9cm}
+	\vspace*{-0.5cm}
 	\caption{Snapshots of the second temporal aggregate network in Example~\ref{exam:temporal_aggregate_network}.
@@
 \begin{example} \label{exam:temporal_aggregate_network}
-	Fig.~\ref{fig:aggregation_gender} shows the snapshots of a temporal aggregate network, which is obtained by aggregating temp-multi-network in Fig.~\ref{fig:example_dataset} on dimension ``Gender".
-The obtained temporal aggregate network is also a temp-multi-network.
-There are 5 snapshots in Fig.~\ref{fig:aggregation_gender}, each of them is corresponding to the snapshot with the same timestamp in Fig.~\ref{fig:example_dataset} (b).
-For each snapshot in Fig.~\ref{fig:aggregation_gender}, each edge $ e' $ is the aggregated edge of a set of edges $ E $ in the corresponding snapshot.
+	Figure~\ref{fig:aggregation_gender} shows the snapshots of a temporal aggregate network, which is obtained by aggregating temp-multi-network in Figure~\ref{fig:example_dataset} on dimension ``Gender".
+The obtained temporal aggregate network is also a temp-multi-network, with vertex table shown in Figure~\ref{fig:exam_cuboid_gender} (a).
+There are still 5 snapshots in Figure~\ref{fig:aggregation_gender}, each of them is corresponding to the snapshot with the same timestamp in Figure~\ref{fig:example_dataset} (b).
+For each snapshot in Figure~\ref{fig:aggregation_gender}, each edge $ e' $ is the aggregated edge of a set of edges $ E $ in the corresponding snapshot.
 Each edge in $ E $ have two vertices aggregated to the two vertices of $ e' $, as 2) in Definition~\ref{def:temp_aggregate_network}.
 In this example, the attribute in $ e' $ is the amount of the attributes of edges in $ E $, i.e., the total transactions between individuals of two genders in each day.
-We can also choose other aggregation functions for edges like COUNT($\ast$), MAX($\ast$), and so on.
-Similarly, Fig.~\ref{fig:aggregation_gender_profession} shows another temporal aggregate network by aggregating temp-multi-network in Fig.~\ref{fig:example_dataset} on dimension ``Gender" and ``Profession".
+We can also choose other aggregation functions for edges like COUNT($\ast$), MAX($\ast$), etc.
+
+	Figure~\ref{fig:aggregation_gender_profession} and Table in Figure~\ref{fig:exam_cuboid_gender_profession} (a) together show another temporal aggregate network by aggregating temp-multi-network in Figure~\ref{fig:example_dataset} on dimension ``Gender" and ``Profession".
 \end{example}
 
-%As in Example~\ref{exam:temporal_aggregate_network}, Fig.~\ref{fig:aggregation_gender} and Fig.~\ref{fig:aggregation_gender_profession} are temporal aggregate networks $ \Gr'_1 $ and $ \Gr'_2 $ aggregated from Fig.~\ref{fig:example_dataset} on $ (Gender,\ast,\ast) $ and $ (Gender,\ast,Profession) $ respectively.
+%As in Example~\ref{exam:temporal_aggregate_network}, Figure~\ref{fig:aggregation_gender} and Figure~\ref{fig:aggregation_gender_profession} are temporal aggregate networks $ \Gr'_1 $ and $ \Gr'_2 $ aggregated from Figure~\ref{fig:example_dataset} on $ (Gender,\ast,\ast) $ and $ (Gender,\ast,Profession) $ respectively.
 For $ \Gr'_1=(\Vr'_1,\Sr'_1,B_1,W'_1) $, $ \Vr'_1 $ is the set of nodes, which are represented by tuples in "Gender" column of Table~\ref{tab:aggregation_gender}.
-$ \Sr'_1 $ is the snapshot array starting from subscript 1 and storing the 5 snapshots in Fig.~\ref{fig:aggregation_gender}.
+$ \Sr'_1 $ is the snapshot array starting from subscript 1 and storing the 5 snapshots in Figure~\ref{fig:aggregation_gender}.
 $ B_1=\{Gender\} $.
@@
 
-\comment{
-From Definition~\ref{def:temp_aggregate_network} and Example~\ref{exam:temporal_aggregate_network}, we can find that aggregation on static-multi-network is a special case of aggregation on temp-multi-network, if there is only one snapshot in temp-multi-network.
+From Definition~\ref{def:temp_aggregate_network} and Example~\ref{exam:temporal_aggregate_network} we can find that aggregation on static-multi-network is a special case of aggregation on temp-multi-network, if there is only one snapshot in temp-multi-network.
 For most cases, compared to aggregation on static-multi-network, aggregation on temp-multi-network contains aggregating each snapshot of the temp-multi-network to condensed snapshot independently.
-}
-
-Obviously, the temporal aggregate network is not the direct answer of OLAP query on temp-multi-network, because temporal aggregate network contains aggregated snapshot at each timestamp, but OLAP query on temp-multi-network requires a summarized snapshot of a specified time range.
+
+Obviously, temporal aggregate network is not the direct answer of OLAP query on temp-multi-network, because temporal aggregate network contains aggregated snapshot at each timestamp, but OLAP query on temp-multi-network requires a summative snapshot of a specified time range.
 However, temporal aggregate network can provide a cheaper way to conduct queries compared to conducting queries directly on the original temp-multi-network.
-We will explain in detail in Section~\ref{sec:queries}.
-%For example, the snapshot in Fig.~\ref{fig:exam_cuboid_gender} (b) can be obtained by merging snapshots in day 2 and day 3 in Fig.~\ref{fig:aggregation_gender}, without generating the intermediate result in Fig.~\ref{fig:exam_inter_result_gender}.
+For example, the snapshot in Figure~\ref{fig:exam_cuboid_gender} (b) can be obtained by merging snapshots in day 2 and day 3 in Figure~\ref{fig:aggregation_gender}, without generating the intermediate result in Figure~\ref{fig:exam_inter_result_gender}.
 We will explain in detail in Section~\ref{subsec:queries}.
@@
 \end{algorithm}
-
-We devise a basic algorithm, as outlined in Algorithm~\ref{alg:view_construct_baseline},  to construct the temporal aggregate network with aggregation $ A' $ from the original network $ \Gr $.
-Note that there are two things to be concerned about aggregation functions:
+Algorithm~\ref{alg:view_construct_baseline} is a basic algorithm to construct a temporal aggregate network upon aggregation $ A' $ from the original network $ \Gr $.
+There are two things to be concerned about aggregation functions:
 \begin{itemize}[leftmargin=*]
@@
 
-	\item If $ f_v =$ COUNT($\ast$), we assign $1$ to all $ W(u),u \in \Vr $, because $ 1 $ is the correct attribute value of each vertex when counting is needed.
+	\item if $ f_v =$ COUNT($\ast$), we should assign $1$ to all $ W(u),u \in \Vr $, because $ 1 $ is the correct attribute value of each vertex when counting is needed.
 The same assignment should be done to numeric attributes of all edges if $ f_e= $ COUNT($\ast$).
@@
 Algorithm~\ref{alg:view_construct_baseline} first conducts the specified aggregation on all vertices of the original network.
-In line~1, we first create a hash structure, $h$, to maintain a mapping from all possible $ B(u),u \in \Vr $ to vertices of the temporal aggregate network.
-In lines~2-6, we group all vertices in $ \Vr $ with the specified aggregation $ A' $ and compute the aggregation result of numeric attributes of vertices with the specified aggregation function $ f_v $.
-Each snapshot $ \Sr[i] $ of $ \Gr $ is aggregated into a smaller representation, i.e., the corresponding snapshot $ \Sr'[i] $ at the same timestamp in $ \Gr' $ (lines~8-18).
+In line~1, we first create a hash structure, $h$, to maintain a mapping from all possible $ B(u),u \in \Vr $ to vertices of the resultant temporal aggregate network.
+In line~2-6, we group all vertices in $ \Vr $ with the specified aggregation $ A' $ and compute the aggregation result of numeric attributes of vertices with the specified aggregation function $ f_v $.
+
+Each snapshot $ \Sr[i] $ of $ \Gr $ should be aggregated into a smaller representation, i.e., the corresponding snapshot $ \Sr'[i] $ at the same timestamp in $ \Gr' $ (line~8-18).
 For each edge $ (u,v,a) $, we first map the two vertices $ u,v $ to $ u',v' $ using $ h $ (line~11-12).
-If there exists an aggregated edge $ (u',v',a') $ in $ \Sr'[i] $, we update $ a' $ with $ a $ using $ f_e $ (lines~16-18), otherwise we insert $ (u',v',a) $ into $ \Sr'[i] $ directly (line~14).
-
-It is easy to derive that the time complexity of Algorithm~\ref{alg:view_construct_baseline} is $ O(|\Vr|+\sum_{i=1}^{t_{end}}{|\Sr[i]|}) $.
-The space used to maintain $ h,W_{\Gr'} $ is $ O(\Vr') $ and we need $ O(|\Vr'|+\sum_{i=1}^{t_{end}}{|\Sr'[i]|}) $ space to maintain $ \Gr' $.
-Moreover, we can easily derive that $ |\Vr'| \leq |\Vr| $ and $ |\Sr'[i]| \leq |\Sr[i]| $.
-As a result, the space complexity of Algorithm~\ref{alg:view_construct_baseline} is $ O(|\Vr|+\sum_{i=1}^{t_{end}}{|\Sr[i]|}) $.
-
-%The time complexity of Algorithm~\ref{alg:view_construct_baseline} is $ O(|\Vr|+\sum_{i=1}^{t_{end}}{|\Sr[i]|}) $, which contains time used for traversing $ \Vr $ and $ \Sr $.
+If there exists an aggregated edge $ (u',v',a') $ in $ \Sr'[i] $, we update $ a' $ with $ a $ using $ f_e $ (line~16-18), otherwise we insert $ (u',v',a) $ into $ \Sr'[i] $ directly (line~14).
+
+The time complexity of Algorithm~\ref{alg:view_construct_baseline} is $ O(|\Vr|+\sum_{i=1}^{t_{end}}{|\Sr[i]|}) $, which contains time used for traversing $ \Vr $ and $ \Sr $.
 The space used to maintain $ h,W_{\Gr'} $ is $ O(\Vr') $ and we need $ O(|\Vr'|+\sum_{i=1}^{t_{end}}{|\Sr'[i]|}) $ space to maintain $ \Gr' $.
@@
 
-\comment{
-Similar to the static aggregate network in static graph cube, temporal aggregate networks can also be constructed from other existing temporal aggregate networks.
-For example, the temporal aggregate network with dimensions $ \{B_1,B_2\} $ can be constructed from the temporal aggregate network with dimensions $ \{B_1,B_2,B_3\} $, $ \{B_1,B_2,B_4\} $.
-The proof can be easily obtained by extending the proof from \cite{zhao2011graph}.
-}
-
+Similar to static aggregate network in static graph cube, temporal aggregate networks can also be construct from other existing temporal aggregate networks, e.g., temporal aggregate network with dimensions $ \{B_1,B_2\} $ can be constructed from temporal aggregate network with dimensions $ \{B_1,B_2,B_3\} $, $ \{B_1,B_2,B_4\} $, etc., instead of being constructed from the large-scale original network.
+The proof can be extended easily from \cite{zhao2011graph}.
 \begin{definition}[Temporal Graph Cube]
@@
 	Given a temporal multidimensional network $\Gr=(\Vr,\Sr,A,W)$, the temporal graph cube is obtained by decomposing $ A $ into all possible aggregations.
-Each aggregation $ A' $ is a node in the temporal graph cube and it corresponds to a temporal aggregate network $ \Gr' $ as defined in Definition~\ref{def:temp_aggregate_network}.
+Each aggregation $ A' $ is a node in the temporal graph cube and corresponds to a temporal aggregate network $ \Gr' $ as difined in Definition~\ref{def:temp_aggregate_network}.
 \end{definition}
 
-In \cite{zhao2011graph}, Zhao et al.\ used equivalently the terms \textit{cuboid}, \textit{view} and \textit{aggregation}.
-In this paper, however, we only use \textit{view} and \textit{aggregation} equivalently, while \textit{temporal cuboid} is used to refer to temporal cuboid query.
+In \cite{zhao2011graph}, Zhao et al.
+use equivalently the terms \textit{cuboid}, \textit{view} and \textit{aggregation}, however in this paper, we only use \textit{view} and \textit{aggregation} equivalently, while \textit{temporal cuboid} is used to refer to temporal cuboid query.
 In following sections, computing a view $ A' $ means materializing the corresponding temporal aggregate network $ \Gr' $ in memory.
-If $ A' $ is precomputed, then for simplicity, $ A' $ also refers to the corresponding temporal aggregate network $ \Gr' $.
-
-For a view $ A' $ in the temporal graph cube, $ dim(A') $ denotes the set of non-$\ast$ dimensions of $ A' $, i.e., $ dim(A')=B $ where $ B $ is the discrete attributes of vertices in $ \Gr' $, the corresponding temporal aggregate network of $ A' $.
+If $ A' $ is precomputed, then for simplicity, $ A' $ also refers to the corresponding temporal aggregate network $ \Gr' $ directly.
+
+For a view $ A' $ in temporal graph cube, similar to static cuboid in static graph cube, $ dim(A') $ denotes the set of non-$\ast$ dimensions of $ A' $, i.e., $ dim(A')=B $ where $ B $ is the discrete attributes of vertices in $ \Gr' $, the corresponding temporal aggregate network of $ A' $.
 For two views $ A' $ and $ A'' $, $ A' $ is an \textit{ancestor} of $ A'' $ and $ A'' $ is a \textit{descendant} of $ A' $ if $ dim(A') \subset dim(A'') $, denoted as $ A' \preceq A'' $.
-Especially, the base view $ A_{base} $ is a view where $ dim(A_{base})=A $, $ A $ is the dimensions of the original temp-multi-network.
-It is easy to see that $ A_{base} $ is a descendant of all other views.
-Another special view is $ A_{apex}=(\ast,\ast,...,\ast) $; and it is an ancestor of all other views in the temporal graph cube.
-%It is easy to check that the
-
-%\comment{
+Especially, the base view $ A_{base} $ is a view where $ dim(A_{base})=A $, $ A $ is the dimensions of the original temp-multi-network temporal graph cube built on.
+$ A_{base} $ don't need to be computed and it's a descendant of all other views.
+Another special view is $ A_{apex}=(\ast,\ast,...,\ast) $, and it's an ancestor of all other views in the temporal graph cube.
 \begin{figure}[t]
 	\begin{center}
-		\includegraphics[width=0.75\columnwidth]{fig/example/cube_lattice.pdf}
+		\includegraphics[width=0.95\columnwidth]{fig/example/cube_lattice.pdf}
 	\end{center}
-	\vspace*{-1cm}
+	\vspace*{-0.5cm}
 	\caption{A sample cube lattice}
-	\vspace*{-0.6cm}
+	\vspace*{-0.4cm}
 	\label{fig:cube_lattice}
@@
 \begin{example} \label{exam:cube_lattice}
-	Fig.~\ref{fig:cube_lattice} shows the temporal graph cube lattice built on the temp-multi-network in Fig.~\ref{fig:example_dataset}, each node on the lattice represents a view.
+	Figure~\ref{fig:cube_lattice} shows the temporal graph cube lattice built on temp-multi-network in Figure~\ref{fig:example_dataset}, each node on the lattice represents a view.
 For each edge in the lattice, the upper view is an ancestor of the lower view.
 \end{example}
-%}
-
 Temporal graph cube has the same form with static graph cube.
@@
 For each temporal aggregate network corresponding to a view, it contains more coarse-grained information than that of temporal aggregate network corresponding to a descendent view at each timestamp.
-In temporal graph cube, users can obtain summarized information in different resolution of the original temp-multi-network in a certain period by traversing the temporal graph cube lattice with specified time range.
-Users can also stay at some nodes in the lattice and query the summarized information in different time ranges.
-In these ways, summarized information of temp-multi-network in different resolutions and time ranges can be analyzed for decision support and business intelligence purposes.
-
-%\subsection{OLAP Queries}\label{subsec:queries}
-\section{Temporal OLAP Queries}  \label{sec:queries}
-Cuboid and crossboid are two important OLAP queries on static-multi-networks, or in static graph cubes \cite{zhao2011graph}.
-In this section, we propose a generalized definition of OLAP queries in temporal graph cube, by extending cuboid and crossboid to temporal cuboid and temporal crossboid respectively.
-%From the previous sections, we can find that the main difference of queries in static graph cube and temporal graph cube is the designation of time range.
-
-%\stitle{Temporal cuboid.}
-\subsection{Temporal Cuboid Query} \label{subsec:cuboid}
-The inputs of temporal cuboid query $ Q=(A',[l,r]) $ in temporal graph cube contain a specified view $A'=(A'_1,A'_2,...,A'_n)$ and a time range $[l,r]$.
-The output is a static aggregate network obtained by the query.
-%As illustrated in Example~\ref{exam:cuboid_query}, the first question can be represented by $ Q=((Gender),[2,3]) $, and the static aggregate network as the answer is shown in Fig.~\ref{fig:exam_cuboid_gender}.
+In temporal graph cube, users can obtain summative information in different resolution of the original temp-multi-network in certain period by traversing the temporal graph cube lattice with specified time range.
+Users can also stay at some nodes in the lattice and query the summative information in different time ranges.
+In these ways, summative information of temp-multi-network in different resolutions and time ranges can be analyzed for decision support and business intelligence purposes.
+
+\subsection{OLAP Queries}\label{subsec:queries}
+Cuboid and crossboid are two important OLAP queries on static-multi-network, or in static graph cube \cite{zhao2011graph}.
+In this section, we give the formal definition of OLAP queries in temporal graph cube, by extending cuboid and crossboid to temporal cuboid and temporal crossboid respectively.
+From the previous sections we can find that the main difference of queries in static graph cube and temporal graph cube is the designation of time range.
+
+\stitle{Temporal cuboid.} The inputs of temporal cuboid query $ Q=(A',[l,r]) $ in temporal graph cube contain a specified view $A'=(A'_1,A'_2,...,A'_n)$ and a time range $[l,r]$.
+The output is a static aggregate network.
+As in Example~\ref{exam:cuboid_query}, the first question can be represented by $ Q=((Gender),[2,3]) $, and the static aggregate network as the answer is shown in Figure~\ref{fig:exam_cuboid_gender}.
 
@@
 \end{algorithm}
-Algorithm~\ref{alg:temp_cuboid_baseline} is a basic algorithm to conduct temporal cuboid query on the original temp-multi-network (or on $ A_{base} $).
-Same as Algorithm~\ref{alg:view_construct_baseline}, Algorithm~\ref{alg:temp_cuboid_baseline} first conducts the specified aggregation on the whole vertex table of the original network, even those vertices who do not exist in any edge of snapshots in $[l,r]$ (lines~1-6).
-In lines~7-15, we merge all snapshots in $[l,r]$ by collecting all edges of those snapshots and summing the numeric attributes of edges sharing the same vertices using $ f_e $.
-Then, in lines~17-25, we map the two vertices of all edges in $ E' $ using $ h $ and compute the aggregation result of edges sharing the same mapped vertices using $ f_e $, which is similar to what Algorithm~\ref{alg:view_construct_baseline} does in each snapshot $ \Sr[i] $ of $ \Gr $ (lines~8-18 of Algorithm~\ref{alg:view_construct_baseline}).
-
-%As we have mentioned in Example~\ref{exam:cuboid_query}, it is necessary to aggregate all vertices in temporal cuboid query, since vertices are time independent and they are available in all time ranges.
-
-%Lines~1-6 in Algorithm~\ref{alg:temp_cuboid_baseline} is the same as lines~1-6 in Algorithm~\ref{alg:view_construct_baseline}.
-In lines~7-15, we merge all snapshots in $[l,r]$ by collecting all edges of those snapshots and summing the numeric attributes of edges sharing the same vertices using $ f_e $.
-Then, in lines~17-25, we map the two vertices of all edges in $ E' $ using $ h $ and compute the aggregation result of edges sharing the same mapped vertices using $ f_e $, which is similar to what Algorithm~\ref{alg:view_construct_baseline} does in each snapshot $ \Sr[i] $ of $ \Gr $ (lines~8-18 of Algorithm~\ref{alg:view_construct_baseline}).
-
-Before analyzing the time and space complexity of Algorithm~\ref{alg:temp_cuboid_baseline}, we first give a brief definition of summarized snapshot.
-\begin{definition}[Summarized Snapshot]
+Algorithm~\ref{alg:temp_cuboid_baseline} is a basic algorithm to conduct temporal cuboid query on original temp-multi-network (or on $ A_{base} $).
+Same as Algorithm~\ref{alg:view_construct_baseline}, Algorithm~\ref{alg:temp_cuboid_baseline} first conducts the specified aggregation on the whole vertex table of the original network, even those vertices who don't exist in any edge of snapshots in $[l,r]$ (line~1-6).
+As we have mentioned in Example~\ref{exam:cuboid_query}, it's necessary to aggregate all vertices in temporal cuboid query, since vertices are time independent and they are available in all time ranges.
+
+Process in line~1-6 is the same as line~1-6 in Algorithm~\ref{alg:view_construct_baseline}.
+In line~7-15, we merge all snapshots in $[l,r]$ by collecting all edges of those snapshots and summing the numeric attributes of edges sharing the same vertices using $ f_e $.
+Then in line~17-25, we map the two vertices of all edges in $ E' $ using $ h $ and compute the aggregation result of edges sharing the same mapped vertices using $ f_e $, which is similar to what Algorithm~\ref{alg:view_construct_baseline} do in each snapshot $ \Sr[i] $ of $ \Gr $ (line~8-18 of Algorithm~\ref{alg:view_construct_baseline}).
+
+Before giving time and space complexity of Algorithm~\ref{alg:temp_cuboid_baseline}, we first give a brief definition of summative snapshot.
+\begin{definition}[Summative Snapshot]
 	\label{def:sum_snap}
-	Given a temporal multidimensional network $\Gr=(\Vr,\Sr,A,W)$, the summarized snapshot $ S $ of $ \Gr $ is a special snapshot of $ \Gr $, which is the network structure in the result of a temporal cuboid query $ Q=(A,[1+t_{base},t_{end}+t_{base}]) $ on $ \Gr $.
+	Given a temporal multidimensional network $\Gr=(\Vr,\Sr,A,W)$, the summative snapshot $ S $ of $ \Gr $ is a special snapshot of $ \Gr $, which is the network structure in the result of a temporal cuboid query $ Q=(A,[1+t_{base},t_{end}+t_{base}]) $ on $ \Gr $.
 \end{definition}
-In other words, summarized snapshot $ S $ of $ \Gr $ can be obtained by merging all snapshots in a snapshot array $ \Sr $.
-
-The time complexity of Algorithm~\ref{alg:temp_cuboid_baseline} contains three parts: conducting aggregation on all vertices (lines~1-6), merging all snapshots in specified time range into $ E' $ (lines~7-15) and aggregating on $ E' $ (lines~17-25).
-Thus, the time complexity of Algorithm~\ref{alg:temp_cuboid_baseline} is $ O(|\Vr|+\sum_{i=l-t_{base}}^{r-t_{base}}|\Sr[i]|+|E'|) $.
-With the definition of summarized snapshot, we can rewrite the time complexity as $ O(|\Vr|+\sum_{i=l-t_{base}}^{r-t_{base}}|\Sr[i]|+|S|) $, since we can easily find $ |E'| \leq |S|$, where $ S $ is the summarized snapshot of $ \Gr $.
-The memory consumed by $V$, $h$ and $W_{G}$ is linearly with respect to $ |V| $ and $ |V| \leq |\Vr| $.
+In other words, summative snapshot $ S $ of $ \Gr $ can be obtained by merging all snapshots in snapshot array $ \Sr $.
+
+The time complexity of Algorithm~\ref{alg:temp_cuboid_baseline} contains three parts: conducting aggregation on all vertices (line~1-6), merging all snapshots in specified time range into $ E' $ (line~7-15) and aggregating on $ E' $ (line~17-25).
+So the time complexity of Algorithm~\ref{alg:temp_cuboid_baseline} is $ O(|\Vr|+\sum_{i=l-t_{base}}^{r-t_{base}}|\Sr[i]|+|E'|) $.
+With the definition of summative snapshot, we can rewrite the time complexity as $ O(|\Vr|+\sum_{i=l-t_{base}}^{r-t_{base}}|\Sr[i]|+|S|) $, since we can easily find $ |E'| \leq |S|$, where $ S $ is the summative snapshot of $ \Gr $.
+The memory consumed by $V$, $h$ and $W_{G}$ is linearly related to $ |V| $ and $ |V| \leq |\Vr| $.
 The size of $ E $, $ E' $ and $ EP $ are all smaller than $ |S| $, so the space complexity of Algorithm~\ref{alg:temp_cuboid_baseline} is $ O(|\Vr|+|S|) $.
 
-Given a temporal cuboid query $ Q=(A',[l,r]) $, if we have precomputed the view $ A' $ with the same aggregation functions, we can derive the result of $ Q $ from $ \Gr' $ by merging snapshots of $ \Gr' $ in $ [l,r] $ instead.
-Due to the space limit, all the proofs of this paper are omitted.
+Given a temporal cuboid query $ Q=(A',[l,r]) $, if we have precomputed the view $ A' $ with the same aggregation functions, we can get the result of $ Q $ from $ \Gr' $ by merging snapshots of $ \Gr' $ in $ [l,r] $ instead.
 
@@
 \end{theorem}
-
-\comment{
+Theorem~\ref{thm:cuboid_by_temp_aggre_network} gives another way to conduct $ Q $.
+The static aggregate network as the result of $ Q $ contains two parts: vertex table and a snapshot presenting the network structure.
+When $ A' $ is precomputed, the vertex table of the resultant static aggregate network is the same with vertex table of $ \Gr' $, the corresponding temporal aggregate network of $ A' $, and the network structure can be obtained by merging all snapshots of $ \Gr' $ in $ [l,r] $.
 \begin{proof}
-	Suppose that the result of $ Q=(A',[l,r]) $ is $ G=(V,E,B,W_{G}) $, and the original temp-multi-network is $ \Gr=(\Vr,\Sr,A,W) $, the temporal aggregate network of $ A' $ is $ \Gr'=(\Vr',\Sr',B,W_{\Gr'}) $.
-$ G $ is obtained from $ \Gr $ by Algorithm~\ref{alg:temp_cuboid_baseline}.
+	Suppose the result of $ Q=(A',[l,r]) $ is $ G=(V,E,B,W_{G}) $, and the original temp-multi-network is $ \Gr=(\Vr,\Sr,A,W) $, the temporal aggregate network of $ A' $ is $ \Gr'=(\Vr',\Sr',B,W_{\Gr'}) $.
+$ G $ is obtainted from $ \Gr $ by Algorithm~\ref{alg:temp_cuboid_baseline}.
 Since aggregating all vertices is the first step of both constructing $ \Gr' $ and obtaining $ G $, we have $ V=\Vr' $ and $ W_{G}=W_{\Gr'} $, i.e., the vertex table of $ G $ can be obtained from vertex table of $ \Gr' $ directly.
-For the network structure of $ G $, we only need to prove that the merging result of snapshots of $ \Gr' $ in $ [l,r] $, $ E' $, is identical to $ E $.
+As for network structure of $ G $, we only need to prove that the merging result of snapshots of $ \Gr' $ in $ [l,r] $, $ E' $, is identical to $ E $.
 
 	Suppose $ l,r $ have been converted to biased timestamps.
-Recall that we have a hash structure $ h $ used to maintain the mapping from $ \{B(u)|u \in \Vr\} $ to aggregated vertices set $ \Vr' $ and $ V $ in Algorithm~\ref{alg:view_construct_baseline} and Algorithm~\ref{alg:temp_cuboid_baseline} respectively.
-Since $ \Vr \rightarrow \{B(u)|u \in \Vr\} $ can also be regarded as a mapping, we can regard $ H $ as a mapping from $ \Vr $ to both $ \Vr' $ and $ V $, i.e., $ H(u)=h(B(u)) $.
-We first ignore the numeric attribute of each edge and prove that $ E'=E $.
-Since $ H $ can map the two vertices of edges in $ \Sr $ to their aggregated vertices, we let $ H^e $ be a mapping from edges in $ \Sr $ to their aggregated edges in $ \Sr' $ and in $ E $, i.e., $ H^e(e)=e' $ where $ e $ is an arbitrary edge in $ \Sr $ and $ e' $ is the aggregated edge of $ e $ in $ \Sr' $ or in $ E $.
-For $ E $, by Algorithm~\ref{alg:temp_cuboid_baseline}, we know that all snapshots of $ \Sr $ in $ [l,r] $ are merged into an intermediate result $ X=\bigcup_{i=l}^{r}\Sr[i] $ first.
-Then, $ E=\{H^e(e)|e \in X\} $.
+Recall the hash structure $ h $ used to maintain the mapping from $ \{B(u)|u \in \Vr\} $ to aggregated vertices set $ \Vr' $ and $ V $ in Algorithm~\ref{alg:view_construct_baseline} and Algorithm~\ref{alg:temp_cuboid_baseline} respectively, since $ \Vr \rightarrow \{B(u)|u \in \Vr\} $ can also be regarded as a mapping, here we can regard $ H $ as a mapping from $ \Vr $ to both $ \Vr' $ and $ V $, i.e., $ H(u)=h(B(u)) $.
+We first ignore the numeric attribute of each edge and prove $ E'=E $.
+Since $ H $ can map the two vertices of edges in $ \Sr $ to their aggregated vertices, let $ H^e $ be a mapping from edges in $ \Sr $ to their aggregated edges in $ \Sr' $ and in $ E $, i.e., $ H^e(e)=e' $ where $ e $ is an arbitrary edge in $ \Sr $ and $ e' $ is the aggregated edge of $ e $ in $ \Sr' $ or in $ E $.
+For $ E $, through Algorithm~\ref{alg:temp_cuboid_baseline} we know that all snapshots of $ \Sr $ in $ [l,r] $ are merged into an intermediate result $ X=\bigcup_{i=l}^{r}\Sr[i] $ first.
+Then $ E=\{H^e(e)|e \in X\} $.
 For $ E' $, we know that $ E' $ is obtained by merging all snapshots of $ \Sr' $ in $ [l,r] $ directly, i.e., $ E'=\bigcup_{i=l}^{r}\Sr'[i] $.
-By Algorithm~\ref{alg:view_construct_baseline}, we have $\forall i, \Sr'[i]=\{H^e(e)|e \in \Sr[i]\} $, so $ E'=\bigcup_{i=l}^{r}\{H^e(e)|e\in\Sr[i]\}=\{H^e(e)|e\in\bigcup_{i=l}^{r}\Sr[i]\} $.
+Through Algorithm~\ref{alg:view_construct_baseline} we have $\forall i, \Sr'[i]=\{H^e(e)|e \in \Sr[i]\} $, so $ E'=\bigcup_{i=l}^{r}\{H^e(e)|e\in\Sr[i]\}=\{H^e(e)|e\in\bigcup_{i=l}^{r}\Sr[i]\} $.
 As a result, $ E=E' $.
 
-	Then, we take numeric attributes of edges into account and suppose that the aggregation functions upon edges in $ \Gr' $ and in $ Q $ are both $ f_e $.
-The original form of edges in $ \Sr $ and in $ \Sr' $ is $ (u,v,a) $.
-We add the timestamp into the form of edges as $ (u,v,a,t) $ to distinguish edges in different snapshots but with the same vertices.
+	Then we take numeric attributes of edges into account and suppose the aggregation functions upon edges in $ \Gr' $ and in $ Q $ are both $ f_e $.
+The original form of edges in $ \Sr $ and in $ \Sr' $ is $ (u,v,a) $, suppose we add the timestamp into the form of edges as $ (u,v,a,t) $ to distinguish edges in different snapshots but with the same vertices.
 Each aggregated edge $ e\in E $ corresponds to a set of edges $TX_{\Sr}(e)=\{(u,v,a,i)|(u,v,a,i)\in \Sr[i],i\in [l,r],H^e((u,v))=(e.u,e.v)\} $, because $ e $ is obtained by merging and aggregating edges in $ TX_{\Sr}(e) $, and $ e.a $ is computed by executing $ f_e $ on multiset $ \{a|(u,v,a,t)\in TX_{\Sr}(e)\} $.
@@
 $ e' $ is obtained by merging edges in $TX_{\Sr'}(e')= \{(u,v,a,i)|(u,v,a,i) \in \Sr'[i],i \in [l,r],(u,v)=(e'.u,e'.v)\} $, and $ e'.a $ is computed by executing $ f_e $ on multiset $ \{a|(u,v,a,t)\in TX_{\Sr'}(e')\} $.
-Furthermore, each $ e'_t\in TX_{\Sr'}(e') $ where $ e'_t=(u,v,a,t) $ corresponds to a set of edges in $ \Sr[t] $, which is $TX_{\Sr[t]}(e'_t)= \{(u,v,a,t)|(u,v,a,t)\in \Sr[t],H^e((u,v))=(e'_t.u,e'_t.v)\} $.
+Further more, each $ e'_t\in TX_{\Sr'}(e') $ where $ e'_t=(u,v,a,t) $ corresponds to a set of edges in $ \Sr[t] $, which is $TX_{\Sr[t]}(e'_t)= \{(u,v,a,t)|(u,v,a,t)\in \Sr[t],H^e((u,v))=(e'_t.u,e'_t.v)\} $.
 $ e'_t.a $ is computed by executing $ f_e $ on multiset $ \{a|(u,v,a,t)\in TX_{\Sr[t]}(e'_t)\} $.
 As a result, $ e'.a $ can be computed by executing $ f_e $ on multiset $ \{a|(u,v,a,t)\in \bigcup_{e'_t\in TX_{\Sr'}(e')}TX_{\Sr[t]}(e'_t)\}=\{a|(u,v,a,t)\in TX_{\Sr}(e')\} $.
-Since $ (e'.u,e'.v)=(e.u,e.v) $, we have $ TX_{\Sr}(e')=TX_{\Sr}(e) $, and thus $ e'.a=e.a $.
-This completes the proof.
-%Finally, we prove that $ E' $, obtained by directly merging snapshots of $ \Gr' $, is equal to $ E $, the network structure in the result of $ Q $ by conducting $ Q $ on $ \Gr $.
+Since $ (e'.u,e'.v)=(e.u,e.v) $, we have $ TX_{\Sr}(e')=TX_{\Sr}(e) $, so $ e'.a=e.a $.
+Finally we prove that $ E' $, obtained by directly merging snapshots of $ \Gr' $, is equal to $ E $, the network structure in the result of $ Q $ by conducting $ Q $ on $ \Gr $.
 \end{proof}
-}
-
-Theorem~\ref{thm:cuboid_by_temp_aggre_network} gives another way to conduct $ Q $.
-The static aggregate network as the result of $ Q $ contains two parts: vertex table and a snapshot presenting the network structure.
-When $ A' $ is precomputed, the vertex table of the resulting static aggregate network is the same with vertex table of $ \Gr' $, the corresponding temporal aggregate network of $ A' $, and the network structure can be obtained by merging all snapshots of $ \Gr' $ in $ [l,r] $.
-
-The algorithm of conducting $ Q $ on $ \Gr' $ is exactly the subprocess in lines~7-15 of Algorithm~\ref{alg:temp_cuboid_baseline} if we replace $ \Gr $ with $ \Gr' $.
+
+The algorithm of conducting $ Q $ on $ \Gr' $ is exactly the subprocess in line~7-15 of Algorithm~\ref{alg:temp_cuboid_baseline} if we replace $ \Gr $ with $ \Gr' $.
 The time complexity of the simpler algorithm is $ O(\sum_{i=l-t_{base}}^{r-t_{base}}|\Sr'[i]|) $.
-It is easy to see that $ |\Sr'[i]| \leq |\Sr[i]| $, so this simpler algorithm is better than the baseline algorithm.
-
-If the view $ A' $ is not precomputed while some other view $ A'' $ is precomputed with the same aggregation functions and $ dim(A') \subset dim(A'') $, we can use the corresponding temporal aggregate network $ \Gr'' $ of $ A'' $ to get the result of $ Q $.
-The algorithm is exactly Algorithm~\ref{alg:temp_cuboid_baseline}, where we only need to replace $ \Gr $ with $ \Gr'' $.
+It's clear that $ |\Sr'[i]| \leq |\Sr[i]| $, so the new algorithm is better than the baseline algorithm.
+
+If view $ A' $ is not precomputed while some other view $ A'' $ is precomputed with the same aggregation functions and $ dim(A') \subset dim(A'') $, we can use the corresponding temporal aggregate network $ \Gr'' $ of $ A'' $ to get the result of $ Q $.
+The algorithm is exactly Algorithm~\ref{alg:temp_cuboid_baseline}, where we only need replace $ \Gr $ with $ \Gr'' $
 
@@
 \end{theorem}
-\comment{
 \begin{proof}
@@
 $ T'' $ is obtained by two group-by operations: group-by on $ (\Vr,A,W) $ with $ A'' $, obtaining $ (\Vr'',B'',W_{\Gr''}) $, and group-by on $ (\Vr'',B'',W_{\Gr''}) $ with $ A' $.
-It is easy to know that the two group-by operations to obtain $ T'' $ is equivalent to the single group-by operation to obtain $ T $, because $ dim(A') \subset dim(A'') $.
+It's easy to know that the two group-by operations to obtain $ T'' $ is equivalent to the single group-by operation to obtain $ T $, because $ dim(A') \subset dim(A'') $.
 So $ T $ and $ T'' $ are the same vertex table.
@@
 The reason is that in line~2-6 of Algorithm~\ref{alg:view_construct_baseline} and Algorithm~\ref{alg:temp_cuboid_baseline}, we simply map $ B(u) $ to the first $ u $ that satisfies $ h(B(u))=NULL $ and the order $ u $ is traversed is uncertain.
-It is not important for group-by operations, but to prove $ E=E'' $, we need to assume that $ u $ is traversed in ascending order first ($ V=V'' $ in this case).
+It's not important for group-by operations, but to prove $ E=E'' $, we need to assume that $ u $ is traversed in ascending order first ($ V=V'' $ in this case).
 
@@
 We first prove $ \forall u\in \Vr, H_1(u)=H_3(H_2(u)) $.
-It is clear that $ [u]_{B'',\Vr}\subseteq [u]_{B,\Vr} $ because $ B\subset B'' $ ($ dim(A')\subset dim(A'') $).
+It's clear that $ [u]_{B'',\Vr}\subseteq [u]_{B,\Vr} $ because $ B\subset B'' $ ($ dim(A')\subset dim(A'') $).
 Since $ H_1(u)=MIN([H_1(u)]_{B,\Vr}) $, $ [H_1(u)]_{B'',\Vr}\subseteq [H_1(u)]_{B,\Vr} $ and $ H_1(u)\in [H_1(u)]_{B'',\Vr}$, we have $ H_1(u)=MIN([H_1(u)]_{B'',\Vr}) $, so $ H_2(H_1(u))=H_1(u) $.
@@
 \end{proof}
-}
-
-The time complexity of conducting $ Q $ on $ \Gr'' $ is $ O(|\Vr''|+\sum_{i=l-t_{base}}^{r-t_{base}}|\Sr''[i]|+|S''|) $, where $ |\Vr''|,|\Sr''[i]| $ and $ |S''| $ are vertex set, snapshot at $ i $ and summarized snapshot of $ \Gr'' $ respectively.
-We also have $ |\Vr''| \leq |\Vr|,|\Sr''[i]| \leq |\Sr[i]|$ and $|S''| \leq |S| $; and in practice, $ |\Vr''|,|\Sr''[i]| $ and $ |S''| $ are much smaller than $ |\Vr|,|\Sr[i]| $ and $ |S| $ respectively.
+
+The time complexity of conducting $ Q $ on $ \Gr'' $ becomes $ O(|\Vr''|+\sum_{i=l-t_{base}}^{r-t_{base}}|\Sr''[i]|+|S''|) $, where $ |\Vr''|,|\Sr''[i]| $ and $ |S''| $ are vertex set, snapshot at $ i $ and summative snapshot of $ \Gr'' $ respectively.
+We can also easily have $ |\Vr''| \leq |\Vr|,|\Sr''[i]| \leq |\Sr[i]|$ and $|S''| \leq |S| $ and in practice, $ |\Vr''|,|\Sr''[i]| $ and $ |S''| $ are much smaller than $ |\Vr|,|\Sr[i]| $ and $ |S| $ respectively.
 
 If we have a set of precomputed views $ \{A_1'',A_2'',...\} $ with the same aggregation functions and for each $ A_i'' $, $ dim(A') \subset dim(A_i'') $, which one should we choose in conducting $ Q $ using Algorithm~\ref{alg:temp_cuboid_baseline}?
-There is a similar problem in static graph cube, in which we only need to choose the view in $ \{A_1'',A_2'',...\} $ with the smallest size, since the time complexity of conducting a query $ Q=(A') $ on the basis of $ A_i'' $ in static graph cube equals the size of $ A_i'' $.
-It is easy to obtain the size of precomputed views of static graph cube in $ O(1) $ time.
+There is a similar problem in static graph cube, in which we only need to choose the view in $ \{A_1'',A_2'',...\} $ with the smallest size, since time complexity of conducting a query $ Q=(A') $ on the basis of $ A_i'' $ in static graph cube equals the size of $ A_i'' $.
+It's easy to obtain the size of precomputed views of static graph cube in $ O(1) $ time.
 
 However, in temporal graph cube, extra time range should be specified in each query, so the time complexity of conducting a query $ Q=(A',[l,r]) $ on $ A_i'' $ is not the size of $ A_i'' $.
-It is hard to compute the accurate time complexity of Algorithm~\ref{alg:temp_cuboid_baseline} in $ O(1) $ time.
+It's hard to compute the accurate time complexity of Algorithm~\ref{alg:temp_cuboid_baseline} in $ O(1) $ time.
 The reasons are as follows:
@@
 	\item If we want to compute the accumulation part ($ \sum_{i=l-t_{base}}^{r-t_{base}}|\Sr[i]| $) in the time complexity of Algorithm~\ref{alg:temp_cuboid_baseline} in $ O(1) $ time, an extra prefix array should be maintained.
-	\item The size of summarized snapshot $ |S| $ is just an upper bound of the number of edges visited in $ E' $ of Algorithm~\ref{alg:temp_cuboid_baseline}.
+	\item The size of summative snapshot $ |S| $ is just an upper bound of the number of edges visited in $ E' $ of Algorithm~\ref{alg:temp_cuboid_baseline}.
 To get the accurate value of $ |E'| $ as fast as possible, we may have to build some indexes to get $ E' $ first.
-However, it is also difficult to get $ |E'| $ in $ O(1) $ time using indexes (we will discuss building indexes in Section~\ref{sec:indexes}).
+However, it is also difficult to get $ |E'| $ in $ O(1) $ time using indexes (we will talk about building indexes in Section~\ref{sec:indexes}).
 \end{itemize}
-
-Interestingly, we can avoid the problem of choosing an ideal $ A_i'' $ by adopting the partial materialization strategy \kw{MinLevel} \cite{zhao2011graph}, which we will discuss in Section~\ref{sec:partial_materialization}.
-%
-%Let's recall the time complexity of Algorithm~\ref{alg:temp_cuboid_baseline}: $ O(|\Vr|+\sum_{i=l-t_{base}}^{r-t_{base}}|\Sr[i]|+|S|) $, where $ \Vr $ and $ \Sr[i] $ are the node set and snapshot of the inputed temp-multi-network, $ S $ is the summarized snapshot of the inputed temp-multi-network.
+We can avoid the problem of choosing an ideal $ A_i'' $ by the partial materialization strategy \kw{MinLevel} introduced in \cite{zhao2011graph}, which we will discuss in Section~\ref{sec:partial_materialization}.
+%
+%Let's recall the time complexity of Algorithm~\ref{alg:temp_cuboid_baseline}: $ O(|\Vr|+\sum_{i=l-t_{base}}^{r-t_{base}}|\Sr[i]|+|S|) $, where $ \Vr $ and $ \Sr[i] $ are the node set and snapshot of the inputed temp-multi-network, $ S $ is the summative snapshot of the inputed temp-multi-network.
 Our goal is to get the value of time complexity of Algorithm~\ref{alg:temp_cuboid_baseline} with corresponding $ \Gr_i'' $ of each $ A_i'' $ as the inputed temp-multi-network in $ O(1) $ time and then choose the lowest time complexity and the corresponding $ \Gr_i'' $.
@@
 %\end{equation}
-%It is easy to update $ pArray $ and $ \Sr''[j] $ according to their definitions when adding new edges at the latest timestamp in each $ \Gr_i'' $ (we will talk about adding new edges into temporal graph cube in Section~\ref{subsec:growing}).
+%It's easy to update $ pArray $ and $ \Sr''[j] $ according to their definitions when adding new edges at the latest timestamp in each $ \Gr_i'' $ (we will talk about adding new edges into temporal graph cube in Section~\ref{subsec:growing}).
 As a result, we can compute the value of time complexity of Algorithm~\ref{alg:temp_cuboid_baseline} with different $ \Gr_i'' $ as the inputed temp-multi-network by $ |\Vr_i''|+pArray[r-t_{base}]-pArray[l-t_{base}-1]+|S_i''| $ in $ O(1) $ time.
@@
 
-After discussing the temporal cuboid query, we can describe the OLAP operations in temporal graph cube, such as roll-up, drill-down and slice-and-dice.
-Suppose that we have conducted a temporal cuboid query $ Q_0=(A_0,[l,r]) $.
-Roll-up means conducting another query $ Q_1=(A_1,[l,r]) $ where $ A_1 $ is an ancestor of $ A_0 $, so that we get a coarser resolution of summarized information of temp-multi-network in the same time range.
-Drill-down is a contrary operation to obtain a finer summarized information in the same time range by conducting $ Q_2=(A_2,[l,r]) $ where $ A_2 $ is a descendent of $ A_0 $.
+After discussing temporal cuboid query in detail, we can clearly describe the support to OLAP operations in temporal graph cube, such as roll-up, drill-down and slice-and-dice.
+Suppose we have conducted a temporal cuboid query $ Q_0=(A_0,[l,r]) $.
+Roll-up means conducting another query $ Q_1=(A_1,[l,r]) $ where $ A_1 $ is an ancestor of $ A_0 $, so that we get a coarser resolution of summative information of temp-multi-network in the same time range.
+Drill-down is a contrary operation to obtain a finer summative information in the same time range by conducting $ Q_2=(A_2,[l,r]) $ where $ A_2 $ is a descendent of $ A_0 $.
 Slice-and-dice can be performed by selecting a subset of vertices in the vertex table of $ Q_0 $'s result and generating the induced network.
-For example, $ Q_0=((Profession),[2,5]) $ in temporal graph cube built on temp-multi-network in Fig.~\ref{fig:example_dataset}, we can choose to build an induced network based on the result of $ Q_0 $ with only ``teacher" and ``student" being selected to show the transactions between ``teacher" and ``student" from day 2 to 5.
+For example, $ Q_0=((Profession),[2,5]) $ in temporal graph cube built on temp-multi-network in Figure~\ref{fig:example_dataset}, we can choose to build an induced network on the basis of the result of $ Q_0 $ with only ``teacher" and ``student" being selected to clearly show the transactions between ``teacher" and ``student" from day 2 to day 5.
 
 We can also extend roll-up and drill-down according to the specified time ranges.
-A time related roll-up means conducting a query $ Q_1=(A_0,[l_1,r_1]) $ where $ l_1 \leq l $ and $ r_1 \geq r $, so that we can get a coarser resolution of summarized information in time axis.
+A time related roll-up means conducting a query $ Q_1=(A_0,[l_1,r_1]) $ where $ l_1 \leq l $ and $ r_1 \geq r $, so that we can get a coarser resolution of summative information in time axis.
 On the contrary, time related drill-down means conducting a query $ Q_2=(A_0,[l_2,r_2]) $ where $ l_2 \geq l $ and $ r_2 \leq r $.
 
-%\stitle{Temporal crossboid.}
-\subsection{Temporal Crossboid Query} \label{subsec:crossboid}
-The inputs of temporal crossboid query $ Q_{cross}=(A'_1,A'_2,[l,r]) $ in temporal graph cube contain two specified views $ A_1'=(A_{11}',A_{12}',...,A_{1n}') $, $ A_2'=(A_{21}',A_{22}',...,A_{2n}') $ and a time interval $ [l,r] $, where $ A_1' \neq A_2' $.
+\stitle{Temporal crossboid.} The inputs of temporal crossboid query $ Q_{cross}=(A'_1,A'_2,[l,r]) $ in temporal graph cube contain two specified views $ A_1'=(A_{11}',A_{12}',...,A_{1n}') $, $ A_2'=(A_{21}',A_{22}',...,A_{2n}') $ and a time interval $ [l,r] $, where $ A_1' \neq A_2' $.
 The output is a static aggregate bipartite network with two types of aggregated vertices corresponding to aggregations $ A_1' $ and $ A_2' $ respectively.
-%For example, the question in Example~\ref{exam:crossboid_query} can be represented by $ Q_{cross}=((Gender),(Profession),[2,3]) $.
+For example, the question in Example~\ref{exam:crossboid_query} can be represented by $ Q_{cross}=((Gender),(Profession),[2,3]) $.
 
 We can conduct a temporal crossboid query directly on the original temp-multi-network.
-However, it is inefficient due to the large size of the original temp-multi-network.
+However, it's inefficient due to the size of the original temp-multi-network.
 We omit the algorithm to conduct a temporal crossboid query on the original temp-multi-network, but give a more efficient way to conduct the query.
@@
 	\label{thm:ans_cross_by_ncd}
-	Given a temporal crossboid query $ Q_{cross}=(A_1',A_2',[l,r]) $, $ Q_{cross} $ can be answered from the result of the temporal cuboid query $ Q=(ncd(A_1',A_2'),[l,r]) $ where $ Q,Q_{cross} $ share the same aggregation function upon vertices and edges.
+	Given a temporal crossboid query $ Q_{cross}=(A_1',A_2',[l,r]) $, $ Q_{cross} $ can be directly answered from the result of temporal cuboid query $ Q=(ncd(A_1',A_2'),[l,r]) $ where $ Q,Q_{cross} $ share the same aggregation function upon vertices and edges.
 \end{theorem}
-\comment{
 \begin{proof}
@@
 \end{proof}
-}
-%With Theorem~\ref{thm:ans_cross_by_ncd}, a temporal crossboid query can be turned into a temporal cuboid query and we have discussed how to conduct a temporal cuboid query efficiently in \stitle{Temporal cuboid} section.
-With Theorem~\ref{thm:ans_cross_by_ncd}, a temporal crossboid query can be turned into a temporal cuboid query, and thus can be solved by our previous techniques.
-
+With Theorem~\ref{thm:ans_cross_by_ncd}, a temporal crossboid query can be turned into a temporal cuboid query and we have discussed how to conduct a temporal cuboid query efficiently in \stitle{Temporal cuboid} section.
 %\begin{theorem}
@@
 Algorithm~\ref{alg:temp_crossboid_on_cuboid} is an algorithm to compute the result of $ Q_{cross}=(A_1',A_2',[l,r]) $ from the result of $ Q=(ncd(A_1',A_2'),[l,r]) $.
-Unlike Algorithm~\ref{alg:temp_cuboid_baseline}, we need aggregate each vertex on two different aggregations $ A_1' $ and $ A_2' $ (lines~3-11).
-For each edge $ (u,v,a) $ in $ G $, we need to create or update two aggregated edges $ (u',v'',\ast) $ and $ (v',u'',\ast) $ (lines~12-27), because the two directions of $ (u,v,a) $ represent two interactions of aggregated vertices respectively (note that we do not assign $ u' \leq v'' $ or $ v' \leq u'' $ in $ E_B $).
+Unlike Algorithm~\ref{alg:temp_cuboid_baseline}, we need aggregate each vertex on two different aggregations $ A_1' $ and $ A_2' $ (line~3-11).
+For each edge $ (u,v,a) $ in $ G $, we need to create or update two aggregated edges $ (u',v'',\ast) $ and $ (v',u'',\ast) $ (line~12-27), because the two directions of $ (u,v,a) $ represent two interactions of aggregated vertices respectively (note that we don't assign $ u' \leq v'' $ or $ v' \leq u'' $ in $ E_B $).
 The time complexity of Algorithm~\ref{alg:temp_crossboid_on_cuboid} is $ O(|V|+|E|) $.
-We can easily derive that $ |V_1|+|V_2| \leq 2|V| $ and $ |E_B| \leq 2|E| $ in Algorithm~\ref{alg:temp_crossboid_on_cuboid}, so the space complexity of Algorithm~\ref{alg:temp_crossboid_on_cuboid} is also $ O(|V|+|E|) $.
-
-\comment{
+We can easily find that $ |V_1|+|V_2| \leq 2|V| $ and $ |E_B| \leq 2|E| $ in Algorithm~\ref{alg:temp_crossboid_on_cuboid}, so the space complexity of Algorithm~\ref{alg:temp_crossboid_on_cuboid} is also $ O(|V|+|E|) $.
+
 \subsection{Growth of Network}\label{subsec:growing}
-Compared to static network, temporal network records ongoing relationships between vertices, which means that we should append new edges into temporal network.
-For example, the temp-multi-network in Fig.~\ref{fig:example_dataset} should record new transactions between any two individuals in day 5 and in all following days.
-Specifically, suppose that we need to add a new edge $ (u,v,t,a) $ with discrete and numeric attributes $ (A(u),W(u),A(v),W(v)) $ of two vertices, there are two situations: 1) $ t-t_{base}=t_{end} $ ($ t=t_{|\Tr|} $, i.e., $ t $ equals the latest timestamp in the temporal graph cube).
+Compared to static network, temporal network records ongoing relationships between vertices, which means we should append new edges into temporal network.
+For example, the temp-multi-network in Figure~\ref{fig:example_dataset} should record new transactions between any two individuals in day 5 and in all following days.
+Specifically, suppose we need to add a new edge $ (u,v,t,a) $ with discrete and numeric attributes $ (A(u),W(u),A(v),W(v)) $ of two vertices, there are two situations: 1) $ t-t_{base}=t_{end} $ ($ t=t_{|\Tr|} $, i.e., $ t $ equals the latest timestamp in the temporal graph cube).
 2) $ t-t_{base}>t_{end} $.
 
-For the original temp-multi-network $ \Gr=(\Vr,\Sr,A,W) $, it is simple to add a new edge in both situations.
+For the original temp-multi-network $ \Gr=(\Vr,\Sr,A,W) $, it's simple to add a new edge in both situations.
 In situation 1), we only need to add $ u,v $ into $ \Vr $, update $ A,W $ with $ (A(u),W(u),A(v),W(v)) $ if $ u $ and $ v $ are new vertices and then $ (u,v,a) $ will be added into $ \Sr[t_{end}] $.
 In situation 2), the only difference is that we should extend $ \Sr $ and create an empty snapshot $ \Sr[t-t_{base}] $, then we add $ (u,v,a) $ into $ \Sr[t-t_{base}] $.
-Finally, we update $ t_{end} $ to $ t-t_{base} $.
-
-For any precomputed view $ A' $ and its corresponding temporal aggregate network $ \Gr'=(\Vr',\Sr',B,W_{\Gr'}) $, if $ u $ is a new vertex in the original temp-multi-network, we need to create or update an aggregated vertex $ u' $ in $ \Vr' $ according to $ h(B(u)) $, where $ h $ is the hash structure used in construction of $ \Gr' $ and update $ h $ if $ h(B(u))=NULL $ (lines~3-6 in Algorithm~\ref{alg:view_construct_baseline}).
-We do the same process for $ v $.
-Then, we map $ (u,v,a) $ to $ (u',v',a) $ (lines~11-12 in Algorithm~\ref{alg:view_construct_baseline}), which can be regarded as the new edge for $ \Gr' $.
-If situation 1) is met, we create or update aggregated edge $ (u',v',\ast) $ in $ \Sr'[t_{end}] $ with $ (u',v',a) $ as lines~13-18 in Algorithm~\ref{alg:view_construct_baseline}.
+Finally we update $ t_{end} $ to $ t-t_{base} $.
+
+For any precomputed view $ A' $ and its corresponding temporal aggregate network $ \Gr'=(\Vr',\Sr',B,W_{\Gr'}) $, if $ u $ is a new vertex in the original temp-multi-network, we need to create or update an aggreagted vertex $ u' $ in $ \Vr' $ according to $ h(B(u)) $, where $ h $ is the hash structure used in construction of $ \Gr' $ and update $ h $ if $ h(B(u))=NULL $ (line~3-6 in Algorithm~\ref{alg:view_construct_baseline}).
+We do the same for $ v $.
+Then we map $ (u,v,a) $ to $ (u',v',a) $ (line~11-12 in Algorithm~\ref{alg:view_construct_baseline}), which can be regarded as the new edge for $ \Gr' $.
+If situation 1) is met, we create or update aggregated edge $ (u',v',\ast) $ in $ \Sr'[t_{end}] $ with $ (u',v',a) $ as line~13-18 in Algorithm~\ref{alg:view_construct_baseline}.
 If situation 2) is met, we also extend $ \Sr' $ and create an empty snapshot $ \Sr'[t-t_{base}] $, then add $ (u',v',a) $ directly into $ \Sr'[t-t_{base}] $ and update $ t_{end} $ to $ t-t_{base} $ in $ \Gr' $.
 
-}
-
-\comment{
 \begin{figure}[t!]
@@
 	\vspace*{-0.4cm}
-	\caption{Snapshots of temp-multi-network in memory at day 5 after a new edge is added}
+	\caption{Snapshots of temp-multi-network in memory at day 5 after new edge is added}
 	\vspace*{-0.4cm}
@@
 	\vspace*{-0.4cm}
-	\caption{Snapshots of temp-multi-network in memory at day 6 after a new edge is added}
+	\caption{Snapshots of temp-multi-network in memory at day 6 after new edge is added}
 	\vspace*{-0.4cm}
@@
 \begin{example} \label{exam:network_growth}
-	Suppose that we need to add two new edges $ e_1=(v_2,v_3,5,10) $ and $ e_2=(v_6,v_9,6,5) $ successively where $ A(v_9)=(female,cn,student) $, $ W(v_9)=800 $ into temporal graph cube built on temp-multi-network in Fig.~\ref{fig:example_dataset} and only two views are precomputed: $ (Gender,\ast,\ast) $ and $ (Gender,\ast,Profession) $.
-Fig.~\ref{fig:add_edge_at_5} shows the snapshots at day 5 of all temp-multi-networks in the temporal graph cube after $ e_1 $ is added.
-Since $ v_2 $ and $ v_3 $ are both females, the self loop edge on ``female" in the 5-th snapshot in Fig.~\ref{fig:aggregation_gender} should be updated to the corresponding self loop in Fig.~\ref{fig:add_edge_at_5} (b).
-Similar update should be performed in the 5-th snapshot in Fig.~\ref{fig:aggregation_gender_profession}, and the result is shown in Fig.~\ref{fig:add_edge_at_5} (c).
+	Suppose we need to add two new edges $ e_1=(v_2,v_3,5,10) $ and $ e_2=(v_6,v_9,6,5) $ successively where $ A(v_9)=(female,cn,student) $, $ W(v_9)=800 $ into temporal graph cube built on temp-multi-network in Figure~\ref{fig:example_dataset} and only two views are precomputed: $ (Gender,\ast,\ast) $ and $ (Gender,\ast,Profession) $.
+Figure~\ref{fig:add_edge_at_5} shows the snapshots at day 5 of all temp-multi-networks in the temporal graph cube after $ e_1 $ is added.
+Since $ v_2 $ and $ v_3 $ are both females, the self loop edge on ``female" in the 5-th snapshot in Figure~\ref{fig:aggregation_gender} should be updated to the corresponding self loop in Figure~\ref{fig:add_edge_at_5} (b).
+Similar update should be performed in the 5-th snapshot in Figure~\ref{fig:aggregation_gender_profession}, and the result is shown in Figure~\ref{fig:add_edge_at_5} (c).
 
 	When adding $ e_2 $, we need to create new snapshot in each temp-multi-network of the temporal graph cube because $ e_2 $ leads to a new timestamp day 6.
-For the original network, we create a new snapshot at day 6 as Fig.~\ref{fig:add_edge_at_6} (a) with only $ e_2 $ being stored after all attributes of $ v_9 $ are added into the vertex table of the original temp-multi-network.
-For other temp-multi-networks of precomputed views, we should also create new snapshots at day 6, holding the aggregated edges of $ e_2 $ as in Fig.~\ref{fig:add_edge_at_6} (b) and (c) after the aggregated vertices of $ v_9 $ are added or updated.
+For the original network, we create a new snapshot at day 6 as Figure~\ref{fig:add_edge_at_6} (a) with only $ e_2 $ being stored after all attributes of $ v_9 $ are added into the vertex table of the original temp-multi-network.
+For other temp-multi-networks of precomputed views, we should also create new snapshots at day 6, holding the aggregated edges of $ e_2 $ as in Figure~\ref{fig:add_edge_at_6} (b) and (c) after the aggregated vertices of $ v_9 $ are added or updated.
 \end{example}
-}
-
-%\section{The Proposed Indexes} \label{sec:indexes}
-\section{The Index-based Approach}\label{sec:indexes}
-In this section, we propose an index-based approach to process the temporal cuboid query (temporal crossboid queries can be transformed to temporal cuboid queries).
-Recall that for a temporal cuboid query $ Q=(A',[l,r]) $, we need to merge snapshots of a certain temp-multi-network in time range $ [l,r] $ whether $ A' $ is precomputed or not (see lines~8-15 of Algorithm~\ref{alg:temp_cuboid_baseline}).
-Merging snapshots in time ranges is similar to the classic range query problem: answering online queries $ q=(func,[l,r]) $ on a numeric array $ Arr $, where $ func $ might be SUM($\ast$), AVERAGE($\ast$), MAX($\ast$) or MIN($\ast$), specifying the needed statistical results of values in range $ [l,r] $ of $ Arr $.
-We can regard merging snapshots in snapshot array as a range query problem on a snapshot array.
+
+\section{Indexes} \label{sec:indexes}
+In this section, we mainly discuss how to build indexes in temporal graph cube to accelerate temporal cuboid query (temporal crossboid query can be turned into temporal cuboid query).
+In Section~\ref{subsec:queries}, given a temporal cuboid query $ Q=(A',[l,r]) $, we merge snapshots of a certain temp-multi-network in time range $ [l,r] $  (i.e., line~8-15 of Algorithm~\ref{alg:temp_cuboid_baseline}), whether $ A' $ is precomputed or not.
+Merging snapshots in time ranges is similar to common range query problem: answering plenty of online queries $ q=(func,[l,r]) $ on a numeric array $ Arr $, where $ func $ could be SUM($\ast$), AVERAGE($\ast$), MAX($\ast$) or MIN($\ast$), specifying the needed statistical result of values in range $ [l,r] $ of $ Arr $.
+We can regard merging snapshots in snapshot array as range query problem on snapshot array.
 
@@
 		\begin{tabular}[t]{c}\hspace*{-0.3cm}
-%			\subfigure[{\scriptsize A numeric array}]{
-%				\includegraphics[width=0.85\columnwidth]{fig/example/example_numeric_array_adjust.pdf}
-%			}
-%			\hspace*{-0.3cm}
-%			\\
-			\subfigure[{\scriptsize A snapshot array extracted from Fig.~\ref{fig:aggregation_gender_profession}}]{
-				\includegraphics[width=0.7\columnwidth]{fig/example/example_snapshot_array.pdf}
+			\subfigure[{\scriptsize A numeric array}]{
+				\includegraphics[width=0.85\columnwidth]{fig/example/example_numeric_array_adjust.pdf}
 			}
 			\hspace*{-0.3cm}
-	%		\\
+			\\
+			\subfigure[{\scriptsize A snapshot array extracted from Figure~\ref{fig:aggregation_gender_profession}}]{
+				\includegraphics[width=0.95\columnwidth]{fig/example/example_snapshot_array.pdf}
+			}
+			\hspace*{-0.3cm}
+			\\
 			\subfigure[{\scriptsize Result of range query $ Q $ in Example~\ref{exam:range_query_num_snap_array}}]{
-				\includegraphics[width=0.25\columnwidth]{fig/example/example_range_query_snapshot.pdf}
+				\includegraphics[width=0.45\columnwidth]{fig/example/example_range_query_snapshot.pdf}
 			}
@@
 	\end{center}
-	\vspace*{-0.6cm}
-	\caption{Range query on a snapshot array}
+	\vspace*{-0.4cm}
+	\caption{Range query on numeric and snapshot array}
 	\vspace*{-0.4cm}
@@
 \begin{example} \label{exam:range_query_num_snap_array}
-Fig.~\ref{fig:range_query_num_snap_array} (a) is a snapshot array of temporal aggregate network of precomputed view $ (Gender,\ast,Profession) $ in Fig.~\ref{fig:aggregation_gender_profession}.
-Here we renumber all vertices and omit the isolated vertices in each snapshot for simplicity.
-Suppose that a range query on the snapshot array in Fig.~\ref{fig:range_query_num_snap_array} (a) is $ Q=((Gender,\ast,Profession),[2,4]) $ with SUM($\ast$) specified upon edges.
-We can derive that the result of $ Q $ as shown in Fig.~\ref{fig:range_query_num_snap_array} (b).
+	Figure~\ref{fig:range_query_num_snap_array} (a) shows a numeric array of length 5.
+Figure~\ref{fig:range_query_num_snap_array} (b) is the snapshot array of temporal aggregate network of precomputed view $ (Gender,\ast,Profession) $ in Figure~\ref{fig:aggregation_gender_profession} but we renumber all vertices and omit the isolated vertices in each snapshot for simplicity.
+For example, range query on numeric array in Figure~\ref{fig:range_query_num_snap_array} (a) can be $ q=(SUM(\ast),[2,4]) $, which queries the amount of values in $ [2,4] $ of the numeric array.
+Range query on snapshot array in Figure~\ref{fig:range_query_num_snap_array} (b) can be $ Q=((Gender,\ast,Profession),[2,4]) $ with SUM($\ast$) specified upon edges.
+The result of $ Q $ is shown in Figure~\ref{fig:range_query_num_snap_array} (c).
 \end{example}
 
-%%%%%%%%%
-\comment{
-Note that there are two differences between the range query on the numeric array and the snapshot array:
+There are mainly two differences between range query on snapshot array and numeric array:
 \begin{itemize}[leftmargin=*]
-	\item We need to merge both the structural information of snapshots and the numeric attributes of edges in snapshots in certain ranges.
-The range query on the snapshot array can be regarded as the range query on a set array, in which we calculate the union of sets in specified range and maintain the statistical results of numeric attributes on all elements (edges).
-
-	\item For the range query on the numeric array, modifying the value at an arbitrary place in the array can be well supported, but updating the size of the array is often hard to support.
-However, in temp-multi-network, with the time goes on, the edges will be added into the temp-multi-network.
-Thus, we need to consider update the size of the array.
+	\item We should merge both the structural information of snapshots and the numeric attributes of edges in snapshots in certain ranges.
+Range query on snapshot array can be regarded as range query on set array, in which we calculate the union of sets in specified range and maintain the statistical results of numeric attributes on all elements (edges).
+
+	\item Adding (or appending) edges should be considered.
+In range query problem on numeric array, modifying the value at an arbitrary place in the array is sometimes being considered, but the size of the array is hardly changed.
+However in temp-multi-network, with the time goes on, more edges will be added into the temp-multi-network, while the past edges are seldom to be modified.
 \end{itemize}
 
-To address these differences, we propose a segment-tree based index structure to handle the range query in the snapshot array.
-}
-
-\comment{
-There are many existing methods to build indexes to accelerate range query on the numeric array.
-In this paper, we implement some representative indexes to accelerate range query on snapshot array and extend them to support self maintenance when new edges are added.
+There are many existing methods to build indexes to accelerate range query on numeric array.
+In this paper we implement some representative indexes to accelerate range query on snapshot array and extend them to support self maintenance when new edges are added.
 Specifically, we divide our problems into two kinds according to aggregation function specified upon edges $ f_e $: 1) $ f_e = $ COUNT($\ast$) or SUM($\ast$).
@@
 
-It is the same with our problem because range query on numeric array can be regarded as a special case of our problem if each snapshot in snapshot array has only one edge and all edges of those snapshots share the same vertices.
+It's the same with our problem because range query on numeric array can be regarded as a special case of our problem if each snapshot in snapshot array has only one edge and all edges of those snapshots share the same vertices.
 As a result, in Section~\ref{subsec:prefix_array}, we briefly discuss how to use prefix array to accelerate temporal cuboid queries when $ f_e $ equals COUNT($\ast$) or SUM($\ast$) and maintain prefix array while new edges are added into the temporal graph cube.
@@
 
-Suppose the summarized snapshot of $ \Gr $ is $ S $, the time complexity and space complexity of Algorithm~\ref{alg:build_prefix_array} are both $ O(t_{end}\times |S|) $.
-
-\stitle{Query.} It is easy to use prefix array to answer $ Q=(A',[l,r]) $ when $ f_e $ is COUNT($\ast$) or SUM($\ast$).
+Suppose the summative snapshot of $ \Gr $ is $ S $, the time complexity and space complexity of Algorithm~\ref{alg:build_prefix_array} are both $ O(t_{end}\times |S|) $.
+
+\stitle{Query.} It's easy to use prefix array to answer $ Q=(A',[l,r]) $ when $ f_e $ is COUNT($\ast$) or SUM($\ast$).
 Suppose conducting $ Q $ we need merge snapshots in $ [l,r] $ of a temp-multi-network $ \Gr $ ($ \Gr $ may not be the corresponding temporal aggregate network of $ A' $, the reason can be found in Section~\ref{subsec:queries}), and prefix array built for $ \Gr $ is $ preArray $, then the result of merging snapshots of $ \Gr $ can be easily obtained by Algorithm~\ref{alg:prefix_array_query}.
@@
 \end{algorithm}
-It is clear that the time complexity of Algorithm~\ref{alg:prefix_array_query} is $ O(|preArray[r]|) $.
+It's clear that the time complextiy of Algorithm~\ref{alg:prefix_array_query} is $ O(|preArray[r]|) $.
 
@@
 If the second situation is met, the time complexity is $ O((t-t_{base}-t_{end})\times |preArray[t_{end}]|) $.
-}
-
-\comment{
 \subsection{Sparse Table} \label{subsec:sparse_table}
@@
 The key part of Algorithm~\ref{alg:stable_build} is the \kw{MergeSnapshotExtre} procedure, which conducts MAX($\ast$) for snapshots.
-The time complexity and space complexity of Algorithm~\ref{alg:stable_build} are both $ O(t_{end}\times log(t_{end})|S|) $ where $ S $ is the summarized snapshot of the inputed temp-multi-network.
+The time complexity and space complexity of Algorithm~\ref{alg:stable_build} are both $ O(t_{end}\times log(t_{end})|S|) $ where $ S $ is the summative snapshot of the inputed temp-multi-network.
 
@@
 However, in our problem, we only need to modify snapshot array at the last place (i.e., adding a new edge to the last snapshot) or create a new snapshot holding the new edge at the end of the snapshot array.
-It is possible to update STable in our problem.
+It's possible to update STable in our problem.
 \begin{algorithm}[t]
@@
 If situation 1) is met, we should update each snapshot in $ STable.f[t_{end}] $ with mapped edge $ (u',v',a,a) $ (line~7-8), so the time complexity is $ O(log(t_{end})) $.
-If situation 2) is met, we should conduct \kw{BuildSinglePlace} for $ STable.f[i],i \in [t_{end}+1,t-t_{base}] $, so the time complexity is $ O((t-t_{base}-t_{end})\times log(t-t_{base})|S|) $, $ S $ is the summarized snapshot of $ \Gr $ which STable is built on.
-
-}
-
-\subsection{The Segment Tree Index} \label{subsec:segment_tree}
-\comment{
+If situation 2) is met, we should conduct \kw{BuildSinglePlace} for $ STable.f[i],i \in [t_{end}+1,t-t_{base}] $, so the time complexity is $ O((t-t_{base}-t_{end})\times log(t-t_{base})|S|) $, $ S $ is the summative snapshot of $ \Gr $ which STable is built on.
+
+\subsection{Segment Tree} \label{subsec:segment_tree}
 Segment tree (STree) is an efficient data structure to accelerate range query on numeric array, and it supports all kinds of statistical functions mentioned above.
@@
 \end{figure}
-For example, Fig.~\ref{fig:exam_segtree} shows the structure of STree built for numeric array in Fig.~\ref{fig:range_query_num_snap_array} (a).
-}
-
-Here we focus mainly on extending the classic segment tree (STree) structure to support range query on snapshot array when $ f_e $ is MAX($\ast$) or MIN($\ast$) and the maintenance of STree when adding new edges.
-For the other aggregation functions, including SUM($\ast$) and AVERAGE($\ast$), can be processed in a similar way.
-Below, we first briefly describe the basic properties of STree.
+For example, Figure~\ref{fig:exam_segtree} shows the structure of STree built for numeric array in Figure~\ref{fig:range_query_num_snap_array} (a).
+In this section we mainly discuss how to extend STree to support range query on snapshot array when $ f_e $ is MAX($\ast$) or MIN($\ast$) and the maintanance of STree when adding new edges.
+
+We first briefly discribe the basic properties of STree.
 \begin{enumerate}
-	\item STree is a full binary tree, maintaining values for an array. If the length of the array is $ N $, the height of STree is $ \lceil log(N) \rceil+1 $.
+	\item STree is a full binary tree, maintaining values for an array. If the length of the array is $ N $, then the height of STree is $ \lceil log(N) \rceil+1 $.
 	\item Each node in STree maintains statistical result of values in a sub-range of the array.
@@
 The above process for a node ends when its range can not be divided (length equals $ 1 $).
-	\item The time complexity of building a STree is $ O(N) $. The space complexity of STree is also $ O(N) $. The time complexity of processing a query $ q=(func,[l,r]) $ is $ O(log(N)) $.
+	\item The time complexity of building a STree is $ O(N) $. The space complexity of STree is still $ O(N) $. The time complexity of conducting a query $ q=(func,[l,r]) $ is $ O(log(N)) $.
 \end{enumerate}
-
-Unlike traditional range query problem, there are two differences in our range query problem: 1) elements in the array and statistical results in nodes of STree are not numeric values but snapshots, with edges in form of $ (u,v,max,min) $; and 2) the range of STree might be expanded because of inserting new edges.
+Differences of our problem are: 1, elements in the array and statistical results in nodes of STree are not numeric values but snapshots, with edges in form of $ (u,v,max,min) $.
+2, the range STree maintains should be expanded because of the new added edges.
 Merging statistical information of nodes is a basic and frequent operation in both building and querying of STree, in which two statistical results of two nodes produce a new result.
-For the first difference, all we need to do is replacing the original operation on numeric values with \kw{MergeSnapshotExtre} procedure (see Algorithm~\ref{alg:stree_query}).
-We will address the second difference in the \stitle{Update} algorithm (see Algorithm~\ref{alg:update_stree}).
-Below, we first briefly describe the index building procedure, followed by the query processing procedure and index updating procedure.
-
-\stitle{STree building.} We omit the detailed algorithm to build the STree for a snapshot array, because we only need to replace the merging operation of two numeric values in the traditional algorithm of building STree for numeric array with the proposed \kw{MergeSnapshotExtre} procedure  (see Algorithm~\ref{alg:stree_query}).
-For example, Fig.~\ref{fig:exam_segtree} illustrates a STree $ STree $ for the snapshot array in Fig.~\ref{fig:range_query_num_snap_array}.
-Note that each node of $ STree $ maintains a snapshot.
-Fig.~\ref{fig:exam_stree_node} shows the snapshot of the node $ [1,3] $ of $ STree $ in Fig.~\ref{fig:exam_segtree}.
-
+For the first difference, all we need to do is replacing the original operation on numeric values with \kw{MergeSnapshotExtre} procedure.
+
+We will talk about the second difference in \stitle{Update.} section for STree. Biased timestamp is not required in STree, since timestamps are not used to access nodes in STree.
+
+\stitle{Build.} In this section we omit the algorithm to build STree for snapshot array, because we only need to replace merging operation of two numeric values in algorithm building STree for numeric array with \kw{MergeSnapshotExtre} procedure.
+Suppose we build a STree $ STree $ for snapshot array in Figure~\ref{fig:range_query_num_snap_array} (b), the structure of $ STree $ can also be shown by Figure~\ref{fig:exam_segtree}, but each node of $ STree $ carries a snapshot.
 \begin{figure}[t]
 	\begin{center}
-		\begin{tabular}[t]{c}\hspace*{-0.3cm}
-\subfigure[{\scriptsize The STree}]{
-				\includegraphics[width=0.5\columnwidth, height=3cm]{fig/example/example_segtree.pdf} \label{fig:exam_segtree}
-			} %\hspace*{-0.3cm}
-\subfigure[{\scriptsize Snapshot in the node $ [1,3] $}]{
-				\includegraphics[width=0.4\columnwidth]{fig/example/example_stree_node_1_3.pdf} 	\label{fig:exam_stree_node}
-			}
-\end{tabular}
+		\includegraphics{fig/example/example_stree_node_1_3.pdf}
 	\end{center}
 	\vspace*{-0.6cm}
-	\caption{A STree built on the snapshot array in Fig.~\ref{fig:range_query_num_snap_array}}
-	\vspace*{-0.6cm}
-	\label{fig:stree}
+	\caption{Snapshot carried by node maintaining range $ [1,3] $ in Figure~\ref{fig:exam_segtree}}
+	\vspace*{-0.2cm}
+	\label{fig:exam_stree_node}
 \end{figure}
-
-As we have mentioned before, the time complexity for building a traditional STree is $ O(N) $.
-Since \kw{MergeSnapshotExtre} will be called in building each node, the time complexity of building STree for snapshot array of length $ N $ is $ O(N|S|) $, where $ S $ is the summarized snapshot of the snapshot array.
-Also, it is easy to derive that the space usage of the STree building procedure is  $ O(N|S|) $.
-
-%The space consumed by STree built for the snapshot array is also $ O(N|S|) $.
+For example, node maintaining range $ [1,3] $ in Figure~\ref{fig:exam_segtree} carries the snapshot shown in Figure~\ref{fig:exam_stree_node}.
+
+As we have mentioned before, time complexity of building STree for numeric array is $ O(N) $.
+Since \kw{MergeSnapshotExtre} could be called in building each node, the time complexity of building STree for snapshot array of length $ N $ is $ O(N|S|) $, where $ S $ is the summative snapshot of the snapshot array.
+The sapce consumed by STree built for the snapshot array is also $ O(N|S|) $.
 Note that each node $ node $ in STree is a struct, where $ node.lchild $ and $ node.rchild $ are left child and right child of $ node $ respectively and $ [node.timel,node.timer] $ is the range which $ node $ maintains.
 For leaves of STree, $ lchild $ and $ rchild $ are $ NULL $.
-Suppose the snapshot array STree built on is $ \Sr $, $ node.snapshot $ can be regarded as the summarized snapshot of snapshot sub-array $ [\Sr[node.timel-t_{base}],...,\Sr[node.timer-t_{base}]] $.
+Suppose the snapshot array STree built on is $ \Sr $, $ node.snapshot $ can be regarded as the summative snapshot of snapshot sub-array $ [\Sr[node.timel-t_{base}],...,\Sr[node.timer-t_{base}]] $.
 STree $ STree $ is also a struct, where $ STree.root $ is the root of $ STree $.
 
-\stitle{Query processing.} Algorithm~\ref{alg:stree_query} conducts the range query on snapshot array using STree, and it shares the same framework with original query algorithm on STree but uses \kw{MergeSnapshotExtre} to merge snapshots.
+\stitle{Query.} Algorithm~\ref{alg:stree_query} conducts the range query on snapshot array using STree, and it shares the same framework with original query algorithm on STree but uses \kw{MergeSnapshotExtre} to merge snapshots.
 Merging snapshots only happens when the current split range $ [timel,timer] $ equals the range held by the current node $ treeNode $ (line~2 in Algorithm~\ref{alg:stree_query}).
-In the worst case, it happens at each depth of STree, so the time complexity of Algorithm~\ref{alg:stree_query} is $ O(log(N)|S|) $.
-For example, suppose we conduct a query $ Q=(\ast,[2,5]) $ on snapshot array in Fig.~\ref{fig:range_query_num_snap_array} (a) (the view in $ Q $ is omitted), we have to merge snapshots in nodes with range $ [2,2] $, $ [3,3] $ and $ [4,5] $ as in grey nodes in Fig.~\ref{fig:exam_segtree}.
+In the worst case, it happens at each depth of STree, so the time complexity of Algorithm~\ref{alg:stree_query} is $ O(log(N)|S|) $, where $ S $ is the summative snapshot.
+
+For example, suppose we conduct a query $ Q=(\ast,[2,5]) $ on snapshot array in Figure~\ref{fig:range_query_num_snap_array} (b) (the view in $ Q $ is omitted), we have to merge snapshots in nodes with range $ [2,2] $, $ [3,3] $ and $ [4,5] $ as in grey nodes in Figure~\ref{fig:exam_segtree}.
 \begin{algorithm}[t]
@@
 	}
-
-\vspace*{0.2cm}
-	{\bf Procedure} {$\kw{MergeSnapshotExtre}(S_a,S_b)$}
-
-	\ForEach{$ e_b \in S_b $}{
-		\If{$\exists e_a \in S_a, e_a.u=e_b.u \wedge e_a.v=e_b.v $}{
-			$ e_a.max \gets MAX(e_a.max,e_b.max) $\;
-			$ e_a.min \gets MIN(e_a.min,e_b.min) $;
-		}
-		\Else{
-			$ S_a \gets S_a \cup \{(e_b.u,e_b.v,e_b.max,e_b.min)\} $;
-		}
-	}
 	\Return;
@@
 
-\stitle{Index updating.} Let $ STree.root.timer $ is the current largest timestamp in the STree.
-When a new edge $ (u,v,t,a) $ with $t>STree.root.timer $ comes, we need to expand the range of STree by creating new nodes to maintain larger range and switch the root of STree to one of the new nodes.
-
-%The largest timestamp that STree maintains is $ STree.root.timer $, so the two cases in updating STree when adding a new edge $ (u,v,t,a) $ are: 1) $ t \leq STree.root.timer $.
+\stitle{Update.} The biggest timestamp that STree maintains is $ STree.root.timer $, so the two situations in updating STree when adding new edge $ (u,v,t,a) $ are: 1) $ t \leq STree.root.timer $.
 2) $ t>STree.root.timer $.
-If case 2) is met, we need to expand the range of STree by creating new nodes to maintain larger range and switch the root of STree to one of the new nodes.
-
-Suppose that $ l=STree.root.timel,r=STree.root.timer $, if $ t>r $, we first create a new node $ newNode $ with range $ [l,2r-l+1] $, which is twice the length of $ [l,r] $, so that $ STree.root $ can be a valid left child of $ newNode $.
-Then, we let $ STree.root $ be the left child of $ newNode $.
-Finally, we let $ newNode $ be the new root of $ STree $.
-If $ [l,2r-l+1] $ still cannot cover $ t $, we continue the process above until $ t $ is coverd.
-The updated $ STree $ is not a fully binary tree, since there is only a left subtree for the new root which violates the basic properties of STree.
-However, it can be seen as a part of a standard STree, which might be completed by continuously added new edges.
-
-\comment{
+If situation 2) is met, we need to expand the range STree maintains by creating new nodes maintaining larger range and switch the root of STree to one of the new nodes.
+
+In detail, suppose $ l=STree.root.timel,r=STree.root.timer $, if $ t>r $, we first create a new node $ newNode $ with range $ [l,2r-l+1] $, which is 2 times the length of $ [l,r] $, so that $ STree.root $ can be a valid left child of $ newNode $.
+Then we let $ STree.root $ be the left child of $ newNode $.
+Finally we let $ newNode $ be the new root of $ STree $.
+If $ [l,2r-l+1] $ still can not cover $ t $, then we continue the process above till $ t $ is coverd.
+The updated $ STree $ is not a fully binary tree, since there is only left subtree for the new root which violates the basic properties of STree.
+However, it can be seen as part of a standard STree, which may be completed by continuously added new edges.
 \begin{figure}[t]
@@
 			\subfigure[{\scriptsize Expanded STree waiting for the new edge}]{
-				\includegraphics[width=0.75\columnwidth, height=3cm]{fig/example/example_segtree_expand.pdf}
+				\includegraphics[width=0.95\columnwidth]{fig/example/example_segtree_expand.pdf}
 			}
@@
 			\subfigure[{\scriptsize Expanded STree being inserted with a new edge}]{
-				\includegraphics[width=0.75\columnwidth, height=3cm]{fig/example/example_segtree_expand_inserted.pdf}
+				\includegraphics[width=0.85\columnwidth]{fig/example/example_segtree_expand_inserted.pdf}
 			}
@@
 	\vspace*{-0.4cm}
-	\caption{Update STree when new edges are added}
+	\caption{Update STree when new edges in the second situation are added}
 	\vspace*{-0.4cm}
@@
 \begin{example} \label{exam:stree_expand}
-	Suppose we have built a STree $ STree $ for snapshot array in Fig.~\ref{fig:range_query_num_snap_array} (a) and $ STree.root.timer=5 $.
-If we want to add the new edge $ e_2 $ with timestamp 6, we should update $ STree $ so that it can cover $ [1,6] $.
-The updated $ STree $ is shown in Fig.~\ref{fig:exam_segtree_expand} (a), where we create a new node $ newNode $ with range $ [1,10] $ and let $ STree.root $ be the $ lchild $ of $ newNode $.
+	Suppose we have built a STree $ STree $ for snapshot array in Figure~\ref{fig:range_query_num_snap_array} (b) and $ STree.root.timer=5 $.
+If we want to add the new edge $ e_2 $ with timestamp 6 in Example~\ref{exam:network_growth}, we should update $ STree $ so that it can cover $ [1,6] $.
+The updated $ STree $ is shown in Figure~\ref{fig:exam_segtree_expand} (a), where we create a new node $ newNode $ with range $ [1,10] $ and let $ STree.root $ be the $ lchild $ of $ newNode $.
 Finally we assign $ newNode $ to be the new root of $ STree $.
-The updated $ STree $ without the nodes presented by dotted rectangles in Fig.~\ref{fig:exam_segtree_expand} (a) is not a complete STree.
-As shown in Fig.~\ref{fig:exam_segtree_expand} (b) (we omit the left subtree of the root for simplicity), only nodes on path from the root to leaf with range $ [6,6] $ are needed to maintain the aggregated edge of $ e_2 $, so we only need to create or update nodes on that path.
+The updated $ STree $ without the nodes presented by dotted rectangles in Figure~\ref{fig:exam_segtree_expand} (a) is not a complete STree.
+
+	As in Figure~\ref{fig:exam_segtree_expand} (b) (we omit the left subtree of the root for simplicity), only nodes on path from the root to leaf with range $ [6,6] $ are needed to maintain the aggregated edge of $ e_2 $, so we only need to create or update nodes on that path.
 \end{example}
-}
 
@@
 Algorithm~\ref{alg:update_stree} is used to update STree.
-In line~1, the condition in the while loop is true which means that the current root of $ STree $ can not cover $ t $.
-So, we need to create a new root, which has a double size of range compared to the current root (line~3-4).
+In line~1, the condition in \textbf{while} is true means that the current root of $ STree $ can not cover $ t $.
+So we need to create a new root, which has a double size of range compared to the current root (line~3-4).
 In line~6, we directly copy the snapshot of the current root to the new root, since there is no possible right child for the new root before new edge is added.
@@
 When $ STree.root.timer \geq t $ is true, we can use \kw{STreeInsertEdge} procedure to update STree.
+The framework of \kw{STreeInsertEdge} is similar to procedure used to update STree in range query problem on numeric array.
 In line~11, we update the snapshot of $ treeNode $ with the mapped edge, since $ t $ is in $ [treeNode.timel,treeNode.timer] $.
-In line~15 and line~22, we need to test whether the left child or the right child exists or not and create left child (lines~16-19) or right child (lines~23-26).
-%We have discussed the reason before, that the STree is not complete after being expanded to maintain a larger range.
-
-The time complexity of Algorithm~\ref{alg:update_stree} contains two parts: creating new root in lines~1-7 and inserting new edge using \kw{STreeInsertEdge} procedure.
-Suppose the length of range maintained by the root of STree is $ len_1=STree.root.timer-STree.root.timel+1 $ before new edge is added, and the length of new range of timestamps in $ \Gr $ becomes $ len_2=t-STree.root.timel+1 $ after $ \Gr $ is updated.
+In line~15 and line~22, we need to test whether the left child or the right child exists or not and create left child (line~16-19) or right child (line~23-26).
+We have discussed the reason before, that the STree is not complete after being expanded to maintain a larger range.
+
+The time complexity of Algorithm~\ref{alg:update_stree} contains two parts: creating new root in line~1-7 and inserting new edge using \kw{STreeInsertEdge} procedure.
+Suppose the length of range maintained by the root of STree is $ len_1=STree.root.timer-STree.root.timel+1 $ before new edge is added, and the length of new range of timestamps in $ \Gr $ becomes $ len_2=t-STree.root.timel+1 $ after $ \Gr $ was updated.
 To cover $ len_2 $, we need repeat the loop in line~1 at least $ x $ times, and we have
@@
 	\label{eqt:new_root_create_times}
-%	\begin{split}
-		len_1*2^x \geq len_2, \quad
-		x \geq log(\frac{len_2}{len_1}).
-%	\end{split}
+	\begin{split}
+		len_1*2^x &\geq len_2\\
+		x &\geq log(\frac{len_2}{len_1}).
+	\end{split}
 \end{equation}
 For each loop, the cost mainly comes from line~6.
-Suppose that the snapshot maintained in root is $ S_{root} $ before a new edge is added, the time complexity of creating the new root is $ O(log(\frac{len_2}{len_1})\times |S_{root}|) $.
-In practice, $ len_2>len_1 $ is hardly true because $ len_1 $, the length of range maintained by root, grows exponentially (lines~3-4) but $ len_2 $ grows linearly since timestamps in real-world temporal graph are dense.
+Suppose the snapshot maintained in root is $ S_{root} $ before new edge is added, the time complexity of creating new root is $ O(log(\frac{len_2}{len_1})\times |S_{root}|) $.
+In practical, $ len_2>len_1 $ is hardly true because $ len_1 $, the length of range maintained by root, grows exponentially (line~3-4) but $ len_2 $ grows linearly since timestamps in real-world temporal graph are dense.
 In \kw{STreeInsertEdge} procedure, let the length of range in the final new root is $ len $, the procedure go through the $ log(len)+1 $ layers of STree, in each layer it updates the snapshot of node covering $ t $ or creates necessary node first.
@@
 
-\section{Effectiveness of the Index} \label{sec:effec_of_indexes}
-In traditional range query problems, indexes are helpful to accelerate the query processing.
-However, similar indexes cannot always work in our problem, since the elements in the array are not numeric values but snapshots.
-
+\section{Effectiveness of Indexes} \label{sec:effec_of_indexes}
+In common range query problems, indexes are helpful to accelerate the queries.
+However, similar indexes can not always work in our problem, since the elements in the array are not numeric values but snapshots.
+
+Consider the first example in Figure~\ref{fig:index_fail_success_example} (a),
 \begin{figure}[t] %\vspace*{-0.5cm}
@@
 		\end{tabular}
-	\vspace*{-0.3cm}
+
 		\caption{Two cases of range query on snapshot array}
-		\vspace*{-0.6cm}
+		\vspace*{-0.4cm}
 		\label{fig:index_fail_success_example}
@@
 \end{figure}
-Consider an example in Fig.~\ref{fig:index_fail_success_example} (a), there is no single edge shared by any two snapshots (edge $ e $ is shared by snapshots means that there exists an edge that share the vertices with $ e $ in each of those snapshots).
+there is no single edge shared by any two snapshots (\textbf{edge $ e $ is shared by snapshots means there exists an edge that share the vertices with $ e $ in each of those snapshots}).
 In this case, if we merge snapshots in $ [t_1,t_4] $, the best choice is the baseline method, i.e., traversing all snapshots in the range and computing the result one by one.
 In baseline method, only $ 4 $ edges will be visited and each of them is visited only once.
-The edges in the result (snapshot at the right of the arrow in Fig.~\ref{fig:index_fail_success_example} (a)) are exactly those $ 4 $ edges, thus the baseline method achieves the highest efficiency and there is no need to build indexes in this case.
-
-Consider the second example in Fig.~\ref{fig:index_fail_success_example} (b), all snapshots share the same edges.
-In this case, if we still merge snapshots in $ [t_1,t_4] $, each edge will be visited $ 4 $ times in the baseline method, therefore it is necessary to build index.
-Next, we describe the measurement of the necessity of index and the key factor we found which affects the necessity of index.
+The edges in the result (snapshot at the right of the arrow in Figure~\ref{fig:index_fail_success_example} (a)) are exactly those $ 4 $ edges, so baseline method achieves the highest efficiency and there is no need to build indexes in this case.
+
+Consider the second example in Figure~\ref{fig:index_fail_success_example} (b), all snapshots share the same edges.
+In this case, if we still merge snapshots in $ [t_1,t_4] $, each edge will be visited $ 4 $ times in baseline method, so it's necessary to build indexes.
+Next, we discribe the measurement of the necessity of indexes and the key factor we found which affects the necessity of indexes.
 \begin{definition}[Acceleration Ratio of Index]
 	\label{def:acceleration_ratio_index}
-	For an array $ Arr $ with numeric values or snapshots, we build a segment tree index on it.
-For a query $ q=(func,[l,r]) $, assume that the basic components are visited $ C_b $ times using the baseline method and $ C_i $ times using the index-based method, the acceleration ratio of the index on $ q $ is $ \frac{C_b}{C_i} $.
+	For an array $ Arr $ holding numeric values or snapshots, suppose we build one kind of index on it.
+For a query $ q=(func,[l,r]) $, suppose the basic components are visited $ C_b $ times using baseline method and $ C_i $ times using index, the acceleration ratio of the index on $ q $ is $ \frac{C_b}{C_i} $.
 \end{definition}
-The basic components in snapshot array and index built on snapshot array are edges.
-We use the number of visited edges as the measure of time consumption when conducting a query using the baseline method and using the index-based method in Definition~\ref{def:acceleration_ratio_index}.
+The basic components in snapshot array and indexes built on snapshot array are edges.
+We use the number of visited edges as the time consumption of conducting a query using baseline method and using indexes in Definition~\ref{def:acceleration_ratio_index}, because from previous analyses we can find that visiting edges is the main part of the execution of query algorithms of baseline method and indexes.
 \begin{definition}[Similarity of Snapshots]
 	\label{def:similarity_snapshots}
-	Given a snapshot array $ snapArr $ starting from $ 1 $ and containing $ n $ snapshots, the summarized snapshot $ S $ of all snapshots in $ snapArr $, $ E=\sum_{i=1}^{n}|snapArr[i]| $, the similarity of snapshots in $ snapArr $ is $ s=\frac{E}{|S|} $.
+	Given a snapshot array $ snapArr $ starting from $ 1 $ and containing $ n $ snapshots, the summative snapshot $ S $ of all snapshots in $ snapArr $, $ E=\sum_{i=1}^{n}|snapArr[i]| $, the similarity of snapshots in $ snapArr $ is $ s=\frac{E}{|S|} $.
 \end{definition}
-In other words, the similarity of snapshots is the ratio of the total number of edges in snapshot array to the size of the summarized snapshot.
+In other words, the similarity of snapshots is the ratio of the total number of edges in snapshot array to the size of the summative snapshot.
 For simplicity, we assume that each snapshot in $ snapArr $ has at least one edge.
@@
 \begin{example}
-	Consider examples in Fig.~\ref{fig:similarity}.
+	Consider examples in Figure~\ref{fig:similarity}.
 	\begin{figure}[t] %\vspace*{-0.5cm}
@@
 			\end{tabular}
-			\vspace*{-0.5cm}
+			\vspace*{-0.3cm}
 			\caption{Four snapshot arrays with different similarity of snapshots}
-			\vspace*{-0.8cm}
+			\vspace*{-0.4cm}
 			\label{fig:similarity}
@@
 	There are 4 snapshot arrays having the same length of 4 but different similarities of snapshots $ s $.
-In Fig.~\ref{fig:similarity} (a), $ s=1 $, and we can see that there is no edge shared by any two snapshots, or, snapshots in Fig.~\ref{fig:similarity} (a) are not similar to each other.
-In Fig.~\ref{fig:similarity} (b) and (d), $ s=4 $, all snapshots share the same edges.
-In Fig.~\ref{fig:similarity} (c), $ s=\frac{5}{3} $, and there are edges shared by some snapshots.
+In Figure~\ref{fig:similarity} (a), $ s=1 $, and we can see that there is no edge shared by any two snapshots, or, snapshots in Figure~\ref{fig:similarity} (a) are not similar to each other.
+In Figure~\ref{fig:similarity} (b) and (d), $ s=4 $, all snapshots share the same edges.
+In Figure~\ref{fig:similarity} (c), $ s=\frac{5}{3} $, and there are edges shared by some snapshots.
 \end{example}
-From the above examples, we can see that with the similarity of snapshots grows, there will be more snapshots in snapshot array which are similar to each other, or, more edges are shared by snapshots.
+From examples above we can see that with the similarity of snapshots grows, there will be more snapshots in snapshot array which are similar to each other, or, more edges are shared by snapshots.
 
@@
 \end{theorem}
-\comment{
 \begin{proof}
-	In Section~\ref{sec:indexes}, we know that the elements in all indexes built on snapshot array are snapshots, which can be regarded as summarized snapshots of different snapshot sub-arrays of the original snapshot array.
-If the similarity of snapshots in $ snapArr $ is $ n $, then all snapshots in $ snapArr $, as well as their summarized snapshot, share the same edges.
-It is clear that all snapshots in indexes also share the same edges with snapshots in $ snapArr $.
-Suppose the indexes built on $ snapArr $ and $ numArr $ are two STrees $ snapSTree $ and $ numSTree $ (the proofs on prefix array and STable are simple, so we only analyse STree here), and summarized snapshot of snapshots in $ snapArr $ is $ S $.
+	In Section~\ref{sec:indexes}, we know that the elements in all indexes built on snapshot array are snapshots, which can be regarded as summative snapshots of different snapshot sub-arrays of the original snapshot array.
+If the similarity of snapshots in $ snapArr $ is $ n $, then all snapshots in $ snapArr $, as well as their summative snapshot, share the same edges.
+It's clear that all snapshots in indexes also share the same edges with snapshots in $ snapArr $.
+Suppose the indexes built on $ snapArr $ and $ numArr $ are two STrees $ snapSTree $ and $ numSTree $ (the proofs on prefix array and STable are simple, so we only analyse STree here), and summative snapshot of snapshots in $ snapArr $ is $ S $.
 In baseline method, conducting $ q $ requires $ r-l+1 $ visits on numeric values in $ numArr $ and $ (r-l+1)|S| $ visits on edges in $ snapArr $.
@@
 \end{proof}
-}
 \begin{theorem}
@@
 	For a snapshot array $ snapArr $ of length $ n $ and starting from 1.
-If similarity of snapshots in $ snapArr $ equals 1, then for query $ q=(func,[l,r]) $ on $ snapArr $, the acceleration ratio of STree is less than or equal to 1.
+If similarity of snapshots in $ snapArr $ equals 1, then for query $ q=(func,[l,r]) $ on $ snapArr $, the acceleration ratios of STable and STree are less than or equal to 1, and the acceleration ratio of prefix array is $ \frac{\sum_{k=l}^{r}|snapArr[k]|}{\sum_{k=1}^{r}|snapArr[k]|} $.
 \end{theorem}
-\comment{
 \begin{proof}
 	Suppose $ l,r $ are biased timestamps.
-Since the similarity of snapshots in $ snapArr $ is 1, there is no edge shared by any snapshots in $ snapArr $, e.g., snapshot array in Fig.~\ref{fig:index_fail_success_example} (a).
-For any summarized snapshot $ S_{ij} $ of sub-array $ [snapArr[i],snapArr[i+1],...,snapArr[j]] $, we can easily get $ |S_{ij}|=\sum_{k=i}^{j}|snapArr[k]| $.
+Since the similarity of snapshots in $ snapArr $ is 1, there is no edge shared by any snapshots in $ snapArr $, e.g., snapshot array in Figure~\ref{fig:index_fail_success_example} (a).
+For any summative snapshot $ S_{ij} $ of sub-array $ [snapArr[i],snapArr[i+1],...,snapArr[j]] $, we can easily get $ |S_{ij}|=\sum_{k=i}^{j}|snapArr[k]| $.
 For STree $ snapSTree $ built for $ snapArr $ (time range in $ q $ should be $ [l+t_{base},r+t_{base}] $ when using STree, and the proof on STable is simple so we omit it here), suppose the set of nodes being merged in conducting $ q $ is $ NS $, we can easily get $ \sum_{node \in NS}|node.snapshot|=\sum_{k=l}^{r}|snapArr[k]| $, where $ \forall node \in NS,|node.snapshot|=\sum_{k=node.timel}^{node.timer}|snapArr[k-t_{base}]| $.
@@
 \end{proof}
-}
-
-The above two theorems show the necessity of building index in two extreme cases.
-As in Theorem~\ref{thm:best_index_efficiency}, if similarity of snapshots in snapshot array equals the length of the snapshot array, the index-based solution achieves the designed acceleration ratio as they perform in range query on numeric arrays.
-As in Theorem~\ref{thm:worst_index_efficiency}, if similarity of snapshots in snapshot array equals 1, STree has no acceleration effect.
-The baseline method is the best approach to conduct any query in this case, because the number of edges in the result is exactly the number of edges being visited in the baseline method.
-
-It is difficult to model the relationship between similarity of snapshots and acceleration ratio of the index-based solution on all possible queries precisely, because similarity of snapshots describes the overall similarity of snapshots in the snapshot array, but in specific queries, snapshots in sub-arrays specified by ranges of the queries may not show the same similarity as the overall similarity.
-However, it is possible to model the relationship roughly.
-If the similarity of snapshots in snapshot array equals 1, there is no edge shared by two snapshots and visited more than once in baseline method.
-If the similarity of snapshots in snapshot array equals the length of the array, all edges are shared by all snapshots.
-In this case, each edge will be visited repeatedly in each cycle of baseline method (line~8 in Algorithm~\ref{alg:temp_cuboid_baseline}), while the index stores summarized snapshots of some sub-arrays of the snapshot array in advance to reduce the number of repeated visits on edges.
+
+The above two theorems make clear the necessity of indexes in two extreme cases.
+As in Theorem~\ref{thm:best_index_efficiency}, if similarity of snapshots in snapshot array equals the length of the snapshot array, all indexes achieve the designed acceleration ratio as they perform in range query on numeric arrays.
+As in Theorem~\ref{thm:worst_index_efficiency}, if similarity of snapshots in snapshot array equals 1, STable and STree have no acceleration effect and prefix array may even have negative effect.
+Baseline method is the best way to conduct any query in this case, because the number of edges in the result is exactly the number of edges being visited in baseline method.
+
+It's difficult to model the relationship between similarity of snapshots and acceleration ratio of each index on all possible queries precisely, because similarity of snapshots discribes the overall similarity of snapshots in snapshot array, but in specific queries, snapshots in sub-arrays specified by ranges of the queries may not show the same similarity as the overall similarity.
+However, it's possible to model the relationship roughly.
+If the similarity of snapshots in snapshot array equals 1, then there is no edge shared by two snapshots and visited more than once in baseline method.
+If the similarity of snapshots in snapshot array equals the length of the array, then all edges are shared by all snapshots.
+In this case, each edge will be visited repeatedly in each cycle of baseline method (line~8 in Algorithm~\ref{alg:temp_cuboid_baseline}), while indexes store summative snapshots of some sub-arrays of the snapshot array in advance to reduce the number of repeated visits on edges.
 With the similarity of snapshots grows from 1 to the length of snapshot array, more edges will be shared by snapshots, making the efficiency of baseline method lower and efficiency of indexes higher.
-As a result, the acceleration ratio of the index grows when similarity of snapshots grows, which will be confirmed in our experiments in Section~\ref{subsec:efficiency_eva}.
-
-The similarity of snapshots also affects the space consumption of the index.
-Since the elements in all snapshot arrays and the STree built on them are snapshots, we use the total number of edges in all snapshots to indicate the space consumption.
-For example, if we build two STrees $ STree_a $ and $ STree_b $ on both snapshot arrays in Fig.~\ref{fig:similarity} (a) and (b), the snapshot in each node of $ STree_b $ has only one edge, while the snapshot in each node of $ STree_a $ may have to store more than one edge, even if Fig.~\ref{fig:similarity} (a) and (b) have the same number of edges.
+As a result, the acceleration ratio of indexes grows when similarity of snapshots grows, which will be proved in experiments in Section~\ref{subsec:efficiency_eva}.
+
+The similarity of snapshots also affects the space consumption of indexes.
+Since the elements in all snapshot arrays and all indexes built on them are snapshots, we use the total number of edges in all snapshots to indicate the space consumption.
+For example, if we build two STrees $ STree_a $ and $ STree_b $ on both snapshot arrays in Figure~\ref{fig:similarity} (a) and (b), the snapshot in each node of $ STree_b $ has only one edge, while the snapshot in each node of $ STree_a $ may have to store more than one edge, even if Figure~\ref{fig:similarity} (a) and (b) have the same number of edges.
 
@@
 	\label{def:space_consum_ratio}
-	Consider an array $ Arr $ holding numeric values or snapshots.
-If $ Arr $ is a snapshot array, suppose the total number of edges in $ Arr $ is $ E_a $, and the total number of edges in the index is $ E_i $.
+	For an array $ Arr $ holding numeric values or snapshots, suppose we build one kind of index on it.
+If $ Arr $ is a snapshot array, let the total number of edges in $ Arr $ is $ E_a $, and the total number of edges in the index is $ E_i $.
 If $ Arr $ is a numeric array, $ E_a,E_i $ are the total number of numeric values in $ Arr $ and in the index respectively.
@@
 It is the same with the array structure of prefix array and STable.
-We can turn indexes into sets holding elements like: $ (SumElement,[l,r]) $, and if an index is built on $ numArr $, $ SumElement $ is the aggregation result of numeric values in $ [l,r] $, otherwise the summarized snapshot of snapshots in $ [l,r] $.
+We can turn indexes into sets holding elements like: $ (SumElement,[l,r]) $, and if an index is built on $ numArr $, $ SumElement $ is the aggregation result of numeric values in $ [l,r] $, otherwise the summative snapshot of snapshots in $ [l,r] $.
 For each index, suppose we build the index on $ numArr $ and $ snapArr $, named $ numIndex $ and $ snapIndex $.
 There must be a bijection between elements in $ numIndex $ and $ snapIndex $ that for each $ i $ in $ numIndex $, there is a corresponding $ j $ in $ snapIndex $ that $ i $ and $ j $ have the same time range $ [l,r] $, since the structures of $ numIndex $ and $ snapIndex $ are the same.
-It is easy to know that the space consumption ratio of $ numIndex $ is $ \frac{|numIndex|}{n} $.
+It's easy to know that the space consumption ratio of $ numIndex $ is $ \frac{|numIndex|}{n} $.
 Since the similarity of snapshots in $ snapArr $ is $ n $, all snapshots in $ snapArr $ and $ snapIndex $ share the same edges.
-Suppose the summarized snapshot of snapshots in $ snapArr $ is $ S $, the space consumption ratio of $ snapIndex $ is $ \frac{|snapIndex||S|}{n|S|} $, since $ |snapIndex|=|numIndex| $, so the space consumption ratio of $ snapIndex $ and $ numIndex $ are equal.
+Suppose the summative snapshot of snapshots in $ snapArr $ is $ S $, the space consumption ratio of $ snapIndex $ is $ \frac{|snapIndex||S|}{n|S|} $, since $ |snapIndex|=|numIndex| $, so the space consumption ratio of $ snapIndex $ and $ numIndex $ are equal.
 \end{proof}
-}
-
-Similar to the acceleration ratio, the space consumption ratio of the index is also negatively affected by the decrease of similarity of snapshots.
-%Specifically, we discuss the space consumption ratio of STree if similarity of snapshots equals 1.
+
+Similar to acceleration ratio of indexes, the space consumption ratio of indexes is affected negatively by the decrease of similarity of snapshots.
+Specifically we discuss the space consumption ratio of STree if similarity of snapshots equals 1.
 \begin{theorem}\label{thm:stree_worst_index_space_ratio}
 	For a snapshot array $ snapArr $ of length $ n $ and starting from 1.
-If similarity of snapshots in $ snapArr $ equals 1, the space consumption ratio of STree built on $ snapArr $ is in $ (\lceil log(n) \rceil,\lceil log(n) \rceil+1] $.
+If similarity of snapshots in $ snapArr $ equals 1, then the space consumption ratio of STree built on $ snapArr $ is in $ (\lceil log(n) \rceil,\lceil log(n) \rceil+1] $.
 \end{theorem}
-\comment{
 \begin{proof}
@@
 Consider the $ (log(n)+1) $-th layer of STree, all nodes on the $ (log(n)+1) $-th layer of STree are leaves.
-It is clear that the total number of edges in snapshots of the leaves is $ m $.
-For each node on the $ log(n) $-th layer, the snapshot in the node is the summarized snapshot of snapshots in the two siblings of the node.
+It's clear that the total number of edges in snapshots of the leaves is $ m $.
+For each node on the $ log(n) $-th layer, the snapshot in the node is the summative snapshot of snapshots in the two siblings of the node.
 Since the similarity of snapshots in $ snapArr $ is 1, no edge is shared by snapshots in $ snapArr $, so the size of snapshot of each node on the $ log(n) $-th layer is the sum of the size of snapshots in the two siblings.
 Thus, the total number of edges in snapshots of nodes on the $ log(n) $-th layer is still $ m $.
-It is the same for nodes on each layer.
+It's the same for nodes on each layer.
 Finally, the total number of edges in snapshots of all nodes in STree is $ (log(n)+1)\times m $, so the space consumption ratio of STree is $ log(n)+1 $.
@@
 \end{proof}
-}
 
 From Theorem~\ref{thm:stree_worst_index_space_ratio}, if similarity of snapshots equals 1, we need more space to store STree, which may be $ log(n)+1 $ times the space of the original snapshot array, while only 2 times the space is needed to store STree if similarity of snapshots equals the length of the original snapshot array.
-%For prefix array and STable, it is impossible to derive a clear mathematical expression of the space consumption ratio related to $ n $ only.
+For prefix array and STable, it's impossible to derive a clear mathematical expression of the space consumption ratio related to $ n $ only.
 But similar to STree, with the decrease of similarity of snapshots, each snapshot in indexes has to store more edges even if the number of edges in its corresponding sub-array of the original snapshot array remains the same.
@@
 
-Based on the above analysis, we can conclude that the necessity of building indexes, which can be determined by acceleration ratio and space consumption ratio of indexes, varies with the similarity of snapshots.
-This is the main difference of range query on a snapshot array compared to range query on a numeric array.
-Based on this observation, it is better to build index on the snapshot array with high similarity of snapshots.
-This is compatible with the implementation strategy of \kw{Temporal\enspace Graph\enspace Cube} presented in the next section, which requires precomputing views with high similarity of snapshots in their snapshot arrays.
+From analysis above, we can conclude that the necessity of building indexes, which can be determined by acceleration ratio and space consumption ratio of indexes, varies with the similarity of snapshots.
+This is the biggest difference of range query on snapshot array compared to range query on numeric array.
+Based on this observation, we'd better build indexes on snapshot array with high similarity of snapshots, which is compatible with the implementation strategy of \kw{Temporal\enspace Graph\enspace Cube} presented in the next section, which requires precomputing views with high similarity of snapshots in their snapshot arrays.
 %In particular, we use, we know that if similarity of snapshots $ s $ equals $ 1 $, baseline method is the best method and there is no need to build indexes.
-If $ s $ equals the length of the snapshot array, indexes achieve the designed acceleration ratio, so it is necessary to build indexes just like what we usually do in common range query problem.
+If $ s $ equals the length of the snapshot array, indexes achieve the designed acceleration ratio, so it's necessary to build indexes just like what we usually do in common range query problem.
 However, in real-world temp-multi-networks and their precomputed temp-aggre-networks, similarities of snapshots in snapshot arrays are hardly to be exactly $ n $ or $ 1 $ ($ n $ is the length of snapshot arrays).
-For a fixed length $ n $, with $ s $ drops from $ n $ to $ 1 $, it is more likely that the number of reduplicate edges visited in baseline method compared to the size of result snapshot decrease in any query, making baseline method more efficient and indexes more unnecessary.
-
-%It is difficult to model the relationship between similarity of snapshots and acceleration ratio of each index on all possible queries precisely, because similarity of snapshots describes the overall similarity of snapshots in snapshot array, but in specific queries, snapshots in ranges of the queries may not show the same similarity as the overall similarity.
+For a fixed length $ n $, with $ s $ drops from $ n $ to $ 1 $, it's more likely that the number of reduplicate edges visited in baseline method compared to the size of result snapshot decrease in any query, making baseline method more efficient and indexes more unnecessary.
+
+%It's difficult to model the relationship between similarity of snapshots and acceleration ratio of each index on all possible queries precisely, because similarity of snapshots discribes the overall similarity of snapshots in snapshot array, but in specific queries, snapshots in ranges of the queries may not show the same similarity as the overall similarity.
 So in Section~\ref{sec:experiment}, we mainly discuss the relationship between similarity of snapshots and the overall acceleration ratio of each index on all possible queries.[deffinition of overall?]
@@
 \section{Partial Materialization} \label{sec:partial_materialization}
-To implement a temporal graph cube, we need precompute, or materialize some or all views in the temporal graph cube, since precomputed views can reduce the response time of OLAP queries and operations like roll-up, drill-down and slice-and-dice as we discussed in Section~\ref{sec:queries}.
-
-%Like static graph cube, there are three possible alternatives: 1) Full materialization.
+To implement a temporal graph cube, we need precompute, or materialize some or all views in the temporal graph cube, since precomputed views can reduce the response time of OLAP queries and operations like roll-up, drill-down and slice-and-dice as we discussed in Section~\ref{subsec:queries}.
+
+Like static graph cube, there are three possible alternatives: 1) Full materialization.
 2) No materialization.
 3) Partial materialization.
-Both the first and the second alternatives are intractable, because: 1) Full materialization means that we need to precompute all possible views, but the number of views grows exponentially with $ |dim(A_{base})| $.
-It is work only if $ |dim(A_{base})| $ is small enough.
+The first and the second alternatives are both unrealistic, because: 1) Full materialization means we need to precompute all possible views, but the number of views grows exponentially with $ |dim(A_{base})| $.
+It's work only if $ |dim(A_{base})| $ is small enough.
 2) Not precomputing any view (except $ A_{base} $) leads to long response time in almost all OLAP queries and operations.
 
-In this work, we adopt a partial materialization strategy, i.e., we select a set of views to be precomputed in order to balance the space consumption and average response time according to the probability distribution of all possible queries.
+For large temp-multi-networks, we can only choose partial materialization, i.e., select a set of views to be precomputed in order to balance the space consumption and average response time according to the probability distribution of all possible queries.
 \textit{View selection} in traditional data cube scenario is a NP-hard problem \cite{karloff1999complexity}.
-It is also a NP-hard problem in static graph cube scenario because traditional data cube can be regarded as a special case of static graph cube \cite{zhao2011graph}.
-Similarly, static graph cube can also be regarded as a special case of temporal graph cube, if only one timestamp exists in the temporal graph cube.
+It is also a NP-hard problem in static graph cube scenario because traditional data cube can be ragarded as a special case of static graph cube \cite{zhao2011graph}.
+Similarly, static graph cube can also be ragarded as a special case of temporal graph cube, if only one timestamp exists in the temporal graph cube.
 Thus, \textit{view selection} problem in temporal graph cube is also a NP-hard problem.
@@
 Those heuristic solutions always measure the effectiveness of the selected views by benefit those views bring.
-Here the concept of \textit{Benefit} was first introduced in \cite{harinarayan1996implementing}, we briefly review the definition of \textit{benefit} below.
+
+\textit{Benefit} was first introduced in \cite{harinarayan1996implementing}, we briefly review the definition of \textit{benefit} below.
 \begin{definition}[Benefit of Selected Views]
@@
 \end{definition}
-
-In greedy algorithm, among all candidate views, the view $ u $ with the largest $ B(u,S_{k-1}) $ is selected to be $ u_k $.
-For the total benefit of view sequence generated by each heuristic solution, the closer to the benefit of the optimal view sequence, the more effective the solution is.
+In greedy algorithm, among all candidate views, the view $ u $ with the biggest $ B(u,S_{k-1}) $ is selected to be $ u_k $.
+For the total benefit of view squence generated by each heuristic solution, the closer to the benefit of the optimal view sequence, the more effective the solution is.
 
 In Definition~\ref{def:benefit_views}, the cost of views is used in representation of the benefit, because the cost of views is also the time complexity or cost of queries in data cube and static graph cube.
-However, cost of views in temporal graph cube (space consumption of the corresponding temporal aggregate networks of views) cannot be used as the cost of temporal cuboid queries.
-First, in Definition~\ref{def:benefit_views}, $ C(u) $ cannot be the cost of temporal cuboid query $ Q=(w,[l,r]) $ if we conduct $ Q $ on $ u $.
-It is similar to $ C(v) $.
-The reason is that there is a specified time range $ [l,r] $ in $ Q $, which does not exist in any query of traditional data cube or static graph cube.
+However, cost of views in temporal graph cube (space consumption of the corresponding temporal aggregate networks of views) can not be used as the cost of temporal cuboid queries.
+First, in Definition~\ref{def:benefit_views}, $ C(u) $ can not be the cost of temporal cuboid query $ Q=(w,[l,r]) $ if we conduct $ Q $ on $ u $.
+It's similar to $ C(v) $.
+The reason is that there is a specified time range $ [l,r] $ in $ Q $, which doesn't exist in any query of traditional data cube or static graph cube.
 In implementation of temporal graph cube, we know nothing about the specified time ranges in all possible queries.
-Second, if we use an expected range $ [l_e,r_e] $ as the representative of all ranges in all queries according to the probability distribution of specified ranges in all queries, we may be able to get the time complexity of conducting $ Q=(w,[l_e,r_e]) $ on $ u $ using the baseline method by precomputing the total size of snapshots in $ [l_e,r_e] $ and the size of summarized snapshot of snapshots in $ [l_e,r_e] $.
+Second, if we use an expected range $ [l_e,r_e] $ as the representative of all ranges in all queries according to the probability distribution of specified ranges in all queries, we may be able to get the time complexity of conducting $ Q=(w,[l_e,r_e]) $ on $ u $ using baseline method by precomputing the total size of snapshots in $ [l_e,r_e] $ and the size of summative snapshot of snapshots in $ [l_e,r_e] $.
 Only in this way can we get a relatively accurate benefit for each $ u $.
-Third, the above precomputing process is very costly, and it is based on conducting all queries with the baseline method.
-%In Section~\ref{sec:effec_of_indexes} and \ref{sec:experiment}, we show the effectiveness of indexes in specific cases, so the cost of temporal cuboid queries is determined by the indexes.
-However, it is more costly to precompute the time complexity of conducting $ Q=(w,[l_e,r_e]) $ on $ u $ using indexes of $ u $, not to mention that timestamps will be added into temporal networks constantly, making that we cannot find a stable $ [l_e,r_e] $.
-
-As a result, the greedy algorithm and its variations are not suitable for view selection problem in temporal graph cube.
-In this paper, we adopt a much simpler solution to select views to be precomputed, \kw{MinLevel}, which was originally introduced in \cite{zhao2011graph}.
+Third, the above precomputing process is very costly, and it is based on conducting all queries with baseline method, but in Section~\ref{sec:effec_of_indexes} and \ref{sec:experiment}, we prove the effectiveness of indexes in specific cases, so the cost of temporal cuboid queries is determined by the indexes.
+However, it's more costly to precompute the time complexity of conducting $ Q=(w,[l_e,r_e]) $ on $ u $ using indexes of $ u $, not to mention that timestamps will be added into temporal networks constantly, making that we can not find a stable $ [l_e,r_e] $.
+
+Thus, greedy algorithm and its variations are not suitable for view selection problem in temporal graph cube.
+In this paper, we adopt a much simpler solution to select views to be precomputed, \kw{MinLevel}, which is introduced in \cite{zhao2011graph}.
 The idea of \kw{MinLevel} is simple: users are more willing to query with small number of dimensions, i.e., $ |dim(A)| $ is small in $ Q=(A,[l,r]) $.
 In \kw{MinLevel}, view $ A $ where $ |dim(A)|=l_0 $ is in the first batch of views to be selected ($ l_0 $ is an empirical value).
-If all the views with $ l_0 $ dimensions have been selected and the number of selected views or the total size needed for precomputing the selected views has not reach the limit, then we continue to select views with $ l_0+1 $ dimensions until we select enough number or size of views.
-In this paper, we select $ k $ views to be precomputed and $ l_0=1 $.
-
-Using \kw{MinLevel}, we precompute views with small number of dimensions; and these views also have high similarity of snapshots in their snapshot arrays (as shown in Table~\ref{tab:materialized_view}).
-In processing temporal cuboid query $ Q=(A',[l,r]) $, if $ A' $ is not precomputed and $ l_0=1 $, only $ A_{base} $ can be used to process the query $ Q $.
-If $ l_0>1 $ and $ |dim(A')|<l_0 $, then there may be some precomputed views $ \{A_1'',A_2'',...\} $ where $ |dim(A_i'')|=l_0 $ can be used to process $ Q $.
-In this case, choosing an arbitrary $ A_i'' $ to process $ Q $ is efficient enough because the size of $ A_i'' $ and its index is usually small since $ l_0 $ is a small value.
-
-\section{Experiments} \label{sec:experiment}
-%In this section, we conduct extensive experiments to evaluate the effectiveness and efficiency of the temporal graph cube model.
+If all the views with $ l_0 $ dimensions have been selected and the number of selected views or the total size needed for precomputing the selected views hasn't reach the limit, then we continue to select views with $ l_0+1 $ dimensions util we select enough number or size of views.
+In this paper we choose to select $ k $ views to be precomputed and $ l_0=1 $.
+
+Using \kw{MinLevel}, we precompute views with small number of dimensions, and these views also have high similarity of snapshots in their snapshot arrays (as shown in Table~\ref{tab:materialized_view}), which is a good news for indexes as mentioned in Section~\ref{sec:effec_of_indexes}.
+In conducting temporal cuboid query $ Q=(A',[l,r]) $ in Section~\ref{subsec:queries}, if $ A' $ is not precomputed and $ l_0=1 $, only $ A_{base} $ can be used to conduct $ Q $.
+If $ l_0>1 $ and $ |dim(A')|<l_0 $, then there may be some precomputed views $ \{A_1'',A_2'',...\} $ where $ |dim(A_i'')|=l_0 $ can be used to conduct $ Q $.
+In this case, choosing an arbitrary $ A_i'' $ to conduct $ Q $ is efficient enough because the size of $ A_i'' $ and its indexes are usually small since $ l_0 $ is a small value.
+
+\section{Experiment} \label{sec:experiment}
+In this section, we conduct extensive experiments to evaluate the effectiveness and efficiency of the temporal graph cube model.
 
@@
 \begin{table}[t!]%\vspace*{-0.3cm}
-	\scriptsize
-	%\small
+	%\scriptsize
+	\small
 	\centering
@@
 
-\stitle{DBLP.} The DBLP datasets covers $ 9 $ areas in computer science: CA (computer architecture), CN (computer network), NS (network security), SE (software engineering), DB (database), TH (computer science theory), CG (computer graphics), AI (artificial intelligence) and HI (human-computer interaction).
-Table~\ref{tab:datasets} illustrates the statistic information of this dataset.
-For each vertex (author), there are three dimensions of information: \kw{Name}, \kw{Area}, \kw{Productivity}.
-Since we classify all publications into $ 9 $ areas, \kw{Area} of an author is one of the $ 9 $ areas where he or she has the most publications ever, which can be regarded as the representative of the focus of his or her papers.
-For \kw{Productivity}, we discrete the number of publications per year of an author into four different buckets, which is shown in Table~\ref{tab:productivity}.
-The number of publications per year of an author equals the total number of publications of the author divided by $ 2022-y $, $ y $ is the first year when the author had his or her first publication.
-\kw{Productivity} specifies the ability of producing academic papers of an author.
-Each temporal edge represents that two authors coauthored a paper at a certain time (year).
-
-%This dataset is extracted from DBLP computer science bibliography data which is downloaded in September, 2021.
+\stitle{DBLP.} This dataset is extracted from dblp computer science bibliography data which is downloaded in September, 2021.
 Specifically, we extract publication information of all conferences and journals listed in \textit{Catalogue of international academic conferences and periodicals recommended by China Computer Federation} (\url{https://www.ccf.org.cn/ccf/contentcore/resource/download?ID=99185}) except conferences and journals which focus on cross field since we can not classify them into AI, DB or other specific fields.
@@
 Since we classify all publications into $ 9 $ areas, \kw{Area} of an author is one of the $ 9 $ areas where he or she has the most publications ever, which can be regarded as the representative of focus of his or her works.
-For \kw{Productivity}, we discrete the number of publications per year of an author into four different buckets, which is shown in Table~\ref{tab:productivity}.
+For \kw{Productivity}, we discretize the number of publications per year of an author into four different buckets, which is shown in Table~\ref{tab:productivity}.
 The number of publications per year of an author equals the total number of publications of the author divided by $ 2022-y $, $ y $ is the first year when the author had his or her first publication.
@@
 \end{table}
+Each temporal edge represents that two authors coauthored a paper at a certain time (year).
 
 %Note that there is no numeric attribute in dimensions of vertices of temp-multi-network in \kw{DBLP}, so we can only specify $ f_v= $ COUNT($\ast$).
-It is not important because the processes of aggregating on vertices are the same when $ f_v $ varies.
+It's not important because the processes of aggregating on vertices are the same when $ f_v $ varies.
 Temporal edges in \kw{DBLP} also have no numeric attribute, so $ f_e $ can only be COUNT($\ast$).
@@
 
-\stitle{IMDB.} The IMDB dataset contains various types of works like movie, short, video, etc.
+\stitle{IMDB.} This dataset is extracted from the Internet Movie Database (IMDB) downloaded in November, 2021.
+The IMDB dataset contains various types of works like movie, short, video, etc.
 Each work has the following attributes: \kw{tile}, \kw{time}, \kw{titleType}, \kw{genre}, \kw{isAdult}, \kw{rating}, \kw{voteNum}.
-\kw{rating} is a numeric attribute, representing the average rating for the work from users.
+\kw{rating} is a numeric attribute, representing the average rating for the work from individual users.
 \kw{voteNum} is the number of votes the work has received.
@@
 \kw{Field} specifies the field that a person belongs to, e.g., movie, short, video, etc., which is obtained by counting the types of the works that the person participates in and choosing the type having the biggest count.
-\kw{Genre} denotes the genre of works that a person usually participates in, which is obtained by the same process in obtaining \kw{Field}.
-\kw{IsAdult} represents if a person mainly works for adult works or not.
+\kw{Genre} specifies the genre of works that a person usually participates in, which is obtained by the same process in obtaining \kw{Field}.
+\kw{isAdult} specifies if a person mainly works for adult works or not.
 \kw{Averating} specifies the average rating of works that a person participates in, and it shows the average quality of works related to the person.
-\kw{Hotness} denotes the hotness of works a person usually participates in, which is expressed by the average vote number of works related to the person.
-Both \kw{Averating} and \kw{Hotness} are discretized as shown in Table~\ref{tab:attr}.
-
-\begin{table}[t!]%\vspace*{-0.3cm}
-	\scriptsize
-	%\small
-	\centering
-	\caption{Attributed information of IMDB} \vspace*{-0.2cm} \label{tab:attr}
-	\begin{tabular}{c c | c c}
-		\toprule
-		\bf Averating & \kw{Averating} value $ x $ & \bf Hotness & Average votes of works $ w $ \cr %\hline %\hline
-		\midrule
-		5 & $ 8 \leq x $ & hot & $ 100,000 \leq w $\cr %\hline
-		4 & $ 6 \leq x < 8 $  &popular & $ 10,000 \leq w < 100,000 $ \cr %\hline
-		3 & $ 4 \leq x < 6 $ & fair & $ 1,000 \leq w < 10,000 $ \cr %\hline
-		2 & $ 2 \leq x < 4 $ & cold & $ w < 1,000 $  \cr %\hline
-		1 & $ x < 2 $  &\cr %\hline
-		\bottomrule
-	\end{tabular}
-	\vspace*{-0.3cm}
-\end{table}
-
-\comment{
+\kw{Hotness} specifies the hotness of works a person usually participates in, which is expressed by the average vote number of works related to the person.
+\kw{Averating} and \kw{Hotness} both need to be discretized, which are shown in Table~\ref{tab:averating} and Table~\ref{tab:hotness} respectively.
 \begin{table}[t!]%\vspace*{-0.3cm}
@@
 \end{table}
-}
-
-We refer to each person (each principal of the work) as a vertex in the temp-multi-network, and two vertices can form a temporal edge if they work together for the same work.
+
+We use persons (principals in works) as the vertices in the temp-multi-network, and two vertices can form a temporal edge if they work together for a same work.
 The timestamp of the temporal edge is the release time of the work, and the numeric attribute of the temporal edge is the average rating of the work.
@@
 \subsection{Effectiveness Evaluation} \label{subsec:effectiveness_eva}
-In this section, we evaluate the effectiveness of temporal graph cube as a decision-support tool on \kw{DBLP}.
+In this section we evaluate the effectiveness of temporal graph cube as a decision-support tool on \kw{DBLP}.
+We will conduct some queries and show some interesting findings, especially time-dependent findings.
 First, we conduct a series of temporal cuboid queries $ Q_1=((\kw{Area}),[2001,2006]) $, $ Q_2=((\kw{Area}),[2006,2011]) $, $ Q_3=((\kw{Area}),[2011,2016]) $, $ Q_4=((\kw{Area}),[2016,2021]) $ on \kw{DBLP}.
 Aggregation functions upon vertices and edges are both COUNT($\ast$).
-The network structures of $ Q_1 $-$ Q_4 $ are shown in Fig.~\ref{fig:dblp_area}, illustrating the co-authorship patterns between authors grouped by different areas in the specified time ranges.
-For simplicity, in Fig.~\ref{fig:dblp_area} (a) we omit those co-authorships with COUNT($\ast$) values less than 10,000, which are also omitted in Fig.~\ref{fig:dblp_area} (b)-(d), regardless of their COUNT($\ast$) values.
-
-\comment{
-\begin{table}[t!]%\vspace*{-0.3cm}
-	\scriptsize
-%	\small
-	\centering
-	\caption{Vertex table of $ Q_1-Q_4 $} \vspace*{-0.2cm} \label{tab:vertex_table_dblp_area}
-	\begin{tabular}{c c| c c| c c}
-		\toprule
-		Area & COUNT($\ast$)  & Area & COUNT($\ast$) &Area & COUNT($\ast$)\cr %\hline %\hline
-		\midrule
-		CA & 228,429 & CN & 156,329&NS & 60,880 \cr %\hline
-		 SE & 114,727  & DB & 102,931& TH & 109,293\cr %\hline
-		CG & 156,982 & AI & 256,048 &HI & 57,264\cr %\hline
-		\bottomrule
-	\end{tabular}
-	\vspace*{-0.4cm}
-\end{table}
-}
-
-\comment{
 \begin{table}[t!]%\vspace*{-0.3cm}
@@
 \end{table}
-}
-
 \begin{figure*}[t!]
@@
 \end{figure*}
-\comment{
-The results are shown in Table~\ref{tab:vertex_table_dblp_area} and Fig.~\ref{fig:dblp_area}.
-The network structures of $ Q_1 $-$ Q_4 $ are shown in Fig.~\ref{fig:dblp_area}, illustrating the co-authorship patterns between authors grouped by different areas in the specified time ranges.
-For simplicity, in Fig.~\ref{fig:dblp_area} (a) we omit those co-authorships with COUNT($\ast$) values less than 10,000, which are also omitted in Fig.~\ref{fig:dblp_area} (b)-(d), regardless of their COUNT($\ast$) values.
-}
-
-Some interesting observations can be obtained in these results.
+The results are shown in Table~\ref{tab:vertex_table_dblp_area} and Figure~\ref{fig:dblp_area}.
+Note that on time scale of years, an author may just be born or pass away at some time.
+But such information is not contained in any dataset we know.
+Also, we have no way to know when a researcher starts and ends his or her research career, so in this experiment, the COUNT($\ast$) values in vertex table shared by $ Q_1 $-$ Q_4 $ are not very informative, and we will focus on the network structures of $ Q_1 $-$ Q_4 $ and numeric information on them.
+The network structures of $ Q_1 $-$ Q_4 $ are shown in Figure~\ref{fig:dblp_area}, illustrating the co-authorship patterns between authors grouped by different areas in the specified time ranges.
+For simplicity, in Figure~\ref{fig:dblp_area} (a) we omit those co-authorships with COUNT($\ast$) values less than 10,000, which are also omitted in Figure~\ref{fig:dblp_area} (b)-(d), regardless of their COUNT($\ast$) values.
+
+Some interesting phenomenons can be found in the results.
 For example, authors in each area co-author most with authors in the same area even in different time ranges.
-We can clearly see that in recent 20 years, the number of co-authorship between each pair of areas increases over time.
-We can also find that in recent 20 years researchers in \kw{AI} co-authored with researchers in \kw{CG} most.
-This is because there are many problems in computer graphics like automatic modeling, image processing and digital photography which can be solved by AI technologies.
-More interestingly, in $ [2001,2006] $, researchers in \kw{TH} co-authored most with researchers in \kw{CA}, but with the time evolves, researchers in \kw{TH} are more willing to co-author with researchers in \kw{AI}.
-The reason may be that theoretical research on AI becomes more and more important with the wide applications of AI in recent years.
-%The above findings can also be obtained from uncut results.
+As for co-authorship between authors in different areas, for example, we can easily find that in recent 20 years, the number of co-authorship between each pair of areas increases over time.
+We can also find in recent 20 years researchers in \kw{AI} co-authored with researchers in \kw{CG} most.
+This is because there are many problems in computer graphics like automatic modeling, image processing and digital photography which can be solved by AI technology.
+More interestingly, in $ [2001,2006] $, researchers in \kw{TH} co-authored most with researchers in \kw{CA}, but with time passes, researchers in \kw{TH} are more willing to co-author with researchers in \kw{AI}.
+The reason may be that theoretical research on Artificial Intelligence becomes more and more important with the wide application of Artificial Intelligence in recent years.
+The above findings can also be obtained from uncut results.
 %[ns and cn,ca and ai;ai and cg;th and ai,ca]
 
-In each period we can zoom into a more fine-grained view by conducting a drill-down operation.
+In each peroid we can zoom into a more fine-grained view by conducting a drill-down operation.
 For example, for $ Q_4=((\kw{Area}),[2016,2021]) $, drill-down can be a query $ Q_4'=((\kw{Area},\kw{Productivity}),[2016,2021]) $.
-The network structure of $ Q_4' $ is shown in Fig.~\ref{fig:dblp_area_pro_2016_2021}.
+The network structure of $ Q_4' $ is shown in Figure~\ref{fig:dblp_area_pro_2016_2021}.
 \begin{figure}
 	\begin{center}
-		\includegraphics[width=0.8\columnwidth]{fig/exp/visio_area_pro_2016_2021.pdf}
+		\includegraphics[width=0.95\columnwidth]{fig/exp/visio_area_pro_2016_2021.pdf}
 	\end{center}
 
-	\vspace*{-0.6cm}
+	\vspace*{-0.4cm}
 	\caption{Network structure in the result of $ Q_4' $}
@@
 For simplicity, we drop edges with weight less than 10,000 and we only keep vertices related to areas in $ \{\kw{AI},\kw{DB}\} $ (it can be regarded as a slice-and-dice operation).
-In Fig.~\ref{fig:dblp_area} (d), there are 117,338 co-authorships between researchers of \kw{AI} and \kw{DB} in $ [2016,2021] $.
-In fine-grained view of Fig.~\ref{fig:dblp_area_pro_2016_2021}, we can see that the most co-authorships belong to researchers of poor and fair productivity in \kw{AI} and \kw{DB}.
+In Figure~\ref{fig:dblp_area} (d), there are 117,338 co-authorships between reseachers of \kw{AI} and \kw{DB} in $ [2016,2021] $.
+In fine-grained view of Figure~\ref{fig:dblp_area_pro_2016_2021}, we can see that the most co-authorships belong to researchers of poor and fair productivity in \kw{AI} and \kw{DB}.
 
@@
 \end{figure*}
-Fig.~\ref{fig:dblp_cross} shows the results of a series of temporal crossboid queries:
+Figure~\ref{fig:dblp_cross} shows the results of a serise of temporal crossboid queries:
 \begin{center}
@@
 \end{center}
-The above queries focus on the cross interaction between \kw{Name} and \kw{Area}, i.e., the co-authorship with each area for each researcher.
-We further slice-and-dice the results on \kw{Name} to show the results related to ``Jiawei Han".
+The above queries all focus on the cross interaction between \kw{Name} and \kw{Area}, i.e., the co-authorship with each area for each researcher.
+We further slice-and-dice the results on \kw{Name} to only show the results related to ``Jiawei Han".
 We can find that in recent 20 years, Jiawei cooperated with researchers in \kw{DB} most.
@@
 \subsection{Efficiency Evaluation} \label{subsec:efficiency_eva}
-%In this section we mainly evaluate the efficiency of temporal graph cube on \kw{IMDB}, especially the efficiency of indexes.
-
-\stitle{Exp-1: Performance of the index-based method.} Here we aim to evaluate how much the index-based solution can accelerate the merging operation of snapshots in time ranges while processing temporal cuboid queries, compared to the baseline algorithm (Algorithm~\ref{alg:temp_cuboid_baseline}).
-As we analyzed before, the average acceleration ratio of the index-based solution can vary if the similarity of snapshots in temp-multi-networks changes.
-In this experiment, we mainly use \kw{IMDB} dataset, since vertices in \kw{IMDB} dataset have 7 dimensions and $ 2^7 $ views can be obtained.
-For convenience, we only materialize views in Table~\ref{tab:materialized_view}, among which we only materialize one view containing dimension \kw{Name}, because \kw{Names} of two persons are hardly the same in \kw{IMDB}, and thus \kw{Name} can be approximately regarded as a primary key and having only one view containing dimension \kw{Name} is enough.
+In this section we mainly evaluate the efficiency of temporal graph cube on \kw{IMDB}, especially the efficiency of indexes.
+
+\stitle{Exp-1: Average acceleration ratio of indexes with different similarity of snapshots.} The most important thing is how much indexes can accelerate the merging operation of snapshots in time ranges while conducting temporal cuboid queries.
+As we analysed before, the average aceleration ratio of indexes can vary if similarity of snapshots in temp-multi-networks changes.
+In this experiment, we only use \kw{IMDB} dataset, since vertices in \kw{IMDB} dataset have 7 dimensions and $ 2^7 $ views can be obtained.
+For convenience, we only materialize views in Table~\ref{tab:materialized_view},
 \begin{table}[t!]%\vspace*{-0.3cm}
-	\scriptsize
-	%\small
+	%\scriptsize
+	\small
 	\centering
-	\caption{Materialized views} \vspace*{-0.2cm} \label{tab:materialized_view}
+	\caption{Materialized views in experiments} \vspace*{-0.2cm} \label{tab:materialized_view}
 	\begin{tabular}{c c c}
@@
 \end{table}
-
-We conduct a series of temporal cuboid queries on materialized views to examine the efficiency of the index-based method (conducting temporal cuboid queries on materialized views are all about merging snapshots in time ranges as we analyzed in Section~\ref{subsec:cuboid}).
-We set a series of time ranges to be specified in the queries, which are shown in Table~\ref{tab:time_ranges_set}.
+among which we only materialize one view containing dimension \kw{Name} because in \kw{IMDB} dataset, \kw{Names} of two persons are hardly the same, so \kw{Name} can be approximately regarded as a primary key and having only one view containing dimension \kw{Name} is enough.
+
+We will conduct a series of temporal cuboid queries on materialized views to examine the efficiency of indexes (conducting temporal cuboid queries on materialized views are all about merging snapshots in time ranges as we analyzed in \stitle{Temporal cuboid} part of Section~\ref{subsec:queries}).
+We manually set a series of time ranges to be specified in the queries, which are shown in Table~\ref{tab:time_ranges_set}.
 \begin{table}[t!]%\vspace*{-0.3cm}
-	\scriptsize
-%	\small
+	%\scriptsize
+	\small
 	\centering
-	\caption{Time ranges of queries} \vspace*{-0.2cm} \label{tab:time_ranges_set}
+	\caption{Time ranges of queries in experiments} \vspace*{-0.2cm} \label{tab:time_ranges_set}
 	\begin{tabular}{c c}
@@
 Ranges at two ends in each length group may be truncated since we try to keep each time range in $ [1878,2028] $.
-Specifically, we set a series of queries $ QS_1,QS_2,...,QS_7 $, where $ QS_i $ is a set of queries specifying the No.$ i $ materialized view in Table~\ref{tab:materialized_view} and covering all time ranges of all lengths in Table~\ref{tab:time_ranges_set}, i.e., $ QS_1=\{((Pro),[1878,1880]),...,((Pro),[2011,2015]),\\((Pro),[1878,1883]),...,((Pro),[2008,2018]),...,\\((Pro),[1878,1928]),...,((Pro),[1963,2028])\} $.
-
-\comment{
+Specifically we set a series of queries $ QS_1,QS_2,...,QS_7 $, where $ QS_i $ is a set of queries specifying the No.$ i $ materialized view in Table~\ref{tab:materialized_view} and covering all time ranges of all lengths in Table~\ref{tab:time_ranges_set}, i.e., $ QS_1=\{((Pro),[1878,1880]),...,((Pro),[2011,2015]),\\((Pro),[1878,1883]),...,((Pro),[2008,2018]),...,\\((Pro),[1878,1928]),...,((Pro),[1963,2028])\} $.
+
+We first set $ f_e= $ SUM($\ast$), and test the efficiency of prefix array (results are similar if $ f_e= $ COUNT($\ast$)). The results are shown in Table~\ref{tab:effi_prearray}.
 \begin{table}[t!]%\vspace*{-0.3cm}
-	\scriptsize
-	%\small
+	%\scriptsize
+	\small
 	\centering
-	\caption{Performance of the index-based solution} \vspace*{-0.2cm} \label{tab:effi_prearray}
-	\begin{tabular}{c c c c c| c c c}
+	\caption{Performance and acceleration ratio of prefix array on materialized views} \vspace*{-0.2cm} \label{tab:effi_prearray}
+	\begin{tabular}{c c c c c}
 		\toprule
-		\makecell[c]{Views\\No.}& $ s $ & \makecell[c]{baseline\\(ms)} &\makecell[c]{STree\\(ms)}&\makecell[c]{acce-ratio\\(ave)} & \makecell[c]{Original\\view size} &  \makecell[c]{STree\\size}&\makecell[c]{STree\\ratio}\cr %\hline %\hline
-		\midrule
-		1&53.48&16,960 &3,960 &3.45 &41,448 &93,975 &2.27 \cr
-		\midrule
-		2&18.16&172,614 &57,637 &2.32 &396,755 &1,077,456 &2.72\cr
-		\midrule
-		3&6.15&279,684 &144,849 &1.59&3,738,125 &13,788,570 &3.69\cr
-		\midrule
-		4&6.07&285,623 &147,565 &1.59&3,758,885 &13,918,066 &3.70 \cr
-		\midrule
-		5&4.70&515,607 &293,546 &1.50&5,467,826 &22,063,352 &4.04\cr
-		\midrule
-		6&3.97&896,386 &550,376 &1.40&8,304,421 &35,837,987 &4.32\cr
-		\midrule
-		7&1.12&6,719,417 &6,366,660 &1.05&37,096,632 &285,623,583 &7.70\cr
+		\makecell[c]{Views\\No.}& $ s $ & \makecell[c]{baseline\\(ms)} &\makecell[c]{pre-array\\(ms)}&\makecell[c]{acce-ratio\\(ave)} \cr %\hline %\hline
+		\midrule
+		1&53.48&17,272&3,216&4.30 \cr
+		\midrule
+		2&18.16&176,853&55,216&2.45\cr
+		\midrule
+		3&6.15&285,748&162,029&1.46\cr
+		\midrule
+		4&6.07&290,319&166,696&1.50\cr
+		\midrule
+		5&4.70&526,306&336,427&1.35\cr
+		\midrule
+		6&3.97&922,681&637,268&1.27\cr
+		\midrule
+		7&1.12&7,063,798&8,271,257&0.81\cr
 		\bottomrule
@@
 \end{table}
-
+%\begin{figure}[t] %\vspace*{-0.5cm}
+%\begin{center}
+%	\includegraphics[width=0.8\columnwidth]{fig/prearray_time.png}
+%	\vspace*{-0.6cm}
+%	\caption{prearray}
+%	\vspace*{-0.4cm}
+%	\label{fig:prearray_time}
+%\end{center}
+%\end{figure}
+\kw{Views No.} is the No.
+of materialized views in Table~\ref{tab:materialized_view}, $ s $ is the similarity of snapshots.
+The third and the fourth columns are time used to conduct all prepared queries on each materialized view using baseline method and prefix array respectively, e.g., in the first line, conducting all queries in $ QS_1 $ takes $ 17,272ms $ using baseline method but $ 3,216ms $ using prefix array.
+\kw{acce-ratio(ave)} is the average acceleration ratio of prefix array on each query.
+In most cases, prefix array can accelerate merging snapshots in time ranges in conducting queries.
+However, the effect of acceleration varies with $ s $.
+$ s $ in the No.1 view is the biggest among the 7 views, and the average acceleration ratio of prefix array is also the biggest, while $ s $ in the No.7 view and the average acceleration ratio of prefix array in the No.7 view are both the lowest.
+We can easily find that the average acceleration ratio of prefix array drops if $ s $ drops in general, which confirms our analysis in Section~\ref{sec:effec_of_indexes}.
+
+However, the similarity of snapshots is not the only difference among the 7 materialized views.
+In Table~\ref{tab:space_consumption_indexes} we can see that the size of materialized views is also different, so in our experiment, we choose the No.5 view as a reference and manually construct some temp-multi-networks, which have different similarity of snapshots but the same length of snapshot array and number of edges in total with the No.5 view.
+The numbers of edges in snapshots of each man-made dataset are almost uniformly distributed.
+The results on man-made datasets are shown in Table~\ref{tab:effi_prearray_man_made}.
 \begin{table}[t!]%\vspace*{-0.3cm}
-	\scriptsize
-	%\small
+	%\scriptsize
+	\small
 	\centering
-	\caption{Performance of the index-based solution} \vspace*{-0.2cm} \label{tab:effi_prearray}
-	\begin{tabular}{c c c c c| c c c}
+	\caption{Performance and acceleration ratio of prefix array on man-made datasets} \vspace*{-0.2cm} \label{tab:effi_prearray_man_made}
+	\begin{tabular}{c c c c c}
 		\toprule
-		\makecell[c]{Views\\No.}& $ s $ & \makecell[c]{baseline\\(ms)} &\makecell[c]{STree\\(ms)}&\makecell[c]{acce-ratio\\(ave)} & \makecell[c]{Original\\view size} &  \makecell[c]{STree\\size}&\makecell[c]{STree\\ratio}\cr %\hline %\hline
-		\midrule
-		1&53.48&16,960 &3,960 &3.45 &41KB &94KB &2.27 \cr
-		\midrule
-		2&18.16&172,614 &57,637 &2.32 &397KB &1.1MB &2.72\cr
-		\midrule
-		3&6.15&279,684 &144,849 &1.59&3.7MB &13.8MB &3.69\cr
-		\midrule
-		4&6.07&285,623 &147,565 &1.59&3.8MB &13.9MB &3.70 \cr
-		\midrule
-		5&4.70&515,607 &293,546 &1.50&5.4MB &22.1MB &4.04\cr
-		\midrule
-		6&3.97&896,386 &550,376 &1.40&8.3MB &35.8MB &4.32\cr
-		\midrule
-		7&1.12&6,719,417 &6,366,660 &1.05&37.1MB &285.6MB &7.70\cr
+		\makecell[c]{Original\\size}& $ s $ & \makecell[c]{baseline\\(ms)} &\makecell[c]{pre-array\\(ms)}&\makecell[c]{acce-ratio\\(ave)} \cr %\hline %\hline
+		\midrule
+		5,467,826 &10&589,636 &442,730 &1.20 \cr
+		\midrule
+		5,467,826 &20&448,802 &234,486 &1.80 \cr
+		\midrule
+		5,467,826 &50&327,947 &98,095 &3.35 \cr
+		\midrule
+		5,467,826 &80&306,467 &64,689 &4.80 \cr
 		\bottomrule
@@
 \end{table}
-}
-
-\begin{table}[t!]%\vspace*{-0.3cm}
-	\scriptsize
-	%\small
+%\begin{figure}[t] %\vspace*{-0.5cm}
+%	\begin{center}
+%		\includegraphics[width=0.8\columnwidth]{fig/create_prearray_time.png}
+%		\vspace*{-0.6cm}
+%		\caption{man-made prearray time}
+%		\vspace*{-0.4cm}
+%		\label{fig:man_made_prearray_time}
+%	\end{center}
+%\end{figure}
+Each data line in Table~\ref{tab:effi_prearray_man_made} represents result on each man-made temp-multi-network.
+For example, in the first data line, the man-made temp-multi-network has 5,467,826 edges as the No.5 materialized view but has similarity of snapshots of 10.
+To conduct similar queries in $ QS_1,...,QS_7 $, baseline method uses 589,636 ms and prefix array uses 442,730 ms, obtaining an acceleration ratio of 1.2.
+In the last data line, the man-made temp-multi-network has the same number of edges but larger similarity of snapshots of 80.
+Prefix array in this case obtains an acceleration ratio of 4.8.
+We can see that the results here are consistent with results in Table~\ref{tab:effi_prearray}.
+Note that the difference of time consumption using baseline method among man-made temp-multi-networks may be due to the implementation of the program and it doesn't affect our results.
+
+We then set $ f_e= $ MAX($\ast$) and use the same queries in $ QS_1,...,QS_7 $ above to test the efficiency of STable and STree (it's similar if $ f_e= $ MIN($\ast$)).
+The results are shown in Table~\ref{tab:effi_stree_stable}.
+\begin{table*}[t!]%\vspace*{-0.3cm}
+	%\scriptsize
+	\small
 	\centering
-	\caption{Performance of the index-based solution (K=1,000, M=1,000,000)} \vspace*{-0.2cm} \label{tab:effi_index}
+	\caption{Performance and acceleration ratio of STree and STable on materialized views} \vspace*{-0.2cm} \label{tab:effi_stree_stable}
+	\begin{tabular}{c c c c c c c}
+		\toprule
+		\makecell[c]{Views\\No.}& $ s $ & \makecell[c]{baseline\\(ms)} &\makecell[c]{STable\\(ms)}&\makecell[c]{acce-ratio\\(STable, ave)}&\makecell[c]{STree\\(ms)}&\makecell[c]{acce-ratio\\(STree, ave)} \cr %\hline %\hline
+		\midrule
+		1&53.48&16,960 &1,313 &10.75 &3,960 &3.45 \cr
+		\midrule
+		2&18.16&172,614 &21,921 &6.30 &57,637 &2.32 \cr
+		\midrule
+		3&6.15&279,684 &54,267 &4.48 &144,849 &1.59 \cr
+		\midrule
+		4&6.07&285,623 &55,414 &4.00 &147,565 &1.59 \cr
+		\midrule
+		5&4.70&515,607 &106,463 &3.82 &293,546 &1.50 \cr
+		\midrule
+		6&3.97&896,386 &195,698 &3.62 &550,376 &1.40 \cr
+		\midrule
+		7&1.12&6,719,417 &NaN&NaN&6,366,660 &1.05 \cr
+		\bottomrule
+	\end{tabular}
+	\vspace*{-0.4cm}
+\end{table*}
+%\begin{figure}[t] %\vspace*{-0.5cm}
+%	\begin{center}
+%		\includegraphics[width=0.8\columnwidth]{fig/stree_and_stable_time.png}
+%		\vspace*{-0.6cm}
+%		\caption{stree and stable}
+%		\vspace*{-0.4cm}
+%		\label{fig:stree_and_stable_time}
+%	\end{center}
+%\end{figure}
+We can see that both STree and STable can accelerate the queries, while the effect of STable is more significant, since there are at most 2 snapshots being operated in STable for every query.
+However, we failed to build STable on the No.7 view because of the huge memory consumption, which we will discuss in Exp-2.
+Similar to prefix array, the effects of STree and STable are influenced by the similarity of snapshots, e.g., on the No.1 view, STree is $ 3.45 $ times faster than baseline method and STable is $ 12.92 $ times faster than baseline method.
+But when similarity of snapshots in views drops, both STree and STable gain poorer results, e.g., on the No.7 view, STree is almost unhelpful, and STable can not even be built.
+
+To eliminate the influence of different size of materialized views, we build indexes on our man-made temp-multi-networks and conduct similar queries in $ QS_1,...,QS_7 $.
+The results are shown in Table~\ref{tab:effi_stree_stable_man_made},
+\begin{table*}[t!]%\vspace*{-0.3cm}
+	%\scriptsize
+	\small
+	\centering
+	\caption{Performance and acceleration ratio of STree and STable on man-made datasets} \vspace*{-0.2cm} \label{tab:effi_stree_stable_man_made}
+	\begin{tabular}{c c c c c c c}
+		\toprule
+		\makecell[c]{Original\\size}& $ s $ & \makecell[c]{baseline\\(ms)} &\makecell[c]{STable\\(ms)}&\makecell[c]{acce-ratio\\(STable, ave)}&\makecell[c]{STree\\(ms)}&\makecell[c]{acce-ratio\\(STree, ave)} \cr %\hline %\hline
+		\midrule
+		5,467,826 &10&359,416 &127,685 &2.77 &280,001 &1.26 \cr
+		\midrule
+		5,467,826 &20&298,525 &81,443 &3.83 &197,733 &1.58 \cr
+		\midrule
+		5,467,826 &50&239,775 &36,002 &6.66 &96,798 &2.43 \cr
+		\midrule
+		5,467,826 &80&225,354 &23,234 &9.56 &67,257 &3.20 \cr
+		\bottomrule
+	\end{tabular}
+	\vspace*{-0.4cm}
+\end{table*}
+%\begin{figure}[t] %\vspace*{-0.5cm}
+%	\begin{center}
+%		\includegraphics[width=0.8\columnwidth]{fig/create_stree_and_stable_time.png}
+%		\vspace*{-0.6cm}
+%		\caption{man-made stree and stable time}
+%		\vspace*{-0.4cm}
+%		\label{fig:man_made_stree_and_stable_time}
+%	\end{center}
+%\end{figure}
+which are similar to results in Table~\ref{tab:effi_stree_stable}.
+The average acceleration ratio of STree and STable both increases when similarity of snapshots increases, and the effect of STable is still more significant.
+
+\stitle{Exp-2: Space consumption of indexes with different similarity of snapshots.} In this experiment we mainly discuss the space consumption of indexes.
+\begin{table*}[t!]%\vspace*{-0.3cm}
+	%\scriptsize
+	\small
+	\centering
+	\caption{Space consumption of indexes on materialized views} \vspace*{-0.2cm} \label{tab:space_consumption_indexes}
+	\begin{tabular}{c c c c c c c c c}
+		\toprule
+		\makecell[c]{Views\\No.}&\makecell[c]{Original\\size}& $ s $ &\makecell[c]{pre-array\\size}&\makecell[c]{pre-array\\ratio}& \makecell[c]{STable\\size} &\makecell[c]{STable\\ratio}&\makecell[c]{STree\\size}&\makecell[c]{STree\\ratio} \cr %\hline %\hline
+		\midrule
+		1&41,448 &53.48&62,535 &1.51 &388,772 &9.38&93,975 &2.27   \cr
+		\midrule
+		2&396,755 &18.16&1,022,351 &2.58  &5,734,822 &14.45&1,077,456 &2.72  \cr
+		\midrule
+		3&3,738,125 &6.15&21,518,053 &5.76  &100,111,214 &26.78&13,788,570 &3.69  \cr
+		\midrule
+		4&3,758,885 &6.07&21,949,182 &5.84  &101,640,912 &27.04&13,918,066 &3.70  \cr
+		\midrule
+		5&5,467,826 &4.70&39,066,700 &7.14  &173,573,474 &31.74&22,063,352 &4.04  \cr
+		\midrule
+		6&8,304,421 &3.97&69,167,227 &8.33  &297,747,375 &35.85&35,837,987 &4.32  \cr
+		\midrule
+		7&37,096,632 &1.12&1,015,573,783 &27.38  &NaN&NaN&285,623,583 &7.70 \cr
+		\bottomrule
+	\end{tabular}
+	\vspace*{-0.4cm}
+\end{table*}
+%\begin{figure}[t] %\vspace*{-0.5cm}
+%	\begin{center}
+%		\includegraphics[width=0.8\columnwidth]{fig/index_space.png}
+%		\vspace*{-0.6cm}
+%		\caption{indexes size}
+%		\vspace*{-0.4cm}
+%		\label{fig:index_size}
+%	\end{center}
+%\end{figure}
+Table~\ref{tab:space_consumption_indexes} shows the space consumption of each index on all materialized views.
+\kw{Original} \kw{size} is the total number of edges in materialized views.
+\kw{pre}\kw{-}\kw{array} \kw{size} is the total number of edges in prefix array built on each view.
+\kw{pre}\kw{-}\kw{array} \kw{ratio} is the space consumption ratio of prefix array built on each view.
+\kw{STable} \kw{size}, \kw{STable} \kw{ratio}, \kw{STree} \kw{size} and \kw{STree} \kw{ratio} are similar.
+We can see that the space consumption ratio of each index grows when similarity of snapshots drops, which confirms our conjecture in Section~\ref{sec:effec_of_indexes}.
+In detail, STree is the most stable and cost-optimal index among the three indexes, because the space consumption ratio of STree is relatively low and has the slowest growth when similarity of snapshots drops.
+Combining the results in Exp-1, STree achieves a good balance between time and space.
+STable here has the highest space consumption ratio, since it maintains two-dimensional snapshot array.
+STable can not be built on the No.7 view since it takes a lot of time and space.
+
+Similarly, we conduct the same experiment on our man-made datasets to explore the relationship between space consumption ratio of indexes and similarity of snapshots again.
+The results are shown in Table~\ref{tab:space_consumption_indexes_man_made},
+\begin{table*}[t!]%\vspace*{-0.3cm}
+	%\scriptsize
+	\small
+	\centering
+	\caption{Space consumption of indexes on man-made datasets} \vspace*{-0.2cm} \label{tab:space_consumption_indexes_man_made}
 	\begin{tabular}{c c c c c c c c}
 		\toprule
-		\makecell[c]{View\\No.}& $ s $ & \makecell[c]{Baseline\\(sec.)} &\makecell[c]{STree\\(sec.)}&\makecell[c]{acce-ratio\\(ave)} & \makecell[c]{View\\ size} &  \makecell[c]{STree\\size}&\makecell[c]{Space\\ratio}\cr %\hline %\hline
-		\midrule
-		1&53.48&17 &4 &4.25 &41K &94K &2.29 \cr
-		\midrule
-		2&18.16&173 &58 &2.98 &397K &1.1M &2.77\cr
-		\midrule
-		3&6.15&280 &145 &1.93&3.7M &13.8M &3.72\cr
-		\midrule
-		4&6.07&286 &148 &1.93&3.7M &13.9M &3.76 \cr
-		\midrule
-		5&4.70&516 &294 &1.76&5.4M &22.1M &4.09\cr
-		\midrule
-		6&3.97&896 &550 &1.63&8.3M &35.8M &4.31\cr
-		\midrule
-		7&1.12&6,719 &6,367 &1.06&37.1M &285.6M &7.70\cr
+		\makecell[c]{Original\\size}& $ s $ &\makecell[c]{pre-array\\size}&\makecell[c]{pre-array\\ratio}& \makecell[c]{STable\\size} &\makecell[c]{STable\\ratio}&\makecell[c]{STree\\size}&\makecell[c]{STree\\ratio} \cr %\hline %\hline
+		\midrule
+		5,467,826 &10&73,934,678 &13.52 &238,281,300 &43.58 &28,776,691 &5.26 \cr
+		\midrule
+		5,467,826 &20&40,179,416 &7.35 &169,629,213 &31.02 &25,472,457 &4.66 \cr
+		\midrule
+		5,467,826 &50&16,362,842 &2.99 &86,337,728 &15.79 &18,116,929 &3.31 \cr
+		\midrule
+		5,467,826 &80&10,276,491 &1.88 &59,063,641 &10.80 &14,966,701 &2.74 \cr
 		\bottomrule
 	\end{tabular}
-	\vspace*{-0.4cm}
-\end{table}
-
-We set $ f_e= $ MAX($\ast$) and use the queries in $ QS_1,\cdots,QS_7 $ to test the efficiency of our index-based algorithm.
-The results are shown in Table~\ref{tab:effi_index}.
-Similar results can also be observed for the other aggregation functions ($ f_e= $ COUNT($\ast$), $ f_e= $ SUM($\ast$), and $ f_e= $ MIN($\ast$)).
-In Table~\ref{tab:effi_index}, \kw{View No.} denotes the No.
-of materialized views in Table~\ref{tab:materialized_view}, and $ s $ is the similarity of snapshots.
-The third and the fourth columns are time used to process all the queries on each materialized view using the baseline method and the index-based algorithm respectively.
-For example, in the first line, processing all queries in $ QS_1 $ takes $ 17s $ using the baseline method, but consumes $ 4s $ using the segment-tree index based algorithm.
-The \kw{acce-ratio(ave)} is the average acceleration ratio of the index-based algorithm on each query, compared to the baseline algorithm.
-In most cases, the index-based algorithm can accelerate merging snapshots in time ranges in conducting queries.
-However, the effect of acceleration varies with $ s $.
-In the No.1 view, where $s$ is the largest, we can see that the index-based solution achieves the best average acceleration ratio.
-We can observe that the average acceleration ratio of the index-based solution drops if $ s $ drops in general, which confirms our analysis in Section~\ref{sec:effec_of_indexes}.
-
-Table~\ref{tab:effi_index} also shows the space usage of the index-based solution (6th-8th columns).
-As can be seen, the size of the segment-tree based index is only several times larger than the original size of the views.
-For example, in the first line, the original view size is 41K, while our index-based solution takes only 94K space, with 2.27\kw{x} more space usage.
-Also, we can see that with $s$ increasing, the space usage of the index-based solution decreases.
-These results demonstrate that our segment-tree based index structure is very space-efficient when $s$ is relatively large.
-However, when $s$ is small, e.g., near to 1, the space overhead of our index-based solution is high.
-Moreover, when $s$ is near to 1, the average acceleration ratio is also near to 1 (i.e., the index-based solution is only slightly better than the baseline method).
-These results indicate that when $s$ is very small, there is no need to build an index.
-
-\stitle{Exp-2: Updating performance of the index-based solution.} Here we evaluate the updating performance of our index-based solution.
-We divide all temporal edges in a materialized view into 10 batches equally according to the order of timestamps, e.g., the first batch of temporal edges are edges with the smallest timestamps, and they are added into the index one by one following the order of timestamps.
-When edges in a single batch are added into the index, we record both the time and space consumption of adding edges in the batch.
-The results are shown in Fig.~\ref{fig:index_update}.
-From Fig.~\ref{fig:index_update}(a), we can see that with the number of batch increasing, the time consumption of the index-updating algorithm increases.
-These results are consistent with our analysis in Section~\ref{subsec:segment_tree}.
-Moreover, we can observe that for a large $s$, the time cost of our index-updating algorithm is low, while for a small $s$, the cost is often high.
-The reason could be that updating STree involves copying snapshot, i.e., snapshot in root, which maintains all snapshots in snapshot array, and thus gets larger if $ s $ gets smaller.
-As shown in Fig.~\ref{fig:index_update}(b), the space consumption of the index-updating algorithm is linear with respect to the number of batches, indicating that our algorithm is space-efficient.
-Likewise, we can observe that the algorithm takes more space for a smaller $s$.
-These results further confirm our analysis in Section~\ref{subsec:segment_tree}.
-
-\begin{figure}[t!]
+	\vspace*{-0.2cm}
+\end{table*}
+%\begin{figure}[t] %\vspace*{-0.5cm}
+%	\begin{center}
+%		\includegraphics[width=0.8\columnwidth]{fig/create_index_size.png}
+%		\vspace*{-0.6cm}
+%		\caption{create indexes size}
+%		\vspace*{-0.4cm}
+%		\label{fig:create_index_size}
+%	\end{center}
+%\end{figure}
+which are similar to results in Table~\ref{tab:space_consumption_indexes}, so we don't describe them again.
+
+\stitle{Exp-3: Updating performance of indexes with different similarity of snapshots.} In this experiment, we mainly discuss the updating performance of each index built on views with different similarity of snapshots, specifically the trend of time and space consumption under continuous addition of new edges.
+However, our datasets (DBLP, IMDB and man-made datasets) have no more edges which can be added after we build temporal graph cubes on them.
+In this experiment we simulate the continuous addition of new edges on indexes by dividing all temporal edges in a materialized view into 10 batches equally according to the order of timestamps, e.g., the first batch of temporal edges are edges with the smallest timestamps, and they are added into indexes one by one according to the order of timestamps.
+When edges in a single batch are added into indexes, we record the total time consumption of adding edges in the batch and current size, represented by the number of stored edges in the indexes.
+As the previous experiments, we use man-made datasets to eliminate the difference on size of materialized views.
+Due to the limitation of space, we directly conduct experiments on man-made datasets.
+
+Similar to previous experiments, we construct 4 man-made datasets having the same number of temporal edges with the No.5 view but different similarity of snapshots, which are denoted by $ s=10 $, $ s=20 $, $ s=50 $ and $ s=80 $.
+\begin{figure*}[t!]
 	\begin{center}
 		\begin{tabular}[t]{c}\hspace*{-0.3cm}
-		%	\subfigure[{\scriptsize Prefix Array}]{
-%				\includegraphics[width=0.25\textwidth]{fig/exp/index_update/index_update_single_a.pdf}
-%			}
-%			\hspace*{-0.3cm}
-%			\subfigure[{\scriptsize STable}]{
-%				\includegraphics[width=0.25\textwidth]{fig/exp/index_update/index_update_single_b.pdf}
-%			}
-%			\hspace*{-0.3cm}
-%			%\vspace*{-0.3cm}\\\hspace*{-0.3cm}
-			\subfigure[{\scriptsize Time consumption}]{
-				\includegraphics[width=0.23\textwidth]{fig/exp/index_update/index_update_single_c.pdf}
-			}
-	%		\\
-%			\hspace*{-0.3cm}
-%			\subfigure[{\scriptsize Prefix Array}]{
-%				\includegraphics[width=0.25\textwidth]{fig/exp/index_update/index_update_single_d.pdf}
-%			}
-%			\hspace*{-0.3cm}
-%			\subfigure[{\scriptsize STable}]{
-%				\includegraphics[width=0.25\textwidth]{fig/exp/index_update/index_update_single_e.pdf}
-%			}
+			\subfigure[{\scriptsize Prefix Array}]{
+				\includegraphics[width=0.25\textwidth]{fig/exp/index_update/index_update_single_a.pdf}
+			}
 			\hspace*{-0.3cm}
-			\subfigure[{\scriptsize Space usage}]{
-				\includegraphics[width=0.23\textwidth]{fig/exp/index_update/index_update_single_f.pdf}
+			\subfigure[{\scriptsize STable}]{
+				\includegraphics[width=0.25\textwidth]{fig/exp/index_update/index_update_single_b.pdf}
+			}
+			\hspace*{-0.3cm}
+			%\vspace*{-0.3cm}\\\hspace*{-0.3cm}
+			\subfigure[{\scriptsize STree}]{
+				\includegraphics[width=0.25\textwidth]{fig/exp/index_update/index_update_single_c.pdf}
+			}
+			\\
+			\hspace*{-0.3cm}
+			\subfigure[{\scriptsize Prefix Array}]{
+				\includegraphics[width=0.25\textwidth]{fig/exp/index_update/index_update_single_d.pdf}
+			}
+			\hspace*{-0.3cm}
+			\subfigure[{\scriptsize STable}]{
+				\includegraphics[width=0.25\textwidth]{fig/exp/index_update/index_update_single_e.pdf}
+			}
+			\hspace*{-0.3cm}
+			\subfigure[{\scriptsize STree}]{
+				\includegraphics[width=0.25\textwidth]{fig/exp/index_update/index_update_single_f.pdf}
 			}
@@
 	\end{center}
-	\vspace*{-0.5cm}
-	\caption{The updating performance of the index-based solution}
+	\vspace*{-0.2cm}
+	\caption{Trend of time and space consumption of indexes under continuous addition of new edges}
 	\vspace*{-0.4cm}
 	\label{fig:index_update}
-\end{figure}
+\end{figure*}
+
+In Figure~\ref{fig:index_update}, (a)-(c) show the trend of time consumption of each index being added with batches of edges in the 4 man-made datasets.
+%We transfer the actual value of time consumption to the ratio of time consumption value of adding each batch of edges to time consumption value of adding the 1-st batch of edges, for example, on curve related to $ s=10 $ in Figure~\ref{fig:index_update} (a), time consumption value of adding the 3-th batch of edges to prefix array is about 1.6 times of time consumption value of adding the 1-st batch to the same prefix array.
+Overall, in Figure~\ref{fig:index_update} (b)-(c), we can see that all four curves in these two figures show an increase, which means the time consumption of adding the back batch of edges of each dataset into both STable and STree are more than adding the front batch of edges.
+This pattern can be explained by our analysis in Section~\ref{subsec:sparse_table} and \ref{subsec:segment_tree}.
+However, after a rise, some curves in Figure~\ref{fig:index_update} (a) show a small decline and eventually stabilize, while curves related to $ s=50 $ and $ s=80 $ do not even have a rising process.
+It can still be explained that, in the final stabilization phase of curves, the last snapshot of the prefix array already shares the same edges with the summative snapshot of snapshot array in temp-multi-network the prefix array built on.
+In this phase, the last snapshot of prefix array to be copied ($ preArray[t_{end}] $ in line~2 of Algorithm~\ref{alg:prefix_array_update}) has a constant size when adding new edges with $ t-t_{base}>t_{end} $, so the total time consumption per batch is constant.
+As for the small decline of curves, it's because in the stabilization phase, regardless of whether $ preArray[t_{end}] $ is copied beforehand, the new edge already exists in the last snapshot of the prefix array when it's finally added, so the branch of Algorithm~\ref{alg:prefix_array_update} in line~5-6 will not be executed, which creates edge and takes more time than branch in line~3-4 in actual running.
+It's easy to know that the larger $ s $ is, the earlier the last snapshot of the prefix array shares the same edges with the summative snapshot, which is shown in Figure~\ref{fig:index_update} (a).
+
+Apart from the overall trend of the curves, in Figure~\ref{fig:index_update} (a)-(c), we can find that in each figure, higher curves are related to smaller values of $ s $, which means for each type of index, when adding the same number of new edges, indexes built on datasets with smaller similarity of snapshots take more time to be updated.
+For example in Figure~\ref{fig:index_update} (a), when adding the same batch of edges, the last snapshot of the prefix array will be copied for the new edges with $ t-t_{base}>t_{end} $.
+When $ s $ is small, the last snapshot of the prefix array built on such a dataset has larger size because snapshots in snapshot array of the original dataset share fewer edges.
+In this case, updating prefix array takes more time.
+Similar reason can be used to explain Figure~\ref{fig:index_update} (b).
+Updating STree also involves copying snapshot, i.e., snapshot in root, which maintains all snapshots in snapshot array, and gets larger if $ s $ gets smaller.
+However, copying snapshot occurs only when creating new root for STree, and since the range maintained by the root grows exponentially, copying snapshot hardly occurs when adding new edges in later batches.
+The difference in time consumption when adding the same batch of new edges of datasets with different similarity of snapshots $ s $ mainly comes from updating the root down to the leaf with new edges.
+It can be speculated from probability that for STree built on datasets with larger $ s $, there is a higher possibility that the snapshot in each node being updated with the new edge already contains that new edge, so the time consumption is slightly less.
+The deeper reason is that more edges are shared among snapshots of the original dataset if $ s $ of the dataset is larger.
+The time consumption of creating these nodes is the same if they do not yet exist.
+Since copying snapshot rarely occurs, the time consumption of updating STree is least influenced by $ s $ of the datasets among the three indexes, which can be shown in Figure~\ref{fig:index_update} (c).
+
+Figure~\ref{fig:index_update} (d)-(f) show the trend of space consumption of each index being added with each batch of edges of the 4 man-made datasets.
+Overall, curves in Figure~\ref{fig:index_update} (d) and (f) are linear, while curves in Figure~\ref{fig:index_update} (e) grow faster than linear curve, because STable maintains a two-dimensional snapshot array, which we discussed in Section~\ref{subsec:sparse_table}.
+The linear curves in Figure~\ref{fig:index_update} (d) and (f) show that prefix array and STree have better scalability than STable.
+For each kind of index, the instances built on datasets with smaller $ s $ have more space consumption and grow faster after each batch of new edges are added.
+The reason is also related to $ s $.
+For example in Figure~\ref{fig:index_update} (d), when adding each batch of new edges, prefix array built on datasets with smaller $ s $ has to copy larger snapshot.
+Among these three indexes, the space consumption of updating STree is still least influenced by $ s $ of the datasets because of the rare occurrence of copying snapshot and close space consumption caused by other operations in updating STree built on datasets with different $ s $.
+The relatively flat curves in Figure~\ref{fig:index_update} (f) also indicate that STree has the best scalability.
 
@@
 Our work is also related to graph summarization and analysis.
-For static graphs, there are some representative works, including graph compression with MDL (Minimum Description Length) principle \cite{navlakha2008graph}, attributed graph compression \cite{wu2014graph} and graph clustering based on vertices partitioning \cite{zhou2009graph}.
-Recently, there exist several studies on static graph summarization, such as summarizing directed acyclic graph (DAG) \cite{zhu2020top}, summarizing multi-relation graph \cite{ke2022multi} where multiple edges of different types may exist between any pair of vertices, and DPGS model \cite{zhou2021dpgs}, which can preserve properties like graph spectrum and the authorities and hubnesses of vertices especially in highly degree-skewed graphs while reconstructing graph.
+For static graph, there are some representative works, including graph compression with MDL (Minimum Description Length) principle \cite{navlakha2008graph}, attributed graph compression \cite{wu2014graph} and graph clustering based on vertices partitioning \cite{zhou2009graph}.
+In recent years there are also some novel works related to static graph summarization, such as summarizing directed acyclic graph (DAG) \cite{zhu2020top}, summarizing multi-relation graph \cite{ke2022multi} where multiple edges of different types may exist between any pair of vertices, and DPGS model \cite{zhou2021dpgs}, which can preserve properties like graph spectrum and the authorities and hubnesses of vertices especially in highly degree-skewed graphs while reconstructing graph.
 For temporal graph and dynamic graph, TimeCrunch \cite{shah2015timecrunch} summarizes a large dynamic graph with a set of important temporal structures using MDL, such as ranged full clique, periodic bipartite core, oneshot star, etc.
-\cite{fernandes2018dynamic,tsalouchidou2018scalable} investigate the problem of summarizing dynamic graph in real time, which use a sliding window of fixed length to summarize the latest snapshots.
+\cite{fernandes2018dynamic,tsalouchidou2018scalable} both investigate the problem of summarizing dynamic graph in real time.
+It is done by using a sliding window of fixed length to summarize the latest snapshots.
 When a new snapshot is generated, the window slides forward, discarding the oldest snapshot in the window and generating a new summary.
-However, in this paper, we can specify arbitrary time window to query summarized result in real time.
-In addition, we summarize the graph based on the selected dimensions of vertices, while the previous studies summarize the graph based on the super-node and super-edge.
+However, in this paper, we can specify arbitrary time window to query summative result in real time.
+In addition, we summarize the graph based on the selected dimensions of vertices, while the previous two works summarize the graph based on the super-node and super-edge.
 MoSSo \cite{ko2020incremental} incrementally summarizes fully dynamic graph.
-The difference of \cite{ko2020incremental} with \cite{fernandes2018dynamic,tsalouchidou2018scalable} is that the edges in the graph are dynamically added and removed, and MoSSo incrementally summarizes the whole graph after any modification on the graph.
+The difference of \cite{ko2020incremental} with the previous two works is that the edges in fully dynamic graph are dynamically added and removed, and MoSSo incrementally summarize the whole graph after any modification on the graph.
 
@@
 In this paper, we extend data warehouse and OLAP technology to temporal multidimensional networks by proposing a new data warehouse model \kw{Temporal\enspace Graph\enspace Cube}, which provides knowledge workers with tools to analyze temporal multidimensional networks.
-We first extend the basic concepts in static graph cube and introduce two new queries, \kw{temporal\enspace cuboid} and \kw{temporal\enspace crossboid}, allowing \kw{Temporal\enspace Graph\enspace Cube} to support OLAP queries on temporal multidimensional networks.
-Then, we propose a segment-tree based index method to accelerate the OLAP queries.
-We also present a new metric to measure the efficiency of the index.
-We conduct extensive experiments on two large real-world datasets, and the results demonstrate the effectiveness and efficiency of the proposed solutions.
-
-%We point out that some classical methods are no longer applicable in the implementation of \kw{Temporal\enspace Graph\enspace Cube}.
-
-%Our experimental results show the effectiveness of \kw{Temporal\enspace Graph\enspace Cube} and corroborate our inferences about the relationship between the efficiency of indexes and the metric.
+We first extend the basic concepts in static graph cube and discuss two basic queries, \kw{temporal\enspace cuboid} and \kw{temporal\enspace crossboid}, allowing \kw{Temporal\enspace Graph\enspace Cube} to support OLAP queries on temporal multidimensional networks.
+Then we extend three typical indexes on common range query problem to accelerate the above queries.
+We find a simple metric that affects the efficiency of indexes and analyze how it affects.
+We point out that some classical methods are no longer applicable in the implementation of \kw{Temporal\enspace Graph\enspace Cube}.
+Our experimental results show the effectiveness of \kw{Temporal\enspace Graph\enspace Cube} and corroborate our inferences about the relationship between the efficiency of indexes and the metric.
 With the support of the implementation strategy for \kw{Temporal\enspace Graph\enspace Cube}, the indexes are able to achieve an acceleration effect.
@@
 %
-
-\comment{
 
@@
 
-}
-
 % trigger a \newpage just before the given reference
@@
 % that's all folks
-
-\begin{IEEEbiography}[{\includegraphics[width=1in,height=1.25in,clip,keepaspectratio]{biophoto/grwang.jpg}}]{Guoren Wang}
-	received the BS, MS, and PhD degrees from the Department of Computer Science, Northeastern University, China, in 1988, 1991, and
-1996, respectively.
-Currently, he is a professor with the Beijing Institute of Technology (BIT), Beijing, China.
-His research interests include graph data management, graph mining, and graph computational systems.
-\end{IEEEbiography}
-\vspace{-10ex}
-\begin{IEEEbiography}[{\includegraphics[width=1in,height=1.25in,clip,keepaspectratio]{biophoto/yuez.jpg}}]{Yue Zeng}
-	is currently a master student at Beijing Institute of Technology (BIT), Beijing, China. His research interests include graph data management and social network analysis.
-\end{IEEEbiography}
-\vspace{-10ex}
-\begin{IEEEbiography}[{\includegraphics[width=1in,height=1.25in,clip,keepaspectratio]{biophoto/RonghuaLi}}]{Rong-Hua Li}
-	received the PhD degree from the Chinese University of Hong Kong, in 2013.
-He is currently a professor with the Beijing Institute of Technology (BIT), Beijing, China.
-His research interests include graph data management and mining, social network analysis, graph computational systems, and graph-based machine learning.
-\end{IEEEbiography}
-\vspace{-10ex}
-\begin{IEEEbiography}[{\includegraphics[width=1in,height=1.30in,clip,keepaspectratio]{biophoto/hcqin}}]{Hongchao Qin}
-is currently a Postdoc at Beijing Institute of Technology, China.
-He received the B.S.
-degree in mathematics, M.E.
-degree and Ph.D.
-degree in computer science from Northeastern University, China in 2013, 2015 and 2020, respectively.
-His current research interests include social network analysis and data-driven graph mining.
-\end{IEEEbiography}
-\vspace{-10ex}
-\begin{IEEEbiography}[{\includegraphics[width=1in,height=1.30in,clip,keepaspectratio]{biophoto/xhshi.jpg}}]{Xuanhua Shi}
-received his Ph.D. degree in Computer Engineering from HUST (China) in 2005. He is a professor in Service Computing Technology and System Lab and Cluster and Grid
-Computing Lab, HUST (China). His current research interests focus on the scalability, resilience and autonomy of large-scale distributed systems, such as peta-scale systems, and data centers.
-\end{IEEEbiography}
-\vspace{-10ex}
-\begin{IEEEbiography}[{\includegraphics[width=1in,height=1.30in,clip,keepaspectratio]{biophoto/ybxia.jpg}}]{Yubin Xia}
-received the deploma degree in software school, Fudan University, Shanghai, China, in 2004, and the Ph.D.
-degree in computer science and technology from Peking University, Beijing, China, in 2010.
-He is now an associate professor in Shanghai Jiao Tong University since September 2012.
-His research interests include computer architecture, operating system, and security.
-\end{IEEEbiography}
-\vspace{-10ex}
-\begin{IEEEbiography}[{\includegraphics[width=1in,height=1.30in,clip,keepaspectratio]{biophoto/xqshang.jpg}}]{Xuequn Shang} 
-received her Ph.D.
-in computer science from University of Magdeburg, Germany, in 2005.
-She is currently a professor in School of Computer Science, Northwestern Polytechnical University, China.
-Her research interests include data mining, bioinformatics and machine learning.
-\end{IEEEbiography}
-\vspace{-10ex}
-\begin{IEEEbiography}[{\includegraphics[width=1in,height=1.30in,clip,keepaspectratio]{biophoto/lhong}}]{Liang Hong}
-received his BS degree and Ph.D. degree in Computer Science at Huazhong University of Science and Technology (HUST) in 2003 and 2009, respectively. Now, he is an associate professor
-in School of Information Management of Wuhan University. His research interests include graph database, spatio-temporal data management and social networks.
-\end{IEEEbiography}
-
-%\begin{IEEEbiography}[{\includegraphics[width=1in,height=1.25in,clip,keepaspectratio]{biophoto/wanggr}}]{Guoren Wang}
-%	received the BS, MS, and PhD degrees from the Department of Computer Science, Northeastern University, China, in 1988, 1991, and
-%1996, respectively.
-Currently, he is a professor with the Beijing Institute of Technology (BIT), Beijing, China.
-His research interests include graph data management, graph mining, and graph computational systems.
-%\end{IEEEbiography}
-%
-%\begin{IEEEbiography}[{\includegraphics[width=1in,height=1.25in,clip,keepaspectratio]{biophoto/zengyue}}]{Yue Zeng}
-%	is currently a master student at Beijing Institute of Technology (BIT), Beijing, China. His research interests include graph data management and social network analysis.
-%\end{IEEEbiography}
-%
-%\begin{IEEEbiography}[{\includegraphics[width=1in,height=1.25in,clip,keepaspectratio]{biophoto/RonghuaLi}}]{Rong-Hua Li}
-%	received the PhD degree from the Chinese University of Hong Kong, in 2013.
-He is currently a professor with the Beijing Institute of Technology (BIT), Beijing, China.
-His research interests include graph data management and mining, social network analysis, graph computational systems, and graph-based machine learning.
-%\end{IEEEbiography}
-%
-%
-%\begin{IEEEbiography}[{\includegraphics[width=1in,height=1.25in,clip,keepaspectratio]{biophoto/RuiMao}}]{Rui Mao}
-%	received the PhD degree in computer science from the University of Texas at Austin, in 2007.
-He is currently a professor in Shenzhen University.
-His research interests include big data analysis and management, content-based similarity query of multimedia and biological data, data mining, and machine learning.
-%\end{IEEEbiography}
-%
-%\begin{IEEEbiography}[{\includegraphics[width=1in,height=1.25in,clip,keepaspectratio]{biophoto/ZhiweiZhang}}]{Zhiwei Zhang}
-%	received the BS degree from Renmin University of China in 2010, and PhD degree from the Chinese University of Hong Kong in 2014.
-He is currently a professor with the Beijing Institute of Technology (BIT), Beijing, China.
-His research interests include federal learning, data pricing and transaction, distributed system, blockchain, and algorithm analysis.
-%\end{IEEEbiography}
-%
-%\begin{IEEEbiography}[{\includegraphics[width=1in,height=1.25in,clip,keepaspectratio]{biophoto/YeYuan}}]{Ye Yuan}
-%	received the BS, MS, and PhD degrees in computer science from Northeastern University, in 2004, 2007, and 2011, respectively.
-He is now a professor with the Beijing Institute of Technology (BIT), Beijing, China.
-His research interests include graph databases, probabilistic databases, and social network analysis.
-%\end{IEEEbiography}
 \end{document}

### 2023-01-05 revision/response.tex
response 1-6

@@
 \end{Comments}
-\noindent \textbf{Response:} The parameter should remain $ (u',v',a,a) $. The reason is that edges stored in snapshots of each tree node are in form of $ () $
+\noindent \textbf{Response:} The parameter should remain $ (u',v',a,a) $.
+In line 11 of Algorithm 5, the algorithm inserts $ e' $ into $ treeNode.snapshot $, which is equivalent to merge two snapshots: $ treeNode.snapshot $ and a temporary snapshot consisting of only $ e' $.
+However, edges in snapshot of each tree node are in form of $ (u,v,max,min) $, so we need to transform $ e' $ into $ (u',v',a,a) $, since $ a $ is both the maximum and minimum value of the numeric attribute in $ e' $.
+$ t $ is only used to determine whether the left child or the right child of $ treeNode $ should also be updated.
 

### 2023-01-06 revision/response.tex
response 1-6

@@
 \end{Comments}
-\noindent \textbf{Response:} test
+\noindent \textbf{Response:} Actually we do use the two ratios to proof the effectiveness of the index.
+Acceleration ratio in Definition 7 and space consumption ratio in Definition 9 theoretically measure the query efficiency and space cost of the index respectively based on the edges' number.
+As in our experiments (see Table 6 of Section 7.3), we show the two ratios in the 5-th and 8-th column to proof the actual effectiveness of the index.
+However, both theoretically and experimentally we find that the query efficiency and space cost of the index are both related to a metric named 'similarity of snapshots' in the manuscript, as shown in Table 6.
+If the value of similarity of snapshot.
+To sum up, we do use the two ratios to proof the effectiveness of the index, and similarity of snapshots is used to
 

### 2023-01-06 revision/response.tex
response 1-7

--- 2023-01-05 revision/response.tex
@@
 \end{Comments}
-\noindent \textbf{Response:} test
+\noindent \textbf{Response:} Actually we do use the two ratios to proof the effectiveness of the index.
+As in our experiments (see Table 6 of Section 7.3), we show the two ratios in the 5-th and 8-th column to proof the actual effectiveness of the index.
+Similarity of snapshots is the metric which has a strong correlation with the two ratios, so it is used to measure the necessity of building index for a materialized view.
+In detail, both theoretically and experimentally we find that larger similarity of snapshots in a materialized view leads to higher acceleration ratio and lower space consumption ratio of the index.
+If the value of similarity of snapshots in a view is as low as $ 1 $, then there is no need to build index for the view and the baseline method to conduct queries is the best method, as we analyzed in Section 5.
+%Acceleration ratio in Definition 7 and space consumption ratio in Definition 9 theoretically measure the query efficiency and space cost of the index respectively based on the edges' number.
+As in our experiments (see Table 6 of Section 7.3), we show the two ratios in the 5-th and 8-th column to proof the actual effectiveness of the index.
+However, both theoretically and experimentally we find that the query efficiency and space cost of the index are both related to a metric named 'similarity of snapshots' in the manuscript, as shown in Table 6.
+If the value of similarity of snapshot.
+To sum up, we do use the two ratios to proof the effectiveness of the index, and similarity of snapshots is used to
 

### 2023-01-10 revision/response.tex
response 1-10

@@
 
-\section{Response to Reviewer \#1.2}
+\section{Response to Reviewer \#2}
 \setcounter{Comments}{0}
 \begin{Comments}
-It would be better to move Definitions 1 and 2 to be after Definition 3, as the latter does not rely on the first two.
+D1: The management of snapshots should be described with more details.
+According to Def.
+2, the snapshot is defined with a single timestamps.
+It looks like that when an edge forms at timestamp t, it never disappears.
+How do we maintain an edge with time range from t1 to t2?
+Otherwise, the limitation or applicability of the proposed method should be discussed.
 \end{Comments}
-\noindent \textbf{Response: } Following your suggestion, we have moved Definitions 1, 2 to be after Definition 3.
+\noindent \textbf{Response:} test
 
 \begin{Comments}
-In the problem formulation, it appears that parameter $\theta$ is not required.
+D2: Following D1, in current experimental datasets, DBLP and IMDB, all edges with single timestamps. I suggest adding experiments with datasets which contain edges with time ranges.
 \end{Comments}
-\noindent \textbf{Response: } $\theta$ is a parameter which can control the window size for each snapshot.
-As shown in Fig.12, we evaluate our algorithms for other window sizes on DBLP.
-Since the results are similar to the case of $\theta=1$, we do the experiments with $\theta$ setting to 1 month/year.
-
-In the revised version, to avoid misunderstanding, we have removed parameter $\theta$ so the window size will be set as 1 month/year.
+\noindent \textbf{Response:} test
 
 \begin{Comments}
- Left column, Page 5, "$cd(u) \geq \mu$ and $\overline{cd}(u) < \mu$" $-->$ "$cd(u) < \mu$ and $\overline{cd}(u) \geq \mu$"
+D3: The effectiveness of partial materialization is not verified in experiments.
 \end{Comments}
-\noindent \textbf{Response: } Thank you very much for pointing out the negligence. We have corrected this error.
+\noindent \textbf{Response:} test
+
+\section{Response to Reviewer \#3}
+\setcounter{Comments}{0}
+\begin{Comments}
+The experimental study only tests the proposed methods in this paper.
+I know the temporal graph cube is a novel problem studied in this paper, thus there is no existing algorithms/methods can direct handle it.
+However, is it possible to adapt some existing methods on graph summarizing, or static graph cube methods to handle the temporal graph cube problem as some baselines?
+Through comparing with modified existing methods can better show the advantages of the proposed methods.
+\end{Comments}
+\noindent \textbf{Response:} test
+
+\begin{Comments}
+ some minor language issues should be addressed. E.g., In line 52, left column, page 2. "a index" $ \rightarrow $ "an index"
+\end{Comments}
+\noindent \textbf{Response:} Thank you very much for pointing out the negligence. We have corrected this error.
 

### 2023-01-11 src2/TempGCube.hpp
prepare code 1-11

@@ -1,0 +1,2344 @@
+#ifndef TEMPGCUBE_H
+#define TEMPGCUBE_H
+
+#include<string>
+#include<fstream>
+#include<vector>
+#include<unordered_map>
+#include<unordered_set>
+#include<algorithm>
+#include<iostream>
+#include<sstream>
+#include<sys/time.h>
+#include<random>
+#define ll long long
+using namespace std;
+
+const double EXP=1e-8;
+
+void split(string victim,vector<string>& holder){
+    int i=0,last=0;
+    while(i<victim.size()){
+        if(victim[i]==','){
+            holder.push_back(string(victim.substr(last,i-last)));
+            last=i+1;
+        }
+        ++i;
+    }
+    holder.push_back(string(victim.substr(last,victim.size()-last)));
+}
+
+int lowerbit(int x){
+    return x&(-x);
+}
+
+int cNumber(int m,int n){
+    int top=1;
+    int mn=m-n;
+    while(m>n){
+        top*=m;
+        m--;
+    }
+    int bot=1;
+    while(mn>0){
+        bot*=mn;
+        mn--;
+    }
+    return top/bot;
+}
+
+struct hashVectorString{
+    size_t operator ()(const vector<string>& theKey)const{
+        hash<string> hasher=hash<string>();
+        size_t res=hasher(theKey[0]);
+        for(int i=1;i<theKey.size();++i){
+            res=res^hasher(theKey[i]);
+        }
+        return res;
+    }
+};
+
+struct hashVectorInt{
+    size_t operator()(const vector<int>& theKey)const{
+        hash<int> hasher=hash<int>();
+        size_t res=hasher(theKey[0]);
+        for(int i=1;i<theKey.size();++i){
+            res=res^hasher(theKey[i]);
+        }
+        return res;
+    }
+};
+
+class VertexTabl{
+public:
+    int attriNum;
+    vector<string> attriVec;
+    vector<int> attriPosInOri;
+    vector<vector<string> > dataList;
+    vector<int> dataCount;
+    unordered_map<vector<string>,int,hashVectorString> vecStringMp;
+
+    bool initFrmFile(string vertexFileName);
+
+    int insert(vector<string>& attri);
+};
+
+class Edge{
+public:
+    int count;
[…]

### 2023-01-11 src2/TempGCube_old.hpp

@@ -1,0 +1,1707 @@
+#ifndef TEMPGCUBE_H
+#define TEMPGCUBE_H
+
+#include<string>
+#include<fstream>
+#include<vector>
+#include<unordered_map>
+#include<unordered_set>
+#include<algorithm>
+#include<iostream>
+#include<sstream>
+#define ll long long
+using namespace std;
+
+const double EXP=1e-8;
+
+void split(string victim,vector<string>& holder){
+    int i=0,last=0;
+    while(i<victim.size()){
+        if(victim[i]==','){
+            holder.push_back(string(victim.substr(last,i-last)));
+            last=i+1;
+        }
+        ++i;
+    }
+    holder.push_back(string(victim.substr(last,victim.size()-last)));
+}
+
+int lowerbit(int x){
+    return x&(-x);
+}
+
+int cNumber(int m,int n){
+    int top=1;
+    int mn=m-n;
+    while(m>n){
+        top*=m;
+        m--;
+    }
+    int bot=1;
+    while(mn>0){
+        bot*=mn;
+        mn--;
+    }
+    return top/bot;
+}
+
+struct hashVectorString{
+    size_t operator ()(const vector<string>& theKey)const{
+        hash<string> hasher=hash<string>();
+        size_t res=hasher(theKey[0]);
+        for(int i=1;i<theKey.size();++i){
+            res=res^hasher(theKey[i]);
+        }
+        return res;
+    }
+};
+
+struct hashVectorInt{
+    size_t operator()(const vector<int>& theKey)const{
+        hash<int> hasher=hash<int>();
+        size_t res=hasher(theKey[0]);
+        for(int i=1;i<theKey.size();++i){
+            res=res^hasher(theKey[i]);
+        }
+        return res;
+    }
+};
+
+class VertexTabl{
+public:
+    int attriNum;
+    vector<string> attriVec;
+    vector<int> attriPosInOri;
+    vector<vector<string> > dataList;
+    unordered_map<vector<string>,int,hashVectorString> vecStringMp;
+
+    bool initFrmFile(string vertexFileName);
+
+    int insert(vector<string>& attri);
+};
+
+class Edge{
+public:
+    int count;
+    double amount,maxv,minv;
+
+    Edge();
[…]

### 2023-01-11 src2/analysis/draw.py

@@ -1,0 +1,94 @@
+import pylab as pl
+import math
+from scipy.interpolate import splev, splprep
+import matplotlib.patches as mpathes
+import matplotlib.pyplot as plt
+
+fig,ax=pl.subplots()
+
+height=20
+width=20
+
+fin=open("graph_area_2001_2006.txt","r")
+
+drawed_vertex=set()
+drawed_vertex_co=dict()
+
+def getnextp(x,y,angle):
+    oriangle=math.atan2(y,x)
+    orilen=math.sqrt(x*x+y*y)
+    return orilen*math.cos(oriangle-angle),orilen*math.sin(oriangle-angle)
+
+basex=width/2
+basey=height/2
+
+startx=0
+starty=height/3
+
+def draw_p(name,val):
+    global startx,starty
+    realx=startx+basex
+    realy=starty+basey
+    drawed_vertex_co[name]=(startx,starty)
+    
+    vertex=mpathes.Circle((startx+basex,starty+basey),1)
+    bx=pl.gca()
+    bx.add_patch(vertex)
+    plt.text(realx,realy,name+str(val),fontsize=17)
+    
+
+    startx,starty=getnextp(startx,starty,math.pi/5)
+
+while True:
+    segf=fin.readline().strip().split(' ')
+    segt=fin.readline().strip().split(' ')
+    val=fin.readline().strip()
+
+    if val=='':
+        break
+
+    # 特别规则
+    # area_list=['DB','AI','SE']
+    # if segf[0] not in area_list or segt[0] not in area_list:
+    #     continue
+
+
+
+    # 特别规则
+    if len(segf)>2:
+        segf=[segf[0]+','+segf[1],segf[2]]
+        segt=[segt[0]+','+segt[1],segt[2]]
+
+
+    if segf[0] not in drawed_vertex:
+        drawed_vertex.add(segf[0])
+        draw_p(segf[0],int(segf[1]))
+    
+    if segt[0] not in drawed_vertex:
+        drawed_vertex.add(segt[0])
+        draw_p(segt[0],int(segt[1]))
+
+    # 特别规则
+    if int(val)<5000:
+        continue
+
+    fromx,fromy=drawed_vertex_co[segf[0]]
+
+    if segf[0]==segt[0]:
+        plt.text(fromx+basex,fromy+basey-0.5,val,fontsize=16)
+        continue
+
[…]

### 2023-01-11 src2/analysis/test.py

@@ -1,0 +1,3 @@
+import math
+
+print(math.atan2(1,0)/math.pi)

### 2023-01-11 src2/analysis_exp/test.py

@@ -1,0 +1,52 @@
+from logging.config import valid_ident
+
+
+def get_timevals(fin):
+    vallist=[]
+    for line in fin.readlines():
+        segs=line.strip().split(' ')
+        if len(segs)==0:
+            continue
+
+        val=int(segs[2])
+        vallist.append(val)
+    
+    return vallist
+
+fin1=open("testOutputCreateBaselineMax.txt","r")
+fin2=open("testOutputCreateStableMax.txt","r")
+
+vallist1=get_timevals(fin1)
+vallist2=get_timevals(fin2)
+ratiolist=[]
+
+for i in range(len(vallist1)):
+    if vallist2[i]==0: #临时措施
+        ratiolist.append(vallist1[i])
+    else:
+        ratiolist.append(vallist1[i]/vallist2[i])
+
+cnt=0
+sumlist1=[]
+sumlist2=[]
+avelist=[]
+sum1=0
+sum2=0
+ratiosum=0
+for i in range(len(vallist1)):
+    sum1=sum1+vallist1[i]
+    sum2=sum2+vallist2[i]
+    ratiosum=ratiosum+ratiolist[i]
+
+    cnt=cnt+1
+    if cnt%50==0:
+        sumlist1.append(sum1)
+        sumlist2.append(sum2)
+        avelist.append(ratiosum/50)
+        sum1=0
+        sum2=0
+        ratiosum=0
+
+print(sumlist1)
+print(sumlist2)
+print(avelist)

### 2023-01-11 src2/baseline.cpp

@@ -1,0 +1,214 @@
+#include"TempGCube.hpp"
+
+#include<iostream>
+using namespace std;
+
+vector<int> TempGCube::logTable=vector<int>();
+
+bool vertexEqual(const vector<string>& a,const vector<string>& b){
+    if(a.size()!=b.size()) return false;
+    for(int i=0;i<a.size();++i){
+        if(a[i]!=b[i]) return false;
+    }
+    return true;
+}
+
+bool vertexLess(const vector<string>& a,const vector<string>& b){
+    int minLen=min(a.size(),b.size());
+    for(int i=0;i<minLen;++i){
+        if(a[i]==b[i]) continue;
+        if(a[i]<b[i]) return true;
+        else return false;
+    }
+    return a.size()<b.size();
+}
+
+struct snap_res{
+    pair<vector<string>,vector<string> > vertexPair;
+    pair<int,int> idPair;
+    Edge e;
+    snap_res(pair<vector<string>,vector<string> > _pair,pair<int,int> _idPair,Edge& _e){
+        vertexPair=_pair;
+        idPair=_idPair;
+        e=_e;
+    }
+
+    bool operator <(const snap_res& b)const{
+        if(vertexEqual(vertexPair.first,b.vertexPair.first)){
+            return vertexLess(vertexPair.second,b.vertexPair.second);
+        }
+        return vertexLess(vertexPair.first,b.vertexPair.first);
+    }
+};
+
+void print_snapshot(SnapShot& snapshot){
+    for(int i=0;i<snapshot.idPairVec.size();++i){
+        cout<<snapshot.idPairVec[i].first<<" "<<snapshot.idPairVec[i].second<<" ";
+        cout<<snapshot.edgePool[i].count<<" "<<snapshot.edgePool[i].amount<<" "<<snapshot.edgePool[i].maxv<<" "<<snapshot.edgePool[i].minv<<endl;
+    }
+}
+
+void print_ans_snapshot(VertexTabl& ansVertexTabl,SnapShot& ans,int type){
+    vector<snap_res> reorganize_ans;
+    for(int i=0;i<ans.edgePool.size();++i){
+        if(ans.edgePool[i].count==0) continue;
+        vector<string>& aVertex=ansVertexTabl.dataList[ans.idPairVec[i].first];
+        vector<string>& bVertex=ansVertexTabl.dataList[ans.idPairVec[i].second];
+        if(vertexLess(aVertex,bVertex)){
[…]

### 2023-01-11 src2/exp/select_batch_baseline.cpp

@@ -1,0 +1,68 @@
+#include"../TempGCube.hpp"
+#include<sys/time.h>
+
+vector<int> TempGCube::logTable=vector<int>();
+
+int main(int argc,char* argv[]){
+    if(argc!=3){
+        cout<<"parameter error"<<endl;
+        return 1;
+    }
+    int start,end;
+    int indexType=0;
+
+    TempGCube tgcube;
+    start=clock();
+    tgcube.init(argv[1],argv[2]);
+    end=clock();
+    cerr<<"init done with "<<(end-start)*1000.0/CLOCKS_PER_SEC<<endl;
+    cerr<<"start time: "<<tgcube.graphList[0].base+1<<" end: "<<tgcube.graphList[0].end+tgcube.graphList[0].base<<endl;
+    cerr<<"vertex num: "<<tgcube.graphList[0].vertexTabl.dataList.size()<<" edge num: "<<tgcube.graphList[0].size<<endl;
+    start=end;
+    // vector<vector<int> > mList={{0},{0,1},{0,1,2},{0,1,2,3},{0,1,2,3,4},{0,1,2,3,4,5}};
+    vector<vector<int> > mList;
+    // tgcube.fullMaterialize();
+    tgcube.selectMaterialize(mList);
+    end=clock();
+    cerr<<"materialize done with "<<(end-start)*1000.0/CLOCKS_PER_SEC<<endl;
+
+    vector<vector<string> > allSegs;
+    vector<vector<int> > allIntParam;
+
+    while(true){
+        string attriList;
+        int timel,timer,type,times;
+        cin>>attriList;
+        
+        if(attriList=="end") break;
+        allIntParam.push_back(vector<int>());
+        int last=allIntParam.size()-1;
+        allIntParam[last].resize(4);
+
+        cin>>allIntParam[last][0]>>allIntParam[last][1]>>allIntParam[last][2]>>allIntParam[last][3];
+        vector<string> segs;
+        split(attriList,segs);
+        allSegs.push_back(segs);
+
+    }
+
+
+    //批量查询
+    timeval starttime,endtime;
+    gettimeofday(&starttime,NULL);
+    for(int i=0;i<allSegs.size();++i){
+        timeval partstart,partend;
+        gettimeofday(&partstart,NULL);
+        for(int j=0;j<allIntParam[i][3];++j){
+            TempGraph ans;
[…]

### 2023-01-11 src2/exp/select_batch_baseline_create.cpp

@@ -1,0 +1,81 @@
+#include"../TempGCube.hpp"
+#include<sys/time.h>
+vector<int> TempGCube::logTable=vector<int>();
+
+int main(int argc,char* argv[]){
+    if(argc!=3){
+        cout<<"parameter error"<<endl;
+        return 1;
+    }
+    int start,end;
+    int indexType=0;
+
+    TempGCube tgcube;
+    start=clock();
+    tgcube.init(argv[1],argv[2]);
+    end=clock();
+    cerr<<"init done with "<<(end-start)*1000.0/CLOCKS_PER_SEC<<endl;
+    cerr<<"start time: "<<tgcube.graphList[0].base+1<<" end: "<<tgcube.graphList[0].end+tgcube.graphList[0].base<<endl;
+    cerr<<"vertex num: "<<tgcube.graphList[0].vertexTabl.dataList.size()<<" edge num: "<<tgcube.graphList[0].size<<endl;
+    start=end;
+    // vector<vector<int> > mList={{0},{0,1},{0,1,2},{0,1,2,3},{0,1,2,3,4}};
+    vector<vector<int> > mList={{0,1,2,3,4}};
+    // tgcube.fullMaterialize();
+    tgcube.selectMaterialize(mList);
+    end=clock();
+    cerr<<"materialize done with "<<(end-start)*1000.0/CLOCKS_PER_SEC<<endl;
+
+    tgcube.createWithSimilarity(1,10);
+    tgcube.createWithSimilarity(1,20);
+    tgcube.createWithSimilarity(1,50);
+    tgcube.createWithSimilarity(1,80);
+    tgcube.materialized[{"pro","field","genre","isadult","averating","10"}]=2;
+    tgcube.materialized[{"pro","field","genre","isadult","averating","20"}]=3;
+    tgcube.materialized[{"pro","field","genre","isadult","averating","50"}]=4;
+    tgcube.materialized[{"pro","field","genre","isadult","averating","80"}]=5;
+    cerr<<"create done"<<endl;
+
+    start=clock();
+    tgcube.buildIndex(indexType);
+    end=clock();
+
+    vector<vector<string> > allSegs;
+    vector<vector<int> > allIntParam;
+
+    while(true){
+        string attriList;
+        int timel,timer,type,times;
+        cin>>attriList;
+        
+        if(attriList=="end") break;
+        allIntParam.push_back(vector<int>());
+        int last=allIntParam.size()-1;
[…]

### 2023-01-11 src2/exp/select_batch_prearray.cpp

@@ -1,0 +1,69 @@
+#include"../TempGCube.hpp"
+#include<sys/time.h>
+
+
+int main(int argc,char* argv[]){
+    if(argc!=3){
+        cout<<"parameter error"<<endl;
+        return 1;
+    }
+    int start,end;
+
+    TempGCube tgcube;
+    start=clock();
+    tgcube.init(argv[1],argv[2]);
+    end=clock();
+    cerr<<"init done with "<<(end-start)*1000.0/CLOCKS_PER_SEC<<endl;
+    cerr<<"start time: "<<tgcube.graphList[0].base+1<<" end: "<<tgcube.graphList[0].end+tgcube.graphList[0].base<<endl;
+    cerr<<"vertex num: "<<tgcube.graphList[0].vertexTabl.dataList.size()<<" edge num: "<<tgcube.graphList[0].size<<endl;
+    start=end;
+    vector<vector<int> > mList={{0},{0,1},{0,1,2},{0,1,2,3},{0,1,2,3,4}};
+    // tgcube.fullMaterialize();
+    tgcube.selectMaterialize(mList);
+    end=clock();
+    cerr<<"materialize done with "<<(end-start)*1000.0/CLOCKS_PER_SEC<<endl;
+    start=end;
+    tgcube.buildIndex(4);
+    end=clock();
+    cerr<<"build prearray done with "<<(end-start)*1000.0/CLOCKS_PER_SEC<<endl;
+
+    vector<vector<string> > allSegs;
+    vector<vector<int> > allIntParam;
+
+    while(true){
+        string attriList;
+        int timel,timer,type,times;
+        cin>>attriList;
+        
+        if(attriList=="end") break;
+        allIntParam.push_back(vector<int>());
+        int last=allIntParam.size()-1;
+        allIntParam[last].resize(4);
+
+        cin>>allIntParam[last][0]>>allIntParam[last][1]>>allIntParam[last][2]>>allIntParam[last][3];
+        vector<string> segs;
+        split(attriList,segs);
+        allSegs.push_back(segs);
+
+    }
+
+
+    //批量查询
+    timeval starttime,endtime;
+    gettimeofday(&starttime,NULL);
+    for(int i=0;i<allSegs.size();++i){
+        timeval partstart,partend;
+        gettimeofday(&partstart,NULL);
+        for(int j=0;j<allIntParam[i][3];++j){
+            TempGraph ans;
[…]

### 2023-01-11 src2/exp/select_batch_prearray_create.cpp

@@ -1,0 +1,82 @@
+#include"../TempGCube.hpp"
+#include<sys/time.h>
+vector<int> TempGCube::logTable=vector<int>();
+
+int main(int argc,char* argv[]){
+    if(argc!=3){
+        cout<<"parameter error"<<endl;
+        return 1;
+    }
+    int start,end;
+    int indexType=4;
+
+    TempGCube tgcube;
+    start=clock();
+    tgcube.init(argv[1],argv[2]);
+    end=clock();
+    cerr<<"init done with "<<(end-start)*1000.0/CLOCKS_PER_SEC<<endl;
+    cerr<<"start time: "<<tgcube.graphList[0].base+1<<" end: "<<tgcube.graphList[0].end+tgcube.graphList[0].base<<endl;
+    cerr<<"vertex num: "<<tgcube.graphList[0].vertexTabl.dataList.size()<<" edge num: "<<tgcube.graphList[0].size<<endl;
+    start=end;
+    // vector<vector<int> > mList={{0},{0,1},{0,1,2},{0,1,2,3},{0,1,2,3,4}};
+    vector<vector<int> > mList={{0,1,2,3,4}};
+    // tgcube.fullMaterialize();
+    tgcube.selectMaterialize(mList);
+    end=clock();
+    cerr<<"materialize done with "<<(end-start)*1000.0/CLOCKS_PER_SEC<<endl;
+
+    tgcube.createWithSimilarity(1,10);
+    tgcube.createWithSimilarity(1,20);
+    tgcube.createWithSimilarity(1,50);
+    tgcube.createWithSimilarity(1,80);
+    tgcube.materialized[{"pro","field","genre","isadult","averating","10"}]=2;
+    tgcube.materialized[{"pro","field","genre","isadult","averating","20"}]=3;
+    tgcube.materialized[{"pro","field","genre","isadult","averating","50"}]=4;
+    tgcube.materialized[{"pro","field","genre","isadult","averating","80"}]=5;
+    cerr<<"create done"<<endl;
+
+    start=clock();
+    tgcube.buildIndex(indexType);
+    end=clock();
+    cerr<<"build prearray done with "<<(end-start)*1000.0/CLOCKS_PER_SEC<<endl;
+
+    vector<vector<string> > allSegs;
+    vector<vector<int> > allIntParam;
+
+    while(true){
+        string attriList;
+        int timel,timer,type,times;
+        cin>>attriList;
+        
+        if(attriList=="end") break;
[…]

### 2023-01-11 src2/exp/select_batch_segtree.cpp

@@ -1,0 +1,77 @@
+//已恢复
+#include"../TempGCube.hpp"
+#include<sys/time.h>
+
+vector<int> TempGCube::logTable=vector<int>();
+
+int main(int argc,char* argv[]){
+    if(argc!=3){
+        cout<<"parameter error"<<endl;
+        return 1;
+    }
+    int start,end;
+    int indexType=5;
+
+    TempGCube tgcube;
+    start=clock();
+    tgcube.init(argv[1],argv[2]);
+    end=clock();
+    cerr<<"init done with "<<(end-start)*1000.0/CLOCKS_PER_SEC<<endl;
+    cerr<<"start time: "<<tgcube.graphList[0].base+1<<" end: "<<tgcube.graphList[0].end+tgcube.graphList[0].base<<endl;
+    cerr<<"vertex num: "<<tgcube.graphList[0].vertexTabl.dataList.size()<<" edge num: "<<tgcube.graphList[0].size<<endl;
+    start=end;
+    // vector<vector<int> > mList={{0},{0,1},{0,1,2},{0,1,2,3},{0,1,2,3,4}};
+    vector<vector<int> > mList={{0},{0,1},{0,1,2}};
+    // tgcube.fullMaterialize();
+    tgcube.selectMaterialize(mList);
+    end=clock();
+    cerr<<"materialize done with "<<(end-start)*1000.0/CLOCKS_PER_SEC<<endl;
+
+    start=end;
+    tgcube.buildIndex(indexType);
+    end=clock();
+    cerr<<"build segtree done with "<<(end-start)*1000.0/CLOCKS_PER_SEC<<endl;
+
+    //just tset
+    cout<<tgcube.graphList[1].treeRoot<<endl;
+
+    vector<vector<string> > allSegs;
+    vector<vector<int> > allIntParam;
+
+    while(true){
+        string attriList;
+        int timel,timer,type,times;
+        cin>>attriList;
+        
+        if(attriList=="end") break;
+        allIntParam.push_back(vector<int>());
+        int last=allIntParam.size()-1;
+        allIntParam[last].resize(4);
+
+        cin>>allIntParam[last][0]>>allIntParam[last][1]>>allIntParam[last][2]>>allIntParam[last][3];
+        vector<string> segs;
+        split(attriList,segs);
+        allSegs.push_back(segs);
+
+    }
+
+
+    //批量查询
+    timeval starttime,endtime;
[…]

### 2023-01-11 src2/exp/select_batch_segtree_create.cpp

@@ -1,0 +1,82 @@
+#include"../TempGCube.hpp"
+#include<sys/time.h>
+vector<int> TempGCube::logTable=vector<int>();
+
+int main(int argc,char* argv[]){
+    if(argc!=3){
+        cout<<"parameter error"<<endl;
+        return 1;
+    }
+    int start,end;
+    int indexType=5;
+
+    TempGCube tgcube;
+    start=clock();
+    tgcube.init(argv[1],argv[2]);
+    end=clock();
+    cerr<<"init done with "<<(end-start)*1000.0/CLOCKS_PER_SEC<<endl;
+    cerr<<"start time: "<<tgcube.graphList[0].base+1<<" end: "<<tgcube.graphList[0].end+tgcube.graphList[0].base<<endl;
+    cerr<<"vertex num: "<<tgcube.graphList[0].vertexTabl.dataList.size()<<" edge num: "<<tgcube.graphList[0].size<<endl;
+    start=end;
+    // vector<vector<int> > mList={{0},{0,1},{0,1,2},{0,1,2,3},{0,1,2,3,4}};
+    vector<vector<int> > mList={{0,1,2,3,4}};
+    // tgcube.fullMaterialize();
+    tgcube.selectMaterialize(mList);
+    end=clock();
+    cerr<<"materialize done with "<<(end-start)*1000.0/CLOCKS_PER_SEC<<endl;
+
+    tgcube.createWithSimilarity(1,10);
+    tgcube.createWithSimilarity(1,20);
+    tgcube.createWithSimilarity(1,50);
+    tgcube.createWithSimilarity(1,80);
+    tgcube.materialized[{"pro","field","genre","isadult","averating","10"}]=2;
+    tgcube.materialized[{"pro","field","genre","isadult","averating","20"}]=3;
+    tgcube.materialized[{"pro","field","genre","isadult","averating","50"}]=4;
+    tgcube.materialized[{"pro","field","genre","isadult","averating","80"}]=5;
+    cerr<<"create done"<<endl;
+
+    start=clock();
+    tgcube.buildIndex(indexType);
+    end=clock();
+    cerr<<"build prearray done with "<<(end-start)*1000.0/CLOCKS_PER_SEC<<endl;
+
+    vector<vector<string> > allSegs;
+    vector<vector<int> > allIntParam;
+
+    while(true){
+        string attriList;
+        int timel,timer,type,times;
+        cin>>attriList;
+        
+        if(attriList=="end") break;
[…]

### 2023-01-11 src2/exp/select_batch_stable.cpp

@@ -1,0 +1,77 @@
+//已恢复
+#include"../TempGCube.hpp"
+#include<sys/time.h>
+
+vector<int> TempGCube::logTable=vector<int>();
+
+int main(int argc,char* argv[]){
+    if(argc!=3){
+        cout<<"parameter error"<<endl;
+        return 1;
+    }
+    int start,end;
+    int indexType=3;
+
+    TempGCube tgcube;
+    start=clock();
+    tgcube.init(argv[1],argv[2]);
+    end=clock();
+    cerr<<"init done with "<<(end-start)*1000.0/CLOCKS_PER_SEC<<endl;
+    cerr<<"start time: "<<tgcube.graphList[0].base+1<<" end: "<<tgcube.graphList[0].end+tgcube.graphList[0].base<<endl;
+    cerr<<"vertex num: "<<tgcube.graphList[0].vertexTabl.dataList.size()<<" edge num: "<<tgcube.graphList[0].size<<endl;
+    start=end;
+    vector<vector<int> > mList={{0},{0,1},{0,1,2},{0,1,2,3},{0,1,2,3,4},{0,1,2,3,4,5}};
+    // vector<vector<int> > mList={{0},{0,1},{0,1,2}};
+    // tgcube.fullMaterialize();
+    tgcube.selectMaterialize(mList);
+    end=clock();
+    cerr<<"materialize done with "<<(end-start)*1000.0/CLOCKS_PER_SEC<<endl;
+
+    start=end;
+    tgcube.buildIndex(indexType);
+    end=clock();
+    cerr<<"build segtree done with "<<(end-start)*1000.0/CLOCKS_PER_SEC<<endl;
+
+    //just tset
+    // cout<<tgcube.graphList[1].treeRoot<<endl;
+
+    vector<vector<string> > allSegs;
+    vector<vector<int> > allIntParam;
+
+    while(true){
+        string attriList;
+        int timel,timer,type,times;
+        cin>>attriList;
+        
+        if(attriList=="end") break;
+        allIntParam.push_back(vector<int>());
+        int last=allIntParam.size()-1;
+        allIntParam[last].resize(4);
+
+        cin>>allIntParam[last][0]>>allIntParam[last][1]>>allIntParam[last][2]>>allIntParam[last][3];
+        vector<string> segs;
+        split(attriList,segs);
+        allSegs.push_back(segs);
+
+    }
+
+
+    //批量查询
[…]

### 2023-01-11 src2/exp/select_batch_stable_create.cpp

@@ -1,0 +1,82 @@
+#include"../TempGCube.hpp"
+#include<sys/time.h>
+vector<int> TempGCube::logTable=vector<int>();
+
+int main(int argc,char* argv[]){
+    if(argc!=3){
+        cout<<"parameter error"<<endl;
+        return 1;
+    }
+    int start,end;
+    int indexType=3;
+
+    TempGCube tgcube;
+    start=clock();
+    tgcube.init(argv[1],argv[2]);
+    end=clock();
+    cerr<<"init done with "<<(end-start)*1000.0/CLOCKS_PER_SEC<<endl;
+    cerr<<"start time: "<<tgcube.graphList[0].base+1<<" end: "<<tgcube.graphList[0].end+tgcube.graphList[0].base<<endl;
+    cerr<<"vertex num: "<<tgcube.graphList[0].vertexTabl.dataList.size()<<" edge num: "<<tgcube.graphList[0].size<<endl;
+    start=end;
+    // vector<vector<int> > mList={{0},{0,1},{0,1,2},{0,1,2,3},{0,1,2,3,4}};
+    vector<vector<int> > mList={{0,1,2,3,4}};
+    // tgcube.fullMaterialize();
+    tgcube.selectMaterialize(mList);
+    end=clock();
+    cerr<<"materialize done with "<<(end-start)*1000.0/CLOCKS_PER_SEC<<endl;
+
+    tgcube.createWithSimilarity(1,10);
+    tgcube.createWithSimilarity(1,20);
+    tgcube.createWithSimilarity(1,50);
+    tgcube.createWithSimilarity(1,80);
+    tgcube.materialized[{"pro","field","genre","isadult","averating","10"}]=2;
+    tgcube.materialized[{"pro","field","genre","isadult","averating","20"}]=3;
+    tgcube.materialized[{"pro","field","genre","isadult","averating","50"}]=4;
+    tgcube.materialized[{"pro","field","genre","isadult","averating","80"}]=5;
+    cerr<<"create done"<<endl;
+
+    start=clock();
+    tgcube.buildIndex(indexType);
+    end=clock();
+    cerr<<"build prearray done with "<<(end-start)*1000.0/CLOCKS_PER_SEC<<endl;
+
+    vector<vector<string> > allSegs;
+    vector<vector<int> > allIntParam;
+
+    while(true){
+        string attriList;
+        int timel,timer,type,times;
+        cin>>attriList;
+        
+        if(attriList=="end") break;
[…]

### 2023-01-11 src2/exp/select_exp.cpp

@@ -1,0 +1,38 @@
+#include"../TempGCube.hpp"
+
+
+int main(int argc,char* argv[]){
+    if(argc!=3){
+        cout<<"parameter error"<<endl;
+        return 1;
+    }
+    int start,end;
+
+    TempGCube tgcube;
+    start=clock();
+    tgcube.init(argv[1],argv[2]);
+    end=clock();
+    cerr<<"init done with "<<(end-start)*1000.0/CLOCKS_PER_SEC<<endl;
+    cerr<<"start time: "<<tgcube.graphList[0].base+1<<" end: "<<tgcube.graphList[0].end+tgcube.graphList[0].base<<endl;
+    cerr<<"vertex num: "<<tgcube.graphList[0].vertexTabl.dataList.size()<<" edge num: "<<tgcube.graphList[0].size<<endl;
+    start=end;
+    vector<vector<int> > mList={{0},{0,1},{0,1,2},{0,1,2,3},{0,1,2,3,4}};
+    // tgcube.fullMaterialize();
+    tgcube.selectMaterialize(mList);
+    end=clock();
+    cerr<<"materialize done with "<<(end-start)*1000.0/CLOCKS_PER_SEC<<endl;
+
+    for(int i=0;i<tgcube.graphList.size();++i){
+        TempGraph& curGraph=tgcube.graphList[i];
+        for(int j=0;j<curGraph.vertexTabl.attriPosInOri.size();++j){
+            cout<<curGraph.vertexTabl.attriPosInOri[j]<<" ";
+        }
+        cout<<endl;
+        for(int j=0;j<curGraph.snapshotVec.size();++j){
+            cout<<curGraph.snapshotVec[j].edgePool.size()<<" ";
+        }
+        cout<<endl<<endl;
+    }
+
+    return 0;
+}

### 2023-01-11 src2/exp/sort.py

@@ -1,0 +1,31 @@
+fin=open("view_size_summative_size_sort.txt","r")
+fin.readline()
+fin.readline()
+fin.readline()
+
+lines=fin.readlines()
+lines=lines[:len(lines)-1]
+
+d=dict()
+i=0
+while True:
+    if i==len(lines): break
+    line=lines[i].strip()
+    theL=len(line)
+    if theL not in d:
+        d[theL]=list()
+
+    d[theL].append((line,lines[i+1]))
+
+    i=i+2
+
+llist=list(d.keys())
+llist.sort()
+
+for theL in llist:
+    for group in d[theL]:
+        print(group[0])
+        temp=group[1]
+        temp=temp.strip().split()
+        print(round(int(temp[0])/int(temp[1]),2))
+

### 2023-01-11 src2/exp/test.py

@@ -1,0 +1,19 @@
+segs1=[(1878,1880),(1891,1895),(1906,1910),(1921,1925),(1936,1940),(1951,1955),(1966,1970),(1981,1985),(1996,2000),(2011,2015)]
+segs2=[(1878,1883),(1888,1898),(1903,1913),(1918,1928),(1933,1943),(1948,1958),(1963,1973),(1978,1988),(1993,2003),(2008,2018)]
+segs3=[(1878,1888),(1883,1903),(1898,1918),(1913,1933),(1928,1948),(1943,1963),(1958,1978),(1973,1993),(1988,2008),(2003,2023)]
+segs4=[(1878,1903),(1878,1918),(1883,1933),(1898,1948),(1913,1963),(1928,1978),(1943,1993),(1958,2008),(1973,2023),(1988,2028)]
+segs5=[(1878,1928),(1878,1943),(1878,1958),(1878,1973),(1888,1988),(1903,2003),(1918,2018),(1933,2028),(1948,2028),(1963,2028)]
+segs=segs1+segs2+segs3+segs4+segs5
+
+
+viewList=['pro,field,genre,isadult,averating,hotness']
+viewList=viewList+['pro,field,genre,isadult,averating']
+viewList=viewList+['pro,field,genre,isadult']
+viewList=viewList+['pro,field,genre']
+viewList=viewList+['pro,field']
+viewList=viewList+['pro']
+
+for view in viewList:
+    for seg in segs:
+        print(view,end=' ')
+        print(str(seg[0])+' '+str(seg[1])+' 1 1000')

### 2023-01-11 src2/exp_dblp/exp.cpp

@@ -1,0 +1,45 @@
+#include"../TempGCube.hpp"
+
+vector<int> TempGCube::logTable=vector<int>();
+
+int main(int argc,char* argv[]){
+    if(argc!=3){
+        cout<<"parameter error"<<endl;
+        return 1;
+    }
+    int start,end;
+
+    TempGCube tgcube;
+    start=clock();
+    tgcube.init(argv[1],argv[2]);
+    end=clock();
+    cerr<<"init done with "<<(end-start)*1000.0/CLOCKS_PER_SEC<<endl;
+    cerr<<"start time: "<<tgcube.graphList[0].base+1<<" end: "<<tgcube.graphList[0].end+tgcube.graphList[0].base<<endl;
+    cerr<<"vertex num: "<<tgcube.graphList[0].vertexTabl.dataList.size()<<" edge num: "<<tgcube.graphList[0].size<<endl;
+    start=end;
+    vector<vector<int> > mList={{1},{2},{1,2}};
+    // tgcube.fullMaterialize();
+    tgcube.selectMaterialize(mList);
+    end=clock();
+    cerr<<"materialize done with "<<(end-start)*1000.0/CLOCKS_PER_SEC<<endl;
+
+    for(int i=0;i<tgcube.graphList.size();++i){
+        
+        TempGraph& curGraph=tgcube.graphList[i];
+        for(int j=0;j<curGraph.vertexTabl.attriPosInOri.size();++j){
+            cout<<curGraph.vertexTabl.attriPosInOri[j]<<" ";
+        }
+        cout<<endl;
+        SnapShot summative;
+        for(int j=0;j<curGraph.snapshotVec.size();++j){
+            cout<<curGraph.snapshotVec[j].edgePool.size()<<" ";
+            SnapShot::mergeSnapShot(summative,curGraph.snapshotVec[j]);
+        }
+        cout<<endl;
+        cout<<curGraph.size<<" "<<summative.edgePool.size()<<" "<<curGraph.size*1.0/summative.edgePool.size()<<endl;
+
+        cout<<endl;
+    }
+
+    return 0;
+}

### 2023-01-11 src2/exp_update/insert_effective.cpp

@@ -1,0 +1,217 @@
+#include"../TempGCube.hpp"
+
+#include<iostream>
+using namespace std;
+
+vector<int> TempGCube::logTable=vector<int>();
+
+bool vertexEqual(const vector<string>& a,const vector<string>& b){
+    if(a.size()!=b.size()) return false;
+    for(int i=0;i<a.size();++i){
+        if(a[i]!=b[i]) return false;
+    }
+    return true;
+}
+
+bool vertexLess(const vector<string>& a,const vector<string>& b){
+    int minLen=min(a.size(),b.size());
+    for(int i=0;i<minLen;++i){
+        if(a[i]==b[i]) continue;
+        if(a[i]<b[i]) return true;
+        else return false;
+    }
+    return a.size()<b.size();
+}
+
+struct snap_res{
+    pair<vector<string>,vector<string> > vertexPair;
+    pair<int,int> idPair;
+    Edge e;
+    snap_res(pair<vector<string>,vector<string> > _pair,pair<int,int> _idPair,Edge& _e){
+        vertexPair=_pair;
+        idPair=_idPair;
+        e=_e;
+    }
+
+    bool operator <(const snap_res& b)const{
+        if(vertexEqual(vertexPair.first,b.vertexPair.first)){
+            return vertexLess(vertexPair.second,b.vertexPair.second);
+        }
+        return vertexLess(vertexPair.first,b.vertexPair.first);
+    }
+};
+
+void print_snapshot(SnapShot& snapshot){
+    for(int i=0;i<snapshot.idPairVec.size();++i){
+        cout<<snapshot.idPairVec[i].first<<" "<<snapshot.idPairVec[i].second<<" ";
+        cout<<snapshot.edgePool[i].count<<" "<<snapshot.edgePool[i].amount<<" "<<snapshot.edgePool[i].maxv<<" "<<snapshot.edgePool[i].minv<<endl;
+    }
+}
+
+void print_ans_snapshot(VertexTabl& ansVertexTabl,SnapShot& ans,int type){
+    vector<snap_res> reorganize_ans;
+    for(int i=0;i<ans.edgePool.size();++i){
+        if(ans.edgePool[i].count==0) continue;
+        vector<string>& aVertex=ansVertexTabl.dataList[ans.idPairVec[i].first];
+        vector<string>& bVertex=ansVertexTabl.dataList[ans.idPairVec[i].second];
+        if(vertexLess(aVertex,bVertex)){
[…]

### 2023-01-11 src2/exp_update/insert_effective_create.cpp

@@ -1,0 +1,225 @@
+#include"../TempGCube.hpp"
+
+#include<iostream>
+using namespace std;
+
+vector<int> TempGCube::logTable=vector<int>();
+
+bool vertexEqual(const vector<string>& a,const vector<string>& b){
+    if(a.size()!=b.size()) return false;
+    for(int i=0;i<a.size();++i){
+        if(a[i]!=b[i]) return false;
+    }
+    return true;
+}
+
+bool vertexLess(const vector<string>& a,const vector<string>& b){
+    int minLen=min(a.size(),b.size());
+    for(int i=0;i<minLen;++i){
+        if(a[i]==b[i]) continue;
+        if(a[i]<b[i]) return true;
+        else return false;
+    }
+    return a.size()<b.size();
+}
+
+struct snap_res{
+    pair<vector<string>,vector<string> > vertexPair;
+    pair<int,int> idPair;
+    Edge e;
+    snap_res(pair<vector<string>,vector<string> > _pair,pair<int,int> _idPair,Edge& _e){
+        vertexPair=_pair;
+        idPair=_idPair;
+        e=_e;
+    }
+
+    bool operator <(const snap_res& b)const{
+        if(vertexEqual(vertexPair.first,b.vertexPair.first)){
+            return vertexLess(vertexPair.second,b.vertexPair.second);
+        }
+        return vertexLess(vertexPair.first,b.vertexPair.first);
+    }
+};
+
+void print_snapshot(SnapShot& snapshot){
+    for(int i=0;i<snapshot.idPairVec.size();++i){
+        cout<<snapshot.idPairVec[i].first<<" "<<snapshot.idPairVec[i].second<<" ";
+        cout<<snapshot.edgePool[i].count<<" "<<snapshot.edgePool[i].amount<<" "<<snapshot.edgePool[i].maxv<<" "<<snapshot.edgePool[i].minv<<endl;
+    }
+}
+
+void print_ans_snapshot(VertexTabl& ansVertexTabl,SnapShot& ans,int type){
+    vector<snap_res> reorganize_ans;
+    for(int i=0;i<ans.edgePool.size();++i){
+        if(ans.edgePool[i].count==0) continue;
+        vector<string>& aVertex=ansVertexTabl.dataList[ans.idPairVec[i].first];
+        vector<string>& bVertex=ansVertexTabl.dataList[ans.idPairVec[i].second];
+        if(vertexLess(aVertex,bVertex)){
[…]

### 2023-01-11 src2/prearray.cpp

@@ -1,0 +1,214 @@
+#include"TempGCube.hpp"
+
+#include<iostream>
+using namespace std;
+
+vector<int> TempGCube::logTable=vector<int>();
+
+bool vertexEqual(const vector<string>& a,const vector<string>& b){
+    if(a.size()!=b.size()) return false;
+    for(int i=0;i<a.size();++i){
+        if(a[i]!=b[i]) return false;
+    }
+    return true;
+}
+
+bool vertexLess(const vector<string>& a,const vector<string>& b){
+    int minLen=min(a.size(),b.size());
+    for(int i=0;i<minLen;++i){
+        if(a[i]==b[i]) continue;
+        if(a[i]<b[i]) return true;
+        else return false;
+    }
+    return a.size()<b.size();
+}
+
+struct snap_res{
+    pair<vector<string>,vector<string> > vertexPair;
+    pair<int,int> idPair;
+    Edge e;
+    snap_res(pair<vector<string>,vector<string> > _pair,pair<int,int> _idPair,Edge& _e){
+        vertexPair=_pair;
+        idPair=_idPair;
+        e=_e;
+    }
+
+    bool operator <(const snap_res& b)const{
+        if(vertexEqual(vertexPair.first,b.vertexPair.first)){
+            return vertexLess(vertexPair.second,b.vertexPair.second);
+        }
+        return vertexLess(vertexPair.first,b.vertexPair.first);
+    }
+};
+
+void print_snapshot(SnapShot& snapshot){
+    for(int i=0;i<snapshot.idPairVec.size();++i){
+        cout<<snapshot.idPairVec[i].first<<" "<<snapshot.idPairVec[i].second<<" ";
+        cout<<snapshot.edgePool[i].count<<" "<<snapshot.edgePool[i].amount<<" "<<snapshot.edgePool[i].maxv<<" "<<snapshot.edgePool[i].minv<<endl;
+    }
+}
+
+void print_ans_snapshot(VertexTabl& ansVertexTabl,SnapShot& ans,int type){
+    vector<snap_res> reorganize_ans;
+    for(int i=0;i<ans.edgePool.size();++i){
+        if(ans.edgePool[i].count==0) continue;
+        vector<string>& aVertex=ansVertexTabl.dataList[ans.idPairVec[i].first];
+        vector<string>& bVertex=ansVertexTabl.dataList[ans.idPairVec[i].second];
+        if(vertexLess(aVertex,bVertex)){
[…]

### 2023-01-11 src2/test.cpp

@@ -1,0 +1,13 @@
+#include<vector>
+#include<iostream>
+using namespace std;
+
+class test{
+public:
+    int a;
+};
+
+int main(){
+    double a=49895;
+    cout<<a<<endl;
+}

### 2023-01-12 src2/TempGCube.hpp
exp 1-12

@@ -1809,7 +1809,7 @@ vector<string> TempGCube::partialGreedyOld(int k){
     }
 
     //print ans
-    vector<string> asString;
+    vector<vector<int>> ans;
     unordered_set<vector<int>,hashVectorInt>::iterator it=S.begin();
     while(it!=S.end()){
         const vector<int>& theans=(*it);

### 2023-01-12 src2/exp/test_partial_greedy.cpp

@@ -1,0 +1,86 @@
+#include"../TempGCube.hpp"
+
+
+int main(int argc,char* argv[]){
+    if(argc!=3){
+        cout<<"parameter error"<<endl;
+        return 1;
+    }
+    timeval start,end;
+    int k;
+    cin>>k;
+
+    TempGCube tgcube;
+    // start=clock();
+    // tgcube.init(argv[1],argv[2]);
+    // end=clock();
+    // cerr<<"init done with "<<(end-start)*1000.0/CLOCKS_PER_SEC<<endl;
+    // cerr<<"start time: "<<tgcube.graphList[0].base+1<<" end: "<<tgcube.graphList[0].end+tgcube.graphList[0].base<<endl;
+    // cerr<<"vertex num: "<<tgcube.graphList[0].vertexTabl.dataList.size()<<" edge num: "<<tgcube.graphList[0].size<<endl;
+
+    int wait;
+    cin>>wait;
+    switch (wait)
+    {
+    case 1:
+    {
+        
+    }
+    break;
+    default:
+        break;
+    }
+
+
+    start=end;
+    vector<string> oldres,newres;
+    oldres=tgcube.partialGreedyOld(k);
+    end=clock();
+    cerr<<"greedy old with "<<(end-start)*1000.0/CLOCKS_PER_SEC<<endl;
+
+    start=end;
+    newres=tgcube.partialGreedyNew(k);
+    end=clock();
+    cerr<<"greedy new with "<<(end-start)*1000.0/CLOCKS_PER_SEC<<endl;
+
+    int diffcnt=0;
+    for(int i=0;i<oldres.size();++i){
+        if(oldres[i]!=newres[i]){
+            diffcnt++;
+            break;
+        }
+    }
+    cout<<diffcnt<<endl;
+    vector<vector<string> > allSegs;
+    vector<vector<int> > allIntParam;
+
+    while(true){
+        string attriList;
+        int timel,timer,type,times;
+        cin>>attriList;
+        
+        if(attriList=="end") break;
+        allIntParam.push_back(vector<int>());
+        int last=allIntParam.size()-1;
+        allIntParam[last].resize(4);
+
+        cin>>allIntParam[last][0]>>allIntParam[last][1]>>allIntParam[last][2]>>allIntParam[last][3];
+        vector<string> segs;
+        split(attriList,segs);
+        allSegs.push_back(segs);
+
+    }
+
+    //批量查询
[…]

### 2023-01-12 src2/exp/test_partial_greedy.cpp
exp 1-13

@@ -12,7 +12,10 @@ int main(int argc,char* argv[]){
 
     TempGCube tgcube;
     // start=clock();
-    // tgcube.init(argv[1],argv[2]);
+    tgcube.init(argv[1],argv[2]);
+    vector<vector<int> > mList={{0,1,2,3,4,5}};
+    tgcube.selectMaterialize(mList);
+    cout<<tgcube.graphList[0]
     // end=clock();
     // cerr<<"init done with "<<(end-start)*1000.0/CLOCKS_PER_SEC<<endl;
     // cerr<<"start time: "<<tgcube.graphList[0].base+1<<" end: "<<tgcube.graphList[0].end+tgcube.graphList[0].base<<endl;

### 2023-01-13 src2/TempGCube.hpp
exp 1-13

@@ -1809,7 +1809,7 @@ vector<string> TempGCube::partialGreedyOld(int k){
     }
 
     //print ans
-    vector<vector<int>> ans;
+    vector<string> asString;
     unordered_set<vector<int>,hashVectorInt>::iterator it=S.begin();
     while(it!=S.end()){
         const vector<int>& theans=(*it);

### 2023-01-13 src2/exp/test_partial_greedy.cpp

@@ -1,5 +1,7 @@
 #include"../TempGCube.hpp"
 
+vector<int> TempGCube::logTable=vector<int>();
+
 
 int main(int argc,char* argv[]){
     if(argc!=3){
@@ -15,7 +17,13 @@ int main(int argc,char* argv[]){
     tgcube.init(argv[1],argv[2]);
     vector<vector<int> > mList={{0,1,2,3,4,5}};
     tgcube.selectMaterialize(mList);
-    cout<<tgcube.graphList[0]
+    cout<<tgcube.graphList[1].size<<" ";
+
+    SnapShotSum tempsnap;
+    for(int i=0;i<tgcube.graphList[1].snapshotVec.size();++i){
+        SnapShotSum::mergeSnapShot(tempsnap,tgcube.graphList[1].snapshotVec[i]);
+    }
+    cout<<tempsnap.edgePool.size()<<endl;
     // end=clock();
     // cerr<<"init done with "<<(end-start)*1000.0/CLOCKS_PER_SEC<<endl;
     // cerr<<"start time: "<<tgcube.graphList[0].base+1<<" end: "<<tgcube.graphList[0].end+tgcube.graphList[0].base<<endl;
@@ -35,55 +43,55 @@ int main(int argc,char* argv[]){
     }
 
 
-    start=end;
-    vector<string> oldres,newres;
-    oldres=tgcube.partialGreedyOld(k);
-    end=clock();
-    cerr<<"greedy old with "<<(end-start)*1000.0/CLOCKS_PER_SEC<<endl;
+    // start=end;
+    // vector<string> oldres,newres;
+    // oldres=tgcube.partialGreedyOld(k);
+    // end=clock();
+    // cerr<<"greedy old with "<<(end-start)*1000.0/CLOCKS_PER_SEC<<endl;
 
-    start=end;
-    newres=tgcube.partialGreedyNew(k);
-    end=clock();
-    cerr<<"greedy new with "<<(end-start)*1000.0/CLOCKS_PER_SEC<<endl;
+    // start=end;
+    // newres=tgcube.partialGreedyNew(k);
+    // end=clock();
+    // cerr<<"greedy new with "<<(end-start)*1000.0/CLOCKS_PER_SEC<<endl;
 
-    int diffcnt=0;
-    for(int i=0;i<oldres.size();++i){
-        if(oldres[i]!=newres[i]){
-            diffcnt++;
-            break;
-        }
-    }
[…]

### 2023-01-13 src2/TempGCube.hpp
exp 1-13

@@ -288,8 +288,8 @@ public:
     void createWithSimilarity(int theModel,int similarity);
     void selectMaterialize(vector<vector<int> >& mList);
     void partialMaterialize(int k);//k 是实例化的cuboid个数
-    vector<string> partialGreedyOld(int k);
-    vector<string> partialGreedyNew(int k);
+    vector<vector<int>> partialGreedyOld(int k);
+    vector<vector<int>> partialGreedyNew(int k);
     void recordMaterialize();
     bool isAncestor(vector<int>& attriPosList,int possibleSon);
     void buildGraphByExist(vector<int>& attriPosList,int existSon);
@@ -845,7 +845,7 @@ void TempGCube::buildIndex(int indexType){
             graphList[i].buildPreArray();
         }
     }else if(indexType==5){
-        for(int i=2;i<graphList.size();++i){//暂时跳过base view
+        for(int i=0;i<graphList.size();++i){//暂时跳过base view
             graphList[i].treeRoot=graphList[i].buildSegmentTree(graphList[i].base+1,graphList[i].base+graphList[i].end);
         }
     }
@@ -1285,13 +1285,15 @@ void TempGCube::queryWithTarget(TempGraph& targetGraph,SnapShot& ansSnapShot,boo
 
 //ans中的snapshot的边的count若是0
 int TempGCube::query(int indexType,int timel,int timer,int type,bool returnAns,vector<string>& attributes,TempGraph& ans){
-    if(materialized.find(attributes)!=materialized.end()){
-        TempGraph& targetGraph=graphList[materialized[attributes]];
+    if(attributes[0]=="name"||materialized.find(attributes)!=materialized.end()){
+        int graphid=0;
+        if(attributes[0]!="name") graphid=materialized[attributes];
+        TempGraph& targetGraph=graphList[graphid];
         ans.snapshotVec.push_back(SnapShot());
         SnapShot& ansSnapShot=ans.snapshotVec[0];
 
         queryWithTarget(targetGraph,ansSnapShot,returnAns,indexType,timel,timer,type);
-        return materialized[attributes];
+        return graphid;
     }else{
         //未被实例化
         //ans里面需自行装载vertexTabl
@@ -1541,7 +1543,7 @@ bool cuboidIsAncestor(vector<int>& son,const vector<int>& father){
     return true;
 }
 
-vector<string> TempGCube::partialGreedyNew(int k){
[…]

### 2023-01-13 src2/exp/test_partial_greedy.cpp

@@ -8,22 +8,22 @@ int main(int argc,char* argv[]){
         cout<<"parameter error"<<endl;
         return 1;
     }
-    timeval start,end;
+    int start,end;
     int k;
     cin>>k;
 
     TempGCube tgcube;
     // start=clock();
     tgcube.init(argv[1],argv[2]);
-    vector<vector<int> > mList={{0,1,2,3,4,5}};
-    tgcube.selectMaterialize(mList);
-    cout<<tgcube.graphList[1].size<<" ";
+    // vector<vector<int> > mList={{0,1,2,3,4,5}};
+    // tgcube.selectMaterialize(mList);
+    // cout<<tgcube.graphList[1].size<<" ";
 
-    SnapShotSum tempsnap;
-    for(int i=0;i<tgcube.graphList[1].snapshotVec.size();++i){
-        SnapShotSum::mergeSnapShot(tempsnap,tgcube.graphList[1].snapshotVec[i]);
-    }
-    cout<<tempsnap.edgePool.size()<<endl;
+    // SnapShotSum tempsnap;
+    // for(int i=0;i<tgcube.graphList[1].snapshotVec.size();++i){
+    //     SnapShotSum::mergeSnapShot(tempsnap,tgcube.graphList[1].snapshotVec[i]);
+    // }
+    // cout<<tempsnap.edgePool.size()<<endl;
     // end=clock();
     // cerr<<"init done with "<<(end-start)*1000.0/CLOCKS_PER_SEC<<endl;
     // cerr<<"start time: "<<tgcube.graphList[0].base+1<<" end: "<<tgcube.graphList[0].end+tgcube.graphList[0].base<<endl;
@@ -35,7 +35,9 @@ int main(int argc,char* argv[]){
     {
     case 1:
     {
-        
+        vector<vector<int>> res=tgcube.partialGreedyOld(k);
+        tgcube.selectMaterialize(res);
+        tgcube.buildIndex(5);
     }
     break;
     default:
@@ -62,36 +64,36 @@ int main(int argc,char* argv[]){
     //     }
     // }
     // cout<<diffcnt<<endl;
-    // vector<vector<string> > allSegs;
-    // vector<vector<int> > allIntParam;
+    vector<vector<string> > allSegs;
+    vector<vector<int> > allIntParam;
 
-    // while(true){
-    //     string attriList;
-    //     int timel,timer,type,times;
-    //     cin>>attriList;
+    while(true){
+        string attriList;
+        int timel,timer,type,times;
[…]

### 2023-01-17 src2/exp/generate_input.py
exp 1-18

@@ -1,0 +1,85 @@
+attlist=["pro","field","genre","isadult","averating","hotness"]
+val=1
+group=dict()
+while val<(1<<6):
+    needle=1
+    needlepos=1
+    curattlist=[]
+    while needle<(1<<6):
+        if (val&needle)!=0:
+            curattlist.append(attlist[needlepos-1])
+
+        needle=needle<<1
+        needlepos=needlepos+1
+
+    if len(curattlist) not in group:
+        group[len(curattlist)]=list()
+    group[len(curattlist)].append(curattlist)
+
+    val=val+1
+
+segslist=["1878 1880",
+"1891 1895",
+"1906 1910",
+"1921 1925",
+"1936 1940",
+"1951 1955",
+"1966 1970",
+"1981 1985",
+"1996 2000",
+"2011 2015",
+"1878 1883",
+"1888 1898",
+"1903 1913",
+"1918 1928",
+"1933 1943",
+"1948 1958",
+"1963 1973",
+"1978 1988",
+"1993 2003",
+"2008 2018",
+"1878 1888",
+"1883 1903",
+"1898 1918",
+"1913 1933",
+"1928 1948",
+"1943 1963",
+"1958 1978",
+"1973 1993",
+"1988 2008",
+"2003 2023",
+"1878 1903",
+"1878 1918",
+"1883 1933",
+"1898 1948",
+"1913 1963",
+"1928 1978",
+"1943 1993",
+"1958 2008",
+"1973 2023",
+"1988 2028",
+"1878 1928",
+"1878 1943",
+"1878 1958",
+"1878 1973",
+"1888 1988",
+"1903 2003",
+"1918 2018",
+"1933 2028",
+"1948 2028",
+"1963 2028"]
+
+fout=open("test_greedy_input.config","w")
+repeatseglist=[]
+for i in range(6,0,-1):
+    repeat=8-i
+    temprepeatlist=[]
+    for segs in segslist:
+        for j in range(repeat):
+            temprepeatlist.append(segs)
+
+    atts=group[i]
+    for j in range(len(temprepeatlist)):
+        temprepeatlist[j]=",".join(atts[j%len(atts)])+" "+temprepeatlist[j]+" 3 1"
+    
+    fout.write("\n".join(temprepeatlist)+"\n")

### 2023-01-18 src2/TempGCube.hpp
exp 1-18

@@ -1,11 +1,11 @@
 #ifndef TEMPGCUBE_H
 #define TEMPGCUBE_H
 
+#include<unordered_set>
+#include<unordered_map>
 #include<string>
 #include<fstream>
 #include<vector>
-#include<unordered_map>
-#include<unordered_set>
 #include<algorithm>
 #include<iostream>
 #include<sstream>
@@ -45,6 +45,19 @@ int cNumber(int m,int n){
         mn--;
     }
     return top/bot;
+}
+
+bool cuboidIsAncestor(vector<int>& son,const vector<int>& father){
+    if(son.size()>father.size()) return false;
+    int last=0;
+    for(int i=0;i<son.size();++i){
+        while(last<father.size()&&son[i]!=father[last]){
+            last++;
+        }
+        if(last==father.size()) return false;
+        last++;
+    }
+    return true;
 }
 
 struct hashVectorString{
@@ -1564,18 +1577,7 @@ void TempGraph::initFrmTempGraph(TempGraph& son,vector<int>& attriPosInSon,vecto
     //建索引（可选）
 }
 
-bool cuboidIsAncestor(vector<int>& son,const vector<int>& father){
-    if(son.size()>father.size()) return false;
-    int last=0;
-    for(int i=0;i<son.size();++i){
-        while(last<father.size()&&son[i]!=father[last]){
-            last++;
-        }
-        if(last==father.size()) return false;
-        last++;
-    }
-    return true;
-}
+
 
 vector<vector<int>> TempGCube::partialGreedyNew(int k){
     // unordered_map<vector<int>,ll,hashVectorInt> cuboidSize,cuboidDeSize;//记录size，底图size

### 2023-01-18 src2/exp/test_partial_greedy.cpp

@@ -4,17 +4,17 @@ vector<int> TempGCube::logTable=vector<int>();
 
 
 int main(int argc,char* argv[]){
-    if(argc!=3){
+    if(argc!=5){
         cout<<"parameter error"<<endl;
         return 1;
     }
     int start,end;
-    int k;
-    cin>>k;
+    int k=atoi(argv[3]);
 
     TempGCube tgcube;
     // start=clock();
     tgcube.init(argv[1],argv[2]);
+    cout<<"init done"<<endl;
     // vector<vector<int> > mList={{0,1,2,3,4,5}};
     // tgcube.selectMaterialize(mList);
     // cout<<tgcube.graphList[1].size<<" ";
@@ -29,8 +29,7 @@ int main(int argc,char* argv[]){
     // cerr<<"start time: "<<tgcube.graphList[0].base+1<<" end: "<<tgcube.graphList[0].end+tgcube.graphList[0].base<<endl;
     // cerr<<"vertex num: "<<tgcube.graphList[0].vertexTabl.dataList.size()<<" edge num: "<<tgcube.graphList[0].size<<endl;
 
-    int greedyType;
-    cin>>greedyType;
+    int greedyType=atoi(argv[4]);
     switch (greedyType)
     {
     case 0:
@@ -56,7 +55,7 @@ int main(int argc,char* argv[]){
         break;
     }
 
-
+    cout<<"materialize done"<<endl;
     // start=end;
     // vector<string> oldres,newres;
     // oldres=tgcube.partialGreedyOld(k);

### 2023-01-18 src2/exp/test_partial_greedy.cpp
exp 1-19

@@ -51,6 +51,7 @@ int main(int argc,char* argv[]){
         tgcube.selectMaterialize(res);
         tgcube.buildIndex(5);
     }
+    break;
     default:
         break;
     }

### 2023-01-19 src2/TempGCube.hpp
exp 1-19

@@ -859,7 +859,7 @@ void TempGCube::buildIndex(int indexType){
             graphList[i].buildPreArray();
         }
     }else if(indexType==5){
-        for(int i=0;i<graphList.size();++i){//暂时跳过base view
+        for(int i=1;i<graphList.size();++i){//暂时跳过base view
             graphList[i].treeRoot=graphList[i].buildSegmentTree(graphList[i].base+1,graphList[i].base+graphList[i].end);
         }
     }
@@ -1306,6 +1306,7 @@ int TempGCube::query(int indexType,int timel,int timer,int type,bool returnAns,v
         ans.snapshotVec.push_back(SnapShot());
         SnapShot& ansSnapShot=ans.snapshotVec[0];
 
+        if(graphid==0) indexType=0;
         queryWithTarget(targetGraph,ansSnapShot,returnAns,indexType,timel,timer,type);
         return graphid;
     }else{
@@ -1354,7 +1355,7 @@ int TempGCube::query(int indexType,int timel,int timer,int type,bool returnAns,v
 
         TempGraph& materializedSon=graphList[materializeId];
         SnapShot biggerAns;
-
+        if(materializeId==0) indexType=0;
         //ave 需要特别处理
         if(type==2) queryWithTarget(materializedSon,biggerAns,returnAns,indexType,timel,timer,1);
         else queryWithTarget(materializedSon,biggerAns,returnAns,indexType,timel,timer,type);

### 2023-01-19 src2/exp/test_partial_greedy.cpp

@@ -41,6 +41,12 @@ int main(int argc,char* argv[]){
     case 1:
     {
         vector<vector<int>> res=tgcube.partialGreedyOld(k);
+        for(int i=0;i<res.size();++i){
+            for(int j=0;j<res[i].size();++j){
+                cout<<res[i][j]<<" ";
+            }
+            cout<<endl;
+        }
         tgcube.selectMaterialize(res);
         tgcube.buildIndex(5);
     }
@@ -48,6 +54,12 @@ int main(int argc,char* argv[]){
     case 2:
     {
         vector<vector<int>> res=tgcube.partialGreedyNew(k);
+        for(int i=0;i<res.size();++i){
+            for(int j=0;j<res[i].size();++j){
+                cout<<res[i][j]<<" ";
+            }
+            cout<<endl;
+        }
         tgcube.selectMaterialize(res);
         tgcube.buildIndex(5);
     }

### 2023-01-19 src2/exp/test_partial_greedy.cpp
exp 1-19

@@ -109,15 +109,16 @@ int main(int argc,char* argv[]){
     }
 
     //批量查询
-    start=clock();
+    timeval starttime,endtime;
+    gettimeofday(&starttime,NULL);
     for(int i=0;i<allSegs.size();++i){
         for(int j=0;j<allIntParam[i][3];++j){
             TempGraph ans;
             int res=tgcube.query(5,allIntParam[i][0],allIntParam[i][1],allIntParam[i][2],false,allSegs[i],greedyType,ans);
         }
     }
-    end=clock();
-    cerr<<"time: "<<(end-start)*1000.0/CLOCKS_PER_SEC<<endl;
+    gettimeofday(&endtime,NULL);
+    cout<<"time: "<<(endtime.tv_sec-starttime.tv_sec)*1000+(endtime.tv_usec-starttime.tv_usec)/1000<<endl;
 
     return 0;
 }

### 2023-01-19 src2/TempGCube.hpp
exp 1-20

@@ -1587,7 +1587,7 @@ vector<vector<int>> TempGCube::partialGreedyNew(int k){
     vector<vector<int> > cuboidList;
 
     ifstream fin;
-    fin.open("partial_greedy_size_desize_imdb.config");
+    fin.open("../partial_greedy_size_desize_imdb.config");
     if(fin.is_open()==false){
         cerr<<"read err"<<endl;
         return vector<vector<int>>();
@@ -1759,7 +1759,7 @@ vector<vector<int>> TempGCube::partialGreedyOld(int k){
     vector<vector<int> > cuboidList;
 
     ifstream fin;
-    fin.open("partial_greedy_size_desize_imdb.config");
+    fin.open("../partial_greedy_size_desize_imdb.config");
     if(fin.is_open()==false){
         cerr<<"read err"<<endl;
         return vector<vector<int>>();
@@ -1793,7 +1793,7 @@ vector<vector<int>> TempGCube::partialGreedyOld(int k){
     unordered_set<vector<int>,hashVectorInt> S;
     S.insert(sourcePos);
 
-    k--;
+    // k--;
     while(k--){
         unordered_map<vector<int>,ll,hashVectorInt> benefit;
         for(int i=0;i<cuboidList.size();++i){
@@ -1862,7 +1862,7 @@ void TempGCube::partialMaterialize(int k){
     int sum=0;
     int attriNum=graphList[0].vertexTabl.attriNum;
     int lastLayer,cNum=0;
-    if(k>=((1<<attriNum)-1)) k=((1<<attriNum)-1)-1;//最后一层不用了
+    if(k>=((1<<attriNum)-1)) k=((1<<attriNum)-1)-1;//最后一层不用了//有问题，但达不到
     for(lastLayer=1;lastLayer<=attriNum&&sum<k;++lastLayer){
         cNum=cNumber(attriNum,lastLayer);
         sum+=cNum;

### 2023-01-20 src2/TempGCube.hpp
exp 1-20

@@ -301,7 +301,7 @@ public:
     void fullMaterialize();
     void createWithSimilarity(int theModel,int similarity);
     void selectMaterialize(vector<vector<int> >& mList);
-    void partialMaterialize(int k);//k 是实例化的cuboid个数
+    void partialMaterialize(int k,int startlayer);//k 是实例化的cuboid个数
     vector<vector<int>> partialGreedyOld(int k);
     vector<vector<int>> partialGreedyNew(int k);
     void recordMaterialize();
@@ -1858,12 +1858,16 @@ vector<vector<int>> TempGCube::partialGreedyOld(int k){
 
 }
 
-void TempGCube::partialMaterialize(int k){
+void TempGCube::partialMaterialize(int k,int startlayer){
     int sum=0;
     int attriNum=graphList[0].vertexTabl.attriNum;
     int lastLayer,cNum=0;
-    if(k>=((1<<attriNum)-1)) k=((1<<attriNum)-1)-1;//最后一层不用了//有问题，但达不到
-    for(lastLayer=1;lastLayer<=attriNum&&sum<k;++lastLayer){
+    int prenum=0;
+    for(int i=1;i<startlayer;++i){
+        prenum+=cNumber(attriNum,i);
+    }
+    if(k>((1<<attriNum)-1-prenum)) k=((1<<attriNum)-1)-prenum;
+    for(lastLayer=startlayer;lastLayer<=attriNum&&sum<k;++lastLayer){
         cNum=cNumber(attriNum,lastLayer);
         sum+=cNum;
     }
@@ -1874,7 +1878,7 @@ void TempGCube::partialMaterialize(int k){
     vector<pair<int,int> > cubeVertexList;
     cubeVertexList.push_back(pair<int,int>(graphList[0].size,0));
 
-    for(int i=lastLayer;i>=1;--i){
+    for(int i=lastLayer;i>=startlayer;--i){
         vector<vector<int> > singleLans;
         getSameLayerCubeVertex(attriNum,i,singleLans);
         if(i==lastLayer){

### 2023-01-20 src2/exp/generate_input.py

@@ -69,10 +69,11 @@ segslist=["1878 1880",
 "1948 2028",
 "1963 2028"]
 
-fout=open("test_greedy_input.config","w")
+fout=open("test_greedy_input_short_fair.config","w")
 repeatseglist=[]
-for i in range(6,0,-1):
-    repeat=8-i
+for i in range(3,0,-1):
+    # repeat=8-i
+    repeat=1
     temprepeatlist=[]
     for segs in segslist:
         for j in range(repeat):

### 2023-01-20 src2/exp/test_partial_greedy.cpp

@@ -4,12 +4,13 @@ vector<int> TempGCube::logTable=vector<int>();
 
 
 int main(int argc,char* argv[]){
-    if(argc!=5){
+    if(argc!=6){
         cout<<"parameter error"<<endl;
         return 1;
     }
     int start,end;
     int k=atoi(argv[3]);
+    int startlayer=atoi(argv[4]);
 
     TempGCube tgcube;
     // start=clock();
@@ -29,12 +30,18 @@ int main(int argc,char* argv[]){
     // cerr<<"start time: "<<tgcube.graphList[0].base+1<<" end: "<<tgcube.graphList[0].end+tgcube.graphList[0].base<<endl;
     // cerr<<"vertex num: "<<tgcube.graphList[0].vertexTabl.dataList.size()<<" edge num: "<<tgcube.graphList[0].size<<endl;
 
-    int greedyType=atoi(argv[4]);
+    int greedyType=atoi(argv[5]);
     switch (greedyType)
     {
     case 0:
     {
-        tgcube.partialMaterialize(k);
+        tgcube.partialMaterialize(k,startlayer);
+        for(int i=1;i<tgcube.graphList.size();++i){
+            for(int j=0;j<tgcube.graphList[i].vertexTabl.attriPosInOri.size();++j){
+                cout<<tgcube.graphList[i].vertexTabl.attriPosInOri[j]<<" ";
+            }
+            cout<<endl;
+        }
         tgcube.buildIndex(5);
     }
     break;

### 2023-01-20 TemporalGraphCube/TemporalGraphCube_revision.tex
response 1-10
response 1-20

@@
 	Let $\Gr=(\Vr, \Er, A, W)$ be an undirected temporal multidimensional network where $\Vr$ and $\Er$ are the set of nodes and edges respectively.
-Edges in $\Er$ are in the form of $(u, v, t, a)$, where $u$, $v$ are nodes in $\Vr$ and $t, a$ are timestamp and numeric attribute respectively attached to edges.
+Edges in $\Er$ are in the form of $(u, v, t, a)$.
+\revision{$ u $ and $ v $ are nodes in $\Vr$.
+$ t $ and $ a $ are timestamp and numeric attribute respectively attached to edges}.
 $A=\{A_1, A_2, ...
-, A_n\}$ represents the dimensions of the network, or $n$ discrete attributes of nodes in $ \Vr $, i.e., $A(u)=\{A_1(u), A_2(u), ...
+, A_n\}$ represents the dimensions of the network or $n$ discrete attributes of nodes in $ \Vr $, i.e., $A(u)=\{A_1(u), A_2(u), ...
 , A_n(u)\}$ where $A_i(u)$ is the actual value of $u$ on the $i$-th attribute.
@@
 The weight of $v'$, $W_{\Gr'}(v')$, is the aggregation result of $W(v)$ for $v \in [v']$ obtained by aggregation function upon vertices specified by user.
+		\item \revision{Let $ [v] $ be an equivalence class of $ v $, where $ v \in \Vr $ and $[v]=\{u|B(u)=B(v),u \in \Vr\}$.
+For each $ v\in \Vr $, $ \exists v' \in \Vr'$ satisfying $v' \in [v]$ and $\nexists u' \in \Vr', u' \neq v'$ satisfying $u' \in [v]$}
 %		\item For any $S'_i$ in $\Sr'$ and each $(u',v',a')$ in $S'_i$, there exists a nonempty maximum edge set $E=\{(u,v,a)|(u,v,a) \in S_i, u \in [u'] \wedge v \in [v']\; or\; u \in [v'] \wedge v \in [u']\}$, $a'$ is the aggregation result of numeric attributes ($a$) of edges in $E$ obtained by aggregation function specified by user.

### 2023-01-20 src2/exp/test_partial_greedy.cpp
exp 1-20

@@ -12,6 +12,8 @@ int main(int argc,char* argv[]){
     int k=atoi(argv[3]);
     int startlayer=atoi(argv[4]);
 
+    cout<<argv[3]<<" "<<argv[4]<<" "<<argv[5]<<endl;
+
     TempGCube tgcube;
     // start=clock();
     tgcube.init(argv[1],argv[2]);

### 2023-01-20 src2/TempGCube.hpp
exp 1-20

@@ -304,6 +304,7 @@ public:
     void partialMaterialize(int k,int startlayer);//k 是实例化的cuboid个数
     vector<vector<int>> partialGreedyOld(int k);
     vector<vector<int>> partialGreedyNew(int k);
+    vector<vector<int>> partialRandom(int k);
     void recordMaterialize();
     bool isAncestor(vector<int>& attriPosList,int possibleSon);
     void buildGraphByExist(vector<int>& attriPosList,int existSon);
@@ -1681,6 +1682,54 @@ vector<vector<int>> TempGCube::partialGreedyNew(int k){
         it++;
     }
     
+    return ans;
+}
+
+vector<vector<int>> TempGCube::partialRandom(int k){
+    vector<vector<int> > cuboidList;
+
+    ifstream fin;
+    fin.open("../partial_greedy_size_desize_imdb.config");
+    if(fin.is_open()==false){
+        cerr<<"read err"<<endl;
+        return vector<vector<int>>();
+    }
+
+    string dataline1;
+    string dataline2;
+    while(!fin.eof()){
+        getline(fin,dataline1);
+        dataline1.erase(dataline1.size()-1);
+        stringstream ss1(dataline1);
+        getline(fin,dataline2);
+        stringstream ss2(dataline2);
+
+        vector<int> attriPos;
+        ll size,deSize;
+
+        while(!ss1.eof()){
+            int val;
+            ss1>>val;
+            attriPos.push_back(val);
+        }
+        ss2>>size>>deSize;
+        cuboidSize[attriPos]=size;
+        cuboidDeSize[attriPos]=deSize;
+        cuboidList.push_back(attriPos);
+        
+    }
+
+    unordered_set<int> visit;
+    vector<vector<int>> ans;
+    for(int i=0;i<k;++i){
+        int pos=rand()%cuboidList.size();
+        if(visit.find(pos)!=visit.end()||cuboidList[pos][0]==-1){
+            i--;
+            continue;
+        }
+        visit.insert(pos);
+        ans.push_back(cuboidList[pos]);
+    }
     return ans;
 }
 

### 2023-01-20 src2/exp/test_partial_greedy.cpp

@@ -73,6 +73,19 @@ int main(int argc,char* argv[]){
         tgcube.buildIndex(5);
     }
     break;
+    case 3:
+    {
+        vector<vector<int>> res=tgcube.partialRandom(k);
+        for(int i=0;i<res.size();++i){
+            for(int j=0;j<res[i].size();++j){
+                cout<<res[i][j]<<" ";
+            }
+            cout<<endl;
+        }
+        tgcube.selectMaterialize(res);
+        tgcube.buildIndex(5);
+    }
+    break;
     default:
         break;
     }

### 2023-01-22 src2/TempGCube.hpp
exp1-23

@@ -1331,28 +1331,37 @@ int TempGCube::query(int indexType,int timel,int timer,int type,bool returnAns,v
         }
         int materializeId=0;
         int materializeValue;
-        if(greedyType!=0){
-            if(greedyType==1){
-                materializeValue=graphList[0].size;
-            }else if(greedyType==2){
-                materializeValue=cuboidDeSize[{-1,0,1,2,3,4,5}];
-            }
-            for(int i=1;i<graphList.size();++i){
-                if(cuboidIsAncestor(attriPosInOri,graphList[i].vertexTabl.attriPosInOri)){
-                    int thisvalue=0;
-                    if(greedyType==1){
-                        thisvalue=cuboidSize[graphList[i].vertexTabl.attriPosInOri];
-                    }else if(greedyType==2){
-                        thisvalue=cuboidDeSize[graphList[i].vertexTabl.attriPosInOri];
-                    }
+        if(greedyType=1){
+            materializeValue=graphList[0].size;
+        }else if(greedyType==2){
+            materializeValue=cuboidDeSize[{-1,0,1,2,3,4,5}];
+        }else{
+            materializeValue=1;
+        }
+        for(int i=1;i<graphList.size();++i){
+            if(cuboidIsAncestor(attriPosInOri,graphList[i].vertexTabl.attriPosInOri)){
+                int thisvalue=0;
+                if(greedyType==1){
+                    thisvalue=cuboidSize[graphList[i].vertexTabl.attriPosInOri];
+                }else if(greedyType==2){
+                    thisvalue=cuboidDeSize[graphList[i].vertexTabl.attriPosInOri];
+                }
 
-                    if(thisvalue<materializeValue){
-                        materializeValue=thisvalue;
-                        materializeId=i;
-                    }
+                if(thisvalue<materializeValue){
+                    materializeValue=thisvalue;
+                    materializeId=i;
                 }
             }
         }
+
+        #ifdef show_chose
+        if(materializeId==0){
+            for(int i=0;i<attriPosInOri.size();++i){
+                cout<<attriPosInOri[i]<<" ";
+            }
+            cout<<endl;
+        }
+        #endif
 
         TempGraph& materializedSon=graphList[materializeId];
         SnapShot biggerAns;

### 2023-01-22 src2/exp/test_partial_greedy.cpp

@@ -1,3 +1,4 @@
+#define show_chose
 #include"../TempGCube.hpp"
 
 vector<int> TempGCube::logTable=vector<int>();

### 2023-01-23 TemporalGraphCube/TemporalGraphCube_revision.tex
exp1-23
exp 1-23

@@
 	\label{def:temp_aggregate_network}
-	Given a temporal multidimensional network $\Gr=(\Vr,\Sr,A,W)$ and an aggregation $A'=(A'_1,A'_2,...,A'_n)$ where $A'_i$ equals $A_i$ or $\ast$, the obtained temporal aggregate network is another temporal multidimensional network $\Gr'=(\Vr',\Sr',B,W_{\Gr'})$ where $B=\{A'_i|A'_i \neq \ast\}$ and
+	Given a temporal multidimensional network $\Gr=(\Vr,\Sr,A,W)$ and an aggregation $A'=(A'_1,A'_2,...,A'_n)$ where $A'_i$ equals $A_i$ or $\ast$, the obtained temporal aggregate network is another temporal multidimensional network $\Gr'=(\Vr',\Sr',B,W_{\Gr'})$ where $\Vr' \subseteq \Vr$, $B=\{A'_i|A'_i \neq \ast\}$ and
 	\begin{enumerate}
-		\item $\Vr' \subseteq \Vr$ and $\forall [v]$, an equivalence class in $\Vr$, where $ v \in \Vr $ and $[v]=\{u|B(u)=B(v),u \in \Vr\}$, $\exists v' \in \Vr'$ satisfying $v' \in [v]$ and $\nexists u' \in \Vr', u' \neq v'$ satisfying $u' \in [v]$.
-The weight of $v'$, $W_{\Gr'}(v')$, is the aggregation result of $W(v)$ for $v \in [v']$ obtained by aggregation function upon vertices specified by user.
 		\item \revision{Let $ [v] $ be an equivalence class of $ v $, where $ v \in \Vr $ and $[v]=\{u|B(u)=B(v),u \in \Vr\}$.
-For each $ v\in \Vr $, $ \exists v' \in \Vr'$ satisfying $v' \in [v]$ and $\nexists u' \in \Vr', u' \neq v'$ satisfying $u' \in [v]$}
+For each $ v\in \Vr $, $ \exists v' \in \Vr'$ satisfying $v' \in [v]$ and $\nexists u' \in \Vr', u' \neq v'$ satisfying $u' \in [v]$.} $W_{\Gr'}(v')$ is the aggregation result of $W(v)$ for $v \in [v']$ obtained by aggregation function upon vertices specified by user.
 %		\item For any $S'_i$ in $\Sr'$ and each $(u',v',a')$ in $S'_i$, there exists a nonempty maximum edge set $E=\{(u,v,a)|(u,v,a) \in S_i, u \in [u'] \wedge v \in [v']\; or\; u \in [v'] \wedge v \in [u']\}$, $a'$ is the aggregation result of numeric attributes ($a$) of edges in $E$ obtained by aggregation function specified by user.

### 2023-01-23 src2/TempGCube.hpp
exp 1-24

@@ -306,6 +306,7 @@ public:
     vector<vector<int>> partialGreedyNew(int k);
     vector<vector<int>> partialRandom(int k);
     void recordMaterialize();
+    void recordMaterialize(int k);
     bool isAncestor(vector<int>& attriPosList,int possibleSon);
     void buildGraphByExist(vector<int>& attriPosList,int existSon);
     bool cmp(int a,int b){
@@ -326,7 +327,7 @@ public:
     //querytype__0:count,1:sum,2:ave,3:max,4:min
     //indexType: 0-base,1-treearr,2-segmenttree
     //return: 0 被实例化，1 未被实例化
-    int query(int indexType,int timel,int timer,int type,bool returnAns,vector<string>& attributes,int greedyType,TempGraph& ans);
+    int query(int indexType,int timel,int timer,int type,bool returnAns,vector<string>& attributes,int greedyType,int k,TempGraph& ans);
     void queryWithTarget(TempGraph& targetGraph,SnapShot& ansSnapShot,bool returnAns,int indexType,int timel,int timer,int type);
     void crossQuery(vector<string>& aAttributes,vector<string>& bAttributes,int indexType,int timel,int timer,int type,CrossBoidRes& ans);
 
@@ -959,6 +960,16 @@ int TempGraph::buildSegmentTree(int timel,int timer){
 }
 
 //记录被materialize的cuboid
+void TempGCube::recordMaterialize(int k){
+    int limit=graphList.size();
+    #ifdef partial14
+    limit=k+1;
+    #endif
+    for(int i=0;i<limit;++i){
+        materialized[graphList[i].vertexTabl.attriVec]=i;
+    }
+}
+
 void TempGCube::recordMaterialize(){
     for(int i=0;i<graphList.size();++i){
         materialized[graphList[i].vertexTabl.attriVec]=i;
@@ -1299,7 +1310,7 @@ void TempGCube::queryWithTarget(TempGraph& targetGraph,SnapShot& ansSnapShot,boo
 }
 
 //ans中的snapshot的边的count若是0
-int TempGCube::query(int indexType,int timel,int timer,int type,bool returnAns,vector<string>& attributes,int greedyType,TempGraph& ans){
+int TempGCube::query(int indexType,int timel,int timer,int type,bool returnAns,vector<string>& attributes,int greedyType,int k,TempGraph& ans){
     if(attributes[0]=="name"||materialized.find(attributes)!=materialized.end()){
         int graphid=0;
[…]

### 2023-01-23 src2/exp/test_partial_greedy.cpp

@@ -1,4 +1,5 @@
-#define show_chose
+// #define show_chose
+#define partial14
 #include"../TempGCube.hpp"
 
 vector<int> TempGCube::logTable=vector<int>();
@@ -38,7 +39,12 @@ int main(int argc,char* argv[]){
     {
     case 0:
     {
+        #ifdef partial14
+        tgcube.partialMaterialize(14,startlayer);
+        #endif
+        #ifndef partial14
         tgcube.partialMaterialize(k,startlayer);
+        #endif
         for(int i=1;i<tgcube.graphList.size();++i){
             for(int j=0;j<tgcube.graphList[i].vertexTabl.attriPosInOri.size();++j){
                 cout<<tgcube.graphList[i].vertexTabl.attriPosInOri[j]<<" ";
@@ -137,7 +143,7 @@ int main(int argc,char* argv[]){
     for(int i=0;i<allSegs.size();++i){
         for(int j=0;j<allIntParam[i][3];++j){
             TempGraph ans;
-            int res=tgcube.query(5,allIntParam[i][0],allIntParam[i][1],allIntParam[i][2],false,allSegs[i],greedyType,ans);
+            int res=tgcube.query(5,allIntParam[i][0],allIntParam[i][1],allIntParam[i][2],false,allSegs[i],greedyType,k,ans);
         }
     }
     gettimeofday(&endtime,NULL);

### 2023-01-24 revision/response.tex
exp 1-24
exp 1-25

@@
 \end{Comments}
-\noindent \textbf{Response:} test
+\noindent \textbf{Response:} [todo].
+The major limitation of static graph cube is that it cannot support temporal multidimensional networks.
+Static graph cube can only be built on static multidimensional networks, e.g., DBLP where temporal information of co-authorships is omitted.
+Consequently, static graph cube cannot support range queries since there is no temporal information in its dataset.
+Static graph cube cannot support latest data because its authors didn't consider that new edges may be added into the static networks.
+Temporal graph cube supports latest data because we update the temporal networks and indexes when new edges are added.
 

### 2023-01-24 src2/TempGCube.hpp

@@ -28,6 +28,10 @@ void split(string victim,vector<string>& holder){
     holder.push_back(string(victim.substr(last,victim.size()-last)));
 }
 
+bool cmpvecint(vector<int>& a,vector<int>& b){
+    return a.size()<b.size();
+}
+
 int lowerbit(int x){
     return x&(-x);
 }
@@ -309,6 +313,7 @@ public:
     void recordMaterialize(int k);
     bool isAncestor(vector<int>& attriPosList,int possibleSon);
     void buildGraphByExist(vector<int>& attriPosList,int existSon);
+    void buildGraphByExist(vector<int>& attriPosList,int existSon,int putpos);
     bool cmp(int a,int b){
         return graphList[a].size>graphList[b].size;
     }
@@ -1527,6 +1532,30 @@ bool TempGCube::isAncestor(vector<int>& attriPosList,int possibleSon){
     return true;
 }
 
+void TempGCube::buildGraphByExist(vector<int>& attriPosList,int existSon,int putpos){
+    // graphList.push_back(TempGraph());
+
+    vector<string>& overallAttriArr=graphList[0].vertexTabl.attriVec;
+
+    TempGraph& son=graphList[existSon];//用于生成当前图的后继
+    vector<int> attriPosInSon;//选中属性在son graph的属性表中的下标列表
+    int last=0;//last<son.vertexTabl.attrinum
+    for(int i=0;i<attriPosList.size();++i){
+        while(last<son.vertexTabl.attriNum){
+            if(son.vertexTabl.attriVec[last]==overallAttriArr[attriPosList[i]]){
+                attriPosInSon.push_back(last);
+                last++;
+                break;
+            }
+            last++;
+        }
+    }
+
+    TempGraph& newGraph=graphList[putpos];
+    newGraph.initFrmTempGraph(son,attriPosInSon,attriPosList);
+    
+}
+
 void TempGCube::buildGraphByExist(vector<int>& attriPosList,int existSon){
     graphList.push_back(TempGraph());
     vector<string>& overallAttriArr=graphList[0].vertexTabl.attriVec;
@@ -1754,6 +1783,9 @@ vector<vector<int>> TempGCube::partialRandom(int k){
         visit.insert(pos);
         ans.push_back(cuboidList[pos]);
     }
+    #ifdef reorder_random
+    sort(ans.begin(),ans.end(),cmpvecint);
+    #endif
     return ans;
 }
 
@@ -1951,6 +1983,11 @@ void TempGCube::partialMaterialize(int k,int startlayer){
[…]

### 2023-01-24 src2/exp/test_partial_greedy.cpp

@@ -1,5 +1,7 @@
 // #define show_chose
-#define partial14
+// #define partial14
+#define reorder_partial
+#define reorder_random
 #include"../TempGCube.hpp"
 
 vector<int> TempGCube::logTable=vector<int>();

### 2023-01-26 TemporalGraphCube/TemporalGraphCube_revision.tex
latex 1-26

@@
 \usepackage{booktabs}
+\usepackage{todonotes}
 
@@
 
-Interestingly, we can avoid the problem of choosing an ideal $ A_i'' $ by adopting the partial materialization strategy \kw{MinLevel} \cite{zhao2011graph}, which we will discuss in Section~\ref{sec:partial_materialization}.
+Interestingly\todo{todo}, we can avoid the problem of choosing an ideal $ A_i'' $ by adopting the partial materialization strategy \kw{MinLevel} \cite{zhao2011graph}, which we will discuss in Section~\ref{sec:partial_materialization}.
 %
@@
 \cite{dehdouh2014columnar} tried to compute data cubes from column-oriented NoSQL data.
-As for graph data, except \cite{zhao2011graph}, some other works focus on heterogeneous networks \cite{yin2012hmgraph,wang2015tsmh}, but none of them focus on temporal multidimensional networks.
+As for graph data, except \cite{zhao2011graph}, some other works focus on heterogeneous networks \cite{yin2012hmgraph,wang2015tsmh}.
+\revision{\cite{wang2014pagrol,chen2020high} improve efficiency of graph OLAP query by parallelization and distribution}.
+However, none of them focus on temporal multidimensional networks.
 
@@
 For static graphs, there are some representative works, including graph compression with MDL (Minimum Description Length) principle \cite{navlakha2008graph}, attributed graph compression \cite{wu2014graph} and graph clustering based on vertices partitioning \cite{zhou2009graph}.
-Recently, there exist several studies on static graph summarization, such as summarizing directed acyclic graph (DAG) \cite{zhu2020top}, summarizing multi-relation graph \cite{ke2022multi} where multiple edges of different types may exist between any pair of vertices, and DPGS model \cite{zhou2021dpgs}, which can preserve properties like graph spectrum and the authorities and hubnesses of vertices especially in highly degree-skewed graphs while reconstructing graph.
+Recently, there exist several studies on static graph summarization, such as summarizing directed acyclic graph (DAG) \cite{zhu2020top}, summarizing multi-relation graph \cite{ke2022multi} where multiple edges of different types may exist between any pair of vertices, and DPGS model \cite{zhou2021dpgs}, which can preserve properties like graph spectrum and the authorities and hubnesses of vertices while reconstructing graph.
+\revision{However, all of them ignore the temporal information of big graph data}.
 For temporal graph and dynamic graph, TimeCrunch \cite{shah2015timecrunch} summarizes a large dynamic graph with a set of important temporal structures using MDL, such as ranged full clique, periodic bipartite core, oneshot star, etc.
-\cite{fernandes2018dynamic,tsalouchidou2018scalable} investigate the problem of summarizing dynamic graph in real time, which use a sliding window of fixed length to summarize the latest snapshots.
-When a new snapshot is generated, the window slides forward, discarding the oldest snapshot in the window and generating a new summary.
+\revision{Some works summary graph streams into one sketche, e.g., \cite{mudannayake2021kmatrix,tang2016graph,ma2021parameter,ashrafi2021gs4,gou2019fast,chen2022scube}.
+\cite{fernandes2018dynamic,tsalouchidou2018scalable} use a sliding window of fixed length to only summarize the latest snapshots, and \cite{ko2020incremental} only summa}.
 However, in this paper, we can specify arbitrary time window to query summarized result in real time.
 In addition, we summarize the graph based on the selected dimensions of vertices, while the previous studies summarize the graph based on the super-node and super-edge.
-MoSSo \cite{ko2020incremental} incrementally summarizes fully dynamic graph.
+MoSSo \cite{} incrementally summarizes fully dynamic graph.
 The difference of \cite{ko2020incremental} with \cite{fernandes2018dynamic,tsalouchidou2018scalable} is that the edges in the graph are dynamically added and removed, and MoSSo incrementally summarizes the whole graph after any modification on the graph.

### 2023-01-26 TemporalGraphCube/TemporalGraphCube_revision.tex
response 1-27

@@
 Data warehouse built on traditional relational database (RDB) data is called data cube \cite{gray1997data}.
-In 2011, Zhao et al.\ \cite{zhao2011graph} proposed \kw{Graph} \kw{Cube} which extends data warehouses and OLAP techniques to analyze static multidimensional networks.
+In 2011, Zhao et al.
+\cite{zhao2011graph} proposed \kw{Graph} \kw{Cube} which extends data warehouses and OLAP techniques to analyze static multidimensional networks.
 For each query, static graph cube returns a static network with summarized information in its structure and statistical values on vertices and edges.
@@
 For temporal graph and dynamic graph, TimeCrunch \cite{shah2015timecrunch} summarizes a large dynamic graph with a set of important temporal structures using MDL, such as ranged full clique, periodic bipartite core, oneshot star, etc.
-\revision{Some works summary graph streams into one sketche, e.g., \cite{mudannayake2021kmatrix,tang2016graph,ma2021parameter,ashrafi2021gs4,gou2019fast,chen2022scube}.
-\cite{fernandes2018dynamic,tsalouchidou2018scalable} use a sliding window of fixed length to only summarize the latest snapshots, and \cite{ko2020incremental} only summa}.
+\revision{Some works (\cite{mudannayake2021kmatrix,tang2016graph,ma2021parameter,ashrafi2021gs4,gou2019fast,chen2022scube}) summarize graph stream into one sketche.
+\cite{fernandes2018dynamic,tsalouchidou2018scalable} use a sliding window of fixed length to only summarize the latest snapshots, and \cite{ko2020incremental} only summarize the current snapshot of a graph stream incrementally and losslessly}.
 However, in this paper, we can specify arbitrary time window to query summarized result in real time.
-In addition, we summarize the graph based on the selected dimensions of vertices, while the previous studies summarize the graph based on the super-node and super-edge.
-MoSSo \cite{} incrementally summarizes fully dynamic graph.
-The difference of \cite{ko2020incremental} with \cite{fernandes2018dynamic,tsalouchidou2018scalable} is that the edges in the graph are dynamically added and removed, and MoSSo incrementally summarizes the whole graph after any modification on the graph.
+\revision{Chen et al.
+\cite{chen2022horae} also studies summarizing snapshots in arbitrary time window, but they ignored the attributes of vertices and different views determined by combinations of those attributes}.
+We summarize graphs based on selected attributes of vertices, \revision{so we can get summarized information between vertices in different resolutions.}
 

### 2023-01-27 TemporalGraphCube/TemporalGraphCube_revision.tex
response 1-28

@@
 If $ l_0>1 $ and $ |dim(A')|<l_0 $, then there may be some precomputed views $ \{A_1'',A_2'',...\} $ where $ |dim(A_i'')|=l_0 $ can be used to process $ Q $.
-In this case, choosing an arbitrary $ A_i'' $ to process $ Q $ is efficient enough because the size of $ A_i'' $ and its index is usually small since $ l_0 $ is a small value.
+In this case, choosing an arbitrary $ A_i'' $ to process $ Q $ is efficient enough because the size of $ A_i'' $ and its index is usually small since $ l_0 $ is a small value.\todo{todo}
 
@@
 In this section, we evaluate the effectiveness of temporal graph cube as a decision-support tool on \kw{DBLP}.
-First, we conduct a series of temporal cuboid queries $ Q_1=((\kw{Area}),[2001,2006]) $, $ Q_2=((\kw{Area}),[2006,2011]) $, $ Q_3=((\kw{Area}),[2011,2016]) $, $ Q_4=((\kw{Area}),[2016,2021]) $ on \kw{DBLP}.
+First, \revision{we build temporal graph cube on \kw{DBLP} and} conduct a series of temporal cuboid queries $ Q_1=((\kw{Area}),[2001,2006]) $, $ Q_2=((\kw{Area}),[2006,2011]) $, $ Q_3=((\kw{Area}),[2011,2016]) $, $ Q_4=((\kw{Area}),[2016,2021]) $.
+\revision{We also build static graph cube on \kw{DBLP} and conduct a cuboid query $ Q_{static}=(\kw{Area}) $}.
 Aggregation functions upon vertices and edges are both COUNT($\ast$).
-The network structures of $ Q_1 $-$ Q_4 $ are shown in Fig.~\ref{fig:dblp_area}, illustrating the co-authorship patterns between authors grouped by different areas in the specified time ranges.
-For simplicity, in Fig.~\ref{fig:dblp_area} (a) we omit those co-authorships with COUNT($\ast$) values less than 10,000, which are also omitted in Fig.~\ref{fig:dblp_area} (b)-(d), regardless of their COUNT($\ast$) values.
+The network structures of $ Q_1 $-$ Q_4 $ \revision{and $ Q_{static} $} are shown in Fig.~\ref{fig:dblp_area}, illustrating the co-authorship patterns between authors grouped by different areas.
+For simplicity, in Fig.~\ref{fig:dblp_area} (a) we omit those co-authorships with COUNT($\ast$) values less than $ 10,000 $, which are also omitted in Fig.~\ref{fig:dblp_area} (b)-(e), regardless of their COUNT($\ast$) values.
 
@@
 			\subfigure[{\scriptsize $ Q_1 $}]{
-				\includegraphics[width=0.23\textwidth]{fig/exp/visio_area_2001_2006.pdf}
+				\includegraphics[width=0.19\textwidth]{fig/exp/visio_area_2001_2006.pdf}
 			}
@@
 			\subfigure[{\scriptsize $ Q_2 $}]{
-				\includegraphics[width=0.23\textwidth]{fig/exp/visio_area_2006_2011.pdf}
+				\includegraphics[width=0.19\textwidth]{fig/exp/visio_area_2006_2011.pdf}
 			}
@@
 			\subfigure[{\scriptsize $ Q_3 $}]{
-				\includegraphics[width=0.23\textwidth]{fig/exp/visio_area_2011_2016.pdf}
+				\includegraphics[width=0.19\textwidth]{fig/exp/visio_area_2011_2016.pdf}
 			}
@@
 			\subfigure[{\scriptsize $ Q_4 $}]{
-				\includegraphics[width=0.23\textwidth]{fig/exp/visio_area_2016_2021.pdf}
+				\includegraphics[width=0.19\textwidth]{fig/exp/visio_area_2016_2021.pdf}
+			}
+			\hspace*{-0.3cm}
+			\subfigure[{\scriptsize $ Q_{static} $}]{
+				\includegraphics[width=0.19\textwidth]{fig/exp/visio_area_static.pdf}
 			}
@@
 	\vspace*{-0.4cm}
-	\caption{Network structures in the results of queries $ Q_1-Q_4 $}
+	\caption{Network structures in the results of queries $ Q_1-Q_4 $ \revision{and $ Q_{static} $.
+$ Q_1=((\kw{Area}),[2001,2006]) $, $ Q_2=((\kw{Area}),[2006,2011]) $, $ Q_3=((\kw{Area}),[2011,2016]) $, $ Q_4=((\kw{Area}),[2016,2021]) $ are temporal cuboid queries, $ Q_{static}=(\kw{Area}) $ is a cuboid query in static graph cube}}
 	\vspace*{-0.4cm}
@@
 Some interesting observations can be obtained in these results.
-For example, authors in each area co-author most with authors in the same area even in different time ranges.
-We can clearly see that in recent 20 years, the number of co-authorship between each pair of areas increases over time.
-We can also find that in recent 20 years researchers in \kw{AI} co-authored with researchers in \kw{CG} most.
-This is because there are many problems in computer graphics like automatic modeling, image processing and digital photography which can be solved by AI technologies.
-More interestingly, in $ [2001,2006] $, researchers in \kw{TH} co-authored most with researchers in \kw{CA}, but with the time evolves, researchers in \kw{TH} are more willing to co-author with researchers in \kw{AI}.
+For example, authors in each area co-author most with authors in the same area \revision{all the time ($ Q_{static} $) and} in different time ranges \revision{($ Q_1-Q_4 $)}.
+We can clearly see that in recent 20 years (\revision{$ Q_1-Q_4 $}), the number of co-authorship between each pair of areas increases over time.
+\revision{However, such results can never be found in $ Q_{static} $}.
+\comment{We can also find that in recent 20 years researchers in \kw{AI} co-authored with researchers in \kw{CG} most.
+This is because there are many problems in computer graphics like automatic modeling, image processing and digital photography which can be solved by AI technologies.}More interestingly, in $ [2001,2006] $, researchers in \kw{TH} co-authored most with researchers in \kw{CA}, but with the time evolves, researchers in \kw{TH} are more willing to co-author with researchers in \kw{AI}.
 The reason may be that theoretical research on AI becomes more and more important with the wide applications of AI in recent years.
-%The above findings can also be obtained from uncut results.
+\revision{However, in $ Q_{static} $ we can only know that researchers in \kw{TH} co-authored most with researchers in \kw{AI}, but ignore the trend above.} %The above findings can also be obtained from uncut results.
 %[ns and cn,ca and ai;ai and cg;th and ai,ca]
 
-In each period we can zoom into a more fine-grained view by conducting a drill-down operation.
+In each time range of temporal cuboid queries we can zoom into a more fine-grained view by conducting a drill-down operation.
 For example, for $ Q_4=((\kw{Area}),[2016,2021]) $, drill-down can be a query $ Q_4'=((\kw{Area},\kw{Productivity}),[2016,2021]) $.
@@
 	\begin{center}
-		\includegraphics[width=0.8\columnwidth]{fig/exp/visio_area_pro_2016_2021.pdf}
+		\includegraphics[width=0.7\columnwidth]{fig/exp/visio_area_pro_2016_2021.pdf}
 	\end{center}
@@
 	\vspace*{-0.6cm}
-	\caption{Network structure in the result of $ Q_4' $}
+	\caption{Network structure in the result of $ Q_4'=((\kw{Area},\kw{Productivity}),[2016,2021]) $}
 	\vspace*{-0.4cm}
@@
 			\subfigure[{\scriptsize $ Q_{cross1} $}]{
-				\includegraphics[width=0.25\textwidth]{fig/exp/dblp_cross_name_area_2001_2006.pdf}
+				\includegraphics[width=0.19\textwidth]{fig/exp/dblp_cross_name_area_2001_2006.pdf}
 			}
@@
 			\subfigure[{\scriptsize $ Q_{cross2} $}]{
-				\includegraphics[width=0.25\textwidth]{fig/exp/dblp_cross_name_area_2006_2011.pdf}
+				\includegraphics[width=0.19\textwidth]{fig/exp/dblp_cross_name_area_2006_2011.pdf}
 			}
@@
 			\subfigure[{\scriptsize $ Q_{cross3} $}]{
-				\includegraphics[width=0.25\textwidth]{fig/exp/dblp_cross_name_area_2011_2016.pdf}
+				\includegraphics[width=0.19\textwidth]{fig/exp/dblp_cross_name_area_2011_2016.pdf}
 			}
@@
 			\subfigure[{\scriptsize $ Q_{cross4} $}]{
-				\includegraphics[width=0.25\textwidth]{fig/exp/dblp_cross_name_area_2016_2021.pdf}
+				\includegraphics[width=0.19\textwidth]{fig/exp/dblp_cross_name_area_2016_2021.pdf}
+			}
+			\hspace*{-0.3cm}
+			\subfigure[{\scriptsize $ Q_{cross-static} $}]{
+				\includegraphics[width=0.19\textwidth]{fig/exp/dblp_cross_name_area_static.pdf}
 			}
@@
 	\vspace*{-0.4cm}
-	\caption{Network structures in the results of $ Q_{cross1}-Q_{cross4} $}
+	\caption{Network structures in the results of $ Q_{cross1}-Q_{cross4} $ \revision{and $ Q_{cross-static} $}.
+\revision{$ Q_{cross1}=((\kw{Name}),(\kw{Area}),[2001,2006]) $, $ Q_{cross2}=((\kw{Name}),(\kw{Area}),[2006,2011]) $, $ Q_{cross3}=((\kw{Name}),(\kw{Area}),[2011,2016]) $, $ Q_{cross4}=((\kw{Name}),(\kw{Area}),[2016,2021]) $ are temporal crossboid queries, $ Q_{cross-static}=((\kw{Name}),(\kw{Area})) $ is a static crossboid query in static graph cube}}
 	\vspace*{-0.4cm}
@@
 \begin{center}
-	$ Q_{cross1}=((\kw{Name}),(\kw{Area}),[2001,2006]) $,\\$ Q_{cross2}=((\kw{Name}),(\kw{Area}),[2006,2011]) $,\\$ Q_{cross3}=((\kw{Name}),(\kw{Area}),[2011,2016]) $,\\$ Q_{cross4}=((\kw{Name}),(\kw{Area}),[2016,2021]) $.
+	$ Q_{cross1}=((\kw{Name}),(\kw{Area}),[2001,2006]) $,\\$ Q_{cross2}=((\kw{Name}),(\kw{Area}),[2006,2011]) $,\\$ Q_{cross3}=((\kw{Name}),(\kw{Area}),[2011,2016]) $,\\$ Q_{cross4}=((\kw{Name}),(\kw{Area}),[2016,2021]) $,
 \end{center}
-The above queries focus on the cross interaction between \kw{Name} and \kw{Area}, i.e., the co-authorship with each area for each researcher.
+\revision{and a static crossboid query $ Q_{cross-static}=((\kw{Name}),(\kw{Area})) $.} Above queries focus on the cross interaction between \kw{Name} and \kw{Area}, i.e., the co-authorship with each area for each researcher.
 We further slice-and-dice the results on \kw{Name} to show the results related to ``Jiawei Han".
-We can find that in recent 20 years, Jiawei cooperated with researchers in \kw{DB} most.
+We can find that in all the queries, Jiawei cooperated with researchers in \kw{DB} most.
 Meanwhile, in recent 10 years he has more and more cooperations with researchers in \kw{AI}, which can be ignored compared to cooperations with researchers in \kw{DB} in early 10 years.
+\revision{However, in static crossboid query $ Q_{cross-static} $ (Figure~\ref{fig:dblp_cross} (e)) we can only find that Jiawei cooperated with researchers in \kw{DB} most, but we ignore that the number of co-authorships between them is decreasing while Jiawei co-authored with researchers in \kw{AI} more and more frequently.}
 

### 2023-01-27 src2/TempGCube.hpp

@@ -1318,7 +1318,12 @@ void TempGCube::queryWithTarget(TempGraph& targetGraph,SnapShot& ansSnapShot,boo
 int TempGCube::query(int indexType,int timel,int timer,int type,bool returnAns,vector<string>& attributes,int greedyType,int k,TempGraph& ans){
     if(attributes[0]=="name"||materialized.find(attributes)!=materialized.end()){
         int graphid=0;
+        #ifndef crossboid
         if(attributes[0]!="name") graphid=materialized[attributes];
+        #endif
+        #ifdef crossboid
+        graphid=materialized[attributes];
+        #endif
         TempGraph& targetGraph=graphList[graphid];
         ans.snapshotVec.push_back(SnapShot());
         SnapShot& ansSnapShot=ans.snapshotVec[0];
@@ -1446,60 +1451,60 @@ int TempGCube::query(int indexType,int timel,int timer,int type,bool returnAns,v
 void TempGCube::crossQuery(vector<string>& aAttributes,vector<string>& bAttributes,int indexType,int timel,int timer,int type,CrossBoidRes& ans){
     //暂时全注释
     // //获得ncd
-    // vector<string>& totalAttributes=graphList[0].vertexTabl.attriVec;
-    // vector<string> ncdAttributes;
-    // vector<int> aAttriPos,bAttriPos;
-    // int aIndex=0;int bIndex=0;
+    vector<string>& totalAttributes=graphList[0].vertexTabl.attriVec;
+    vector<string> ncdAttributes;
+    vector<int> aAttriPos,bAttriPos;
+    int aIndex=0;int bIndex=0;
     
-    // for(int i=0;i<totalAttributes.size();++i){
-    //     bool yes=false;
-    //     if(aIndex<aAttributes.size()&&totalAttributes[i]==aAttributes[aIndex]){
-    //         yes=true;aIndex++;
-    //         aAttriPos.push_back(ncdAttributes.size());
-    //     }
-    //     if(bIndex<bAttributes.size()&&totalAttributes[i]==bAttributes[bIndex]){
-    //         yes=true;bIndex++;
-    //         bAttriPos.push_back(ncdAttributes.size());
-    //     }
+    for(int i=0;i<totalAttributes.size();++i){
+        bool yes=false;
[…]

### 2023-01-27 src2/exp_dblp/exp.cpp

@@ -1,6 +1,154 @@
+#define crossboid
 #include"../TempGCube.hpp"
 
 vector<int> TempGCube::logTable=vector<int>();
+
+bool vertexEqual(const vector<string>& a,const vector<string>& b){
+    if(a.size()!=b.size()) return false;
+    for(int i=0;i<a.size();++i){
+        if(a[i]!=b[i]) return false;
+    }
+    return true;
+}
+
+bool vertexLess(const vector<string>& a,const vector<string>& b){
+    int minLen=min(a.size(),b.size());
+    for(int i=0;i<minLen;++i){
+        if(a[i]==b[i]) continue;
+        if(a[i]<b[i]) return true;
+        else return false;
+    }
+    return a.size()<b.size();
+}
+
+struct snap_res{
+    pair<int,int> idPair;
+    Edge e;
+    snap_res(pair<int,int> _pair,Edge& _e){
+        idPair=_pair;
+        e=_e;
+    }
+
+    bool operator <(const snap_res& b)const{
+        if(idPair.first==b.idPair.first){
+            return idPair.second<b.idPair.second;
+        }
+        return idPair.first<b.idPair.first;
+    }
+};
+
+struct snap_res_str{
+    pair<vector<string>,vector<string> > vertexPair;
+    Edge e;
+    snap_res_str(pair<vector<string>,vector<string> > _pair,Edge& _e){
+        vertexPair=_pair;
+        e=_e;
+    }
+
+    bool operator <(const snap_res_str& b)const{
+        if(vertexEqual(vertexPair.first,b.vertexPair.first)){
+            return vertexLess(vertexPair.second,b.vertexPair.second);
+        }
+        return vertexLess(vertexPair.first,b.vertexPair.first);
+    }
+};
+
+void print_materialize_ans_snapshot(TempGraph& tgraph,SnapShot& ans,int type){
+    vector<snap_res> reorganize_ans;
+    for(int i=0;i<ans.edgePool.size();++i){
+        if(ans.edgePool[i].count==0) continue;
+        if(ans.idPairVec[i].first<ans.idPairVec[i].second){
+            reorganize_ans.push_back(snap_res(ans.idPairVec[i],ans.edgePool[i]));
+        }else{
+            reorganize_ans.push_back(snap_res(pair<int,int>(ans.idPairVec[i].second,ans.idPairVec[i].first),ans.edgePool[i]));
+        }
+    }
[…]

### 2023-01-28 TemporalGraphCube/TemporalGraphCube_revision.tex
response 1-29

@@
 
-Interestingly\todo{todo}, we can avoid the problem of choosing an ideal $ A_i'' $ by adopting the partial materialization strategy \kw{MinLevel} \cite{zhao2011graph}, which we will discuss in Section~\ref{sec:partial_materialization}.
+As a result, in this paper we choose an arbitrary $ A_i'' $ with least $ |dim(A_i'')| $ in those precomputed views.
 %
@@
 If all the views with $ l_0 $ dimensions have been selected and the number of selected views or the total size needed for precomputing the selected views has not reach the limit, then we continue to select views with $ l_0+1 $ dimensions until we select enough number or size of views.
-In this paper, we select $ k $ views to be precomputed and $ l_0=1 $.
-
-Using \kw{MinLevel}, we precompute views with small number of dimensions; and these views also have high similarity of snapshots in their snapshot arrays (as shown in Table~\ref{tab:materialized_view}).
+In this paper, we select $ k $ views to be precomputed and $k$ is also an empirical value.
+
+\comment{Using \kw{MinLevel}, we precompute views with small number of dimensions; and these views also have high similarity of snapshots in their snapshot arrays (as shown in Table~\ref{tab:materialized_view}).
 In processing temporal cuboid query $ Q=(A',[l,r]) $, if $ A' $ is not precomputed and $ l_0=1 $, only $ A_{base} $ can be used to process the query $ Q $.
 If $ l_0>1 $ and $ |dim(A')|<l_0 $, then there may be some precomputed views $ \{A_1'',A_2'',...\} $ where $ |dim(A_i'')|=l_0 $ can be used to process $ Q $.
-In this case, choosing an arbitrary $ A_i'' $ to process $ Q $ is efficient enough because the size of $ A_i'' $ and its index is usually small since $ l_0 $ is a small value.\todo{todo}
+In this case, choosing an arbitrary $ A_i'' $ to process $ Q $ is efficient enough because the size of $ A_i'' $ and its index is usually small since $ l_0 $ is a small value.}
 
@@
 \stitle{Exp-1: Performance of the index-based method.} Here we aim to evaluate how much the index-based solution can accelerate the merging operation of snapshots in time ranges while processing temporal cuboid queries, compared to the baseline algorithm (Algorithm~\ref{alg:temp_cuboid_baseline}).
+\revision{We will also compare other types of indexes with STree used in this paper later, such as prefix array and sparse table}.
 As we analyzed before, the average acceleration ratio of the index-based solution can vary if the similarity of snapshots in temp-multi-networks changes.
@@
 These results indicate that when $s$ is very small, there is no need to build an index.
+
+\begin{table}[t!]%\vspace*{-0.3cm}
+	\scriptsize
+	%\small
+	\centering
+	\caption{\revision{Performance of prefix array and sparse table}} \vspace*{-0.2cm} \label{tab:effi_other_index}
+	\begin{tabular}{c c c c c c}
+		\toprule
+		\makecell[c]{View\\No.}& $ s $ &\makecell[c]{acce-ratio\\preArr} &\makecell[c]{Space ratio\\preArr}&\makecell[c]{acce-ratio\\STable}&\makecell[c]{Space ratio\\STable}\cr %\hline %\hline
+		\midrule
+		1&53.48&5.37 & 1.51 &12.92 &9.38 \cr
+		\midrule
+		2&18.16&3.20 & 2.58 &7.87 &14.45 \cr
+		\midrule
+		3&6.15 &1.76 & 5.76 &5.15 &26.78 \cr
+		\midrule
+		4&6.07 &1.74 & 5.84 &5.15 &27.04 \cr
+		\midrule
+		5&4.70 &1.56 & 7.14 &4.84 &31.74 \cr
+		\midrule
+		6&3.97 &1.45 & 8.33 &4.58 &35.85 \cr
+		\midrule
+		7&1.12 &0.85 &27.38 &OM & OM \cr
+		\bottomrule
+	\end{tabular}
+	\vspace*{-0.4cm}
+\end{table}
+\revision{We also implement prefix array (preArr, only supports $ f_e= $ SUM($\ast$)) and sparse table (STable, only supports $ f_e= $ MAX($\ast$) or MIN($\ast$)) to conduct the same queries as a comparison.
+The results are shown in Table~\ref{tab:effi_other_index}.
+We can see that the acceleration ratio of prefix array is close to our solution (STree) but with more space consumption in most cases.
+The performance of prefix array is also influenced by similarity of snapshots, as we analyzed in Section~\ref{sec:effec_of_indexes}.
+The acceleration ratio of sparse table is much higher than that of prefix array and STree, but consumes much more space.
+Building sparse table even leads to an out-of-memory on the No.
+7 view.
+Similarly, the performance of sparse table is also influenced by similarity of snapshots.
+Overall, our index-based method, STree, is the best in these three method considering both acceleration ratio and space consumption ratio.}
 
@@
 			\subfigure[{\scriptsize Time consumption}]{
-				\includegraphics[width=0.23\textwidth]{fig/exp/index_update/index_update_single_c.pdf}
+				\includegraphics[width=0.24\textwidth]{fig/exp/index_update/index_update_single_c.pdf}
 			}
@@
 	\caption{The updating performance of the index-based solution}
-	\vspace*{-0.4cm}
+	\vspace*{-0.1cm}
 	\label{fig:index_update}
 \end{figure}
+
+\begin{figure}
+	\begin{center}
+		\includegraphics[width=0.9\columnwidth]{fig/exp/minlevel/minlevel.pdf}
+	\end{center}
+	\vspace*{-0.6cm}
+	\caption{\revision{Performance of strategies in partial materialization. $ k $ is the number of views to be materialized}}
+	\vspace*{-0.4cm}
+	\label{fig:minlevel}
+\end{figure}
+\noindent\revision{\stitle{Exp-3: Performance of \kw{MinLevel} in partial materialization.} In this experiment we also use \kw{IMDB}.
+The greedy strategy introduced in Section~\ref{sec:partial_materialization} is not suitable for partial materialization in temporal graph cube due to the uncertain time range specified in queries, which we have analyzed in Section~\ref{sec:partial_materialization}.
+Instead, we choose a random strategy, i.e., selecting $ k $ views to be materialized randomly, as a comparison to \kw{MinLevel}.
+We use total response time of 40 temporal cuboid queries to evaluate the performance.
+In these queries, the number of queries in the format of $ ((A_1,...,A_{x}),[l,r]) $ is almost twice as many as the number of queries in the format of $ ((A_1,...,A_{x+1}),[l,r]) $, because users are more willing to query with less dimensions.
+The results are shown in Figure~\ref{fig:minlevel}.
+We can see that as $ k $ increases, all of the 4 strategies achieve better performance because more views are materialized.
+With proper setting of $ l_0 $, e.g., $ l_0=4 $, \kw{MinLevel} achieves the best performance since most of the queries specified by users have no more dimensions than $ 4 $, and these queries are more possible to be accelerated compared to the case when \kw{Random} strategy is used.}
 
@@
 \revision{Chen et al.
-\cite{chen2022horae} also studies summarizing snapshots in arbitrary time window, but they ignored the attributes of vertices and different views determined by combinations of those attributes}.
+\cite{chen2022horae} also study summarizing snapshots in arbitrary time window, but they ignored the attributes of vertices and different views determined by combinations of those attributes}.
 We summarize graphs based on selected attributes of vertices, \revision{so we can get summarized information between vertices in different resolutions.}
@@
 We conduct extensive experiments on two large real-world datasets, and the results demonstrate the effectiveness and efficiency of the proposed solutions.
+\revision{Besides, there are other types of temporal networks which are not discussed in our work, for example, temporal networks where edges have both start and end timestamps.
+It is difficult to assign realistic meaning to some possible positional relationships between the interval of a temporal edge and interval specified in a query.
+Data warehouse and OLAP technology based on these special datasets are waiting for further discussion.}
 

### 2023-01-28 TemporalGraphCube/fig/exp/minlevel/draw_col.py

@@ -1,0 +1,136 @@
+import matplotlib.pyplot as plt
+import math
+
+# name = ['graph size', 'kClist', 'PIVOTER','PEANUTS',  'DPColor', 'DPColorPath']
+# name = ['MPC', 'MPC+', 'MQPC','MQPC+']
+# name=['MQPCO-B','MQPCO-B+','MQPCO-E','MQPCO-E+']
+name=['Random','MinLevel-$l_0=2$','MinLevel-$l_0=3$','MinLevel-$l_0=4$']
+# col = ['magenta', "#5e3448",'black','blue','#20457c','coral']
+# col = ['#003399', '#701112','#037365', '#0aa0d9','#e63f0a', '#bea32e']
+col = ['#003399', '#0aa0d9','#e63f0a', '#bea32e']
+# col = ['lightcoral', 'lightsteelblue', 'magenta', 'g', ]
+# lj = [277.449512+16.146156, 2706.948,    1584.688, 6511916.0/1024,1605.584, 1606.284,]
+# ber = [ 53.195760 +2.740924, 261.908,  294.568, 1234896.0/1024,299.068,301.136]        
+
+# 4 4 5 clique
+# dblp=[11480,12408,8353,9096]
+# imdb=[65559,68550,77359,81911]
+# hospital=[1170,717,87,48]
+# lkml=[1500000+200000,1500000+200000,127435,113122]
+# enron=[930145,1052619,24648,24480]
+
+# 4 6 5 clique
+# dblp=[7721,7783,6147,6335]
+# imdb=[47552,46134,43822,44998]
+# hospital=[40,61,27,40]
+# lkml=[1000000+100000,1000000+100000,84629,71328]
+# enron=[814691,592926,11005,9172]
+
+# 4 6 5 core
+# dblp=[7950,7981,6680,6853]
+# imdb=[47420,45003,64455,65602]
+# hospital=[41,63,28,42]
+# lkml=[1000000+100000,1000000+100000,54025,41272]
+# enron=[761204,566714,16101,13488]
+
+data=[
+    [591150,611916,600403,378592],
+    [587477,589516,557325,330050],
+    [596565,586713,523027,326943],
+    [445001,585203,439161,190269],
+    [393173,568459,394048,189310]
+]
+
+
+# dName = ['web-BerkStan','com-LiveJournal']
+dName = ['k=6','k=8','k=10','k=12','k=14']
[…]

### 2023-01-28 TemporalGraphCube/fig/exp/minlevel/draw_col_template.py

@@ -1,0 +1,131 @@
+import matplotlib.pyplot as plt
+import math
+
+# name = ['graph size', 'kClist', 'PIVOTER','PEANUTS',  'DPColor', 'DPColorPath']
+# name = ['MPC', 'MPC+', 'MQPC','MQPC+']
+# name=['MQPCO-B','MQPCO-B+','MQPCO-E','MQPCO-E+']
+name=['MQPCL-B','MQPCL-B+','MQPCL-E','MQPCL-E+']
+# col = ['magenta', "#5e3448",'black','blue','#20457c','coral']
+# col = ['#003399', '#701112','#037365', '#0aa0d9','#e63f0a', '#bea32e']
+col = ['#003399', '#0aa0d9','#e63f0a', '#bea32e']
+# col = ['lightcoral', 'lightsteelblue', 'magenta', 'g', ]
+# lj = [277.449512+16.146156, 2706.948,    1584.688, 6511916.0/1024,1605.584, 1606.284,]
+# ber = [ 53.195760 +2.740924, 261.908,  294.568, 1234896.0/1024,299.068,301.136]        
+
+# 4 4 5 clique
+# dblp=[11480,12408,8353,9096]
+# imdb=[65559,68550,77359,81911]
+# hospital=[1170,717,87,48]
+# lkml=[1500000+200000,1500000+200000,127435,113122]
+# enron=[930145,1052619,24648,24480]
+
+# 4 6 5 clique
+dblp=[7721,7783,6147,6335]
+imdb=[47552,46134,43822,44998]
+hospital=[40,61,27,40]
+lkml=[1000000+100000,1000000+100000,84629,71328]
+enron=[814691,592926,11005,9172]
+
+# 4 6 5 core
+# dblp=[7950,7981,6680,6853]
+# imdb=[47420,45003,64455,65602]
+# hospital=[41,63,28,42]
+# lkml=[1000000+100000,1000000+100000,54025,41272]
+# enron=[761204,566714,16101,13488]
+
+
+
+
+data = [dblp, imdb,hospital,lkml,enron]
+# dName = ['web-BerkStan','com-LiveJournal']
+dName = ['DBLP','IMDB','Hospital','LKML','Enron']
+patterns = ['.', 'x', '\\', '//']#, 'O', '.']
+fz = 23
+
+plt.rcParams['pdf.fonttype'] = 42
+plt.rcParams['ps.fonttype'] = 42
[…]

### 2023-01-29 revision/response.tex
latex 1-26
response 1-30

@@
 Static graph cube cannot support latest data because its authors didn't consider that new edges may be added into the static networks.
-Temporal graph cube supports latest data because we update the temporal networks and indexes when new edges are added.
+Temporal graph cube supports latest data because we will update the temporal networks and indexes when new edges are added.
 
@@
 \end{Comments}
-\noindent \textbf{Response:} test
+\noindent \textbf{Response:} Following your advice, we have added experiments of existing methods in Section 7.2 and Exp-1 of Section 7.3 to evaluate the effectiveness and efficiency of our model.
+First, in Section 7.2 we add experimental results of queries in static graph cube.
+By comparing the query results we show that queries in temporal graph cube can reveal hidden information which may be ignored using queries in static graph cube.
+Second, at the end of Exp-1 of Section 7.3 we implement two other kinds of indexes, prefix array and sparse table, to accelerate range queries of temporal graph cube.
+These two indexes both can achieve $ O(1) $ time complexity in conducting range queries on normal numeric arrays.
+However, in the case of snapshot arrays, only sparse table achieves higher acceleration ratio, but with unacceptable space consumption ratio (sometimes out of memory).
+Overall, segment-tree based method in manuscript is the most suitable method to accelerate range queries in temporal graph cube.
 
@@
 \end{Comments}
-\noindent \textbf{Response:} test
+\noindent \textbf{Response:} Thanks for pointing out this problem.
+We have reviewed more works mainly related to graph OLAP and graph stream summarization in Section 8 of the revised version, and we have added discussion about limitations of all the mentioned existing works.
 
@@
 \end{Comments}
-\noindent \textbf{Response:} test
+\noindent \textbf{Response:} It is reasonable for a temporal edge to have only one timestamp, because in many cases, durations or end time of temporal edges are meaningless.
+For example, DBLP only records date of publication of research papers.
+For a research paper, the end time of publication or existence is meaningless.
+We just need to focus on the fact that at a certain time, some researchers have published a certain paper.
+Given a time range $ [t_1,t_2] $, it's easy to determine whether a research paper is published in $ [t_1,t_2] $.
+It's the same with movies in IMDB.
+Another example is email communication network, which is also temporal network.
+Temporal edges in email communication network contain only timestamp of sending the email, and there is no need to store timestamp of finishing sending the email or timestamp of deleting the email.
+We just need to focus on the fact that there was an email exchange between certain people at a certain time, or we can consider this as an instant activity.
+
+The temporal edges you mentioned do exist in temporal networks, such as phone calls network, since each phone call lasts for a while. However,
 
@@
 
-\section{Response to Reviewer \#2.1}
-\setcounter{Comments}{0}
-\begin{Comments}
-As mentioned in related works, some existing works study the dense subgraphs, quasi-cliques in temporal graphs.
-Can they be used in finding the communities in temporal graphs?
-Some discussion can be given in the introduction.
-\end{Comments}
-\noindent \textbf{Response: }
-The existing algorithm for mining quasi-cliques can not be applied in temporal graphs.
-We can design novel algorithms for mining quasi-cliques in temporal networks.
-However, since the problem of mining quasi-cliques is NP-hard in static networks, the problem of mining quasi-cliques in temporal networks may be NP-hard, too.
-
-In this manuscript, we focus on the density-based clustering algorithm for temporal graphs, so our definition is relative to the algorithm of SCAN.
-The proposed TSCAN algorithm only needs polynomial-time to get the answer and it runs quickly in practice.
-
-We have added some additional discussion in the introduction to describe them as above.
-
-\begin{Comments}
-It should be better to give a comparison between the result of proposed method and the ground truth if there are available datasets.
-Some potential competitors can be discussed in the paper.
-\end{Comments}
-\noindent \textbf{Response: } The available datasets do not have communities of ground truth in the temporal situation, so it is hard to compare  between the result of proposed method and the ground truth.
-We have tested 4 evaluation metrics in exp-1, exp-2 and exp-3 which can demonstrate the effectiveness of our proposed algorithms (see Fig.8-11).
-We also update new case studies which are much more interpretable to show the results of TSCAN (see Fig.13 in the revised version).
-
-\begin{Comments}
-The formulated model contains many parameters. Several attempts may required to get an optimal setting. 
-\end{Comments}
-\noindent \textbf{Response: } Thank you for your insightful comments.
-In exp-3 we have done effectiveness testing with varying the parameters $\mu$, $\tau$ and $\epsilon$.
-In the revised version, we have added more analyses of seeking better parameters settings (see exp-4 in section 4.1).
-
-\section{Response to Reviewer \#2.2}
-\setcounter{Comments}{0}
-\begin{Comments}
-1)The article is very hard to read.
-I’m familiar with dynamic networks and community detection, but it took me 3 hours to understand really what the authors propose, not talking about fully understanding all the optimization strategies.
-
-2) I think that some ideas and concepts are not clear for the authors themselves, or that they should better position their work relatively to the state of the art.
-
-\end{Comments}
-\noindent \textbf{Response: } Following your suggestion, we have re-positioned some definitions and examples, so it is easier to be understood.
-
-\begin{Comments}
-	The authors do not seem to provide any implementation of their method.
-Reproducibility is now recognized a very important question in science, and, I think that in 2019, it is not possible any more to propose a complex algorithm that cannot be reproduced in a couple of hours without providing a complete code that the reviewers can test.
-\end{Comments}
-\noindent \textbf{Response: } Thanks to your insightful comments. Following your suggestion, we have uploaded the codes on Github (\url{https://github.com/VeryLargeGraph/TSCAN}).
-
-%\begin{Comments}
-%The principle of the method should be the most important thing to consider in the paper.
-I do not think it makes sense to 1) propose a new approach and 2) propose a complex method to optimize it, in the same paper.
-We should first be convinced that the method is interesting before taking care of making it scalable.
-To convince the reader that the method is interesting, it should 1)be presented clearly, 2) be tested on tasks, and compared to related algorithms.
-%\end{Comments}
-%\noindent \textbf{Response: } Thanks to your insightful comments. Let me introduce our work.
-%
-%Our goal is to identify the communities in a temporal network that are stable over time. 
-%Note that, the traditional existing community detection algorithms focus mainly on traditional graphs, thus they also cannot be directly used for detecting stable communities in temporal graphs.
-%To efficiently find the stable communities, we develop a new community detection algorithm based on the density-based graph clustering framework.
-We also propose several carefully-designed pruning techniques to significantly speed up the proposed algorithm.
-
-\begin{Comments}
-Many choices seem arbitrary, or not well supported by the practice, which might be due to a lack of knowledge of the literature. For instance:
-
--the authors describe their method as a method for link streams, but it seems that the first step of their algorithm requires to build snapshots.
-There their method is a snapshot based method.
-Starting from a link stream makes no difference, any snapshot algorithm could require to first build snapshot of the desired duration.
-
--The authors talk about dynamic networks, but in fact it seems that the order of snapshots makes no difference, so they could work with any multislice/multiplex network.
-
-\end{Comments}
-\noindent \textbf{Response: } Thank you for your helpful comments.
-I think that building snapshots make it better to describe the model and the problem definitions.
-In reality, we do not need to build snapshots in the progress of the algorithms.
-We only need to fetch the neighbors and the attached temporal information of each node (see Algorithm 1-3).
-Also, some existing researches [1][2] for community detection or subgraph discovery in temporal networks all build snapshots for considering the common properties of some clusters.
-
-[1] Shuai Ma, Renjun Hu, Luoshu Wang, Xuelian Lin, and Jinpeng Huai. Fast Computation of Dense Temporal Subgraphs. ICDE 2017.
-
-[2] Ashwin Paranjape, Austin R. Benson, Jure Leskovec. Motifs in Temporal Networks. WSDM 2017.
-
-It is right that the order of snapshots makes no difference, so our algorithms can also work with the multislice/multiplex networks.
-However, the researches about mining stable communities in multislice/multiplex networks are also elusive now.
-%In practice, temporal networks are special cases of multislice/multiplex networks as shown in ref.[3][4].
-
-%[3]
-
-%[4]
-
-\begin{Comments}
-	The authors decide to use the structural similarity (without never explaining why), but the rest of the method and optimization could in fact work with any similarity measure, right ?
-\end{Comments}
-\noindent \textbf{Response: } Yes, it is.
-We use Eq.(1) to define the structural similarity because it measures the number of common neighbor of $u$ and $v$ (normalization by the product of number of their neighbors), same as SCAN proposed by Xu in KDD07.
-
-The computation of the structural similarity is expensive in practice, because we need to compute the set-intersection of neighbors of the considering two nodes.
-Besides, other similar definitions for the structural similarity all need the item of the set-intersection of neighbors of the considering two nodes, too.
-So, different definitions for the structural similarity make little difference to the acceleration ratio of the proposed optimized algorithms.
-
-\begin{Comments}	
-	The authors define 4 metrics to evaluate their results, but they are poorly explained, as I understand them, they are not dynamic, since they are simply defined on the multigraph of the cumulated graph.
-If that is well the case, why not compare the results with any community detection algorithm run on this network ?
-\end{Comments}
-\noindent \textbf{Response: } The proposed 4 metrics are motivated by separability, density, cohesiveness and clustering coefficient which are used to evaluate the communities in the static graphs, proposed by Yang in ICDM2012.
-We modified them a little so the temporal edges can be counted and they can be used to evaluate the communities in temporal graphs.
-As we all know, the community detection algorithm in static graph can not be used directly in the temporal networks, or the multigraphs either.
-Since our work mainly focus on the density-based graph clustering, we have compared our proposed TSCAN with the modified traditional density-based graph clustering algorithm PSCAN-W (see section 4, Fig.7-10).
-
-Following your suggestions, we have given clear intuitions about the four evaluation metrics of the communities in the temporal graphs (see Table.4).
-
-\begin{Comments}	
-	why talk about snapshot and de-temporal graphs? I could not see a difference between the two in the text.
-\end{Comments}
-\noindent \textbf{Response: } %The $i$-th snapshot of $\mathcal G$ is a temporal subgraph ${\mathcal G}_i=(\mathcal{V}, \mathcal{E}_i)$ in which $\mathcal{E}_i$ be a set of edges that are extracted from $\mathcal E$ in the time interval $(t_i-\theta, t_i]$.
-%For a temporal graph $\mathcal G$, its \emph{de-temporal} graph is referred to as $G=(V, E)$ by ignoring all the timestamps associated with the temporal edges. 
-Snapshot ${\mathcal G}_i$ is a temporal graph that contains all the edges in time interval $(t_i-\theta, t_i]$.
-\emph{De-temporal} graph $G$ of $\mathcal{G}$ is a simple graph that contains all the edges in time interval $(t_0, t_{\mathcal{T}}]$, in which same edge with different time will be existing only once.
-
-Snapshot is a temporal graph and \emph{de-temporal} graph is a static graph.
-$G$ is a simple summarization of temporal graph $\mathcal G$. 
-Also, $G_i$  is the \emph{de-temporal} graph of snapshot $\mathcal G_i$.
-Obviously, $G = \bigcup_{t_0}^{t_{\mathcal{T}} }G_i$.
-
-\begin{Comments}
-Another point that the author should keep in mind is to try to keep their work concise when possible. Maybe some parts of it could go into an annex, so that the core of the paper becomes readable
-\end{Comments}
-\noindent \textbf{Response: }We have combined some parts together and re-positioned some algorithms and examples, so it is easier to be understood.
-
-\begin{Comments}
-
-To finish, I think that the authors have not made great effort to compare their work (qualitatively or quantitatively) with the state of the art.
-They start from the premises that they" are the first to study the problem of mining stable communities in temporal graphs”.
-But in this paper, if I understand correctly, stable communities means that nodes cannot change communities which is rather a limit than a strength in general, since networks can change completely in different times, and giving them a unique affiliation is often misleading.
-But this is a point of view, stable communities can very well be useful in some contexts, however, some methods to study them already exist, such as Matias et al.
-2016 (Statistical clustering of temporal networks through a dynamic stochastic block model), Gauvin et al.
-2014 (Detecting the Community Structure and Activity Patterns of Temporal Networks: A Non-Negative Tensor Factorization Approach), Aynaud et al.
-2011 (Multi-Step Community Detection and Hierarchical Time Segmentation in Evolving Networks), etc.
-Even without comparing to those methods, one could at least compare to a simple clustering of the “de-temporal” weighted graph.
-\end{Comments}
-\noindent \textbf{Response: } In our works, we mainly focus on detecting stable communities by density-based clustering.
-I have downloaded the mentioned references and they study different models of communities in the temporal graph, so our proposed algorithms are hard to compare with them.
-
-In our experiments, we have treated PSCAN-W as a baseline of a simple clustering of the weighted de-temporal graph (Figs.8-10).
-We transform the temporal graph into a weighted de-temporal graph (weight of each edge is the number of temporal edges in the temporal graph), and then PSCAN-W invokes the density-based graph clustering algorithm (SCAN) in the weighted de-temporal graph.
-
-\begin{Comments}
-
-some English mistakes.
-P1:in the face-to-face contact network
-In the collaboration network, each edge represents two authors, u and v, coauthored a paper at time t.
--to identify a densely-connected community structure that are stable over time
--Similarity, most other existing community detection algorithms
-
-some remarks.
-P3:
--its de-temporal graph: de-temporal is not a usual name for this classic process, and you do not precise if the network is a multigraph (as it should be according to your description) or not.
--bad reference, [18] is not using sliding windows
-
-\end{Comments}
-\noindent \textbf{Response: } Following your suggestion, we fixed those typos and re-check the manuscript again and again to reduce the typos as much as possible.
-
-\begin{Comments}
-	the concepts in the density-based graph clustering framework (SCAN): it would have been important to explain what is this algorithm, why is it interesting, what is density exact, etc.
-beforehand.
-(Dates from 2007!)
-	Is the approach comparable with Falkowski et al: Studying Community Dynamics with an Incremental Graph Mining Algorithm.
-
-\end{Comments}
-\noindent \textbf{Response: } Thanks to your careful comments.
-Our work is not comparable with the work proposed by Falkowski.
-Most previous community detection studies on dynamic graphs aim to maintain communities that evolve over time.
-Unlike this goal, our work mainly focuses on detecting stable communities in the temporal network based on density-based clustering methods.
-There are a huge number of papers on community detection in dynamic (temporal) graphs, due to the space limit, in our initial submission, we have to ignore some of those references, and focus on surveying the references on "stable community detection" and "structural graph clustering" (SCAN).
-
-%Following your suggestion, we have explained more about the structural graph clustering algorithm (SCAN) so it is better to be understood.
-
-\begin{Comments}
-
-	P10: Case-study: not interpretable by reader, could you find a real-life network to illustrate ?
-\end{Comments}
-\noindent \textbf{Response: } Following your suggestion, we have updated the case studies and introduced more backgrounds, so they are much more interpretable in the revised version.
-
-\section{Response to Reviewer \#3 }
-\setcounter{Comments}{0}
-\begin{Comments}
-Definition 5 for stable communities is problematic.
-Consider a (3, 3, 0.6)-stable cores $c_1$.
-Suppose nodes $v_1$, $v_2$ and $v_3$ are simultaneously similar to $c_1$ in snapshots $t_1$, $t_2$, and $t_3$ and nodes $v_4$, $v_5$ and $v_6$ are simultaneously similar to $c_1$ in snapshots $t_4$, $t_5$, and $t_6$.
-This may be the case that professor $c_1$ moves to another place and has a new group of coauthors.
-According to Def.
-5, all nodes will be assigned to the same stable cluster.
-However, ($v_1$, $v_2$, $v_3$) and ($v_4$, $v_5$, $v_6$) should not be in the same stable community.
-
-\end{Comments}
-\noindent \textbf{Response: } Thanks to your insightful comments.
-In our manuscript, definition 5 for stable communities is a relaxed version so it might have the problem as you described.
-However, if we change the definition to distinguish those nodes which are clustered in different time, we will perform several more frequent pattern minings (each one need $O(C_{\mathcal{T}}^\tau)$ time) and get much more overlap clusters.
-Those will result in much additional computation time and new problem of choosing the overlap clusters.
-So, we choose this relaxed definition, results of four evaluation metrics and case studies confirm the effectiveness of our model.
-
-\begin{Comments}
-The selection of parameters $\mu$, $\tau$, and $\epsilon$ needs a further discussion: how do they influence the results and how to set them in practice.
-\end{Comments}
-\noindent \textbf{Response: } Thank you for your insightful comments.
-In exp-3 we have done effectiveness testings with varying the parameters $\mu$, $\tau$ and $\epsilon$.
-In the revised version, we have added more analyses of seeking better parameters settings (see exp-4 in section 4.1).
-
-\begin{Comments}
-	The experiments are weak, especially no formal baselines are included.
-\end{Comments}
-\noindent \textbf{Response: } Since our work mainly focuses on the density-based graph clustering, we have compared our proposed TSCAN with the modified traditional density-based graph clustering algorithm PSCAN-W (see section 4, Fig.7-10).
-We treat PSCAN-W as a baseline and it can be found that PSCAN-W performs worse than our proposed algorithm TSCAN in the effectiveness testings.
-Also, the case studies demonstrate the results of PSCAN-W and TSCAN.
-It can be seen that our proposed model TSCAN is much better than the baseline PSCAN-W.
-
-\begin{Comments}
- Para 2, Introduction states "Most existing community ...
-do not consider the temporal information of the links", how about those community detection algorithms on temporal networks, e.g.
-ref.
-[35], [36].
-\end{Comments}
-\noindent \textbf{Response: } Thank you very much for pointing out the negligence.
-We want to say that most traditional existing community detection do not consider the temporal information of the links.
-However, the problem of mining community in temporal graphs are studied in recent years.
-
-Following your suggestions, we have changed the expressions in the introduction.
-
-\begin{Comments}
-The notations in the preliminaries are heavy, which makes the section a little bit hard to follow. Consider including a table to summarize these notations.
-\end{Comments}
-\noindent \textbf{Response: } Following your suggestion, we have added Table.1 to summaries the notations.
-
-\begin{Comments}
-$\mathcal{T}$ is used as both the number of timestamps (line 6, page 2) and the number of snapshots (line 59, page 2).
-Indeed, the transformation from timestamps to snapshots is not clear.
-How to select $t_i$ and can time intervals $(t_i-\theta, t_i]$ overlap?
-\end{Comments}
-\noindent \textbf{Response: } Thank you very much for pointing out the negligence.
-In our experiments, we choose $t_i$  to be an arithmetic progression so each $t_i$ could represent different month/year.
-For a given time interval $\theta$, a snapshot is a temporal subgraph generated in a $\theta$-length sliding window.
-%In the experiments, we set $\theta$ to a default value of 1 month/year which means that every snapshot contains all the temporal edges in a one month/year length sliding window.
-If $\theta=1$, $(t_i-\theta, t_i]$ would not overlap. Else if If $\theta>1$, $(t_i-\theta, t_i]$ would overlap.
-
-As shown in Fig.12 of the last version, we evaluate our algorithms for other window sizes on DBLP.
-Since the results are similar to the case of $\theta=1$, we do the following experiments with $\theta$ setting to 1 month/year.
-
-In the revised version, to avoid misunderstanding, we removed all the parameter $\theta$ so $(t_i-\theta, t_i]$ will be the time interval.
-
-\begin{Comments}
-The statement "Since only one edge is different for any two consecutive snapshots" (line 49, page 4) is not straightforward.
-How about the case in Fig.2 that multiple edges are associated with the same timestamps.
-As a result, the incremental maintenance in line 19 of Algorithm 1 is also not clear.
-\end{Comments}
-\noindent \textbf{Response: } Thanks to your careful comments.
-Due to the limitation of space, we omit some descriptions.
-Clearly, $|N_i(u)|$ and $|N_i(v)|$ are easy to get and they can be stored as constants in the structure of the temporal network(similar to adjacency list in the static graph).
-In the revised version, we use $hashset$ to compute the $|N_i(u) \cap N_i(v)|$ so it only needs time of $O(m)$.
-
-\begin{Comments}
- typos
-
-a) line 11 page 1: stable community $-->$ stable communities
-
-b) line 40, page 1: Similarity $-->$ Similarly
-
-c) line 44, page 1: that are stable over $-->$ that is stable over
-
-d) line 18, page 2: get exact stable core $-->$ cores
-
-e) line 25, page 3: $(\mu, \tau, \epsilon)$-stable u $-->$ $(\mu, \tau, \epsilon)$-stable core u
-
-f) equation in line 51, page 8: $(u, v)\in \mathcal{E}$ $-->$ $(u, v, t)\in \mathcal{E}$
-
-g) line 46, page 8: StrongCore $-->$ StableCore
-
-\end{Comments}
-\noindent \textbf{Response: } Following your suggestion, we have fixed the typos in this revision.
-
-\section{Response to Reviewer \#4 }
-\setcounter{Comments}{0}
-\begin{Comments}
-The authors frequently misuse the sentence "statistically significant" and "significantly outperforms" while comparing the results of their algorithm with its competitors.
-No statistical tests were performed (I strongly suggest to apply something like a Bonferroni-Dunn test for statistical significance).
-
-\end{Comments}
-\noindent \textbf{Response: } Thanks to your insightful comments.
-We have added Bonferroni-Dunn test for effectiveness testing of the compared algorithms in the revised version (see Table.5 in exp-2 of section 4.1).
-
-\begin{Comments}
-The authors do not provide public links to their method (and competitors) implementation.
-To enhance reproducibility - and to support open science - all the code must be packaged and released at submission time.
-Nowadays, I feel this aspect must represent a mandatory step to allow publication of any paper that introduces a new algorithm/analysis.
-\end{Comments}
-\noindent \textbf{Response: } Thanks to your insightful comments. Following your suggestion, we have uploaded the codes on Github (\url{https://github.com/VeryLargeGraph/TSCAN}).
-
-\begin{Comments}
-Competitor analysis.
-I understand the controlled testing against variations of the proposed algorithm, however, I think that external evaluation against alternative solutions could represent a plus to support this work.
-Among your reference - in [33] - is introduced a family of approaches called "Cross-Time Community Discovery" whose aim seems - to some extent - similar to the one of this study (i.e., identify stable communities over time).
-Is it possible to identify some algorithms having such rationale (even pursuing it in a different manner w.r.t.
-the proposed algorithm) to propose an actual comparison and discuss the different contexts of applicability?
-\end{Comments}
-\noindent \textbf{Response: } In our works, we mainly focus on detecting stable communities by density-based clustering.
-The works in the references mainly study different models of communities in the temporal graph.
-For example, in "Community Discovery in Dynamic Networks: a Survey", the "Cross-Time Community Discovery" study four situations of fixed/evolving memberships, fixed/evolving properties.
-As our work is based on none-attributed graph, we may compare with the works of evolving memberships, fixed properties.
-But the existed works are not focusing on stable communities, and the models are not density-based.
-So, our proposed algorithms are hard to compare with them.
-
-In our experiments, we propose PSCAN-W as a baseline algorithm.
-The PSCAN-W algorithm invokes the density-based graph clustering algorithm (SCAN) in the transformed weighted de-temporal graph.
-Our proposed model TSCAN is tested to have much better effectiveness then PSCAN-W (see Figs.8-10), and a little slower than PSCAN-W (see Figs.14).
-So, our proposed model can enhance SCAN into the temporal graphs to find stable communities.
-However, some other graph clustering/communities discovery models can motivated by us to be transformed into a stable one in temporal graph.
-But they may cause large increase of computing time.
-
 \end{document}

### 2023-01-30 revision/response.tex
response 1-31

@@
 
-\item test
+\item As suggested, we have added experiments of existing methods in Section 7.2 and Exp-1 of Section 7.3 to evaluate the effectiveness and efficiency of our model.
+\item We have added experiments related to partial materialization strategy in Exp-3 of Section 7.3.
+\item We have reviewed more related works and added discussion about limitations of all the mentioned existing works in Section 8.
+\item We have added brief discussion about applicability and limitation of our work in Section 9.
 
@@
 \end{Comments}
-\noindent \textbf{Response:} [todo].
-The major limitation of static graph cube is that it cannot support temporal multidimensional networks.
-Static graph cube can only be built on static multidimensional networks, e.g., DBLP where temporal information of co-authorships is omitted.
+\noindent \textbf{Response:} The major limitation of static graph cube is that it cannot support temporal multidimensional networks.
+Static graph cube can only be built on static multidimensional networks, e.g., DBLP without temporal information of co-authorships.
 Consequently, static graph cube cannot support range queries since there is no temporal information in its dataset.
@@
 \end{Comments}
-\noindent \textbf{Response:} test
+\noindent \textbf{Response:} Following your advice, we have tried to update some definitions by replacing sentences separated by punctuation with relatively complete sentences.
 
@@
 In detail, both theoretically and experimentally we find that larger similarity of snapshots in a materialized view leads to higher acceleration ratio and lower space consumption ratio of the index.
-If the value of similarity of snapshots in a view is as low as $ 1 $, then there is no need to build index for the view and the baseline method to conduct queries is the best method, as we analyzed in Section 5.
+If the value of similarity of snapshots in a view is as low as $ 1 $, then there is no need to build index for the view and the baseline method is the best method, as we analyzed in Section 5.
 %Acceleration ratio in Definition 7 and space consumption ratio in Definition 9 theoretically measure the query efficiency and space cost of the index respectively based on the edges' number.
@@
 We just need to focus on the fact that at a certain time, some researchers have published a certain paper.
-Given a time range $ [t_1,t_2] $, it's easy to determine whether a research paper is published in $ [t_1,t_2] $.
+Given a time range $ [t_1,t_2] $, we only need to determine whether a research paper is published in $ [t_1,t_2] $.
 It's the same with movies in IMDB.
@@
 
-The temporal edges you mentioned do exist in temporal networks, such as phone calls network, since each phone call lasts for a while. However,
+Besides our work, almost all related works reviewed in the revised version define temporal edges with only one timestamp.
+The temporal edges you mentioned do exist in some temporal networks, such as phone calls network, since each phone call lasts for a while.
+However, it is difficult to assign realistic meaning to some possible positional relationships between the interval of a temporal edge and interval specified in a query if aggregation function on edges $ f_e $ is COUNT($\ast$) (or SUM($\ast$), MAX($\ast$), MIN($\ast$)).
+Suppose $ (u,v,t_s,t_e) $ be a phone call between $ u,v $ which starts at $ t_s $ and ends at $ t_e $.
+Given a query $ [t_1,t_2] $ satisfying $ t_1<t_s<t_2<t_e $, it is hard to tell what the aggregation result of $ (u,v) $ is if $ f_e $ is COUNT($\ast$), not to mention that there may be numeric attribute in temporal edges and $ f_e $ is SUM($\ast$) (or other aggregation functions).
+There may be a reasonable scenario that $ f_e $ is Duration($\ast$), i.e., asking for the total time of connections between two vertices or two groups of vertices.
+But it's insufficient to only support Duration($\ast$).
+
+Overall, datasets containing temporal edges with single timestamp are common in our research field.
+The motivation of temporal graph cube based on temporal networks containing temporal edges with time range should be further discussed, which should be included in a new work.
+We have added brief discussion about applicability and limitation of our work in Section 9 of the revised version.
 
@@
 \end{Comments}
-\noindent \textbf{Response:} test
+\noindent \textbf{Response:} Thanks for your advice.
+As we have responsed in D1, the motivation of temporal graph cube based on temporal networks containing temporal edges with time range should be further discussed and it is better to be included in future new works.
 
@@
 \end{Comments}
-\noindent \textbf{Response:} test
+\noindent \textbf{Response:} Thanks for reminding us. We have added relevant experiments in Exp-3 of Section 7.3.
 
@@
 \end{Comments}
-\noindent \textbf{Response:} test
+\noindent \textbf{Response:} Thanks for your advice. We have added experiments in both Section 7.2 and Exp-1 of Section 7.3. Please refer to the response to comment 4 of reviewer \#1 for more details.
 

### 2023-01-30 TemporalGraphCube/TemporalGraphCube_revision.tex
response 1-30
response 1-31

@@
 %		\item For any $S'_i$ in $\Sr'$ and each $(u',v',a')$ in $S'_i$, there exists a nonempty maximum edge set $E=\{(u,v,a)|(u,v,a) \in S_i, u \in [u'] \wedge v \in [v']\; or\; u \in [v'] \wedge v \in [u']\}$, $a'$ is the aggregation result of numeric attributes ($a$) of edges in $E$ obtained by aggregation function specified by user.
-		\item $\forall u',v' \in \Vr'$ where $u' \leq v'$ and any $\Sr[i], i \in [1,t_{end}]$, if there exists a nonempty maximum edge set $E=\{(u,v,a)|(u,v,a) \in \Sr[i],(u \in [u'] \wedge v \in [v']) \vee (u \in [v'] \wedge v \in [u']) \}$, then $ \exists (u',v',a') \in \Sr'[i] $, where $a'$ is the aggregation result of numeric attributes of edges in $E$ obtained by aggregation function upon edges specified by user.
+		\item $\forall u',v' \in \Vr'$ where $u' \leq v'$ and \revision{any $\Sr[i]$ for $ i \in [1,t_{end}]$}, if there exists a nonempty maximum edge set $E=\{(u,v,a)|(u,v,a) \in \Sr[i],(u \in [u'] \wedge v \in [v']) \vee (u \in [v'] \wedge v \in [u']) \}$, then $ \exists (u',v',a') \in \Sr'[i] $ where $a'$ is the aggregation result of numeric attributes of edges in $E$ obtained by aggregation function upon edges specified by user.
 	\end{enumerate}
@@
 	\label{def:sum_snap}
-	Given a temporal multidimensional network $\Gr=(\Vr,\Sr,A,W)$, the summarized snapshot $ S $ of $ \Gr $ is a special snapshot of $ \Gr $, which is the network structure in the result of a temporal cuboid query $ Q=(A,[1+t_{base},t_{end}+t_{base}]) $ on $ \Gr $.
+	Given a temporal multidimensional network $\Gr=(\Vr,\Sr,A,W)$, the summarized snapshot $ S $ of $ \Gr $ is a special snapshot of $ \Gr $ \revision{and it is the network structure in the result of a temporal cuboid query $ Q=(A,[1+t_{base},t_{end}+t_{base}]) $ on $ \Gr $}.
 \end{definition}
@@
 	\label{def:ncd}
-	Given two different views $ A_1' $ and $ A_2' $, the common descendant of $ A_1' $ and $ A_2' $, $ cd(A_1',A_2') $ is also a view in temporal graph cube, satisfying $ dim(A_1') \cup dim(A_2') \subseteq dim(cd(A_1',A_2')) $.
-The nearest common descendant of $ A_1' $ and $ A_2' $, $ ncd(A_1',A_2') $, is one of the common descendants satisfying $ dim(ncd(A_1',A_2'))=dim(A_1') \cup dim(A_2') $.
+	Given two different views $ A_1' $ and $ A_2' $, \revision{$ cd(A_1',A_2') $ is common descendant of $ A_1' $ and $ A_2' $ and it is also a view in temporal graph cube satisfying $ dim(A_1') \cup dim(A_2') \subseteq dim(cd(A_1',A_2')) $.
+$ ncd(A_1',A_2') $ is the nearest common descendant of $ A_1' $ and $ A_2' $ and it is one of the common descendants satisfying $ dim(ncd(A_1',A_2'))=dim(A_1') \cup dim(A_2') $.}
 \end{definition}
@@
 	\label{def:similarity_snapshots}
-	Given a snapshot array $ snapArr $ starting from $ 1 $ and containing $ n $ snapshots, the summarized snapshot $ S $ of all snapshots in $ snapArr $, $ E=\sum_{i=1}^{n}|snapArr[i]| $, the similarity of snapshots in $ snapArr $ is $ s=\frac{E}{|S|} $.
+	Given a snapshot array $ snapArr $ starting from $ 1 $ and containing $ n $ snapshots.
+\revision{Suppose the summarized snapshot of all snapshots in $ snapArr $ is $ S $ and $ E=\sum_{i=1}^{n}|snapArr[i]| $}, the similarity of snapshots in $ snapArr $ is $ s=\frac{E}{|S|} $.
 \end{definition}
@@
 	Consider an array $ Arr $ holding numeric values or snapshots.
-If $ Arr $ is a snapshot array, suppose the total number of edges in $ Arr $ is $ E_a $, and the total number of edges in the index is $ E_i $.
+If $ Arr $ is a snapshot array, suppose the total number of edges in $ Arr $ is $ E_a $ and the total number of edges in the index is $ E_i $.
 If $ Arr $ is a numeric array, $ E_a,E_i $ are the total number of numeric values in $ Arr $ and in the index respectively.
@@
 Similarly, the performance of sparse table is also influenced by similarity of snapshots.
-Overall, our index-based method, STree, is the best in these three method considering both acceleration ratio and space consumption ratio.}
+Overall, our index-based method, STree, is the best in these three methods considering both acceleration ratio and space consumption ratio.}
 

### 2023-01-31 revision/response.tex
response 2-1

@@
 \item As suggested, we have added experiments of existing methods in Section 7.2 and Exp-1 of Section 7.3 to evaluate the effectiveness and efficiency of our model.
+\item We have analyzed how to easily adapt our method to support temporal networks with temporal edges containing time range at the end of Section 7.1.
 \item We have added experiments related to partial materialization strategy in Exp-3 of Section 7.3.
 \item We have reviewed more related works and added discussion about limitations of all the mentioned existing works in Section 8.
-\item We have added brief discussion about applicability and limitation of our work in Section 9.
 
@@
 \end{Comments}
-\noindent \textbf{Response:} It is reasonable for a temporal edge to have only one timestamp, because in many cases, durations or end time of temporal edges are meaningless.
-For example, DBLP only records date of publication of research papers.
-For a research paper, the end time of publication or existence is meaningless.
-We just need to focus on the fact that at a certain time, some researchers have published a certain paper.
-Given a time range $ [t_1,t_2] $, we only need to determine whether a research paper is published in $ [t_1,t_2] $.
+\noindent \textbf{Response:} Thanks for your advice.
+We do omitted the case where temporal edges contain time ranges.
+The motivation of our work is based on the two datasets we found, DBLP and IMDB, where temporal edges contain only one timestamp.
+The reason is that DBLP only records date of publication of research papers and for each research paper, there is no end time of publication or existence.
+We only focus on the fact that at a certain time, some researchers have published a certain paper.
 It's the same with movies in IMDB.
-Another example is email communication network, which is also temporal network.
-Temporal edges in email communication network contain only timestamp of sending the email, and there is no need to store timestamp of finishing sending the email or timestamp of deleting the email.
-We just need to focus on the fact that there was an email exchange between certain people at a certain time, or we can consider this as an instant activity.
+%There are Email communication network is another example.
+Temporal edges in email communication network contain only timestamp of sending the email, and there is no timestamp of finishing sending the email or timestamp of deleting the email.
+Sending email is considered as an instant activity.
 
-Besides our work, almost all related works reviewed in the revised version define temporal edges with only one timestamp.
-The temporal edges you mentioned do exist in some temporal networks, such as phone calls network, since each phone call lasts for a while.
-However, it is difficult to assign realistic meaning to some possible positional relationships between the interval of a temporal edge and interval specified in a query if aggregation function on edges $ f_e $ is COUNT($\ast$) (or SUM($\ast$), MAX($\ast$), MIN($\ast$)).
-Suppose $ (u,v,t_s,t_e) $ be a phone call between $ u,v $ which starts at $ t_s $ and ends at $ t_e $.
-Given a query $ [t_1,t_2] $ satisfying $ t_1<t_s<t_2<t_e $, it is hard to tell what the aggregation result of $ (u,v) $ is if $ f_e $ is COUNT($\ast$), not to mention that there may be numeric attribute in temporal edges and $ f_e $ is SUM($\ast$) (or other aggregation functions).
-There may be a reasonable scenario that $ f_e $ is Duration($\ast$), i.e., asking for the total time of connections between two vertices or two groups of vertices.
-But it's insufficient to only support Duration($\ast$).
+Our method can be adapted for maintaining temporal edges with time range.
+The key is to regard each temporal edge as a series of temporal edges containing only one timestamp which is in the original time range.
+In detail, for a temporal edge $ (u,v,t_s,t_e) $, we can regard $ (u,v,t_s,t_e) $ as $ (t_e-t_s) $ temporal edges with single timestamp $ (u,v,t_s+0.5),(u,v,t_s+1.5),...,(u,v,t_e-0.5) $.
+Aggregation function on temporal edges COUNT($\ast$) can be re-defined as: asking for the total count of time units in connections between two vertices or two groups of vertices (COUNT($\ast$) can also be regarded as Duration($\ast$) in this case).
+For a temporal edge $ (u,v,t_s,t_e) $ with time range $ [t_s,t_e] $ and a query $ [t_1,t_2] $ with COUNT($\ast$) satisfying $ t_1<t_s<t_2<t_e $, the aggregation result of $ (u,v) $ should be $ (t_2-t_s) $.
+We regard $ (u,v,t_s,t_e) $ as temporal edges with single timestamp $ (u,v,t_s+0.5),(u,v,t_s+1.5),...,(u,v,t_e-0.5) $, and only $ (u,v,t_s+0.5),(u,v,t_s+1.5),...,(u,v,t_2-0.5) $ are in range $ [t_1,t_2] $, so there are total $ (t_2-0.5-(t_s+0.5)+1)=(t_2-t_s) $ time units in range $ [t_1,t_2] $, which is consist with the above result.
+In the practical we can let all timestamps be multiplied by 2.
+In this case, using query $ [2t_1,2t_2] $ with COUNT($\ast$) we can obtain the same result.
+Finally we can continue to use STree to accelerate the above query.
 
-Overall, datasets containing temporal edges with single timestamp are common in our research field.
-The motivation of temporal graph cube based on temporal networks containing temporal edges with time range should be further discussed, which should be included in a new work.
-We have added brief discussion about applicability and limitation of our work in Section 9 of the revised version.
+Overall, our method can be easily modified to support temporal networks containing temporal edges with time range. We have added the above discussion to the end of Section 7.1 of the revised version.
 
@@
 \noindent \textbf{Response:} Thanks for your advice.
-As we have responsed in D1, the motivation of temporal graph cube based on temporal networks containing temporal edges with time range should be further discussed and it is better to be included in future new works.
+We have further built temporal networks contain edges with time range based on IMDB, since vertices in IMDB has enough number of dimensions.
+We randomly assign time ranges to each of the original temporal edge.
+The experimental results of a series of temporal queries are similar to our results before.
+The reason is that we don't need to modify the index.
+As we mentioned in the response of D1, we can transform temporal edges with time range into a series of temporal edges with one timestamp.
+The only difference is that all timestamps are multiplied by 2.
+So the time complexity of conducting a range query is almost the same.
+Meanwhile, the theoretical analysis in Section 5 still holds since snapshot is still maintained by node of STree, so similarity of snapshots still affects acceleration ratio and space consumption ratio of the index.
+%One possible way is to manually generate suitable datasets.
+However, we do not have a priori knowledge to guide us in designing time range for temporal edges.
+Also, as we analyzed in response to D1, only Duration($\ast$) is the reasonable aggregation function on temporal edges with time range, and conducting temporal queries on temporal edges with time range using Duration($\ast$) is equivalent to conducting temporal queries on temporal edges with single timestamp using COUNT($\ast$).
+The reasons are as follows: for a temporal edges $ (u,v,t_s,t_e) $ with time range $ [t_s,t_e] $ and a query $ [t_1,t_2] $ with Duration($\ast$) satisfying $ t_1<t_s<t_2<t_e $, the aggregation result of $ (u,v) $ is $ (t_2-t_s) $.
+We can regard $ (u,v,t_s,t_e) $ as $ (t_e-t_s) $ temporal edges with single timestamp $ (u,v,t_s+0.5),(u,v,t_s+1.5),...,(u,v,t_e-0.5) $.
+In the practical we can let all timestamps be multiplied by 2.
+In this case, using query $ [2t_1,2t_2] $ with COUNT($\ast$) we can obtain the same result.
+We don't need to modify the index and there is only slight difference between the time complexity of conducting the above queries.
 
@@
 \end{Comments}
-\noindent \textbf{Response:} Thanks for reminding us. We have added relevant experiments in Exp-3 of Section 7.3.
+\noindent \textbf{Response:} Thanks for reminding us.
+We have added relevant experiments in Exp-3 of Section 7.3.
+In Exp-3 we use four partial materialization strategies: Random strategy and MinLevel with $ l_0 $ equals $ 2,3,4 $.
+We have analyzed in Section 6 that the traditional greedy strategy can not be used in partial materialization of temporal graph cube because of the uncertain time range specified by user in queries, which do not exist in traditional OLAP model.
+Given $ k $, Random strategy selects $ k $ views randomly to be materialized.
+Since users are more willing to query with less dimensions, we assume that the number of queries with $ x $ dimensions is twice as many as the number of queries with $ x+1 $ dimensions.
+The results in Figure 13 show that as $ k $ increases, all of the 4 strategies achieve better performance because more views are materialized.
+Among the 4 strategies, MinLevel with $ l_0=4 $ achieves the best performance because queries specified by users with no more 4 dimensions take up a major part, and these queries are more possible to be accelerated compared to the case when Random strategy is used.
+As a result, with proper setting of $ l_0 $, MinLevel is the most suitable method for partial materialization of temporal graph cube.
 
@@
 \end{Comments}
-\noindent \textbf{Response:} Thanks for your advice. We have added experiments in both Section 7.2 and Exp-1 of Section 7.3. Please refer to the response to comment 4 of reviewer \#1 for more details.
+\noindent \textbf{Response:} It's indeed possible to adapt existing methods as baselines.
+We have added experiments in both Section 7.2 and Exp-1 of Section 7.3.
+First, in Section 7.2 we add experimental results of queries in static graph cube.
+Our idea is to compare the results obtained from static graph cube and temporal graph cube.
+By comparing the query results we show that queries in temporal graph cube can reveal hidden information which may be ignored using queries in static graph cube.
+Second, at the end of Exp-1 of Section 7.3 we implement two other kinds of indexes, prefix array and sparse table, to accelerate range queries of temporal graph cube.
+The reason is that prefix array and sparse table are both classic methods to accelerate range query in numeric array, and they both can achieve $ O(1) $ time complexity in conducting range queries.
+However, in the case of snapshot arrays, only sparse table achieves higher acceleration ratio, but with unacceptable space consumption ratio (sometimes out of memory).
+Above results show the advantage of segment-tree based method in manuscript, which achieves a balance between efficiency and space consumption.
 

### 2023-01-31 TemporalGraphCube/TemporalGraphCube_revision.tex
response 2-1

@@
 
+\revision{In the above datasets, temporal edges contain only single timestamp.
+There other types of temporal networks with temporal edges containing time range, which are not considered here.
+However, our method can be easily adapted for such datasets with similar performance.
+The key is to regard each temporal edge as a series of temporal edges containing only one timestamp which is in the original time range.
+We should also re-define aggregation function on temporal edges COUNT($\ast$) as asking for the total count of time units in connections between two vertices or two groups of vertices.
+For example, for a temporal edge $ (u,v,t_s,t_e) $, we can regard $ (u,v,t_s,t_e) $ as $ (t_e-t_s) $ temporal edges with single timestamp $ (u,v,t_s+0.5),(u,v,t_s+1.5),...,(u,v,t_e-0.5) $.
+For a query $ [t_1,t_2] $ with COUNT($\ast$) satisfying $ t_1<t_s<t_2<t_e $, the aggregation result of $ (u,v) $ should be $ (t_2-t_s) $.
+From another perspective, only $ (u,v,t_s+0.5),(u,v,t_s+1.5),...,(u,v,t_2-0.5) $ are in range $ [t_1,t_2] $, so there are total $ (t_2-0.5-(t_s+0.5)+1)=(t_2-t_s) $ time units in range $ [t_1,t_2] $, which is consist with the previous result.
+In the practical we can let all timestamps be multiplied by 2.
+In this case, using query $ [2t_1,2t_2] $ with COUNT($\ast$) we can obtain the same result.
+Finally we can continue to use STree to accelerate the above query.}
+
 \subsection{Effectiveness Evaluation} \label{subsec:effectiveness_eva}
@@
 Aggregation functions upon vertices and edges are both COUNT($\ast$).
-The network structures of $ Q_1 $-$ Q_4 $ \revision{and $ Q_{static} $} are shown in Fig.~\ref{fig:dblp_area}, illustrating the co-authorship patterns between authors grouped by different areas.
+The network structures of $ Q_1 $-$ Q_4 $ and $ Q_{static} $ are shown in Fig.~\ref{fig:dblp_area}, illustrating the co-authorship patterns between authors grouped by different areas.
 For simplicity, in Fig.~\ref{fig:dblp_area} (a) we omit those co-authorships with COUNT($\ast$) values less than $ 10,000 $, which are also omitted in Fig.~\ref{fig:dblp_area} (b)-(e), regardless of their COUNT($\ast$) values.
@@
 Some interesting observations can be obtained in these results.
-For example, authors in each area co-author most with authors in the same area \revision{all the time ($ Q_{static} $) and} in different time ranges \revision{($ Q_1-Q_4 $)}.
-We can clearly see that in recent 20 years (\revision{$ Q_1-Q_4 $}), the number of co-authorship between each pair of areas increases over time.
+For example, \revision{authors in each area co-author most with authors in the same area all the time ($ Q_{static} $) and in different time ranges ($ Q_1-Q_4 $)}.
+We can clearly see that in recent 20 years ($ Q_1-Q_4 $), the number of co-authorship between each pair of areas increases over time.
 \revision{However, such results can never be found in $ Q_{static} $}.
@@
 We conduct extensive experiments on two large real-world datasets, and the results demonstrate the effectiveness and efficiency of the proposed solutions.
-\revision{Besides, there are other types of temporal networks which are not discussed in our work, for example, temporal networks where edges have both start and end timestamps.
-It is difficult to assign realistic meaning to some possible positional relationships between the interval of a temporal edge and interval specified in a query.
-Data warehouse and OLAP technology based on these special datasets are waiting for further discussion.}
 
